### 2015-07-28 paper.tex
added figures, changed up to v9

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

%\documentclass[journal,transmag]{IEEEtran}% Comment this line out if you need a4paper

\documentclass[10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\usepackage[ruled,vlined]{algorithm2e}

\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}

\def\lc{\left\lfloor}   
\def\rc{\right\rfloor}

\usepackage{amsmath,amssymb}

\usepackage{tabularx}
\usepackage{tikz,hyperref,graphicx,units}
\usepackage{subfigure}
\usepackage{benktools}

\usepackage{caption}
\usepackage{epstopdf}
\renewcommand{\captionfont}{\footnotesize}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bg}{\mathbf{g}}
\newcommand{\bj}{\mathbf{j}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mG}{\mathcal{G}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}
\newcommand{\mR}{\mathcal{R}}

\newcommand{\bfc}{W}
\newcommand{\Qinf}{Q_{\infty}}
\newcommand{\st}[1]{_\text{#1}}
\newcommand{\rres}{r\st{res}}
\newcommand{\pos}[1]{(#1)^+}
\newcommand{\depth}{\operatorname{depth}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\convhull}{\operatorname{ConvexHull}}
\newcommand{\minksum}{\operatorname{MinkowskiSum}}

\newcommand{\specialcell}[2][c]{ \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcolumntype{L}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\RaggedLeft\hspace{0pt}}p{#1}}

\title{\LARGE \bf
An Algorithm to Reduce Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9] }

\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
For robot control problems where the dynamics of the environment and the reward function are unknown, one technique is to learn a policy that attempts to match a supervisor's demonstration . A state of the art method in learning from demonstration is known as Dataset Aggregation, or DAgger. DAgger treats learning from demonstration as a supervised learning problem.The algorithm iteratively trains a policy on labeled data and then estimates states the robot is likely to encounter by executing the trained policy and has the supervisor tell the robot what controls it should have applied. Some successes of DAgger have been achieving state of the art performance on both Mario and Atari video game benchmarks, flying a quadcopter through a forest and teaching a robot to follow verbal instructions. One potential limitation though of DAgger is that it requires the supervisor to label the control for every state the robot visits during training, which can be expensive and tedious if the supervisor is a human. We propose estimating where the train policy is likely to mis-predict the supervisor's control, which we define as area of risk and then only having the supervisor label these states. Areas of risk can occur if the state is far from training data or if it has been incorrectly classified during the supervised learning. We propose identifying these areas via a modified version of the One Class SVM, which is used to estimate a level set of the distribution trained on. Then only states outside of this boundary are queried. Initial results suggest \todo{once we polish the experiments tomorrow and Wednesday}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
 Consider a robot trying to learn a task, such as driving a rc car around a track with other cars. In this task, the robot may have no prior information other than visual demonstrations from a human demonstrator. With no knowledge of a underlying cost function or system dynamics traditional control techniques are not practical.  One method in robotics that can handle such a situation is called Learning from demonstrations.  In the past, these methods  have  achieved state of the art performance  in a variety of applications.\cite{ross2013learning,pomerleau1989alvinn,schulman2013case}

One approach to LfD is to train a policy, or a  function estimator (either a classifier or regressor), to predict a supervisor's behavior given training data of the  observations (input) and actions (output) performed while accomplishing a task. However the robot's actions affect the next state observed, which violates the standard i.i.d assumption that is common in most statistical learning approaches. Ross et al. proved that this can cause the error in the estimator to compound over the time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the distribution it was trained on and encounters new states it can't generalize to.  Ross and Bagnell overcome this by presenting an iterative method that first trains a policy on the data observed using standard supervised learning techniques then tries the policy out in the environment to see what states are likely to occur under the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration and the policy is retrained \cite{ross2010reduction}. The DAgger method has been used since to teach a robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

\begin{figure}[t!]
\centering
\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
\caption{ An illustrative example of estimating the risk area in the data collected for a simulated self driving car around a track with other cars. The green area corresponds to points that are likely to occur under the expert demonstrations, where outside are points that would occur with low probability and thus are considered high risk. } 
\vspace*{-10pt}
\label{fig:dis_traveled}
\end{figure}

During learning, implementations of DAgger require the supervisor to manually label the controls the robot should have applied for each states it visits. If the supervisor, is a human this can be tedious and expensive. We are interested in having the supervisor only need to provide labels in areas of high risk, or where the robot is likely to mis-predict the controllers actions to reduce the workload on the controller.  A state can be risky for 2 reasons: 1) its is far from the states trained on, which potentially means our policy will mis-predict the supervisor \cite{tokdar2010importance} 2)  the state in the training set is being mis-predicted, so the state, although visited, doesn't have good control yet

To estimate where the robot's current policy is likely to mis-predict the supervisor, we  leverage a property in statistical machine learning that a trained model will be able to generalize within the distribution it is trained on \cite{tokdar2010importance}. This property can be seen used in importance sampling when data is collected from one distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One approach then is to estimate the distribution the policy is trained on and then ask for the supervisor to take over if the  probability of the current state is low under the estimated distribution. However, the amount of data needed to accurately estimate the density increases exponentially with the dimension of state space \cite{nadaraya1964estimating}. If we are working with partial observations like image data this could be impractical.  Thus, we propose using a modified version of a technique known as the One Class SVM that only tries to estimate the level set of the density trained on \cite{scholkopf2001estimating} and has been shown to successfully work on image data before in the context of outlier detection \cite{liu2014unsupervised}.

We make the following assumptions access to an environment where a robot can try out policies and sample trajectories and access to a supervisor that is able to provide demonstrations and tell the robot the control it should have applied after each iteration. We also assume that we are able to collect a series of partial observations from the environment and the controls applied. Lastly, we assume the observations encapsulate the Markov assumption in such that the probability of one is only dependent on the last observation and the controls applied.

Our contributions to date are framing the problem of asking for help in an online setting as estimating the support of a distribution and proposing a modified version of the One Class SVM,that both estimates the level set of a distribution and carves out areas in the support where we know our policy will mis-predict the supervisor, to identify states of high risk.  Initial results on a Mario AI video game, averaged over 20 levels,  suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 queries to the supervisor, while DAgger required 2800 queries.  \todo{These are preliminary results and I want to test on more mario experiments and the self driving car, also look at robustness to hyperparamters such as $\nu$ before I am confident in them}

\section{Related Work}
The field of learning from demonstration has achieved state of the art performance in a variety of areas within robotics \cite{argall2009survey}. Abbeel et al. used an iLQR controller around helicopter trajectories demonstrated by an expert to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of neural networks on video data and tracking markers to imitate a human arms movements on a 37 degree of freedom humaniod robot \cite{billard2001learning}. Schulman et al. used a non-linear warping, thin plate splines, on collected trajectories of a human controlling a PR2 and tying knots with a rope. Then transferred the demonstrations to the new unseen initial configurations of the rope~\cite{schulman2013case}.

 A subset of the learning from demonstration field is working within the assumption of no known dynamics and no access to a cost function. Under these assumptions, one approach to learning from demonstration is to collect a set of trajectories and controls from a supervisor and then treat the problem as a supervised learning problem that regresses on a function from state space to controls~\cite{argall2009survey}. Pomerleau et al. used this approach on raw image data and controls provided by a person driving a car and learned a policy that allowed a car to travel on a highway. However, they observed if the car deviated from the middle of the road it would not know how to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and proved the amount of error accumulated is squared in the time horizon of a policy and proposed a learning algorithm, SMILE, that stochastically mixes the supervisor's control with the robots during training. Thus allowing the robot to explore states the supervisor hasn't seen before~\cite{ross2010efficient}.

Ross and Bagnell then improved upon this method with DAgger an iterative method that first trains a policy on the data observed using standard supervised learning techniques and tries the policy out in the environment to see what states are likely to occur under the robots policy. The supervisor then tells the robot what controls it should applied after each iteration and the policy is retrained with an aggregate of all data seen before \cite{ross2010reduction}.

A quad-copter using DAgger learned how to fly through a forest using only HOG features extracted from visual images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q learning methods to achieve state of the art performance on the common Atari game benchmark in Reinforcement Learning \cite{NIPS2014_5421}. Duvallet use DAgger to teach robots to follow verbal instructions about where to move sematically in a building with a training set of humans following similar verbal instructions \cite{duvallet2013imitation}. Levine et al. extended the iterative learning paradigm through Guided Policy Search, which replaces the expert with iLQG and uses KL divergence constraints to train the policy to match the distributions of the controllers \cite{levine2015end}.

One limitation of DAgger is that it requires the demonstrator, or supervisor, to "label" every state the policy visits during learning. The act of labeling can be very tedious and expensive when the supervisor is a human. To reduce this Judah et al. proposed applying active learning technique to only query the supervisor for states that are likely to be visited under the current policy and are likely to be mis-predicted under the current policy\cite{judah2011active,judah2012active}. A drawback of this approach though is that it requires estimating the distribution of states, which can be difficult in high dimensions. Furthermore, their use of query by committee reduces their policy's function class to non-kernelized linear classifiers \cite{gilad2005query}, which could potentially hurt the ability of a policy to generalize.

In order to tell where a policy is likely to mis-predict,we  leverage a property in statistical machine learning that a trained model will be able to generalize within the distribution it is trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One approach is to  estimate the probability density the policy is trained on. However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.

 Several other approaches have been proposed to tell when your estimator is likely to not generalize \cite{2003novelty}.Knox and Ng used a nearest neighbors approach to try and estimate if a point was close to $k$ neighbors, however it was shown to be susceptible to outliers because nearest neighbor only uses local information about the data \cite{knox1998algorithms}. Manevitz and Yousef trained a neural network filter to try and reconstruct the data and if the reconstruction error is high, they mark the point as likely to be outside of the estimators generalization ability. Manevitz and Yousef mention  that finding the right architecture can be task specific and require a lot of hyperparameter tuning  \cite{manevitz2002one}. The One Class SVM proposed by Scholk{\"o}pf et al. estimates a user defined level set of the distribution it is trained on by solving a convex quadratic program   to find the support vectors that encompasses the data. The method has been theoretically shown to approximate the level set of a density estimate in the asymptomatic  limit of sample and also its regularization term has the nice property of being equivalent to the quantile function\cite{vert2006consistency}. It has also been shown to successfully work on outlier detection for raw image data~\cite{liu2014unsupervised}.

\section{Problem Statement}

\subsection{Notation and Background}
\todo{figure out sensor model, meeting with Sergey next week about safe learning with out assuming a human is available I can ask him then}
Define $\mathbf{x} \in \mathcal{X}$ as state space for a robot, for example $\mathbf{x}$ could be an image from a camera feed or a vector of joint angles. Define $\mathbf{u} \in \mathcal{U}$ as the class of controls for an agent, which could be for example torque control applied to a robot or discrete commands such as in a video game. The environment is modeled to have dynamics that are stationary and Markovian, such that the the probability of state $\mathbf{x_{t+1}}$ can be determined from $\mathbf{x}_t$ and $\mathbf{u}_t$, or $p(\bx_{t+1}|\bu_t,\bx_t)$.  We represent a probability distribution over the initial state of the environment $p(\bx_0)$.. Denote a trajectory as series of states visited and the controls applied  as $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$.  A trajectory that is defined with state space only and not controls is $\tau_{\bx} = (\bx_0,....,\bx_T)$.

A policy is a function from state space to controls, $\pi: \bx \rightarrow \bu$. A policy could be $\pi_\theta: \bx \rightarrow \mathbf{u}$, which is a  function that is specified by a vector of parameters  $\theta$.The vector of parameters $\theta$ can be for example weights in a neural network or the  vectors in a Support Vector Machine. A policy, $\pi_{\theta}$ in an environment with $p(\bx_0)$ and $p(\bx_{t+1}|\bx_t,\bu_t)$ induces a distribution on the possible trajectories:$ p(\tau_\bx | \theta)= p(\bx_0)\prod_{i=0}^{T-1}p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. Also $\pi_{\theta}$ in an environment with $p(\bx_0)$ and $p(\bx_{t+1}|\bx_t,\bu_t)$  induces a distribution on states visited $p(\mathbf{x}|\theta)$.

 The following is a way to convert from $p(\bx_t|\theta)$ to $p(\bx|\theta)$. Let $p(\bx_t|\theta)$ be the distribution of states visited at time $t$ if the robot follows the policy $\pi_{\theta}$ for $t-1$ time steps. Calculating this from $p(\tau_{\bx}|\theta)$ is mean marginalizing over the previous timesteps $p(\bx_t|\theta) = \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. The average distribution on states is now defined as $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.

We do not know the distributions: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$,$p(\tau_{\bx}|
\bx)$ or $p(\bx|\theta)$. But we assume we have a stochastic real robot or a simulator such that given any state $\bx_t$ and control $\bu_t$, it will move into a state $\bx_{t+1}$ such that $\bx_{t+1} \sim p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. Note that $p(\tau_{\bx}|\theta)$ is high dimensional because $\bx$ is high dimensional.

Given $\pi_{\theta}$ we want to identify a set of highly probable trajectories and the associated highly probable states. We assume we are given some initial state $\bx_0$. We  "roll-out" the policy using the robot with the policy to sample the resulting trajectory and set of states reached, which provides a sequence of highly probably states under $p(\tau_{\bx}|\theta)$.Rather than estimating $p(\bx|\theta)$ or $p(\tau_{\bx}|\theta)$, we draw samples from them.

The objective in policy learning can be framed as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$. The cost function is user defined and task specific. For each state $\bx_{t}$ and control $\bu_t$ the robot receives a penalty related to how far it is from the goal state. For example, in task of inserting a peg into a hole the cost function can be distance to desired final state \cite{levine2015end}.  We also do not know the cost function. But we do have access to a "supervisor", an algorithm or human that uses some policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given an initial set of $N$ training/demonstration trajectories resulting from this policy: $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$.

Next, we define a "surrogate" loss function $l$, which gives the distance between any pair of control values: in the continuous case $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$ or in a discrete case

 \vspace{-2ex}
\begin{align}
 l(\bu_0,\bu_1) = \left\{
     \begin{array}{lr}
       1 & : \bu_0 = \bu_1\\
       0 & : \bu_0 \neq \bu_1
     \end{array}
   \right.
\end{align}

Given a candidate policy $\theta$, we can use the surrogate loss function to compute how "close" it is to the competent controller's policy $\tilde{\pi}$.

We want to compute a policy $\pi_{\theta}$ that minimizes the expected surrogate loss where the expectation is taken over the distribution of states.

 \vspace{-2ex}
\begin{align}\label{eq:LFD_obj}
\underset{\theta}{\min} \: E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}(\bx))]
\end{align}

The optimization problem in Eq. \ref{eq:LFD_obj} compares the action taken of the policy $\pi_\theta$ and  the competent controller, $\tilde{\pi}$  weighted by the probability of  the state occurring $p(\bx|\theta)$.

Eq. \ref{eq:LFD_obj} is hard to solve because  the objective is not convex and we only have access to $\tilde{\pi}(x)$, where $x$ is a state in one of the demonstrations or $\bx \in \mathcal{D}$. To address these issues Stephane and Ross proposed an iterative method known as DAgger\cite{ross2010reduction}.

 \subsection{DAgger: Dataset Aggregation}
 DAgger is an iterative algorithm that repeats two steps for $K$ iterations. 
 In Eq. \ref{eq:LFD_obj}, the objective involves both the parameterized policy $\pi_{\theta}$ and the average distribution of states with respect to the policy, $p(\bx|\theta)$. DAgger iteratively minimizes $\pi_{\theta}$ on the collected dataset of examples $\mathcal{D}$ and then adds new states of high probability under $\pi_\theta$ by sampling via policy roll outs from $p(\bx|\theta)$.

\subsubsection{Step 1}
At iteration $k=0$ given a dataset $\mathcal{D}_0$, the training set with $N_0$ demonstrated trajectories mapping $\bx$ to $\bu$. DAgger solves the following supervised learning problem with respect to the surrogate loss function.

 \vspace{-2ex}
\begin{align}\label{eq:super_objj}
\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{N}\sum_{t=1}^T l(\pi_{\theta}(\bx_t^{i}),\bu_{t}^i)
\end{align}

This is a supervised learning problem and can be solved using standard machine learning techniques, for example a support vector machine or a neural network. The surrogate losses mentioned early like Squared Euclidean distance or an Indicator function are appropriate optimization objectives.

 To handle the fact that the competent actor's policy contains noise $\epsilon$, we employ a regularization technique in the optimization. Regularization is a technique to control the smoothness of the function that is fit to the sampled data. It is a common technique to make the estimator robust to zero mean noise on data. In practice it is a penalty term on either  the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.

 \subsubsection{Step 2}
DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\theta_{k=1}$. For every state visited, DAgger requests the competent controller to provide the appropriate control/label. Formally, for a given sampled trajectory  $\tau = (\bx_1,\bu_1,...,\bx_T\bu_T )$. The competent controller provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ to the trajectory $\tau = (\bx_1,\tilde{\bu}_1,...,\bx_T, \tilde{\bu}_T )$.  This can be very tedious for a human. The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.

Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss  goes to zero. Since DAgger requires rolling out the policy at each iteration, one way to terminate the algorithm is when the performance of the rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined threshold $\gamma$.

Dagger works well in both simulation and real world experiments. It also has theoretical guarantees that it will converge in the limit to the competent controller's policy. However, using policy rollouts means the robot can enter dangerous states, which could damage a robot in a non simulation system. For example, when DAgger was used on a quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}. A state can be risky for 2 reasons: 1) its is far from the states trained on, which potentially means our policy will mis-predict the supervisor and incur high surrogate loss \cite{tokdar2010importance} 2) the surrogate loss associated with the state is high, so the state, although visited, doesn't have good control yet. Furthermore, iterations are tedious because if a human is the supervisor requires manual "labeling" of every state visited with the appropriate control.

To address these limitations, we propose to 1) avoid highly risky states entirely via terminating the policy roll-out and 2) recognize slightly risky states and request human input for these and to reduce the burden on the human trainer. One way to do this is to define risk in terms of distance to the nearest neighbor, but this vulnerable to outliers in the known set of states. Another option is to fit a distribution to the known set of states, which requires an exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}. We propose using a modified version of the technique known as the One Class SVM that  estimates a boundary of the density \cite{scholkopf2001estimating}.

\subsection{Estimation of a Distribution's Level Set}\label{sec:level}
\todo{Work with Florian on the first paragraph to make it less abstract and specific to the robotics}
Support estimation can be defined as minimizing a function that contains the volume of a given probability distribution. Formally we define it as follows let $\mathbf{x}_1,...,\mathbf{x}_n $ be i.i.d. random variables in a set $\mathcal{X}$ with distribution $P$. Let $\mathcal{G}$ be a class of measurable subsets of $\mathcal{X}$ and let $\lambda$ be a real function defined on $\mathcal{G}$. The quantile function with respect to $(P,\lambda,\mathcal{G})$ is

\vspace{-2ex}
\begin{align}\label{eq:quantile}
U(\gamma) = \mbox{inf} \lbrace \lambda(G):P(G) \geq \gamma, G \in \mathcal{G} \rbrace \: 0<\gamma \leq 1
\end{align}

We denote by $G(\gamma)$ the $G \in \mathcal{G}$ that attains the infinimum. The most common choice of $\lambda$ is Lebesgue measure, in which case $G(\gamma)$ is the minimum volume $G \in \mathcal{G}$ that contains at least a fraction $\gamma$ of the the probability mass. Thus, $G(1)$ is the support of the density $p$ corresponding to $P$, assuming it exists.

To handle high dimensional densities $P$, work by Scholk{\"o}pf et al.  looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}. They then minimize a SV  regularizer which, using a kernel, controls the smoothness of the estimated function describing $G$. In terms of the quantile function described in Eq. \ref{eq:quantile}, the approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$. Here $(w,\rho)$ are a weight vector and offset parameterizing a hyperplane in the feature space associated with a kernel.

\begin{figure*}[ht]
\centering
\subfigure[Race Car Simulator]{%
\vspace{-0.5ex}\includegraphics[width=5cm , height = 4cm]{figures/Slide1.jpg}
\label{fig:subfigure1}}
\quad
\subfigure[Expert Demonstrations]{%
\includegraphics[width=5.5cm, height = 4.5cm]{figures/exp_dist.eps}
\label{fig:subfigure2}}
\subfigure[Estimated Support of Expert Demonstrations]{%
\includegraphics[width=5.5cm, height = 4.5cm]{figures/ocm_example.png}
\label{fig:subfigure3}}

\caption{\todo{Want to change this to highlight $\nu$ effect on level set estimation} A race car is driven around a track in Fig. \ref{fig:subfigure1} by an expert demonstrator. The state space of the car is represented as the x and y positions on the track or $\mathbf{s} = [x,y]$. In Fig. \ref{fig:subfigure2}, the demonstrations are plotted in state space. In Fig. \ref{fig:subfigure3}, the support is estimated using the decision function in \ref{eq:decision_func}. As illustrated the support accurately describes the boundary of the expert trajectory. }
\label{fig:support_example}
\end{figure*}

Let $\Phi$ be a feature map $\mathcal{X} \rightarrow \mathcal{F}$, i.e. a map into an inner product space $\mathcal{F}$ such that the inner product in the image of $\Phi$ can be computed by evaluating some  kernel

\vspace{-2ex}
\begin{align}
k(\bx_0,\bx_1) = \langle\Phi(\bx_0),\Phi(\bx_1)\rangle
\end{align}

such as the Gaussian kernel

\vspace{-2ex}
\begin{align}
k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}
\end{align}

The main idea is to solve an optimization problem that separates the origin, we solve the following quadratic problem:

\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
\underset{w\in F, \mathbf{\xi} \in \mR, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \\
\end{align}

The parameter $\nu$ controls the penalty on slack terms and asymptotically approaches is equivalent to $\gamma$ \cite{vert2006consistency}.  The decision function then becomes

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho)
\end{align}

Where $g(x) = 1$ indicates in the support region and $(g) = -1$ denotes being outside the support region. The dual form of the optimization takes the form of a Quadratic Program with respect to the Gram Matrix \cite{scholkopf2001estimating}.

Estimating the level set of a distribution can be a measure of the generalization ability of $\pi_{\theta}$ to points not within $\mathcal{D}$. However, it does not account for the fact that for a given $\theta$ or  solution to Eq. \ref{eq:super_objj}. $\pi_\theta$ may not correctly match the competent controller's controls for all points train on. To account for this, we propose a modification to the One Class SVM denote:

\begin{align}
y_i = \left\{
     \begin{array}{lr}
       1 & : \pi_{\theta}(\bx_i) =\bu_i\\
       -1 & : \pi_{\theta}(\bx_i) \neq \bu_i
     \end{array}
   \right.
\end{align}

or $y_i$ is $1$ if the control applied matches the competent controller and $-1$ if it differs. In the regression case the decision between $1$ and $-1$ can be set by a some threshold on a L2-norm or $||\pi_{\theta}(\bx_i)-\bu_i||$. We use $y_i$ to modify the optimization as follows:

\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
\underset{w\in F, \mathbf{\xi} \in \mR^l, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}
\end{align}

Points that are mis-predicted are then enforced to lie on the opposite of the hyper-plane in the feature space $\phi(\bx)$, which carves out holes in the support region around them. The dual formulation, which is what is solved in practice, can be derived as

\vspace{-2ex}
\begin{align}\label{eq:dual_sup}
\underset{\alpha\in \mathcal{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1 
\end{align}

Our decision boundary function $g(\bx)$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n \alpha_i y_i k(\bx_i,\bx) - \rho$. To compute the $\rho$ term,we leverage the fact that for an optimal solution the inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating}.

\subsection{SHEATH:Support-based HElp AquisiTion from Humans}

Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the competent controller's control,which we define as the region of low risk.  In the statistics community, a known property is that estimators are function will mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the competent controller provide labels when the robot leaves this boundary. Furthermore to avoid entering pathological states that are far from the competent controller's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$. The risk threshold, $r_0$, is user defined based on the task.

\subsubsection{Step 1}
Similar to DAgger at iteration $k$ the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$ by solving Eq. \ref{eq:super_objj}. We then estimate the level set of the distribution being trained on by solving the optimization for the One Class SVM or $\ref{eq:primal_sup}$ on the dataset $\mathcal{D}_k$. We now have a decision boundary $g_k(\bx)$, which is $1$ if the region is in the low risk area and $-1$ otherwise . The parameter $\nu$ is an estimate of how much probability mass is contained in the level set and can be use to control the size of the low risk region.

 \subsubsection{Step 2}
 In DAgger the policy that was rolled out is $\pi_{\theta_k}$, however this could potential encounter pathological states that are far from the initial set of demonstrations $\mathcal{D}_0$. To prevent this we terminate the rolled out policy if the risk, or distance from the support, is above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of labeling every state now the competent controller is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.  These states are then added to the dataset $\mathcal{D}_{k+1}$ and the algorithm goes back to Step 1.

An implicit trade off exists between what how much of the distribution is contained in the selected level set and the amount of exploration the robot is allowed. If the level set is large the robot will be allowed to explore in this region and potentially make more mistakes with respect to the expert, but learn faster. If the level set contains a smaller fraction of data, then the expert will be in control more and the robot will learn at a slower rate.

\section{Theoretical Analysis}

\subsection{Convergence Rate}
\todo{These are ideas still in progress}
The convergence rate of DAgger is dependent on the probability of the expert taking over at each iteration $\beta_i$ \cite{ross2010reduction}. For SHEATH, this corresponds to the probability of leaving the support or $p(g(\mathbf{x}) = -1|\pi_{\theta_i})$ . The intuition is that the larger the level set parameter $\nu$ is the lower the probability of leaving is and thus faster convergence rate, but potentially less safe exploration. Not sure if a formal proof is going to be possible though with assuming known dynamics, still looking into it. However, we can experimentally demonstrate this.

\section{Experiments}
\subsection{Driving Example}
A common benchmark in RL is a car driving around a track avoiding other cars \cite{argall2009survey}. In our driving simulator a car is driven around a rectangular track and has orange cars placed on the track as well that need to be dodged. If the car falls off the track, it is placed back on to the center. Our control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$. Our supervisor is a solver that uses state space search through the driving simulator to plan the next control.

We have the supervisor drive around the track 3 times and then collect the raw images observed. We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV. For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.. We initialized both Dagger and SHEATH with two expert demonstrations for each level. For the optimization of Eq. \ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.

We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track. Initial results averaged over 1 level shown in Fig.  suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.

\begin{figure}[t!]
\centering
\includegraphics[width=6cm, height=6cm]{figures/race_car_track_example.png}
\caption{ An example image from the racing simulator. The car is meant to drive around a rectangular track and dodge other cars. The supervisor drives around the track for 3 iterations and HOG features are extracted from the images.  }

\vspace*{-10pt}
\label{fig:race_car}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=8cm, height=6cm]{figures/dagger_sheath_no_cars.png}
\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track. Initial results averaged over 1 level shown suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.  }

\vspace*{-10pt}
\label{fig:car_cost}
\end{figure}

\subsection{Super Mario Bros}
Super Mario Bros. is a platform video game where the character, Mario, must move across each stage by avoiding being hit by enemies and falling into gaps, and before running out of time. We used the simulator from a recent Mario Bros. AI competition which can randomly generate stages of varying difficulty (more difficult gaps and types of enemies) \cite{marioAI}. Our goal is to train the computer to play the game based on current game features as input. Our expert is a near optimal $A^*$ search algorithm that plans ahead using the game simulator. An action consists of 4 binary variables indicating which subset of buttons we should press in $\lbrace \mbox{left},\mbox{right},\mbox{jump},\mbox{speed} \rbrace$. For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $C\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.. We initialized both Dagger and SHEATH with two expert demonstrations for each level. For the optimization of Eq. \ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $c=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.

\begin{figure}[t!]
\centering
\includegraphics[width = 6cm ]{figures/mario.png}
\caption{ An example image from the Mario AI simulator. Mario faces many challenges to reach an end of a level, such as gaps, jumps and enemies.  }

\vspace*{-10pt}
\label{fig:dis_traveled}
\end{figure}

\begin{figure}[ht]
\centering

\includegraphics[width=8cm, height = 4.5cm]{figures/dagger_sheath_mario.eps}

\caption{We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.  Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties. We compare performance of our method and DAgger. In Fig. \ref{fig:mario_results}, we report the performance of distance traveled vs. the number of labels provided by the competent controller. Initial results, averaged over 20 levels, suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.   \todo{I think these results are promising but want to make clear they are very preliminary and want to run more experiments on Mario and the self driving car to ensure that we can actually do this reliable. Also, the jaggedness is concerning and needs to be looked in to, my intuition is telling me that Mario is just a very chaotic environment though. I am going to average over more levels to see if it improves}}
\label{fig:mario_results}
\end{figure}

We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.  Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties. We compare performance of our method and DAgger. In Fig. \ref{fig:mario_results}, we report the performance of distance traveled vs. the amount of time a level was tried.  Initial results, averaged over 20 levels,  suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.

\subsection{Other Experiment}
\todo{Florian and I are discussing different ideas for this one, maybe a controller for an arm or something along the lines of learning to grasp in clutter}

\section{Discussion and Future Work}

\bibliographystyle{IEEEtranS}
\bibliography{references}

\end{document}

### 2015-07-28 paper.tex
some of Jeff's comments

@@
 \title{\LARGE \bf
-An Algorithm to Reduce Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9] }
+An Algorithm to Reduce a Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9] }
 
@@
 \begin{abstract}
-For robot control problems where the dynamics of the environment and the reward function are unknown, one technique is to learn a policy that attempts to match a supervisor's demonstration .
+For robot control problems where the dynamics of the environment and the reward function are unknown, one technique is to learn a policy that attempts to match a supervisor's demonstration, also known as learning from demonstration .
 A state of the art method in learning from demonstration is known as Dataset Aggregation, or DAgger.
-DAgger treats learning from demonstration as a supervised learning problem.The algorithm iteratively trains a policy on labeled data and then estimates states the robot is likely to encounter by executing the trained policy and has the supervisor tell the robot what controls it should have applied.
+DAgger treats learning from demonstration as an iterative supervised learning problem.The algorithm alternates between training a policy on labeled data and then acquiring labels on states the robot is likely to encounter by executing the trained policy and having the supervisor tell the robot what controls it should have applied.
 Some successes of DAgger have been achieving state of the art performance on both Mario and Atari video game benchmarks, flying a quadcopter through a forest and teaching a robot to follow verbal instructions.
 One potential limitation though of DAgger is that it requires the supervisor to label the control for every state the robot visits during training, which can be expensive and tedious if the supervisor is a human.
-We propose estimating where the train policy is likely to mis-predict the supervisor's control, which we define as area of risk and then only having the supervisor label these states.
-Areas of risk can occur if the state is far from training data or if it has been incorrectly classified during the supervised learning.
+We propose estimating where the train policy is likely to mis-predict the supervisor's control, which we define as areas of risk and then only having the supervisor label these states.
+Areas of risk can occur if the state is far from training data or if it has been incorrectly classified during the supervised learning step.
 We propose identifying these areas via a modified version of the One Class SVM, which is used to estimate a level set of the distribution trained on.
@@
 Schulman et al.
-used a non-linear warping, thin plate splines, on collected trajectories of a human controlling a PR2 and tying knots with a rope.
-Then transferred the demonstrations to the new unseen initial configurations of the rope~\cite{schulman2013case}.
+used a non-linear warping, thin plate splines, on collected trajectories of a human controlling a PR2 and tying knots with a rope then transferred the demonstrations to the new unseen initial configurations of the rope~\cite{schulman2013case}.
 
@@
 Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the competent controller's control,which we define as the region of low risk.
-In the statistics community, a known property is that estimators are function will mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.
+In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.
 Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the competent controller provide labels when the robot leaves this boundary.
@@
 A common benchmark in RL is a car driving around a track avoiding other cars \cite{argall2009survey}.
-In our driving simulator a car is driven around a rectangular track and has orange cars placed on the track as well that need to be dodged.
+In our driving simulator, the car must stay on a rectangular track and dodge the orange cars that are on the track as well.
 If the car falls off the track, it is placed back on to the center.
-Our control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$.
+The car's control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
+The internal state space of the car is xy-coordinates and the angle it is facing.
 Our supervisor is a solver that uses state space search through the driving simulator to plan the next control.
 
-We have the supervisor drive around the track 3 times and then collect the raw images observed.
+We have the supervisor drive around the track 2 times and then collect the raw images observed.
 We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV.
-For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert..
-We initialized both Dagger and SHEATH with two expert demonstrations for each level.
+For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.
 For the optimization of Eq.
@@
 
-We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track.
+We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track, versus the number of queries made to the supervisor.
 Initial results averaged over 1 level shown in Fig.
@@
 Initial results averaged over 1 level shown suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
-}
+\todo{Run this over many trials}  }
 

### 2015-07-28 paper.tex
modified a few comments

@@
 
-Given a candidate policy $\theta$, we can use the surrogate loss function to compute how "close" it is to the competent controller's policy $\tilde{\pi}$.
+Given a candidate policy $\theta$, we can use the surrogate loss function to compute how "close" it is to the supervisor's policy $\tilde{\pi}$.
 
@@
 The optimization problem in Eq.
-\ref{eq:LFD_obj} compares the action taken of the policy $\pi_\theta$ and  the competent controller, $\tilde{\pi}$  weighted by the probability of  the state occurring $p(\bx|\theta)$.
+\ref{eq:LFD_obj} compares the action taken of the policy $\pi_\theta$ and  the supervisor, $\tilde{\pi}$  weighted by the probability of  the state occurring $p(\bx|\theta)$.
 
@@
 
- To handle the fact that the competent actor's policy contains noise $\epsilon$, we employ a regularization technique in the optimization.
+ To handle the fact that the supervisor's policy contains noise $\epsilon$, we employ a regularization technique in the optimization.
 Regularization is a technique to control the smoothness of the function that is fit to the sampled data.
@@
 DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\theta_{k=1}$.
-For every state visited, DAgger requests the competent controller to provide the appropriate control/label.
-Formally, for a given sampled trajectory  $\tau = (\bx_1,\bu_1,...,\bx_T\bu_T )$.
-The competent controller provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ to the trajectory $\tau = (\bx_1,\tilde{\bu}_1,...,\bx_T, \tilde{\bu}_T )$.
+For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
+Formally, for a given sampled trajectory  $\tau = (\bx_1,\bu_1,...,\bx_T,\bu_T )$.
+The supervisor provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ to the trajectory $\tau = (\bx_1,\tilde{\bu}_1,...,\bx_T, \tilde{\bu}_T )$.
 This can be very tedious for a human.
@@
 Dagger works well in both simulation and real world experiments.
-It also has theoretical guarantees that it will converge in the limit to the competent controller's policy.
+It also has theoretical guarantees that it will converge in the limit to the supervisor's policy.
 However, using policy rollouts means the robot can enter dangerous states, which could damage a robot in a non simulation system.
@@
 \underset{w\in F, \mathbf{\xi} \in \mR, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \\
+\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag
 \end{align}
@@
 \ref{eq:super_objj}.
-$\pi_\theta$ may not correctly match the competent controller's controls for all points train on.
+$\pi_\theta$ may not correctly match the supervisor's controls for all points train on.
 To account for this, we propose a modification to the One Class SVM denote:
@@
 
-or $y_i$ is $1$ if the control applied matches the competent controller and $-1$ if it differs.
+or $y_i$ is $1$ if the control applied matches the supervisor and $-1$ if it differs.
 In the regression case the decision between $1$ and $-1$ can be set by a some threshold on a L2-norm or $||\pi_{\theta}(\bx_i)-\bu_i||$.
@@
 
-Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the competent controller's control,which we define as the region of low risk.
+Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the supervisor's control,which we define as the region of low risk.
 In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.
-Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the competent controller provide labels when the robot leaves this boundary.
-Furthermore to avoid entering pathological states that are far from the competent controller's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$.
+Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the supervisor provide labels when the robot leaves this boundary.
+Furthermore to avoid entering pathological states that are far from the supervisor's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$.
 The risk threshold, $r_0$, is user defined based on the task.
@@
 To prevent this we terminate the rolled out policy if the risk, or distance from the support, is above some threshold $r(\bx_t) > r_0$.
-Furthermore, instead of labeling every state now the competent controller is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.
+Furthermore, instead of labeling every state now the supervisor is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.
 These states are then added to the dataset $\mathcal{D}_{k+1}$ and the algorithm goes back to Step 1.
@@
 \ref{fig:mario_results}, we report the performance of distance traveled vs.
-the number of labels provided by the competent controller.
+the number of labels provided by the supervisor.
 Initial results, averaged over 20 levels, suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.

### 2015-07-29 paper.tex
added new figure to illustrate risk sensitive SVM

@@
 \centering
-\subfigure[Race Car Simulator]{%
-\vspace{-0.5ex}\includegraphics[width=5cm , height = 4cm]{figures/Slide1.jpg}
+\subfigure[Kernel Density Estimation of Sampled Data]{%
+\vspace{-0.5ex}\includegraphics[width=5.5cm , height = 4.5cm]{figures/kde_gmm.eps}
 \label{fig:subfigure1}}
 \quad
-\subfigure[Expert Demonstrations]{%
-\includegraphics[width=5.5cm, height = 4.5cm]{figures/exp_dist.eps}
+\subfigure[One Class SVM]{%
+\includegraphics[width=5.5cm, height = 4.5cm]{figures/kde_gmm_ocm.eps}
 \label{fig:subfigure2}}
-\subfigure[Estimated Support of Expert Demonstrations]{%
-\includegraphics[width=5.5cm, height = 4.5cm]{figures/ocm_example.png}
+\subfigure[Risk Sensitive One Class SVM]{%
+\includegraphics[width=5.5cm, height = 4.5cm]{figures/kde_gmm_mocm.eps}
 \label{fig:subfigure3}}
 
-\caption{\todo{Want to change this to highlight $\nu$ effect on level set estimation} A race car is driven around a track in Fig.
-\ref{fig:subfigure1} by an expert demonstrator.
-The state space of the car is represented as the x and y positions on the track or $\mathbf{s} = [x,y]$.
+\caption{Data is sampled from a Gaussian Mixture Model and in Fig.
+\ref{fig:subfigure1}, the red points are those that the trained policy, $\pi_{theta}$ will mis-predict.
 In Fig.
-\ref{fig:subfigure2}, the demonstrations are plotted in state space.
+\ref{fig:subfigure2} the One Class SVM is fit to the data and tries to estimate the areas of low risk (the light green region), while it is able to estimates the area where the majority of the data lies it also encloses the points the trained policy is mis-predicting.
 In Fig.
-\ref{fig:subfigure3}, the support is estimated using the decision function in \ref{eq:decision_func}.
-As illustrated the support accurately describes the boundary of the expert trajectory.
-}
+\ref{fig:subfigure3}, the Risk Sensitive One Class SVM is able to effectively remove the red points from the region of low risk.}
 \label{fig:support_example}

### 2015-07-30 paper.tex
Revised first half.

@@
 \newcommand{\specialcell}[2][c]{ \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
-
+\newcommand{\acro}{SHIV}
 \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
@@
 
-\title{\LARGE \bf
-An Algorithm to Reduce a Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9] }
+\title{\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies from Demonstrations }
 
@@
 \begin{abstract}
-For robot control problems where the dynamics of the environment and the reward function are unknown, one technique is to learn a policy that attempts to match a supervisor's demonstration, also known as learning from demonstration .
-A state of the art method in learning from demonstration is known as Dataset Aggregation, or DAgger.
-DAgger treats learning from demonstration as an iterative supervised learning problem.The algorithm alternates between training a policy on labeled data and then acquiring labels on states the robot is likely to encounter by executing the trained policy and having the supervisor tell the robot what controls it should have applied.
-Some successes of DAgger have been achieving state of the art performance on both Mario and Atari video game benchmarks, flying a quadcopter through a forest and teaching a robot to follow verbal instructions.
-One potential limitation though of DAgger is that it requires the supervisor to label the control for every state the robot visits during training, which can be expensive and tedious if the supervisor is a human.
-We propose estimating where the train policy is likely to mis-predict the supervisor's control, which we define as areas of risk and then only having the supervisor label these states.
-Areas of risk can occur if the state is far from training data or if it has been incorrectly classified during the supervised learning step.
-We propose identifying these areas via a modified version of the One Class SVM, which is used to estimate a level set of the distribution trained on.
-Then only states outside of this boundary are queried.
-Initial results suggest \todo{once we polish the experiments tomorrow and Wednesday}
-
+For robot control problems where no reward function is known and the dynamics of the environment are not specified, the
+learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
+demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
+the problem of determining a policy as an iterative supervised learning problem which alternates between executing a
+trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. In this
+work, we propose a novel algorithm, \acro~which is based on DAgger and which estimates the riskiness of states
+encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
+states used for training the current policy. Since learning a quantile function for high-dimensional input data is
+challenging, we instead modify an SVN-based approach to quantile estimation that employs regularization to solve this
+problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
+user-defined quantile super-levelset is encountered. Our approach furthermore reduces the amount of neccessary
+supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
+In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
+DAgger, our approach results in similar performance levels as DAgger while reducing the amount of required supervisor
+control inputs by more than {\color{blue}[-- TODO --]} percent.
 \end{abstract}
@@
 \section{Introduction} 
- Consider a robot trying to learn a task, such as driving a rc car around a track with other cars.
-In this task, the robot may have no prior information other than visual demonstrations from a human demonstrator.
-With no knowledge of a underlying cost function or system dynamics traditional control techniques are not practical.
-One method in robotics that can handle such a situation is called Learning from demonstrations.
-In the past, these methods  have  achieved state of the art performance  in a variety of applications.\cite{ross2013learning,pomerleau1989alvinn,schulman2013case}
+Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
+against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
+underlying cost function describing the task, traditional model based control approaches are often not applicable. In
+these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching the robot how to
+accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.
 
-One approach to LfD is to train a policy, or a  function estimator (either a classifier or regressor), to predict a supervisor's behavior given training data of the  observations (input) and actions (output) performed while accomplishing a task.
-However the robot's actions affect the next state observed, which violates the standard i.i.d assumption that is common in most statistical learning approaches.
-Ross et al.
-proved that this can cause the error in the estimator to compound over the time and lead to performance degradation that is proportional to the time horizon of the task squared.
-The intuition behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the distribution it was trained on and encounters new states it can't generalize to.
-Ross and Bagnell overcome this by presenting an iterative method that first trains a policy on the data observed using standard supervised learning techniques then tries the policy out in the environment to see what states are likely to occur under the robot's trained policy.
-The supervisor then tells the robot what controls it should applied after each iteration and the policy is retrained \cite{ross2010reduction}.
-The DAgger method has been used since to teach a robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
+One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
+supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
+while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
+of states encountered during the execution of a policy are not independent random variables, thus making statistical
+inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
+time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
+behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
+distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
+presenting an iterative method that first trains a policy on the data observed using standard supervised learning
+techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
+the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
+and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
+robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
+through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
 
@@
 \includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
-\caption{ An illustrative example of estimating the risk area in the data collected for a simulated self driving car around a track with other cars.
-The green area corresponds to points that are likely to occur under the expert demonstrations, where outside are points that would occur with low probability and thus are considered high risk.
+\caption{ 
+Given a set of states corresponding to images of a race-track simulation (visualized in $\mathbb{R}^2$) with expert
+control inputs, we consider a quantile super levelset estimate (shaded) as an approximation of the riskiness of
+executing the trained policy at a given state. By varying the quantile threshold, we can increase or decrease the size
+of the quantile super-levelset area. In our approach, points outside the super-levelset are considered risky and, during
+training, roll-outs of the policy that leave the super-levelset require control demonstrations from the supervisor,
+while roll-outs within the super-levelset can be performed autonomously.
 }
@@
 
-During learning, implementations of DAgger require the supervisor to manually label the controls the robot should have applied for each states it visits.
-If the supervisor, is a human this can be tedious and expensive.
-We are interested in having the supervisor only need to provide labels in areas of high risk, or where the robot is likely to mis-predict the controllers actions to reduce the workload on the controller.
-A state can be risky for 2 reasons: 1) its is far from the states trained on, which potentially means our policy will mis-predict the supervisor \cite{tokdar2010importance} 2)  the state in the training set is being mis-predicted, so the state, although visited, doesn't have good control yet
+During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
+should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
+human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
+reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
+executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
+required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
+training data in its vicinity, which potentially means our policy will mis-predict the supervisor
+\cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
+nonetheless. If an accurate density estimation corresponding to
+the pairs of visited states and control signals is available, the first scenario can be captured by regions of
+state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
+is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
+model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
+machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
+demonstrations.
+%
+%Vague!!!
+%This property can be seen used in importance sampling when data is collected from one distribution, but tested on
+%another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
+%
+While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
+space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
+representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
+SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
+\cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
+image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
+estimate where the local policy estimate is inconsistent with the expert demonstrations.
 
-To estimate where the robot's current policy is likely to mis-predict the supervisor, we  leverage a property in statistical machine learning that a trained model will be able to generalize within the distribution it is trained on \cite{tokdar2010importance}.
-This property can be seen used in importance sampling when data is collected from one distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}.
-One approach then is to estimate the distribution the policy is trained on and then ask for the supervisor to take over if the  probability of the current state is low under the estimated distribution.
-However, the amount of data needed to accurately estimate the density increases exponentially with the dimension of state space \cite{nadaraya1964estimating}.
-If we are working with partial observations like image data this could be impractical.
-Thus, we propose using a modified version of a technique known as the One Class SVM that only tries to estimate the level set of the density trained on \cite{scholkopf2001estimating} and has been shown to successfully work on image data before in the context of outlier detection \cite{liu2014unsupervised}.
+To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
+where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
+and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
+inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
+able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
+analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
+the Markovian assumption).
 
-We make the following assumptions access to an environment where a robot can try out policies and sample trajectories and access to a supervisor that is able to provide demonstrations and tell the robot the control it should have applied after each iteration.
-We also assume that we are able to collect a series of partial observations from the environment and the controls applied.
-Lastly, we assume the observations encapsulate the Markov assumption in such that the probability of one is only dependent on the last observation and the controls applied.
-
-Our contributions to date are framing the problem of asking for help in an online setting as estimating the support of a distribution and proposing a modified version of the One Class SVM,that both estimates the level set of a distribution and carves out areas in the support where we know our policy will mis-predict the supervisor, to identify states of high risk.
-Initial results on a Mario AI video game, averaged over 20 levels,  suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 queries to the supervisor, while DAgger required 2800 queries.
-\todo{These are preliminary results and I want to test on more mario experiments and the self driving car, also look at robustness to hyperparamters such as $\nu$ before I am confident in them}
+Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
+demonstrations and reduces supervisor
+burdon by asking for supervisor demonstrations only in `risky' states. 
+We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
+of the distribution of states with demonstrations and additionally
+and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
+risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
+peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
+averaged over 20 levels.
+{\color{blue}[-- FINALIZE --]}
 
 \section{Related Work}
-The field of learning from demonstration has achieved state of the art performance in a variety of areas within robotics \cite{argall2009survey}.
-Abbeel et al.
-used an iLQR controller around helicopter trajectories demonstrated by an expert to successfully learn a series of aerobatics stunts \cite{abbeel2007application}.
-Billard and Matari used a hierarchy of neural networks on video data and tracking markers to imitate a human arms movements on a 37 degree of freedom humaniod robot \cite{billard2001learning}.
-Schulman et al.
-used a non-linear warping, thin plate splines, on collected trajectories of a human controlling a PR2 and tying knots with a rope then transferred the demonstrations to the new unseen initial configurations of the rope~\cite{schulman2013case}.
+The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
+\cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
+to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
+neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
+robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
+to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
+configurations of the~\cite{schulman2013case}.
 
- A subset of the learning from demonstration field is working within the assumption of no known dynamics and no access to a cost function.
-Under these assumptions, one approach to learning from demonstration is to collect a set of trajectories and controls from a supervisor and then treat the problem as a supervised learning problem that regresses on a function from state space to controls~\cite{argall2009survey}.
-Pomerleau et al.
-used this approach on raw image data and controls provided by a person driving a car and learned a policy that allowed a car to travel on a highway.
-However, they observed if the car deviated from the middle of the road it would not know how to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting demonstrations~\cite{pomerleau1989alvinn}.
-Ross et al.
-studied this effect and proved the amount of error accumulated is squared in the time horizon of a policy and proposed a learning algorithm, SMILE, that stochastically mixes the supervisor's control with the robots during training.
-Thus allowing the robot to explore states the supervisor hasn't seen before~\cite{ross2010efficient}.
+A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
+the robot and the environment are not known and that no access to a cost function describing a given task is available.
+Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
+problem can be treated as a supervised learning problem that determines a function from state space to
+controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
+associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
+travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
+not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
+demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
+rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
+stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
+robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.
 
-Ross and Bagnell then improved upon this method with DAgger an iterative method that first trains a policy on the data observed using standard supervised learning techniques and tries the policy out in the environment to see what states are likely to occur under the robots policy.
-The supervisor then tells the robot what controls it should applied after each iteration and the policy is retrained with an aggregate of all data seen before \cite{ross2010reduction}.
+Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
+policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
+the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
+controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
+before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
+\cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
+(HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
+methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
+\cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
+to move sematically in a building with a training set consisting of of humans following similar verbal instructions
+\cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
+Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.
 
-A quad-copter using DAgger learned how to fly through a forest using only HOG features extracted from visual images \cite{ross2013learning}.
-Guo et al.
-combined DAgger with Deep Q learning methods to achieve state of the art performance on the common Atari game benchmark in Reinforcement Learning \cite{NIPS2014_5421}.
-Duvallet use DAgger to teach robots to follow verbal instructions about where to move sematically in a building with a training set of humans following similar verbal instructions \cite{duvallet2013imitation}.
-Levine et al.
-extended the iterative learning paradigm through Guided Policy Search, which replaces the expert with iLQG and uses KL divergence constraints to train the policy to match the distributions of the controllers \cite{levine2015end}.
+One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
+provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
+algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
+human or an algorithm with a high computational demand.
 
-One limitation of DAgger is that it requires the demonstrator, or supervisor, to "label" every state the policy visits during learning.
-The act of labeling can be very tedious and expensive when the supervisor is a human.
-To reduce this Judah et al.
-proposed applying active learning technique to only query the supervisor for states that are likely to be visited under the current policy and are likely to be mis-predicted under the current policy\cite{judah2011active,judah2012active}.
-A drawback of this approach though is that it requires estimating the distribution of states, which can be difficult in high dimensions.
-Furthermore, their use of query by committee reduces their policy's function class to non-kernelized linear classifiers \cite{gilad2005query}, which could potentially hurt the ability of a policy to generalize.
+In prior work, Judah et al. proposed applying active learning techniques to only query the supervisor for states that are likely to be
+visited under the current policy and are likely to be mis-predicted under the current policy
+\cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
+density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
+approach is based on `query by committee', and considers only non-kernelized linear classifiers to represent the
+learned policy~\cite{gilad2005query}, thus restricting the class of policies which can be modelled with the approach.
 
-In order to tell where a policy is likely to mis-predict,we  leverage a property in statistical machine learning that a trained model will be able to generalize within the distribution it is trained on \cite{tokdar2010importance}.
-This property is used in importance sampling when data is collected from one distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}.
-One approach is to  estimate the probability density the policy is trained on.
+%[Let's discuss this part]
+{\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
+an incorrect control input, we leverage a
+property in statistical machine learning that a trained model will be able to generalize within the distribution it is
+trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
+distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
+approach is to estimate the probability density of states the policy is trained on.
 However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.
 
- Several other approaches have been proposed to tell when your estimator is likely to not generalize \cite{2003novelty}.Knox and Ng used a nearest neighbors approach to try and estimate if a point was close to $k$ neighbors, however it was shown to be susceptible to outliers because nearest neighbor only uses local information about the data \cite{knox1998algorithms}.
-Manevitz and Yousef trained a neural network filter to try and reconstruct the data and if the reconstruction error is high, they mark the point as likely to be outside of the estimators generalization ability.
-Manevitz and Yousef mention  that finding the right architecture can be task specific and require a lot of hyperparameter tuning  \cite{manevitz2002one}.
-The One Class SVM proposed by Scholk{\"o}pf et al.
-estimates a user defined level set of the distribution it is trained on by solving a convex quadratic program   to find the support vectors that encompasses the data.
-The method has been theoretically shown to approximate the level set of a density estimate in the asymptomatic  limit of sample and also its regularization term has the nice property of being equivalent to the quantile function\cite{vert2006consistency}.
-It has also been shown to successfully work on outlier detection for raw image data~\cite{liu2014unsupervised}.
+Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
+to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
+neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
+susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
+\cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
+at a point was high, the point was considered as likely to be outside of the estimators domain within which
+generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
+and might require a large amount of hyperparameter tuning.
+
+Our approach is in particular based on the One Class SVM proposed by Scholk{\"o}pf et al. which estimates a user
+defined quantile level set for a collection of training data by solving a convex quadratic program  to find support
+vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
+asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
+In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for outlier detection of high-dimensional 
+image data.
 
 \section{Problem Statement}
+\subsection{Notation and Background}
+{\color{blue} [-- TODO: SENSOR MODEL --]}
+We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
+high-dimensional vectors corresponding to images from a camera, or joint angles and object poses in the environment.
+We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
+nature. The environment is
+modeled to have dynamics that are stationary and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
+\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
+so that $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
+When no confusion arises, we denote the probability density over the initial state also by $p:\mathcal{X}\to
+\mathbb{R}$. By a trajectory, we mean a finite series of pairs of $T$ states visited and corresponding
+control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
+and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
+At times we will also consider trajectories in state space only, in which case a trajectory corresponds
+to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.
 
-\subsection{Notation and Background}
-\todo{figure out sensor model, meeting with Sergey next week about safe learning with out assuming a human is available I can ask him then}
-Define $\mathbf{x} \in \mathcal{X}$ as state space for a robot, for example $\mathbf{x}$ could be an image from a camera feed or a vector of joint angles.
-Define $\mathbf{u} \in \mathcal{U}$ as the class of controls for an agent, which could be for example torque control applied to a robot or discrete commands such as in a video game.
-The environment is modeled to have dynamics that are stationary and Markovian, such that the the probability of state $\mathbf{x_{t+1}}$ can be determined from $\mathbf{x}_t$ and $\mathbf{u}_t$, or $p(\bx_{t+1}|\bu_t,\bx_t)$.
-We represent a probability distribution over the initial state of the environment $p(\bx_0)$..
-Denote a trajectory as series of states visited and the controls applied  as $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$.
-A trajectory that is defined with state space only and not controls is $\tau_{\bx} = (\bx_0,....,\bx_T)$.
+By a policy, we mean a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
+We shall in particular consider classes of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
+parameter $\theta\in \mathbb{R}^d$ corresponding to support vectors of a Support Vector Machine (SVM).
+Any such policy, $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
+induces a density on state-space trajectories of length $T+1$: $p(\tau | \theta)=
+p(\bx_0)\prod_{i=0}^{T-1}p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$, for $\tau = (\bx_0, \bx_1, \ldots, \bx_N)\in
+\mathcal{X}^{N+1}$.
 
-A policy is a function from state space to controls, $\pi: \bx \rightarrow \bu$.
-A policy could be $\pi_\theta: \bx \rightarrow \mathbf{u}$, which is a  function that is specified by a vector of parameters  $\theta$.The vector of parameters $\theta$ can be for example weights in a neural network or the  vectors in a Support Vector Machine.
-A policy, $\pi_{\theta}$ in an environment with $p(\bx_0)$ and $p(\bx_{t+1}|\bx_t,\bu_t)$ induces a distribution on the possible trajectories:$ p(\tau_\bx | \theta)= p(\bx_0)\prod_{i=0}^{T-1}p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$.
-Also $\pi_{\theta}$ in an environment with $p(\bx_0)$ and $p(\bx_{t+1}|\bx_t,\bu_t)$  induces a distribution on states visited $p(\mathbf{x}|\theta)$.
+$p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
+$\pi_{\theta}$ for $t-1$ time steps which can be calculated by marginalization $p(\bx_t|\theta) =
+\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction},
+the average density on states is now defined as $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
+While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
+\bx)$ or $p(\bx|\theta)$, but instead assume that we have a stochastic real robot or a simulator such that for any state
+$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ such that $\bx_{t+1}$ follows the distribution corresponding
+to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. In particular, when 'rolling out' trajectories under a policy
+$\pi_{\theta}$, we utilize the robot or simulator to 'sample' the resulting stochastic trajectories rather than
+estimating than estimating $p(\bx|\theta)$ itself.
 
- The following is a way to convert from $p(\bx_t|\theta)$ to $p(\bx|\theta)$.
-Let $p(\bx_t|\theta)$ be the distribution of states visited at time $t$ if the robot follows the policy $\pi_{\theta}$ for $t-1$ time steps.
-Calculating this from $p(\tau_{\bx}|\theta)$ is mean marginalizing over the previous timesteps $p(\bx_t|\theta) = \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$.
-The average distribution on states is now defined as $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
+Typically, the objective in policy learning can be framed as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$
+of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
+\mathcal{U})^{T+1}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
+For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
+be considered \cite{levine2015end}.  In our present setting, we do not know the cost function itself, but instead have access to a "supervisor", 
+an algorithm or human that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
+an initial set of $N$ stochastic demonstration trajectories $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
+which are the result of the supervisor applying this policy.
 
-We do not know the distributions: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$,$p(\tau_{\bx}|
-\bx)$ or $p(\bx|\theta)$.
-But we assume we have a stochastic real robot or a simulator such that given any state $\bx_t$ and control $\bu_t$, it will move into a state $\bx_{t+1}$ such that $\bx_{t+1} \sim p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$.
-Note that $p(\tau_{\bx}|\theta)$ is high dimensional because $\bx$ is high dimensional.
+Next, we define a ``surrogate'' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$,
+while in the discrete case $l(\bu_0,\bu_1) = 1$ if $\bu_0 \neq \bu_1$ and $l(\bu_0, \bu_1)=0$ otherwise.
 
-Given $\pi_{\theta}$ we want to identify a set of highly probable trajectories and the associated highly probable states.
-We assume we are given some initial state $\bx_0$.
-We  "roll-out" the policy using the robot with the policy to sample the resulting trajectory and set of states reached, which provides a sequence of highly probably states under $p(\tau_{\bx}|\theta)$.Rather than estimating $p(\bx|\theta)$ or $p(\tau_{\bx}|\theta)$, we draw samples from them.
-
-The objective in policy learning can be framed as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$.
-The cost function is user defined and task specific.
-For each state $\bx_{t}$ and control $\bu_t$ the robot receives a penalty related to how far it is from the goal state.
-For example, in task of inserting a peg into a hole the cost function can be distance to desired final state \cite{levine2015end}.
-We also do not know the cost function.
-But we do have access to a "supervisor", an algorithm or human that uses some policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given an initial set of $N$ training/demonstration trajectories resulting from this policy: $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$.
-
-Next, we define a "surrogate" loss function $l$, which gives the distance between any pair of control values: in the continuous case $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$ or in a discrete case
-
- \vspace{-2ex}
-\begin{align}
- l(\bu_0,\bu_1) = \left\{
-     \begin{array}{lr}
-       1 & : \bu_0 = \bu_1\\
-       0 & : \bu_0 \neq \bu_1
-     \end{array}
-   \right.
-\end{align}
-
-Given a candidate policy $\theta$, we can use the surrogate loss function to compute how "close" it is to the supervisor's policy $\tilde{\pi}$.
-
-We want to compute a policy $\pi_{\theta}$ that minimizes the expected surrogate loss where the expectation is taken over the distribution of states.
+Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how "close" the policy's
+returned control intput $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
+$\tilde{\pi}(\bx)\in \mathcal{U}$.
+Our objective then consists of determining a policy $\pi_{\theta}$ minimizing the expected surrogate loss where the expectation is taken over the distribution of states.
 
@@
 \begin{align}\label{eq:LFD_obj}
-\underset{\theta}{\min} \: E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}(\bx))]
+\underset{\theta}{\min} \: E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}(\bx))].
 \end{align}
 
-The optimization problem in Eq.
-\ref{eq:LFD_obj} compares the action taken of the policy $\pi_\theta$ and  the supervisor, $\tilde{\pi}$  weighted by the probability of  the state occurring $p(\bx|\theta)$.
-
-Eq.
-\ref{eq:LFD_obj} is hard to solve because  the objective is not convex and we only have access to $\tilde{\pi}(x)$, where $x$ is a state in one of the demonstrations or $\bx \in \mathcal{D}$.
-To address these issues Stephane and Ross proposed an iterative method known as DAgger\cite{ross2010reduction}.
+The optimization problem in Eq. \ref{eq:LFD_obj} is typically non-convex and difficult to solve since we only have
+access to samples from the supervisor's policy $\tilde{\pi}$ arising from the demonstration trajectories $\mathcal{D}$.
+To address these issues Stephane and Ross proposed an iterative method known as DAgger \cite{ross2010reduction}.
 
  \subsection{DAgger: Dataset Aggregation}
- DAgger is an iterative algorithm that repeats two steps for $K$ iterations. 
- In Eq.
-\ref{eq:LFD_obj}, the objective involves both the parameterized policy $\pi_{\theta}$ and the average distribution of states with respect to the policy, $p(\bx|\theta)$.
-DAgger iteratively minimizes $\pi_{\theta}$ on the collected dataset of examples $\mathcal{D}$ and then adds new states of high probability under $\pi_\theta$ by sampling via policy roll outs from $p(\bx|\theta)$.
+Note that Eq. \ref{eq:LFD_obj} involves both the parameterized policy $\pi_{\theta}$ and the average distribution of
+states with respect to the policy, $p(\bx|\theta)$.
+Let us recall that Dataset Aggregation (DAgger) is an iterative algorithm developed by \cite{ross2010reduction} which iterates two basic steps for $K$ iterations to find an optimal policy under this objective.
+DAgger iteratively minimizes $\pi_{\theta}$ on the collected dataset of examples $\mathcal{D}$ and then adds new states
+of high probability under $\pi_\theta$ by sampling via policy `roll outs' from $p(\bx|\theta)$. 
+{\color{blue} [-- F: DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
+made more precise then and refer to the algorithm --]}
 
 \subsubsection{Step 1}
-At iteration $k=0$ given a dataset $\mathcal{D}_0$, the training set with $N_0$ demonstrated trajectories mapping $\bx$ to $\bu$.
-DAgger solves the following supervised learning problem with respect to the surrogate loss function.
+At iteration $k=0$ an initial dataset $\mathcal{D}_0$ of $N_0$ supervisor demonstration trajectories 
+with $T+1$ time steps: $\tau^i=(\bx_0^i, \bu_0^i, \ldots, \bx_T^i, \bu_T^i)\in (\mathcal{X}\times\mathcal{U})^{T+1}$ for $i\in \{0, \ldots, N_0\}$
+mapping states to control
+inputs is provided. DAgger solves the following optimization problem with respect to the surrogate loss function:
 
@@
 \begin{align}\label{eq:super_objj}
-\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{N}\sum_{t=1}^T l(\pi_{\theta}(\bx_t^{i}),\bu_{t}^i)
+\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{N_0}\sum_{t=0}^T l(\pi_{\theta}(\bx_t^{i}),\bu_{t}^i).
 \end{align}
 
-This is a supervised learning problem and can be solved using standard machine learning techniques, for example a support vector machine or a neural network.
-The surrogate losses mentioned early like Squared Euclidean distance or an Indicator function are appropriate optimization objectives.
+This problem can be considered as a supervised learning problem in particular and can be solved using standard machine
+learning techniques, for example a support vector machine or a neural network.
 
- To handle the fact that the supervisor's policy contains noise $\epsilon$, we employ a regularization technique in the optimization.
-Regularization is a technique to control the smoothness of the function that is fit to the sampled data.
-It is a common technique to make the estimator robust to zero mean noise on data.
-In practice it is a penalty term on either  the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.
+To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
+{ \color{blue} [-- F: Make precise --]}
+can be considered as present in policy's output. We employ a regularization technique in the optimization which is
+used to control the smoothness of the function that is fit to the sampled data.
+In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.
 
@@
 For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
-Formally, for a given sampled trajectory  $\tau = (\bx_1,\bu_1,...,\bx_T,\bu_T )$.
-The supervisor provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ to the trajectory $\tau = (\bx_1,\tilde{\bu}_1,...,\bx_T, \tilde{\bu}_T )$.
-This can be very tedious for a human.
+Formally, for a given sampled trajectory  $\tau = (\bx_0,\bu_0,...,\bx_T,\bu_T )$.
+The supervisor provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
 The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.
 
-Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss  goes to zero.
-Since DAgger requires rolling out the policy at each iteration, one way to terminate the algorithm is when the performance of the rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined threshold $\gamma$.
+Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss approaches zero. Since DAgger
+requires rolling out the policy at each iteration, one way to terminate the algorithm is when the performance of the
+rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined
+threshold $\gamma$. {\color{blue} [-- F: Also talk about $\beta_i$ weights in DAgger --]}.
 
-Dagger works well in both simulation and real world experiments.
-It also has theoretical guarantees that it will converge in the limit to the supervisor's policy.
-However, using policy rollouts means the robot can enter dangerous states, which could damage a robot in a non simulation system.
-For example, when DAgger was used on a quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
-A state can be risky for 2 reasons: 1) its is far from the states trained on, which potentially means our policy will mis-predict the supervisor and incur high surrogate loss \cite{tokdar2010importance} 2) the surrogate loss associated with the state is high, so the state, although visited, doesn't have good control yet.
-Furthermore, iterations are tedious because if a human is the supervisor requires manual "labeling" of every state visited with the appropriate control.
+Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore
+has guarantees guarantees the convergence to the supervisor's policy {\color{blue} [-- F: ONLY AN ERROR BOUND, RIGHT? --]}. 
+However, policy rollouts can result in the robot entering dangerous states. For example, when DAgger was used on a
+quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
+We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
+previously trained states, which potentially means our policy will mis-predict the supervisor and incur high surrogate
+loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so the state, although visited, does
+not model the supervisor's control inputs correctly. Furthermore providing correct control inputs or ``labeling'' at each
+iteration and each state in DAgger can be tedious or costly.
 
-To address these limitations, we propose to 1) avoid highly risky states entirely via terminating the policy roll-out and 2) recognize slightly risky states and request human input for these and to reduce the burden on the human trainer.
-One way to do this is to define risk in terms of distance to the nearest neighbor, but this vulnerable to outliers in the known set of states.
-Another option is to fit a distribution to the known set of states, which requires an exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}.
-We propose using a modified version of the technique known as the One Class SVM that  estimates a boundary of the density \cite{scholkopf2001estimating}.
+To address these limitations, we propose to 1) avoid highly risky states entirely by early termination the policy
+roll-out that enter these regions and 2) to recognize non-risky states and to not request human input for these,
+thereby reducing the burden on the human trainer.
 
-\subsection{Estimation of a Distribution's Level Set}\label{sec:level}
-\todo{Work with Florian on the first paragraph to make it less abstract and specific to the robotics}
+One way to do this is to define risk in terms of distance to a nearest neighbor, but this approach is vulnerable to
+outliers in the known set of states. Another option is to fit a density to the known set of states, which requires an
+exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}. We propose using a
+modified version of the technique known as the One Class SVM that implicitly approximately estimates a boundary of a user defined quantile of
+a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
+
+\subsection{Estimation of Quantile Level Sets}\label{sec:level}
+{\color{blue} [-- REVISED UP TO HERE --]}
 Support estimation can be defined as minimizing a function that contains the volume of a given probability distribution.
@@
 
-\subsection{SHEATH:Support-based HElp AquisiTion from Humans}
+\subsection{The \acro~algorithm}
 
@@
 \section{Theoretical Analysis}
-
+{\color{blue} [-- TEXT FROM HERE IS STILL ROUGH AND CHANGING --]}
 \subsection{Convergence Rate}

### 2015-07-30 paper.tex
Version 10, ready for Anka's comments.

@@
 
-\title{\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies from Demonstrations }
+\title{\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies
+from Demonstrations {\color{blue}(v.10)} }
 
@@
 demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
-the problem of determining a policy as an iterative supervised learning problem which alternates between executing a
-trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. In this
-work, we propose a novel algorithm, \acro~which is based on DAgger and which estimates the riskiness of states
+the problem of determining a policy as an iterative supervised learning problem. DAgger alternates between executing a
+trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. 
+We propose a novel algorithm, \acro~ based on DAgger which estimates the riskiness of states
 encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
-states used for training the current policy. Since learning a quantile function for high-dimensional input data is
+states used for training the current policy and which additionally takes empirical surrogate loss of the current policy
+into account. Since learning a quantile function for high-dimensional input data is
 challenging, we instead modify an SVN-based approach to quantile estimation that employs regularization to solve this
 problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
-user-defined quantile super-levelset is encountered. Our approach furthermore reduces the amount of neccessary
+user-defined quantile super-levelset is encountered. Our approach empirically reduces the amount of neccessary
 supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
 In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
-DAgger, our approach results in similar performance levels as DAgger while reducing the amount of required supervisor
+DAgger, our approach results in similar peak performance levels as DAgger while reducing the amount of required supervisor
 control inputs by more than {\color{blue}[-- TODO --]} percent.
@@
 \section{Introduction} 
-Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
+Consider the problem of teaching a robot a complex task such cooking a meal or racing a toy car around a track
 against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
-underlying cost function describing the task, traditional model based control approaches are often not applicable. In
+underlying cost function describing the task, traditional model-based control approaches are often not applicable. In
 these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching the robot how to
@@
 One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
-supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
+supervisor's behavior given training data consisting of pairs of observations (input) and control inputs (output) performed
 while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
 of states encountered during the execution of a policy are not independent random variables, thus making statistical
-inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
+inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over 
 time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
@@
 presenting an iterative method that first trains a policy on the data observed using standard supervised learning
-techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
-the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
+techniques and then tries (or 'rolls out') the policy in the environment to see what states are likely to occur under
+the robot's trained policy.  The supervisor then tells the robot what controls it should have applied after each iteration
 and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
@@
 Given a set of states corresponding to images of a race-track simulation (visualized in $\mathbb{R}^2$) with expert
-control inputs, we consider a quantile super levelset estimate (shaded) as an approximation of the riskiness of
+control inputs, we consider a modified quantile super-levelset estimate (shaded) as an approximation of the riskiness of
 executing the trained policy at a given state. By varying the quantile threshold, we can increase or decrease the size
 of the quantile super-levelset area. In our approach, points outside the super-levelset are considered risky and, during
-training, roll-outs of the policy that leave the super-levelset require control demonstrations from the supervisor,
+training, roll-outs of the policy that leave the super-levelset require control input demonstrations from the supervisor,
 while roll-outs within the super-levelset can be performed autonomously.
@@
 should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
-human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
+human or an algorithm with a high time complexity, this can be tedious or expensive. We are hence interested in
 reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
 executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
-required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
+required due to high risk. We postulate that a state can be risky for 2 reasons: 1) we encounter a state which has a low density of
 training data in its vicinity, which potentially means our policy will mis-predict the supervisor
-\cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
+\cite{tokdar2010importance} 2) the state is potentially near previously visited states, but the control-input is mis-predicted
 nonetheless. If an accurate density estimation corresponding to
 the pairs of visited states and control signals is available, the first scenario can be captured by regions of
-state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
+state-space with a low density estimate. Areas of low density are then considered to be risky since insufficient data
 is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
@@
 image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
-estimate where the local policy estimate is inconsistent with the expert demonstrations.
+estimate where the local policy estimate is inconsistent with the expert demonstrations in the sense that the incurred
+surrogate loss of the current policy relative to the expert demonstration is above a threshold $\varepsilon>0$.
 
-To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
+To apply our approach, we make the same basic assumptions as DAgger: 1) we require access to an environment
 where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
@@
 Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
-demonstrations and reduces supervisor
-burdon by asking for supervisor demonstrations only in `risky' states. 
-We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
-of the distribution of states with demonstrations and additionally
-and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
-risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
-peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
-averaged over 20 levels.
-{\color{blue}[-- FINALIZE --]}
+demonstrations and reduces supervisor burdon by asking for supervisor demonstrations only in `risky' states. We achieve
+this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets of the
+distribution of states with demonstrations and additionally `carves out' areas in state space we know our policy
+will mis-predict the supervisor, thus identifying states of high risk.  Our experimental results on a Super Mario Atari
+video game, suggest \acro~is able to reach DAgger's peak performance of surviving for an average of 2200 simulation
+steps with only 1200 queries to the supervisor, while DAgger required 2800 queries averaged over 20 levels.
 
@@
 to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
-configurations of the~\cite{schulman2013case}.
+configurations of the rope~\cite{schulman2013case}.
 
-A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
+A subset of research in the field of learning from demonstrations is working with the assumptions that the dynamics of
 the robot and the environment are not known and that no access to a cost function describing a given task is available.
@@
 associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
-travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
-not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
+travel on a highway. However, they observed that if the car deviated from the middle of the road, the learned policy was
+not able to recover. This behavior was attributed to the fact the car only drove in middle of the road while collecting
 demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
@@
 controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
-before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
+before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. In
 \cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
@@
 to move sematically in a building with a training set consisting of of humans following similar verbal instructions
-\cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
+\cite{duvallet2013imitation}. In a related work, Levine et al. recently extended the iterative learning paradigm through Guided Policy
 Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.
@@
 One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
-provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
-algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
-human or an algorithm with a high computational demand.
+provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory
+at every iteration of the algorithm. Providing these control inputs can be very tedious or expensive both in the case
+where the `supervisor' is a human or an algorithm with a high computational cost.
 
-In prior work, Judah et al. proposed applying active learning techniques to only query the supervisor for states that are likely to be
-visited under the current policy and are likely to be mis-predicted under the current policy
+In prior work, Judah et al. proposed applying active learning techniques to only query the supervisor for states that
+are likely to be visited under the current policy and are likely to be mis-predicted under the current policy
 \cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
-density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
-approach is based on `query by committee', and considers only non-kernelized linear classifiers to represent the
-learned policy~\cite{gilad2005query}, thus restricting the class of policies which can be modelled with the approach.
+density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the approach is
+based on `query by committee', and considers only non-kernelized linear classifiers to represent the learned
+policy~\cite{gilad2005query}, thus restricting the class of policies which can be modelled with the approach.
 
 %[Let's discuss this part]
-{\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
-an incorrect control input, we leverage a
-property in statistical machine learning that a trained model will be able to generalize within the distribution it is
-trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
-distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
-approach is to estimate the probability density of states the policy is trained on.
-However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.
+{\color{blue}[-- IMPROVE THIS PARAGRAPH --]} 
+In order to determine state space regions where a policy is likely to determine an incorrect control input, we leverage
+a common realization in statistical machine learning: a trained model will likely be able to generalize only in 
+regions near which sufficient training data is available \cite{tokdar2010importance}. 
+%F:Don't like this, discuss:
+%This property is used in importance sampling when data is collected from one
+%distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. 
+One approach to estimate such regions is to estimate the probability density for the training data. However, the amount of data needed
+to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.
 
@@
 at a point was high, the point was considered as likely to be outside of the estimators domain within which
-generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
+generalization was possible. Manevitz and Yousef conjecture that finding the right architecture for this purpose can be task specific
 and might require a large amount of hyperparameter tuning.
@@
 {\color{blue} [-- TODO: SENSOR MODEL --]}
-We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
-high-dimensional vectors corresponding to images from a camera, or joint angles and object poses in the environment.
+We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task. An example is given by
+high-dimensional vectors corresponding to images from a camera, or the robot's joint angles and object poses in the environment.
 We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
@@
 When no confusion arises, we denote the probability density over the initial state also by $p:\mathcal{X}\to
-\mathbb{R}$. By a trajectory, we mean a finite series of pairs of $T$ states visited and corresponding
-control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
+\mathbb{R}$. By a trajectory, we mean a finite sequence of pairs of $T+1$ states visited and corresponding
+control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
 and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
@@
 
-$p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
+Let $p(\bx_t|\theta)$ denote the probability density value of a state visited at time $t$ if the robot follows the policy
 $\pi_{\theta}$ for $t-1$ time steps which can be calculated by marginalization $p(\bx_t|\theta) =
@@
 While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
-\bx)$ or $p(\bx|\theta)$, but instead assume that we have a stochastic real robot or a simulator such that for any state
-$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ such that $\bx_{t+1}$ follows the distribution corresponding
-to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. In particular, when 'rolling out' trajectories under a policy
-$\pi_{\theta}$, we utilize the robot or simulator to 'sample' the resulting stochastic trajectories rather than
-estimating than estimating $p(\bx|\theta)$ itself.
+\bx)$ or $p(\bx|\theta)$, we instead assume that we have a stochastic real robot or a simulator such that for any state
+$\bx_t$ and control $\bu_t$, we can sample the resulting next state $\bx_{t+1}$ from the distribution corresponding
+to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. In particular, when `rolling out' trajectories under a policy
+$\pi_{\theta}$, we utilize the robot or simulator to `sample' the resulting stochastic trajectories rather than
+estimating $p(\bx|\theta)$ itself.
 
@@
 \mathcal{U})^{T+1}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
-For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
-be considered \cite{levine2015end}.  In our present setting, we do not know the cost function itself, but instead have access to a "supervisor", 
+For example, for the task of inserting a peg into a hole, the distance between the peg's current and desired final state can
+be considered \cite{levine2015end}.  In our present setting, we do not know the cost function itself, but instead have
+access to a ``supervisor'', 
 an algorithm or human that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
@@
 
-Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how "close" the policy's
+Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how close the policy's
 returned control intput $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
@@
  \subsubsection{Step 2}
-DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\theta_{k=1}$.
-For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
-Formally, for a given sampled trajectory  $\tau = (\bx_0,\bu_0,...,\bx_T,\bu_T )$.
-The supervisor provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
+ DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\pi_{\theta_{k=1}}$.
+ For every state visited, DAgger requests the supervisor to provide the appropriate control/label after the roll-out is
+ finished. Formally, for a given sampled trajectory  $\tau = (\bx_0,\bu_0,...,\bx_T,\bu_T )$. The supervisor provides
+ labels $\tilde{\bu}_t$, where $\bu_t \sim \tilde{\pi}(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
 The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.
 
-Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss approaches zero. Since DAgger
-requires rolling out the policy at each iteration, one way to terminate the algorithm is when the performance of the
-rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined
-threshold $\gamma$. {\color{blue} [-- F: Also talk about $\beta_i$ weights in DAgger --]}.
+Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss approaches zero or is below a
+predefined threshold.
+
+{\color{blue}[-- F: Also talk about $\beta_i$ weights in DAgger --]}.
 
@@
 previously trained states, which potentially means our policy will mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so the state, although visited, does
-not model the supervisor's control inputs correctly. Furthermore providing correct control inputs or ``labeling'' at each
-iteration and each state in DAgger can be tedious or costly.
+loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so that at
+that state, supervisor's policy is not correctly approximated. Furthermore providing correct control inputs or ``labeling'' at each
+iteration and each state in DAgger can be tedious and costly.
 
-To address these limitations, we propose to 1) avoid highly risky states entirely by early termination the policy
+\emph{To address these limitations, we propose to 1) avoid highly risky states entirely by early termination the policy
 roll-out that enter these regions and 2) to recognize non-risky states and to not request human input for these,
-thereby reducing the burden on the human trainer.
+thereby reducing the burden on the human trainer. }
 
-One way to do this is to define risk in terms of distance to a nearest neighbor, but this approach is vulnerable to
-outliers in the known set of states. Another option is to fit a density to the known set of states, which requires an
+One way to define risk is to consider the distance between a state and a nearest neighbor in the training set, but this approach is vulnerable to
+outliers. Another option is to fit a density to the training set, which requires an
 exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}. We propose using a
-modified version of the technique known as the One Class SVM that implicitly approximately estimates a boundary of a user defined quantile of
+modified version of the technique known as the One Class SVM that implicitly and approximately estimates a boundary of a user defined quantile of
 a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
@@
 \subsection{Estimation of Quantile Level Sets}\label{sec:level}
-{\color{blue} [-- REVISED UP TO HERE --]}
-Support estimation can be defined as minimizing a function that contains the volume of a given probability distribution.
-Formally we define it as follows let $\mathbf{x}_1,...,\mathbf{x}_n $ be i.i.d.
-random variables in a set $\mathcal{X}$ with distribution $P$.
-Let $\mathcal{G}$ be a class of measurable subsets of $\mathcal{X}$ and let $\lambda$ be a real function defined on $\mathcal{G}$.
-The quantile function with respect to $(P,\lambda,\mathcal{G})$ is
-
+We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
+independent and identically distributed samples $\mathbf{x}_1,...,\mathbf{x}_n\in \mathcal{X}$.
+In most general terms, the quantile function for $P$ and subject to a class of measurable subsets $\mathcal{G}$ of $\mathcal{X}$ is
+defined by
 \vspace{-2ex}
@@
 \end{align} 
+$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes the measure which most commonly is given by the Lebesgue measure.
+Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
+measure (i.e. volume) for each $\gamma\in [0,1]$ (this set is in general not necessarily unique). 
+$G(\gamma)$ denotes a set of minimum measure $G \in \mathcal{G}$ with $P(G(\gamma))\ge \gamma$. Note in particular that $G(1)$ is the support of the density $p$ corresponding to $P$, if $p$ exists.
 
-We denote by $G(\gamma)$ the $G \in \mathcal{G}$ that attains the infinimum.
-The most common choice of $\lambda$ is Lebesgue measure, in which case $G(\gamma)$ is the minimum volume $G \in \mathcal{G}$ that contains at least a fraction $\gamma$ of the the probability mass.
-Thus, $G(1)$ is the support of the density $p$ corresponding to $P$, assuming it exists.
-
-To handle high dimensional densities $P$, work by Scholk{\"o}pf et al.
+To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al.
 looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}.
-They then minimize a SV  regularizer which, using a kernel, controls the smoothness of the estimated function describing $G$.
-In terms of the quantile function described in Eq.
-\ref{eq:quantile}, the approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$.
-Here $(w,\rho)$ are a weight vector and offset parameterizing a hyperplane in the feature space associated with a kernel.
+By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
+derives an approximation of the quantile function described in Eq. \ref{eq:quantile}, which in particular has rigorous
+convergence guarantees asymptotically when a normalized Gaussian kernel $k$ is chosen and bandwidths decay at an
+appropriately chosen rate as the number of samples tends to infinity \cite{vert2006consistency}.
+This approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$,
+$f_w(\mathbf{x}) = \sum_i w_i k(\mathbf{x}_i, \mathbf{x})$
+and $(w,\rho)$ denote the weight vector and offset parameterizing a hyperplane in the feature space associated with a
+Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}$.
 
@@
 
-\caption{Data is sampled from a Gaussian Mixture Model and in Fig.
-\ref{fig:subfigure1}, the red points are those that the trained policy, $\pi_{theta}$ will mis-predict.
-In Fig.
-\ref{fig:subfigure2} the One Class SVM is fit to the data and tries to estimate the areas of low risk (the light green region), while it is able to estimates the area where the majority of the data lies it also encloses the points the trained policy is mis-predicting.
-In Fig.
-\ref{fig:subfigure3}, the Risk Sensitive One Class SVM is able to effectively remove the red points from the region of low risk.}
+\caption{We display synthetic data sampled from a Gaussian Mixture Model with three Gaussian components. In Fig.
+\ref{fig:subfigure1}, the red points denote those that we assume a trained policy, $\pi_{theta}$ will mis-predict (i.e.
+encounter large loss for). In Fig. \ref{fig:subfigure2}, the One Class SVM is fit to the data and tries to estimate the
+areas of low risk (the light green region). While the densest area of data samples is enclosed, the standard One Class
+svm is not able to incorporate information about samples on which our policy incurrs large loss. In Fig.
+\ref{fig:subfigure3}, our modification - Risk Sensitive One Class SVM - is able to effectively remove the red points
+with high loss from the region of low risk.}
 \label{fig:support_example}
@@
 
-Let $\Phi$ be a feature map $\mathcal{X} \rightarrow \mathcal{F}$, i.e.
-a map into an inner product space $\mathcal{F}$ such that the inner product in the image of $\Phi$ can be computed by evaluating some  kernel
+Let $\Phi:\mathcal{X}\to \mathcal{F}$ denote the feature map corresponding to our exponential kernel, mapping the
+observation space $\mathcal{X}$ into a Hilbert space $(\mathcal{F}, \langle, \rangle)$ such that $k(\bx, \bx') = \langle
+\Phi(\bx), \Phi(\bx')\rangle$.
 
+The One Class SVM proposed by \cite{scholkopf2001estimating} determines a hyperplane in feature space $\mathcal{F}$
+maximally separating the input data from the origin:
 \vspace{-2ex}
-\begin{align}
-k(\bx_0,\bx_1) = \langle\Phi(\bx_0),\Phi(\bx_1)\rangle
+\begin{align}\label{eq:primal_sup}
+    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
+\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
 \end{align}
 
-such as the Gaussian kernel
-
-\vspace{-2ex}
-\begin{align}
-k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}
-\end{align}
-
-The main idea is to solve an optimization problem that separates the origin, we solve the following quadratic problem:
-
-\vspace{-2ex}
-\begin{align}\label{eq:primal_sup}
-\underset{w\in F, \mathbf{\xi} \in \mR, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag
-\end{align}
-
-The parameter $\nu$ controls the penalty on slack terms and asymptotically approaches is equivalent to $\gamma$ \cite{vert2006consistency}.  The decision function then becomes
+Here, the parameter $\nu$ controls the penalty or `slack term' and asymptotically approaches $\gamma$ \cite{vert2006consistency}
+in the quantile definition when bandwidths decay at appropriate rates as the number of samples increases. The decision
+function, determining point membership in the approximate quantile levelset is given by
 
@@
 \begin{align}\label{eq:decision_func}
-g(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho)
+g(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
 \end{align}
 
-Where $g(x) = 1$ indicates in the support region and $(g) = -1$ denotes being outside the support region.
-The dual form of the optimization takes the form of a Quadratic Program with respect to the Gram Matrix \cite{scholkopf2001estimating}.
+Where, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
+$g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
+if $x$ lies strictly in the quantile sub-levelset. The dual form of the optimization yields a Quadratic Program 
+that can be solved efficiently \cite{scholkopf2001estimating}.
 
-Estimating the level set of a distribution can be a measure of the generalization ability of $\pi_{\theta}$ to points not within $\mathcal{D}$.
-However, it does not account for the fact that for a given $\theta$ or  solution to Eq.
-\ref{eq:super_objj}.
-$\pi_\theta$ may not correctly match the supervisor's controls for all points train on.
-To account for this, we propose a modification to the One Class SVM denote:
+For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
+a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available.
+However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
+optimizing Eq. \ref{eq:super_objj} may still incur a large surrogate loss. To account for this, we propose a
+modification to the One Class SVM:
 
@@
      \begin{array}{lr}
-       1 & : \pi_{\theta}(\bx_i) =\bu_i\\
-       -1 & : \pi_{\theta}(\bx_i) \neq \bu_i
+         1 & : l(\pi_{\theta}(\bx_i),\bu_i)\le \varepsilon\\
+         -1 & : l(\pi_{\theta}(\bx_i),\bu_i)>\varepsilon
      \end{array}
@@
 \end{align}
-
-or $y_i$ is $1$ if the control applied matches the supervisor and $-1$ if it differs.
-In the regression case the decision between $1$ and $-1$ can be set by a some threshold on a L2-norm or $||\pi_{\theta}(\bx_i)-\bu_i||$.
-We use $y_i$ to modify the optimization as follows:
+Where, in the case when $l$ denotes discrete $0-1$ loss, we set $\varepsilon = 0$, while in the continuous $L_2$ loss
+case, $\varepsilon$ is a user defined threshold specifying allowable surrogate loss.
+We use $y_i$ to modify the One Class SVM optimization objective as follows:
 
@@
 \begin{align}\label{eq:primal_sup}
-\underset{w\in F, \mathbf{\xi} \in \mR^l, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}
+    \underset{w\in F, \mathbf{\xi} \in \mathbb{R}^l, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
+\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}.
 \end{align}
 
-Points that are mis-predicted are then enforced to lie on the opposite of the hyper-plane in the feature space $\phi(\bx)$, which carves out holes in the support region around them.
-The dual formulation, which is what is solved in practice, can be derived as
+States that incur loss above the $\varepsilon$ threshold are then enforced to lie on the opposite side of the
+hyper-plane separating the origin from the data in the feature space. Practically, this modification corresponds to
+`carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
+exluded from the super-levelset.
 
+The dual formulation to the modified optimization problem, which is solved in practice, is 
 \vspace{-2ex}
 \begin{align}\label{eq:dual_sup}
-\underset{\alpha\in \mathcal{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
-\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1 
+\underset{\alpha_i\in \mathbb{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
+\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1.
 \end{align}
 
-Our decision boundary function $g(\bx)$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n \alpha_i y_i k(\bx_i,\bx) - \rho$.
-To compute the $\rho$ term,we leverage the fact that for an optimal solution the inequalities in Eq.
-\ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$.
-Therefore we can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating}.
+Our corresponding decision function $g:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n
+\alpha_i y_i k(\bx_i,\bx) - \rho$. To compute the $\rho$ term, we leverage the fact that for an optimal solution the
+inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
+can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating} {\color{blue} [-- F:
+explain this more --]}.
 
@@
 
-Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the supervisor's control,which we define as the region of low risk.
-In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.
-Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the supervisor provide labels when the robot leaves this boundary.
-Furthermore to avoid entering pathological states that are far from the supervisor's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$.
-The risk threshold, $r_0$, is user defined based on the task.
+Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
+predict the supervisor's control, by means of the thresholded surrogate just discussed.  
+% Too vague:
+%In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
+%Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
+To reduce the burdon on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
+$\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
+above a threshold $\varepsilon$ chosen by the user.
+The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
+resulting risk-aware quantile super-levelset and we terminate roll-outs that are at a task-specific threshold $r(\bx) = \sum_i^n
+\alpha_i \bx_i k(\bx_i,\bx)-\rho>r_0$ away from the decision boundary $g$ corresponding to this modified super-levelset.
 
+{\color{blue} [-- F: use formal algorithm and explain here instead --]} 
 \subsubsection{Step 1}
-Similar to DAgger at iteration $k$ the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$ by solving Eq.
-\ref{eq:super_objj}.
-We then estimate the level set of the distribution being trained on by solving the optimization for the One Class SVM or $\ref{eq:primal_sup}$ on the dataset $\mathcal{D}_k$.
-We now have a decision boundary $g_k(\bx)$, which is $1$ if the region is in the low risk area and $-1$ otherwise .
-The parameter $\nu$ is an estimate of how much probability mass is contained in the level set and can be use to control the size of the low risk region.
+
+Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
+by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
+training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
+This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.
 
  \subsubsection{Step 2}
- In DAgger the policy that was rolled out is $\pi_{\theta_k}$, however this could potential encounter pathological states that are far from the initial set of demonstrations $\mathcal{D}_0$.
-To prevent this we terminate the rolled out policy if the risk, or distance from the support, is above some threshold $r(\bx_t) > r_0$.
-Furthermore, instead of labeling every state now the supervisor is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.
-These states are then added to the dataset $\mathcal{D}_{k+1}$ and the algorithm goes back to Step 1.
+ In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
+ robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
+ above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
+ provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
+ dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.
 
-An implicit trade off exists between what how much of the distribution is contained in the selected level set and the amount of exploration the robot is allowed.
-If the level set is large the robot will be allowed to explore in this region and potentially make more mistakes with respect to the expert, but learn faster.
-If the level set contains a smaller fraction of data, then the expert will be in control more and the robot will learn at a slower rate.
+We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
+between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
+supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
+incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
+areas and obtain more labels from the supervisor in those regions.
 
 \section{Theoretical Analysis}
-{\color{blue} [-- TEXT FROM HERE IS STILL ROUGH AND CHANGING --]}
+{\color{blue} [-- VERY ROUGH FROM HERE --]} 
 \subsection{Convergence Rate}
-\todo{These are ideas still in progress}
-The convergence rate of DAgger is dependent on the probability of the expert taking over at each iteration $\beta_i$ \cite{ross2010reduction}.
-For SHEATH, this corresponds to the probability of leaving the support or $p(g(\mathbf{x}) = -1|\pi_{\theta_i})$ .
-The intuition is that the larger the level set parameter $\nu$ is the lower the probability of leaving is and thus faster convergence rate, but potentially less safe exploration.
-Not sure if a formal proof is going to be possible though with assuming known dynamics, still looking into it.
-However, we can experimentally demonstrate this.
+{\color{blue} [-- F: Please discuss $\beta_i$ when introducing DAgger --]} 
+The convergence rate of DAgger is dependent on the probability of the expert taking over at each iteration $\beta_i$
+\cite{ross2010reduction}. For \acro, this corresponds to the probability of leaving the support or $p(g(\mathbf{x}) =
+-1|\pi_{\theta_i})$ . The intuition is that the larger the level set parameter $\nu$ is the lower the probability of
+leaving is and thus we obtain faster convergence rates, but potentially need to apply risky roll-outs. We are not sure if a formal proof 
+will be possible. However, we can experimentally demonstrate this.
 
@@
 \subsection{Driving Example}
-A common benchmark in RL is a car driving around a track avoiding other cars \cite{argall2009survey}.
-In our driving simulator, the car must stay on a rectangular track and dodge the orange cars that are on the track as well.
-If the car falls off the track, it is placed back on to the center.
-The car's control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
-The internal state space of the car is xy-coordinates and the angle it is facing.
-Our supervisor is a solver that uses state space search through the driving simulator to plan the next control.
+A common benchmark in Reinforcement Learning is that of a car driving around a track while avoiding collisions with
+other cars \cite{argall2009survey}. We implemented a car simulator where the car must stay on a rectangular track and
+avoid autonomously controlled cars that drive on the same track. If the car accidentally leaves the track, it is placed
+back on the center of the track at a nearby position. The car's control input space is  $\mathcal{U} = \lbrace -15^\circ, 0, 15^\circ \rbrace$
+instantly changing the angle of the car that drives at a unit speed. The internal state space of the car is given by the
+xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
+state space search through the driving simulator to plan the next control {\color{blue} [-- F: be more precise --]}.
 
-We have the supervisor drive around the track 2 times and then collect the raw images observed.
-We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV.
-For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.
-For the optimization of Eq.
-\ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
+The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
+and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
+Oriented Gradients (HOG) features using OpenCV. These histograms serve as the \emph{observable state space}
+$\mathcal{X}$. For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
+policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
+validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
+exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution. 
+{\color{blue} [-- F: what about $r_0$? --]}
 
-We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track, versus the number of queries made to the supervisor.
-Initial results averaged over 1 level shown in Fig.
+We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
+defined to be total number of times the car left the track or collided with the other cars on the track. We compare the
+cost to the number of control input demonstrations queried from the supervisor.
+Initial results over 1 level shown in Fig.
 suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
@@
 \includegraphics[width=6cm, height=6cm]{figures/race_car_track_example.png}
-\caption{ An example image from the racing simulator.
-The car is meant to drive around a rectangular track and dodge other cars.
-The supervisor drives around the track for 3 iterations and HOG features are extracted from the images.
-}
+\caption{ An example image from the racing simulator. The car has to drive around a rectangular track and avoid other
+cars. The supervisor drives around the track three times and HOG features are extracted from the images to represent
+observable states.  }
 
@@
 \includegraphics[width=8cm, height=6cm]{figures/dagger_sheath_no_cars.png}
-\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track.
-Initial results averaged over 1 level shown suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
-\todo{Run this over many trials}  }
+\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is given
+    by the number of times the car left the track or collided with the other cars on the track. Initial results averaged
+    over 1 level suggest a $75\%$ reduction in the number of queries needed for \acro~compared to DAgger.}
 
@@
 Super Mario Bros.
-is a platform video game where the character, Mario, must move across each stage by avoiding being hit by enemies and falling into gaps, and before running out of time.
+is a platform video game where the character, Mario, must move across each level by avoiding being hit by enemies and falling into gaps, and before running out of time.
 We used the simulator from a recent Mario Bros.
@@
 Our expert is a near optimal $A^*$ search algorithm that plans ahead using the game simulator.
-An action consists of 4 binary variables indicating which subset of buttons we should press in $\lbrace \mbox{left},\mbox{right},\mbox{jump},\mbox{speed} \rbrace$.
-For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $C\gamma=0.01$, which was set via cross validation on the initial training examples from our expert..
-We initialized both Dagger and SHEATH with two expert demonstrations for each level.
-For the optimization of Eq.
-\ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $c=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
+The set of allowable control inputs $\mathcal{U}$ consists of 4 binary variables indicating which subset of buttons we
+should press in $\lbrace \mbox{left},\mbox{right},\mbox{jump},\mbox{speed} \rbrace$. For both DAgger and \acro~, we use
+a Linear Support Vector Machine (SVM) as the policy representation, with the regularization on the slack variable given
+by $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert. We initialized
+both Dagger and \acro~with two expert demonstrations for each level. For the optimization of Eq. \ref{eq:dual_sup} in
+\acro~, we used an exponenital kernel with a bandwidth of $c=0.01$ and $\nu = 0.95$ to account for a $95\%$ quantile.
 
@@
 
-\caption{We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.
-Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties.
-We compare performance of our method and DAgger.
-In Fig.
-\ref{fig:mario_results}, we report the performance of distance traveled vs.
-the number of labels provided by the supervisor.
-Initial results, averaged over 20 levels, suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.
-\todo{I think these results are promising but want to make clear they are very preliminary and want to run more experiments on Mario and the self driving car to ensure that we can actually do this reliable.
-Also, the jaggedness is concerning and needs to be looked in to, my intuition is telling me that Mario is just a very chaotic environment though.
-I am going to average over more levels to see if it improves}}
+\caption{We compare performance in terms of average distance traveled by Mario per stage before dying, running out of
+time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the
+stage.  Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps,
+except with fewer enemies and gaps than stages of harder difficulties. We compare performance of our method and DAgger.
+In Fig. \ref{fig:mario_results}, we report the performance of distance traveled vs. the number of labels provided by the
+supervisor. Initial results, averaged over 20 levels, suggest \acro~ was able to reach DAgger's peak performance of a
+distance around 2200 with only 1200 labels, while DAgger required 2800. {\color{blue} [-- very preliminary --]}}
 \label{fig:mario_results}
@@
 
-We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.
-Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties.
-We compare performance of our method and DAgger.
-In Fig.
-\ref{fig:mario_results}, we report the performance of distance traveled vs.
-the amount of time a level was tried.
-Initial results, averaged over 20 levels,  suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.
-
-\subsection{Other Experiment}
-\todo{Florian and I are discussing different ideas for this one, maybe a controller for an arm or something along the lines of learning to grasp in clutter}
+\subsection{Other Experiments}
+{\color{blue} [-- maybe a controller for a robot arm --]}
 

### 2015-08-08 paper.tex
added car experiments

--- 2015-07-30 paper.tex
@@
 
-\title{\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies from Demonstrations }
+\title{\LARGE \bf \acro: Reducing Supervision in DAgger using SVM-based Risk }
 
@@
 \begin{abstract}
-For robot control problems where no reward function is known and the dynamics of the environment are not specified, the
+For robot control problems where the reward function  and the dynamics of the environment are not specified, the
 learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
@@
 states used for training the current policy. Since learning a quantile function for high-dimensional input data is
-challenging, we instead modify an SVN-based approach to quantile estimation that employs regularization to solve this
+challenging, we instead modify an SVM-based approach to quantile estimation that employs regularization to solve this
 problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
@@
 underlying cost function describing the task, traditional model based control approaches are often not applicable. In
-these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching the robot how to
+these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching a robot how to
 accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.
@@
 
-The optimization problem in Eq. \ref{eq:LFD_obj} is typically non-convex and difficult to solve since we only have
-access to samples from the supervisor's policy $\tilde{\pi}$ arising from the demonstration trajectories $\mathcal{D}$.
+The optimization problem in Eq.
+\ref{eq:LFD_obj} is  typically non-convex.
+It can also be difficult to solve, since we only have access to samples from the supervisor's policy $\tilde{\pi}$ arising from the demonstration trajectories $\mathcal{D}$.
 To address these issues Stephane and Ross proposed an iterative method known as DAgger \cite{ross2010reduction}.
@@
 rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined
-threshold $\gamma$. {\color{blue} [-- F: Also talk about $\beta_i$ weights in DAgger --]}.
+threshold $\gamma$ \footnote{In the orginal DAgger the policy rolled out was stochastically mixed with the expert, thus with probability $\beta$ it would either take the expert's action or the robots.
+The use of this stochasitically mix policy was for theoretical analysis.
+In practice, it is recommended to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}
 
@@
 
-\subsection{The \acro~algorithm}
+\subsection{SHIV: SVM-Based Reduction in Human Intervention}
 
@@
 Furthermore, instead of labeling every state now the supervisor is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.
-These states are then added to the dataset $\mathcal{D}_{k+1}$ and the algorithm goes back to Step 1.
-
-An implicit trade off exists between what how much of the distribution is contained in the selected level set and the amount of exploration the robot is allowed.
-If the level set is large the robot will be allowed to explore in this region and potentially make more mistakes with respect to the expert, but learn faster.
-If the level set contains a smaller fraction of data, then the expert will be in control more and the robot will learn at a slower rate.
-
-\section{Theoretical Analysis}
-{\color{blue} [-- TEXT FROM HERE IS STILL ROUGH AND CHANGING --]}
-\subsection{Convergence Rate}
-\todo{These are ideas still in progress}
-The convergence rate of DAgger is dependent on the probability of the expert taking over at each iteration $\beta_i$ \cite{ross2010reduction}.
-For SHEATH, this corresponds to the probability of leaving the support or $p(g(\mathbf{x}) = -1|\pi_{\theta_i})$ .
-The intuition is that the larger the level set parameter $\nu$ is the lower the probability of leaving is and thus faster convergence rate, but potentially less safe exploration.
-Not sure if a formal proof is going to be possible though with assuming known dynamics, still looking into it.
-However, we can experimentally demonstrate this.
+These states are then added to the dataset $\mathcal{D}_{k}$
 
@@
 A common benchmark in RL is a car driving around a track avoiding other cars \cite{argall2009survey}.
-In our driving simulator, the car must stay on a rectangular track and dodge the orange cars that are on the track as well.
+In our driving simulator, the car must stay on the road of polygonal track.
 If the car falls off the track, it is placed back on to the center.
+We sample the polygonal track by sampling points from a Gaussian with a mean that is the centered of the video game work space.
+The convex hull of the sampled points is then computed.
 The car's control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
@@
 We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV.
-For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.
+For both DAgger and SHIV, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.
 For the optimization of Eq.
-\ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
+\ref{eq:dual_sup} in SHIV we used a radial basis function as well for the kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
 
-We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track, versus the number of queries made to the supervisor.
-Initial results averaged over 1 level shown in Fig.
-suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
+We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
+In Fig.
+\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV only using only the traditional One-Class SVM without the modification.
+Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
+\ref{fig:car_cost} suggest an $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
 
@@
 The car is meant to drive around a rectangular track and dodge other cars.
-The supervisor drives around the track for 3 iterations and HOG features are extracted from the images.
-}
+The supervisor drives around the track for 3 iterations and HOG features are extracted from the images.}
 
@@
 \centering
-\includegraphics[width=8cm, height=6cm]{figures/dagger_sheath_no_cars.png}
-\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of times the car left the track and the number of times the car collided with the other cars on the track.
-Initial results averaged over 1 level shown suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
-\todo{Run this over many trials}  }
+\includegraphics[width=8cm, height=6cm]{figures/dagger_shiv_one_class.eps}
+\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the number of times the car left the track.
+Initial results averaged over 30$\%$ level shown suggest an $70\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
+}
 

### 2015-08-08 paper.tex
Updates from ShareLaTeX

--- 2015-07-30 paper.tex
@@
 
-\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Ken Goldberg$^2$% <-this % stops a space
+\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan, Ken Goldberg$^2$% <-this % stops a space
 \thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny\}@berkeley.edu}}%
@@
 into account. Since learning a quantile function for high-dimensional input data is
-challenging, we instead modify an SVN-based approach to quantile estimation that employs regularization to solve this
+challenging, we instead modify an SVM-based approach to quantile estimation that employs regularization to solve this
 problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a

### 2015-08-09 paper.tex
added bullet points

--- 2015-08-08 paper.tex
@@
 
-\title{\LARGE \bf \acro: Reducing Supervision in DAgger using SVM-based Risk }
+\newboolean{include-notes}
+\setboolean{include-notes}{true}
+\newcommand{\adnote}[1]{\ifthenelse{\boolean{include-notes}}%
+ {\textcolor{green}{\textbf{AD: #1}}}{}}
 
-\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Ken Goldberg$^2$% <-this % stops a space
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny\}@berkeley.edu}}%
+\title{Iterative Imitation Learning with Reduced Human Supervision}
+
+\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^2$% <-this % stops a space
+\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny, anca\}@berkeley.edu}}%
 \thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
@@
 \begin{abstract}
+In traditional Imitation Learning, a human expert provides a few demonstrations to the robot, which then extrapolates these examples to new situations.
+One challenge is that during execution, any small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
+Iterative imitation learning algorithms such as DAgger \cite{}\adnote{cite} address this by iteratively executing a trained policy, and asking the expert for examples along the visited states, which are then aggregated with the previous training data.
+However, such algorithms rely much more heavily on extensive human supervision.
+
+Our goal is to reduce the amount of human supervision required in imitation learning, without harming performance, thus bridging traditional and iterative imitation learning.
+\emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}
+
+We introduce a method for iterative imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
+Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher succhess rates for the same number of queries to the expert.
+
+%A trained policy can have a high risk of predicting the wrong action for a state for two reasons: 1) the state is too far away from the training states, and 2) the state is in an area in which the learner has historically struggled.
+We introduce a method for iterative imitation learning that estimates regions of high risk based on these two criteria, and limits queries to the supervisor to only high risk states.
+Our method instantiates stream based active learning, with a query selection strategy that generalizes novelty detection to querying in areas that are inherently difficult to correctly label.
+
+\adnote{Old abstract:}
+
 For robot control problems where the reward function  and the dynamics of the environment are not specified, the
@@
 
-In prior work, Judah et al. proposed applying active learning techniques to only query the supervisor for states that are likely to be
-visited under the current policy and are likely to be mis-predicted under the current policy
+In prior work, Judah et al. proposed applying active learning techniques to improve the learninng ability of an algorithm given a fixed budget. 
 \cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
 density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
-approach is based on `query by committee', and considers only non-kernelized linear classifiers to represent the
-learned policy~\cite{gilad2005query}, thus restricting the class of policies which can be modelled with the approach.
+at each iteration only one labeled state was given. Thus, the robot could potentially be required to try out many more iterations of learning in order to successfully accomplished the task.
+
+\begin{enumerate}
+\item Our work is different than traditional pool base active learning for two reasons 1) the data comes in as a stream (i.e.
+we decided whether to label or not label the sample vs.
+using a pool base methods) 2) the estimator being trained is part of the parametrization of the distribution of states being encountered at run time, thus violating the i.i.d assumption common in these methods.
+\item Some techniques that can handle these approaches are 1) uncertainty sampling , or measuring some confidence level in a classifier and deciding whether to label or not.
+2) Query by committee, which involves sampling a committee of hypothesises from a version space of consistent classifiers 3) Density weighted model, which fitting a density to the unlabeled pool and then using a technique such as uncertainty sampling or query by committee to chose the label with the highest uncertainity times the density under the model.
+The reason for density weighted model is because the previous approaches are prone to labeling outliers \cite{settles2008analysis}.
+\item Our approach can be considered a query selective strategy that uses the ideas of density weighted models.
+The level set estimation of the One Class SVM is a binary decision metric of how close a point is to the global support points that define its neighbors.
+Then our hole punching technique places a "prior" on points that are likely to be misclassified condition on the fact that points nearby are misclassified.
+Thus, encapsulating both a notion of uncertainity and distance to relative points.
+\item One point that I've been thinking about is that traditional active learning is about training an estimator on some fix distribution and then trying to predict how the estimator will change given new points sampled from the same distribution.
+Thus most approaches work on the estimator themselves (query by committee sampling different hypotheses or uncertainty sampling measuring confidence).
+This assumption is violated in DAgger because you are sampling from a new distribution each iteration different from what is trained on.
+Thus, a confidence threshold such as (distance to hyperplane for an svm) would be misleading because if the point was drawn from a different distribution it could be very far from the hyperplane, but have a different label than that side of the hyperplane.
+Thus, we purpose not looking at the estimator but at the data itself.
+We make an assumption that points close to other points in our feature space will have similar labels, but the outliers are unknown and will need new labels.
+I suggest we run a uncertainty sampling technique vs.
+SHIV to verify all this.
+
+\end{enumerate}
 
@@
 \includegraphics[width=8cm, height=6cm]{figures/dagger_shiv_one_class.eps}
-\caption{ We compare performance in terms of optimization of the underlying cost function $c(\bx,\bu)$, which is the number of times the car left the track.
-Initial results averaged over 30$\%$ level shown suggest an $70\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
-}
-
+\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
+In Fig.
+\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV only using only the traditional One-Class SVM without the modification.
+Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
+\ref{fig:car_cost} suggest an $70\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
 \vspace*{-10pt}

### 2015-08-12 paper.tex
Anca's comments

@@
 
+\renewcommand{\baselinestretch}{.99}
+
 \title{Iterative Imitation Learning with Reduced Human Supervision}
@@
 \begin{abstract}
-In traditional Imitation Learning, a human expert provides a few demonstrations to the robot, which then extrapolates these examples to new situations.
-One challenge is that during execution, any small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
-Iterative imitation learning algorithms such as DAgger \cite{}\adnote{cite} address this by iteratively executing a trained policy, and asking the expert for examples along the visited states, which are then aggregated with the previous training data.
-However, such algorithms rely much more heavily on extensive human supervision.
+In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then offline learns a policy to extrapolate these examples to new situations.
+One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
 
-Our goal is to reduce the amount of human supervision required in imitation learning, without harming performance, thus bridging traditional and iterative imitation learning.
+Online imitation learning algorithms such as DAgger address this by iteratively executing a trained policy, and asking the expert for examples along the states visted by that policy.
+These new examples are then aggregated with the previous training data.
+Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.
+
+Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance, thus combining the benefits of both online and offline imitation learning approaches.
 \emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}
 
-We introduce a method for iterative imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
-Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher succhess rates for the same number of queries to the expert.
+We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
+Our algorithm, SHIV (\adnote{spell it out}), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise.
+Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher success rates for the same number of queries to the expert.
 
@@
 
-\adnote{Old abstract:}
+% \adnote{Old abstract:}
 
-For robot control problems where the reward function  and the dynamics of the environment are not specified, the
-learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
-demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
-the problem of determining a policy as an iterative supervised learning problem which alternates between executing a
-trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. In this
-work, we propose a novel algorithm, \acro~which is based on DAgger and which estimates the riskiness of states
-encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
-states used for training the current policy. Since learning a quantile function for high-dimensional input data is
-challenging, we instead modify an SVM-based approach to quantile estimation that employs regularization to solve this
-problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
-user-defined quantile super-levelset is encountered. Our approach furthermore reduces the amount of neccessary
-supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
-In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
-DAgger, our approach results in similar performance levels as DAgger while reducing the amount of required supervisor
-control inputs by more than {\color{blue}[-- TODO --]} percent.
+% For robot control problems where the reward function  and the dynamics of the environment are not specified, the
+% learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
+% demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
+% the problem of determining a policy as an iterative supervised learning problem which alternates between executing a
+% trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. In this
+% work, we propose a novel algorithm, \acro~which is based on DAgger and which estimates the riskiness of states
+% encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
+% states used for training the current policy. Since learning a quantile function for high-dimensional input data is
+% challenging, we instead modify an SVM-based approach to quantile estimation that employs regularization to solve this
+% problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
+% user-defined quantile super-levelset is encountered. Our approach furthermore reduces the amount of neccessary
+% supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
+% In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
+% DAgger, our approach results in similar performance levels as DAgger while reducing the amount of required supervisor
+% control inputs by more than {\color{blue}[-- TODO --]} percent.
  \end{abstract}
@@
 \section{Introduction}
+
+We focus on \emph{model-free imitation learning} problems.
+In this problem domain, the robot learns a task, such as grasping an object while pushing clutter out of the way \adnote{we need to put this in fig 1 and refer to it here}, from \emph{examples} provided by a human \emph{expert}.
+The robot does not have direct access to a reward function that describes the task, nor to a dynamics model informing it how its actions will affect the world.
+
+Thus, instead of planning for the task, the robot directly learns a \emph{policy}, mapping states (or in some cases observations) to actions.
+It does this based on examples, which are state-action pairs performed by the expert while demonstrating the task.
+See section 4.1 of \cite{} \adnote{cite Argall LfD survey} for more details.
+
+Traditional approaches work \emph{offline}, passively receiving examples from the expert first, and then approximating a state-action mapping in a second phase.
+One challenge that these approaches face is that when the robot is executing its trained policy, its actions affect the resulting next state, meaning the visited states are not independent random variables.
+The practical consequence is that small but often inevitable differences from the supervisor's policy cause the sequence of visited states to drift far from the region of space where the robot has seen training examples, leading to poor performance.
+
+For example, when training an autonomous car to drive on the highway, the car will deviate form the middle of the road and will not be able to recover, because all the trainign examples are from the middle of the road \cite{pomerleau1989alvinn}.
+Theoretically, the number of mistakes made by the robot in such cases may not scale just linearly, but \emph{quadratically} with the time horizon of the task \cite{} \adnote{cite ross first paper}.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
+\caption{ 
+Given a set of states corresponding to images of a race-track simulation (visualized in $\mathbb{R}^2$) with expert
+control inputs, we consider a quantile super levelset estimate (shaded) as an approximation of the riskiness of
+executing the trained policy at a given state. By varying the quantile threshold, we can increase or decrease the size
+of the quantile super-levelset area. In our approach, points outside the super-levelset are considered risky and, during
+training, roll-outs of the policy that leave the super-levelset require control demonstrations from the supervisor,
+while roll-outs within the super-levelset can be performed autonomously. \adnote{figure and caption need work}
+}
+\vspace*{-10pt}
+\label{fig:dis_traveled}
+\end{figure}
+
+\emph{Online} imitation learning approaches address this by iteratively gathering more examples form the expert \cite{}\adnote{cite Dagger and precusors or follow ups that fit this, e.g.
+the previous paper form ross}.
+DAgger is such an algorithm, and works by training a policy on existing examples, but then ``rolling it out'' (execute it) to see what states are likely to occur under this new policy.
+The expert then provides examples in the new states, correcting the robot's policy, and these examples are aggregated with the previous ones in a training set for the next iteration.
+
+With such algorithms, the number of mistakes has indeed been proven to scale only linearly with the time horizon, as opposed to quadratically \cite{}.
+DAgger and related algorithms have seen a wide range of applications, from quadrotor flight to natural languge to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
+
+On the other hand, online algorithms also place significantly more burden on the expert.
+DAgger requires the expert to manually provide controls or actions that the robot should have taken for each and every state it visits when rolling out the current best policy estimate.
+
+Our goal is to reduce the burden on the expert without harming performance, by more carefully selecting when to ask for examples:
+\begin{quote}
+\emph{The robot should not bother the human expert when its policy has low risk of error. Instead, it should only ask for new examples in regions of high risk.}
+\end{quote}
+
+\adnote{talk about how we define risk}
+
+\adnote{list contributions: }
+
+\adnote{1. an online active imitation learning algorithm that actively decided whether to query the expert or not; we generalize novelty detection, and talk about relation to active learning}
+
+\adnote{2. a theoretical analysis?}
+
+\adnote{3. an experiment in two parts: an indepth analysis on a simple domain, and a comparison to state of the art in a complex nonprehensile manipulation domain}
+
+\adnote{loop back to beginning, we enable the robot to be actively decide when to ask for examples, reducing expert burden}
+
+\adnote{Old intro:}
+
 Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
@@
 these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching a robot how to
-accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.
+accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.\adnote{these are very random things to cite for LfD, FYI - there is a survey by Argall that usually gets cited}
 
@@
 through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
-\caption{ 
-Given a set of states corresponding to images of a race-track simulation (visualized in $\mathbb{R}^2$) with expert
-control inputs, we consider a quantile super levelset estimate (shaded) as an approximation of the riskiness of
-executing the trained policy at a given state. By varying the quantile threshold, we can increase or decrease the size
-of the quantile super-levelset area. In our approach, points outside the super-levelset are considered risky and, during
-training, roll-outs of the policy that leave the super-levelset require control demonstrations from the supervisor,
-while roll-outs within the super-levelset can be performed autonomously.
-}
-\vspace*{-10pt}
-\label{fig:dis_traveled}
-\end{figure}
 
@@
 \section{Related Work}
+\adnote{Should eliminate this section and bring in the important bits in the intro and in the description of the method.
+For things that belog in the intro, this is a restatement and takes up space.
+For things that pertain to our method, this is too early and thus hard to explain yet.
+As a result, the related work section is kind of useless as a section, although much of the content in it can be very useful in other parts of the paper.}
+
 The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics

### 2015-08-12 paper.tex
updated experiments

@@
 training, roll-outs of the policy that leave the super-levelset require control demonstrations from the supervisor,
-while roll-outs within the super-levelset can be performed autonomously. \adnote{figure and caption need work}
+while roll-outs within the super-levelset can be performed autonomously. 
 }
@@
 With such algorithms, the number of mistakes has indeed been proven to scale only linearly with the time horizon, as opposed to quadratically \cite{}.
-DAgger and related algorithms have seen a wide range of applications, from quadrotor flight to natural languge to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
+DAgger and related algorithms have seen a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
 
@@
 \subsection{Driving Example}
-A common benchmark in RL is a car driving around a track avoiding other cars \cite{argall2009survey}.
-In our driving simulator, the car must stay on the road of polygonal track.
-If the car falls off the track, it is placed back on to the center.
-We sample the polygonal track by sampling points from a Gaussian with a mean that is the centered of the video game work space.
+A common benchmark in Reinforcement Learning  is a car driving around a track avoiding other cars \cite{argall2009survey}.
+To illustrate our methods ability in high dimensions, the car must follow a polygonal track using only HOG features extracted from images.
+If the car falls off the track, it is placed back on the center facing the angle of the polygonal track piece.
+We sample the polygonal track by drawing points from a Gaussian with a mean that is the centered of the video game work space.
 The convex hull of the sampled points is then computed.
@@
 We have the supervisor drive around the track 2 times and then collect the raw images observed.
-We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV.
+We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV,  where the size of $\bx$ is $27926$.
 For both DAgger and SHIV, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.
@@
 
+To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
+The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
+We measured the performance of our modified One Class SVM to the confidence measure, in terms of how many states are estimated to be of low risk (i.e.
+correctly classified) and are of actually high risk on the first policy roll out.
+Results  are averaged over 50 tracks and shown in Table \ref{table:active_comp}.
+
 We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
 In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV only using only the traditional One-Class SVM without the modification.
+\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV using only the traditional One-Class SVM without the modification.
 Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
-\ref{fig:car_cost} suggest an $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+\ref{fig:car_cost} suggest a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{ R{4cm}||R{1.65cm}|R{1.65cm}|R{1.65cm}  }
+ %\hline
+ %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
+ %\hline 
+ & \multicolumn{1}{c}{Mis-Prediction Error} \\
+ \hline
+ Risk Sensitive One Class SVM &  $16 \pm 2\%$\\
+Estimated Confidence & $59 \pm 3\%$\\
+ %\hline
+\end{tabular}
+   \caption { \footnotesize  To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
+The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
+We measured the performance of our modified One Class SVM to the confidence measure, in terms of how many states are estimated to be of low risk (i.e.
+correctly classified) and are of actually high risk on the first policy roll out.
+Results  are averaged over 50 randomly generated tracks.
+   }
+		\tablabel{opt-p-comparison}
+\label{table:active_comp}
+\end{table}
 
@@
 \centering
-\includegraphics[width=6cm, height=6cm]{figures/race_car_track_example.png}
-\caption{ An example image from the racing simulator.
-The car is meant to drive around a rectangular track and dodge other cars.
-The supervisor drives around the track for 3 iterations and HOG features are extracted from the images.}
+\includegraphics[width=8cm, height=6cm]{figures/race_car.png}
+\caption{ An example image from the racing simulator of a sampled polygonal track..
+The car is meant to drive around an not fall off.
+It is placed back on the center if it does fall off.
+The supervisor drives around the track for 2 iterations and HOG features are extracted from the images to form a feature space of }
 
@@
 In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV only using only the traditional One-Class SVM without the modification.
+\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV using only the traditional One-Class SVM without the modification.
 Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
@@
 
-\subsection{Super Mario Bros}
-Super Mario Bros.
-is a platform video game where the character, Mario, must move across each stage by avoiding being hit by enemies and falling into gaps, and before running out of time.
-We used the simulator from a recent Mario Bros.
-AI competition which can randomly generate stages of varying difficulty (more difficult gaps and types of enemies) \cite{marioAI}.
-Our goal is to train the computer to play the game based on current game features as input.
-Our expert is a near optimal $A^*$ search algorithm that plans ahead using the game simulator.
-An action consists of 4 binary variables indicating which subset of buttons we should press in $\lbrace \mbox{left},\mbox{right},\mbox{jump},\mbox{speed} \rbrace$.
-For both DAgger and SHEATH, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $C\gamma=0.01$, which was set via cross validation on the initial training examples from our expert..
-We initialized both Dagger and SHEATH with two expert demonstrations for each level.
-For the optimization of Eq.
-\ref{eq:dual_sup} in SHEATH we used a radial basis function as well for the kernel with a bandwidth of $c=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
+\subsection{Grasping In Clutter}
+To illustrate how our technique can be used in the continuous case and with a human demonstrator. 
+We look at having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
+We used Box2D a physics simulator to model the virtual world.
+The arm, shown in Fig.
+\ref{fig:box2d_arm}, consists of 3 degrees of freedom and has a parallel jaw gripper.
+For input the human demonstrator provides controls through an XBox controller.
+The left and right joystick determined the x and y velocity of the center of the end effector.
+The left bumper of the controller provided a binary input for opening and closing the gripper.
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width = 6cm ]{figures/mario.png}
-\caption{ An example image from the Mario AI simulator. Mario faces many challenges to reach an end of a level, such as gaps, jumps and enemies.  }
+\todo{double check this section with Sammy}
+Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and scaler value in the range $[0,1]$ that measured the position of the gripper, 1 being opened and zero being closed.
+For our representation of $\pi_{\theta}$, we used linear ridge regression.
+We defined two cost functions, $C(\bx,\bu)$, as the sum of the number of objects knocked off the table and 1 for not successfully grasping the target object.
 
-\vspace*{-10pt}
-\label{fig:dis_traveled}
-\end{figure}
+In experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out.
+At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $5\%$ of the width of the table.
 
-\begin{figure}[ht]
-\centering
+In Figure , we show both the cost function associated with knocking an object off the table and the one associated with being able to successfully grasp an object or not.
+\todo{Finalize results then discuss them}
 
-\includegraphics[width=8cm, height = 4.5cm]{figures/dagger_sheath_mario.eps}
-
-\caption{We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.
-Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties.
-We compare performance of our method and DAgger.
-In Fig.
-\ref{fig:mario_results}, we report the performance of distance traveled vs.
-the number of labels provided by the supervisor.
-Initial results, averaged over 20 levels, suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.
-\todo{I think these results are promising but want to make clear they are very preliminary and want to run more experiments on Mario and the self driving car to ensure that we can actually do this reliable.
-Also, the jaggedness is concerning and needs to be looked in to, my intuition is telling me that Mario is just a very chaotic environment though.
-I am going to average over more levels to see if it improves}}
-\label{fig:mario_results}
-\end{figure}
-
-We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.
-Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties.
-We compare performance of our method and DAgger.
-In Fig.
-\ref{fig:mario_results}, we report the performance of distance traveled vs.
-the amount of time a level was tried.
-Initial results, averaged over 20 levels,  suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.
-
-\subsection{Other Experiment}
-\todo{Florian and I are discussing different ideas for this one, maybe a controller for an arm or something along the lines of learning to grasp in clutter}
+\subsection{Surigcal Experiment}
 

### 2015-08-12 paper.tex
updated experiments

@@
 \centering
-\includegraphics[width=8cm, height=6cm]{figures/race_car.png}
+\includegraphics[width=6cm, height=6cm]{figures/race_car.png}
 \caption{ An example image from the racing simulator of a sampled polygonal track..
@@
 \todo{double check this section with Sammy}
-Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and scaler value in the range $[0,1]$ that measured the position of the gripper, 1 being opened and zero being closed.
+Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, 1 being opened and zero being closed.
 For our representation of $\pi_{\theta}$, we used linear ridge regression.
@@
 
+\begin{figure}[t!]
+\centering
+\includegraphics[width=6cm, height=6cm]{figures/box2D_arm.png}
+\caption{  The arm, modeled with Box2D, consists of 3 degrees of freedom and has a parallel jaw gripper.
+For input the human demonstrator provides controls through an XBox controller.
+The left and right joystick determined the x and y velocity of the center of the end effector.
+The left bumper of the controller provided a binary input for opening and closing the gripper.
+Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, 1 being opened and zero being closed.
+}
+
+\vspace*{-10pt}
+\label{fig:box2D_arm.png}
+\end{figure}
+
 \subsection{Surigcal Experiment}

### 2015-08-18 paper.tex
added to related work

@@
 
-\title{Iterative Imitation Learning with Reduced Human Supervision}
+%\title{Iterative Imitation Learning with Reduced Human Supervision [v11]}
+%\title{SHIV:  Reducing Human Supervision for Robot Active Learning [v11]}
 
-\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^2$% <-this % stops a space
+\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations}
+
+\author{Michael Laskey$^1$, Sam Staszak, Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^2$% <-this % stops a space
 \thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny, anca\}@berkeley.edu}}%
@@
 \begin{abstract}
-In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then offline learns a policy to extrapolate these examples to new situations.
+The SHIV algorithm proposes an alternative to previous query selection methods for stream-based active learning to the non-stationary distributions encountered in robot control.
+To reduce operator burden, the Svm-based reduction in Human InterVention (SHIV) algorithm only requests supervision for sufficiently risky or novel states.
+
+In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
 One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
 
-Online imitation learning algorithms such as DAgger address this by iteratively executing a trained policy, and asking the expert for examples along the states visted by that policy.
-These new examples are then aggregated with the previous training data.
+\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the expert for additional examples along the states visited by that policy.
 Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.
 
-Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance, thus combining the benefits of both online and offline imitation learning approaches.
+Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance.
 \emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}
@@
 We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
-Our algorithm, SHIV (\adnote{spell it out}), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise.
+Our algorithm, SHIV (SVM-Based Reduction in Human Intervention), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise.
 Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher success rates for the same number of queries to the expert.
@@
 
-Thus, instead of planning for the task, the robot directly learns a \emph{policy}, mapping states (or in some cases observations) to actions.
-It does this based on examples, which are state-action pairs performed by the expert while demonstrating the task.
-See section 4.1 of \cite{} \adnote{cite Argall LfD survey} for more details.
+Thus, to achieve the task, the robot directly learns a \emph{policy}, mapping states (or in some cases observations) to actions, which eliminates the need for a reward or a model.
+It does this based on examples, which are state-action pairs performed by the expert while demonstrating the task (see section 4.1 of \cite{argall2009survey}  for more details).
 
 Traditional approaches work \emph{offline}, passively receiving examples from the expert first, and then approximating a state-action mapping in a second phase.
-One challenge that these approaches face is that when the robot is executing its trained policy, its actions affect the resulting next state, meaning the visited states are not independent random variables.
+One challenge that these approaches face is that when the robot is executing its trained policy, its actions affect the resulting next state.
+That makes the visited states not independent random variables.
 The practical consequence is that small but often inevitable differences from the supervisor's policy cause the sequence of visited states to drift far from the region of space where the robot has seen training examples, leading to poor performance.
 
-For example, when training an autonomous car to drive on the highway, the car will deviate form the middle of the road and will not be able to recover, because all the trainign examples are from the middle of the road \cite{pomerleau1989alvinn}.
-Theoretically, the number of mistakes made by the robot in such cases may not scale just linearly, but \emph{quadratically} with the time horizon of the task \cite{} \adnote{cite ross first paper}.
+For example, when training an autonomous car to drive on the highway, the car will deviate form the middle of the road and will not be able to recover, because all the training examples are from the middle of the road \cite{pomerleau1989alvinn}.
+Theoretically, the number of mistakes made by the robot in such cases may not scale just linearly, but \emph{quadratically} with the time horizon of the task \cite{ross2010efficient}.
 
@@
 
-\emph{Online} imitation learning approaches address this by iteratively gathering more examples form the expert \cite{}\adnote{cite Dagger and precusors or follow ups that fit this, e.g.
-the previous paper form ross}.
+\emph{Online} imitation learning approaches address this by iteratively gathering more examples form the expert \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
 DAgger is such an algorithm, and works by training a policy on existing examples, but then ``rolling it out'' (execute it) to see what states are likely to occur under this new policy.
@@
 
-With such algorithms, the number of mistakes has indeed been proven to scale only linearly with the time horizon, as opposed to quadratically \cite{}.
+With such algorithms, the number of mistakes has indeed been proven to scale only linearly with the time horizon, as opposed to quadratically \cite{ross2010efficient}.
 DAgger and related algorithms have seen a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
@@
 
-\adnote{talk about how we define risk}
+States can have high risk for two complementary reasons: (1) they are far from the training examples --- this type of risk is studied under novelty or outlier detection \cite{hodge2004survey}; or (2) they lie in a region that has proven to be difficult to correctly label in the past, despite there being training data in that region.
 
-\adnote{list contributions: }
+Our main contribution is integrating this notion of risk into online imitation learning.
+We introduce SHIV (), which builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to evaluate this risk.
 
-\adnote{1. an online active imitation learning algorithm that actively decided whether to query the expert or not; we generalize novelty detection, and talk about relation to active learning}
+We analyze our algorithm on a car track example, studying the risk evaluation method along with its robustness to the selection of a threshold for how risk adverse the robot should be.
+We also compare it with state of the art online imitation learning on a more complex task of nonprehensile grasping in clutter.
+Our results suggest that SHIV learns policies with higher success rates for the same budget of expert examples.
 
-\adnote{2. a theoretical analysis?}
+Overall, our work enables robots to actively decide when to ask for examples during online imitation learning, reducing the burden on the user and paving the way towards more effective human-robot interactions.
 
-\adnote{3. an experiment in two parts: an indepth analysis on a simple domain, and a comparison to state of the art in a complex nonprehensile manipulation domain}
+% \adnote{Old intro:}
 
-\adnote{loop back to beginning, we enable the robot to be actively decide when to ask for examples, reducing expert burden}
+% Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
+% against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
+% underlying cost function describing the task, traditional model based control approaches are often not applicable. In
+% these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching a robot how to
+% accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.\adnote{these are very random things to cite for LfD, FYI - there is a survey by Argall that usually gets cited}
 
-\adnote{Old intro:}
+% One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
+% supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
+% while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
+% of states encountered during the execution of a policy are not independent random variables, thus making statistical
+% inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
+% time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
+% behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
+% distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
+% presenting an iterative method that first trains a policy on the data observed using standard supervised learning
+% techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
+% the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
+% and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
+% robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
+% through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
 
-Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
-against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
-underlying cost function describing the task, traditional model based control approaches are often not applicable. In
-these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching a robot how to
-accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.\adnote{these are very random things to cite for LfD, FYI - there is a survey by Argall that usually gets cited}
+% During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
+% should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
+% human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
+% reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
+% executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
+% required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
+% training data in its vicinity, which potentially means our policy will mis-predict the supervisor
+% \cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
+% nonetheless. If an accurate density estimation corresponding to
+% the pairs of visited states and control signals is available, the first scenario can be captured by regions of
+% state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
+% is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
+% model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
+% machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
+% demonstrations.
+% %
+% %Vague!!!
+% %This property can be seen used in importance sampling when data is collected from one distribution, but tested on
+% %another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
+% %
+% While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
+% space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
+% representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
+% SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
+% \cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
+% image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
+% estimate where the local policy estimate is inconsistent with the expert demonstrations.
 
-One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
-supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
-while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
-of states encountered during the execution of a policy are not independent random variables, thus making statistical
-inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
-time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
-behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
-distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
-presenting an iterative method that first trains a policy on the data observed using standard supervised learning
-techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
-the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
-and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
-robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
-through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
+% To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
+% where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
+% and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
+% inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
+% able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
+% analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
+% the Markovian assumption).
 
-During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
-should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
-human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
-reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
-executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
-required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
-training data in its vicinity, which potentially means our policy will mis-predict the supervisor
-\cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
-nonetheless. If an accurate density estimation corresponding to
-the pairs of visited states and control signals is available, the first scenario can be captured by regions of
-state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
-is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
-model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
-machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
-demonstrations.
-%
-%Vague!!!
-%This property can be seen used in importance sampling when data is collected from one distribution, but tested on
-%another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
-%
-While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
-space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
-representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
-SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
-\cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
-image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
-estimate where the local policy estimate is inconsistent with the expert demonstrations.
-
-To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
-where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
-and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
-inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
-able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
-analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
-the Markovian assumption).
-
-Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
-demonstrations and reduces supervisor
-burdon by asking for supervisor demonstrations only in `risky' states. 
-We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
-of the distribution of states with demonstrations and additionally
-and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
-risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
-peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
-averaged over 20 levels.
-{\color{blue}[-- FINALIZE --]}
+% Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
+% demonstrations and reduces supervisor
+% burdon by asking for supervisor demonstrations only in `risky' states. 
+% We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
+% of the distribution of states with demonstrations and additionally
+% and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
+% risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
+% peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
+% averaged over 20 levels.
+% {\color{blue}[-- FINALIZE --]}
 
 \section{Related Work}
-\adnote{Should eliminate this section and bring in the important bits in the intro and in the description of the method.
-For things that belog in the intro, this is a restatement and takes up space.
-For things that pertain to our method, this is too early and thus hard to explain yet.
-As a result, the related work section is kind of useless as a section, although much of the content in it can be very useful in other parts of the paper.}
 
-The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
-\cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
-to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
-neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
-robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
-to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
-configurations of the~\cite{schulman2013case}.
+Work related to ours can be grouped in two categories: work related to the active learning aspect, and work related to the risk evaluation aspect.
 
-A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
-the robot and the environment are not known and that no access to a cost function describing a given task is available.
-Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
-problem can be treated as a supervised learning problem that determines a function from state space to
-controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
-associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
-travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
-not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
-demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
-rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
-stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
-robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.
+\noindent\textbf{Active Imitation Learning.}
+SHIV instantiates \emph{stream-based} active learning ~\cite{atlas1990training,cohn1994improving}, it receives the stream of states induced by executing the current best policy estimate, and actively decides for each state whether to query the expert or not.
 
-Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
-policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
-the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
-controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
-before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
-\cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
-(HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
-methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
-\cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
-to move sematically in a building with a training set consisting of of humans following similar verbal instructions
-\cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
-Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.
+Stream-based active learning has two ingredients: a stream, given here by the policy, and a query selection method.
+Typical query selection methods are estimator-centric: they evaluate the estimator's confidence (e.g.
+distance from the classification hyperplane \cite{tong2002support}), implicitly assuming a fixed distribution --- that the new data is sampled from the same distribution as the previous training data.
+Although such methods have been proposed for online imitation learning (see dogged learning \cite{chernova2009interactive,grollman2007dogged}),
+online imitation learning violates the fixed distribution assumption because each new policy induces a new distribution of states .
+Another way to measure confidence is query by committee, which uses a committee of hypothesis classifiers that are trained on different subset of training data and only labels points for which they disagree.
+Judah et al.
+has proposed using this approach towards online imitation learning\cite{judah2011active,judah2012active}, however it has been shown when training and test distributions are different this can perform worse than randomly selecting points \cite{burbidge2007active}.
 
-One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
-provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
-algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
-human or an algorithm with a high computational demand.
+Instead, we contribute a query selection method that is data-centric, evaluating confidence based on novelty
+and on historically mislabeled regions.
+%Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.
+Our results suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector.
 
-In prior work, Judah et al. proposed applying active learning techniques to improve the learninng ability of an algorithm given a fixed budget. 
-\cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
-density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
-at each iteration only one labeled state was given. Thus, the robot could potentially be required to try out many more iterations of learning in order to successfully accomplished the task.
+\noindent\textbf{Risk via Novelty Detection.}
+One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
+trained on \cite{tokdar2010importance}.
+Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution, making it difficult for a model to correctly predict its label.
+One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled.
+However, the amount of data needed to accurately do so scales exponentially in the number of dimensions \cite{nadaraya1964estimating}.
 
-\begin{enumerate}
-\item Our work is different than traditional pool base active learning for two reasons 1) the data comes in as a stream (i.e.
+An alternative to evaluating the probability of a data point is to measure distance to its nearest neighbors \cite{knox1998algorithms}. However, this approach was shown to be
+susceptible to outliers since nearest neighbors mostly incorporate local information about the data \cite{hodge2004survey}.
+
+Our approach is based on the One Class SVM proposed by Scholk{\"o}pf et al., which estimates a particular quantile level set for the training data by solving a convex quadratic program  to find support
+vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
+asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
+In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for novelty detection in high-dimensional 
+image data.
+
+% The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
+% \cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
+% to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
+% neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
+% robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
+% to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
+% configurations of the~\cite{schulman2013case}.
+
+% A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
+% the robot and the environment are not known and that no access to a cost function describing a given task is available.
+% Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
+% problem can be treated as a supervised learning problem that determines a function from state space to
+% controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
+% associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
+% travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
+% not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
+% demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
+% rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
+% stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
+% robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.
+
+% Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
+% policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
+% the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
+% controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
+% before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
+% \cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
+% (HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
+% methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
+% \cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
+% to move sematically in a building with a training set consisting of of humans following similar verbal instructions
+% \cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
+% Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.
+
+% One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
+% provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
+% algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
+% human or an algorithm with a high computational demand.
+
+% In prior work, Judah et al. proposed applying active learning techniques to improve the learninng ability of an algorithm given a fixed budget. 
+% \cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
+% density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
+% at each iteration only one labeled state was given. Thus, the robot could potentially be required to try out many more iterations of learning in order to successfully accomplished the task.
+
+% \begin{enumerate}
+% \item Our work is different than traditional pool base active learning for two reasons 1) the data comes in as a stream (i.e.
 we decided whether to label or not label the sample vs.
 using a pool base methods) 2) the estimator being trained is part of the parametrization of the distribution of states being encountered at run time, thus violating the i.i.d assumption common in these methods.
-\item Some techniques that can handle these approaches are 1) uncertainty sampling , or measuring some confidence level in a classifier and deciding whether to label or not.
+% \item Some techniques that can handle these approaches are 1) uncertainty sampling , or measuring some confidence level in a classifier and deciding whether to label or not.
 2) Query by committee, which involves sampling a committee of hypothesises from a version space of consistent classifiers 3) Density weighted model, which fitting a density to the unlabeled pool and then using a technique such as uncertainty sampling or query by committee to chose the label with the highest uncertainity times the density under the model.
 The reason for density weighted model is because the previous approaches are prone to labeling outliers \cite{settles2008analysis}.
-\item Our approach can be considered a query selective strategy that uses the ideas of density weighted models.
+% \item Our approach can be considered a query selective strategy that uses the ideas of density weighted models.
 The level set estimation of the One Class SVM is a binary decision metric of how close a point is to the global support points that define its neighbors.
@@
 Thus, encapsulating both a notion of uncertainity and distance to relative points.
-\item One point that I've been thinking about is that traditional active learning is about training an estimator on some fix distribution and then trying to predict how the estimator will change given new points sampled from the same distribution.
+% \item One point that I've been thinking about is that traditional active learning is about training an estimator on some fix distribution and then trying to predict how the estimator will change given new points sampled from the same distribution.
 Thus most approaches work on the estimator themselves (query by committee sampling different hypotheses or uncertainty sampling measuring confidence).
@@
 
-\end{enumerate}
+% \end{enumerate}
 
-%[Let's discuss this part]
-{\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
-an incorrect control input, we leverage a
-property in statistical machine learning that a trained model will be able to generalize within the distribution it is
-trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
-distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
-approach is to estimate the probability density of states the policy is trained on.
+% %[Let's discuss this part]
+% {\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
+% an incorrect control input, we leverage a
+% property in statistical machine learning that a trained model will be able to generalize within the distribution it is
+% trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
+% distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
+% approach is to estimate the probability density of states the policy is trained on.
 However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.
 
-Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
-to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
-neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
-susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
-\cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
-at a point was high, the point was considered as likely to be outside of the estimators domain within which
-generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
-and might require a large amount of hyperparameter tuning.
+% Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
+% to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
+% neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
+% susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
+% \cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
+% at a point was high, the point was considered as likely to be outside of the estimators domain within which
+% generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
+% and might require a large amount of hyperparameter tuning.
 
-Our approach is in particular based on the One Class SVM proposed by Scholk{\"o}pf et al. which estimates a user
-defined quantile level set for a collection of training data by solving a convex quadratic program  to find support
-vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
-asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
-In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for outlier detection of high-dimensional 
-image data.
+% Our approach is in particular based on the One Class SVM proposed by Scholk{\"o}pf et al. which estimates a user
+% defined quantile level set for a collection of training data by solving a convex quadratic program  to find support
+% vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
+% asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
+% In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for outlier detection of high-dimensional 
+% image data.
 

### 2015-08-18 paper.tex
changed arm

--- 2015-08-12 paper.tex
@@
 In experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out.
-At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $5\%$ of the width of the table.
+At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
 

### 2015-08-19 paper.tex
changed figures

@@
 \centering
-\subfigure[Kernel Density Estimation of Sampled Data]{%
-\vspace{-0.5ex}\includegraphics[width=5.5cm , height = 4.5cm]{figures/kde_gmm.eps}
-\label{fig:subfigure1}}
-\quad
-\subfigure[One Class SVM]{%
-\includegraphics[width=5.5cm, height = 4.5cm]{figures/kde_gmm_ocm.eps}
-\label{fig:subfigure2}}
-\subfigure[Risk Sensitive One Class SVM]{%
-\includegraphics[width=5.5cm, height = 4.5cm]{figures/kde_gmm_mocm.eps}
-\label{fig:subfigure3}}
+
+\includegraphics[width=16cm , height = 5cm]{figures/active_learning/Slide1.jpg}
 
@@
 
-\begin{table}[t]
+\begin{figure}[t]
 \centering
-\begin{tabular}{ R{4cm}||R{1.65cm}|R{1.65cm}|R{1.65cm}  }
- %\hline
- %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
- %\hline 
- & \multicolumn{1}{c}{Mis-Prediction Error} \\
- \hline
- Risk Sensitive One Class SVM &  $16 \pm 2\%$\\
-Estimated Confidence & $59 \pm 3\%$\\
- %\hline
-\end{tabular}
+\includegraphics[width=9cm, height=8cm]{figures/risk_bar.eps}
    \caption { \footnotesize  To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
@@
    }
-		\tablabel{opt-p-comparison}
-\label{table:active_comp}
-\end{table}
+
+\label{fig:active_comp}
+\end{figure}
 

### 2015-08-19 paper.tex
Updates from ShareLaTeX

--- 2015-08-18 paper.tex
@@
 \begin{abstract}
-The SHIV algorithm proposes an alternative to previous query selection methods for stream-based active learning to the non-stationary distributions encountered in robot control.
-To reduce operator burden, the Svm-based reduction in Human InterVention (SHIV) algorithm only requests supervision for sufficiently risky or novel states.
+Algorithms such as DAgger for robot learning from demonstrations can be very effective for problems where system dynamics and reward functions are unknown, but can impose a burden on supervisors to provide labels (control signals) as states are encountered during policy rollouts.
+To reduce this burden we introduce a new query selection method for stream-based active learning.
+The SHIV algorithm (Svm-based reduction in Human InterVention) only requests supervision for risky stater.
+To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
+We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) multi-joint robot arm grasping in clutter simulation with Box2D, and 3) surgical needle insertion.
+Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of 3x to 5x).
 
-In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
+%In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
 One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
 
-\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the expert for additional examples along the states visited by that policy.
+%\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the expert for additional examples along the states visited by that policy.
 Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.
 
-Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance.
+%Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance.
 \emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}
 
-We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
+%We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
 Our algorithm, SHIV (SVM-Based Reduction in Human Intervention), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise.
-Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher success rates for the same number of queries to the expert.
 
@@
 In experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out.
-At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
+At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $5\%$ of the width of the table.
 

### 2015-08-21 paper.tex
Anca and Ken's changes

@@
 \begin{abstract}
-Algorithms such as DAgger for robot learning from demonstrations can be very effective for problems where system dynamics and reward functions are unknown, but can impose a burden on supervisors to provide labels (control signals) as states are encountered during policy rollouts.
-To reduce this burden we introduce a new query selection method for stream-based active learning.
-The SHIV algorithm (Svm-based reduction in Human InterVention) only requests supervision for risky stater.
+Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system dynamics and reward functions are unknown.
+However, they impose a burden on supervisors to demonstrate labels (control signals) as the robot encounters new states when iteratively executing its new best policy.
+We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
+SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
 To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) multi-joint robot arm grasping in clutter simulation with Box2D, and 3) surgical needle insertion.
-Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of 3x to 5x).
+We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) 6DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
+Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of \adnote{fill in}).%[I hope more!
+- ken]
 
-%In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
+%In traditional imitation learning, a human supervisor provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
 One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
 
-%\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the expert for additional examples along the states visited by that policy.
+%\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the supervisor for additional examples along the states visited by that policy.
 Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.
@@
 
-We focus on \emph{model-free imitation learning} problems.
-In this problem domain, the robot learns a task, such as grasping an object while pushing clutter out of the way \adnote{we need to put this in fig 1 and refer to it here}, from \emph{examples} provided by a human \emph{expert}.
-The robot does not have direct access to a reward function that describes the task, nor to a dynamics model informing it how its actions will affect the world.
+In \emph{model-free} robot learning from demonstration, a robot learns to perform a task, such as driving or grasping \adnote{we need to put this in fig 1 and refer to it here}, from examples provided by a competent \emph{supervisor}, usually a human.
+The problem is model-free\adnote{no dynamics model makes it model free, no reward is independent from that; suggest: in such problems, both the ...} if both the system dynamics and the reward function are unspecified, eg.
+dynamics model may be highly non-linear or noisy and the reward function may trade-off multiple factors and/or depend on future states.
+The robot must learn a policy mapping states to actions as it explores new states \adnote{not typical of model free lfd, instead the robot must learn a policy mapping states to actions from the demonstrated examples.}\cite{argall2009survey}.
 
-Thus, to achieve the task, the robot directly learns a \emph{policy}, mapping states (or in some cases observations) to actions, which eliminates the need for a reward or a model.
-It does this based on examples, which are state-action pairs performed by the expert while demonstrating the task (see section 4.1 of \cite{argall2009survey}  for more details).
-
-Traditional approaches work \emph{offline}, passively receiving examples from the expert first, and then approximating a state-action mapping in a second phase.
-One challenge that these approaches face is that when the robot is executing its trained policy, its actions affect the resulting next state.
-That makes the visited states not independent random variables.
-The practical consequence is that small but often inevitable differences from the supervisor's policy cause the sequence of visited states to drift far from the region of space where the robot has seen training examples, leading to poor performance.
-
-For example, when training an autonomous car to drive on the highway, the car will deviate form the middle of the road and will not be able to recover, because all the training examples are from the middle of the road \cite{pomerleau1989alvinn}.
-Theoretically, the number of mistakes made by the robot in such cases may not scale just linearly, but \emph{quadratically} with the time horizon of the task \cite{ross2010efficient}.
+In the standard supervised setting, a policy is learned offline from a fixed set of examples.
+When the robot executes this policy, the sequential process can quickly evolve away from the initial set of states.
+The learned policy is not helpful in unfamiliar states, leading to robot failures (crashes or dropping objects).
+For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states on the side of the road where it has not encountered before, so its policy quickly fails \cite{pomerleau1989alvinn}.
+Theoretically, the number of mistakes made by the robot in such cases  can scale quadratically with the time horizon of the task \cite{ross2010efficient}.
 
@@
 \caption{ 
-Given a set of states corresponding to images of a race-track simulation (visualized in $\mathbb{R}^2$) with expert
-control inputs, we consider a quantile super levelset estimate (shaded) as an approximation of the riskiness of
-executing the trained policy at a given state. By varying the quantile threshold, we can increase or decrease the size
-of the quantile super-levelset area. In our approach, points outside the super-levelset are considered risky and, during
-training, roll-outs of the policy that leave the super-levelset require control demonstrations from the supervisor,
-while roll-outs within the super-levelset can be performed autonomously. 
+Conceptual illustration of robot states (projected onto the plane) with quantile levelset (shaded) for measuring the riskiness of
+executing the current policy as distance from the levelset boundary.  In SHIF, supervisor demonstrations are only requested when risky states are encountered. 
 }
@@
 
-\emph{Online} imitation learning approaches address this by iteratively gathering more examples form the expert \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
-DAgger is such an algorithm, and works by training a policy on existing examples, but then ``rolling it out'' (execute it) to see what states are likely to occur under this new policy.
-The expert then provides examples in the new states, correcting the robot's policy, and these examples are aggregated with the previous ones in a training set for the next iteration.
+\emph{On-line}\adnote{inconsistency here beetween offline and on-line instead of online} imitation learning approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+In DAgger, a series of policies are learned.
+In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for the  new stats, which are then aggregated with the previous examples for the next iteration.
+The number of mistakes in DAgger scales linearly with the time horizon \cite{ross2010efficient}.
+DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
 
-With such algorithms, the number of mistakes has indeed been proven to scale only linearly with the time horizon, as opposed to quadratically \cite{ross2010efficient}.
-DAgger and related algorithms have seen a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
+One drawback is that such online algorithms increase the burden on the supervisor.
+Our goal is to reduce supervisor burden without degrading robot performance, \emph{by only requesting demonstrations for risky states.
+}
 
-On the other hand, online algorithms also place significantly more burden on the expert.
-DAgger requires the expert to manually provide controls or actions that the robot should have taken for each and every state it visits when rolling out the current best policy estimate.
+Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that  has been historically misclassified.
+%\adnote{Ken's version below does not seem to represent what we actually do.}
+%the action associated with a state under the current policy yield a resulting state that is inconsistent with the expected next state. [how do we measure 2? - Ken]
 
-Our goal is to reduce the burden on the expert without harming performance, by more carefully selecting when to ask for examples:
-\begin{quote}
-\emph{The robot should not bother the human expert when its policy has low risk of error. Instead, it should only ask for new examples in regions of high risk.}
-\end{quote}
+We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which reduces supervisor burden by enabling the robot to only request supervision for risky states.
+SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions (like those encountered when executing a new policy at each iteration).
+It builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating}.
 
-States can have high risk for two complementary reasons: (1) they are far from the training examples --- this type of risk is studied under novelty or outlier detection \cite{hodge2004survey}; or (2) they lie in a region that has proven to be difficult to correctly label in the past, despite there being training data in that region.
-
-Our main contribution is integrating this notion of risk into online imitation learning.
-We introduce SHIV (), which builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to evaluate this risk.
-
-We analyze our algorithm on a car track example, studying the risk evaluation method along with its robustness to the selection of a threshold for how risk adverse the robot should be.
-We also compare it with state of the art online imitation learning on a more complex task of nonprehensile grasping in clutter.
-Our results suggest that SHIV learns policies with higher success rates for the same budget of expert examples.
-
-Overall, our work enables robots to actively decide when to ask for examples during online imitation learning, reducing the burden on the user and paving the way towards more effective human-robot interactions.
+We compare SHIV with DAgger in three experiments: 1) a driving simulator, 2) 6DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
+Our analysis suggests that compared to DAgger, SHIV learns a policy that performs significantly better given the same amount of human supervision.
+Conversely, SHIV significantly reduces supervisory burden (by a factor of \adnote{fill in}) while achieving the same performance.
 
@@
 % model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
-% machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
+% machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with supervisor
 % demonstrations.
@@
 % image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
-% estimate where the local policy estimate is inconsistent with the expert demonstrations.
+% estimate where the local policy estimate is inconsistent with the supervisor demonstrations.
 
@@
 \section{Related Work}
-
-Work related to ours can be grouped in two categories: work related to the active learning aspect, and work related to the risk evaluation aspect.
+\adnote{stick to either learning from demonstration or imitation learning}
+Below we summarize related work in robot\adnote{robot learnign too broad, active approaches to learning from demonstration perhaps} learning and in risk evaluation.
 
 \noindent\textbf{Active Imitation Learning.}
-SHIV instantiates \emph{stream-based} active learning ~\cite{atlas1990training,cohn1994improving}, it receives the stream of states induced by executing the current best policy estimate, and actively decides for each state whether to query the expert or not.
+SHIV instantiates \emph{stream-based} active learning ~\cite{atlas1990training,cohn1994improving}.
+It iteratively receives the stream of states induced by executing the current best policy estimate, and actively decides for each state whether to query the supervisor or not.
 
 Stream-based active learning has two ingredients: a stream, given here by the policy, and a query selection method.
-Typical query selection methods are estimator-centric: they evaluate the estimator's confidence (e.g.
-distance from the classification hyperplane \cite{tong2002support}), implicitly assuming a fixed distribution --- that the new data is sampled from the same distribution as the previous training data.
+Typical query selection methods are estimator-centric: they evaluate the estimator's confidence, e.g.
+distance from the classification hyperplane \cite{tong2002support}, implicitly assuming a stationary distribution --- that the new data is sampled from the same distribution as the previous training data.
 Although such methods have been proposed for online imitation learning (see dogged learning \cite{chernova2009interactive,grollman2007dogged}),
-online imitation learning violates the fixed distribution assumption because each new policy induces a new distribution of states .
-Another way to measure confidence is query by committee, which uses a committee of hypothesis classifiers that are trained on different subset of training data and only labels points for which they disagree.
+online imitation learning violates the stationary distribution assumption because each new policy induces a new distribution of states.
+An alternative to distance-based measures of confidence is query by committee, which uses a committee of hypothesized classifiers\adnote{don't have to be classifiers, repalce with estimators maybe} that are trained on different subset of training data and only labels points for which they disagree\adnote{you evaluate confidence based on disagreement, not only label points for which they disagree; so rephrase to "..subsets of data.
+Confidence is based on the level of agreement or disagreement among these hypotheses."}.
 Judah et al.
-has proposed using this approach towards online imitation learning\cite{judah2011active,judah2012active}, however it has been shown when training and test distributions are different this can perform worse than randomly selecting points \cite{burbidge2007active}.
+has proposed using this approach towards online imitation learning\cite{judah2011active,judah2012active}, however it has been shown when training and test distributions are different this can perform worse than randomly selecting points\adnote{points confusing; suggest: than randomly selecting which states to query} \cite{burbidge2007active}.
 
-Instead, we contribute a query selection method that is data-centric, evaluating confidence based on novelty
+In SHIV, we use a query selection method that allows a non-stationary distribution, evaluating confidence based on novelty (is the state an outlier to the training distribution)
 and on historically mislabeled regions.
 %Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.
-Our results suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector.
+Our results suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (either distance or query by committee based).
 
@@
 % The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
-% \cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
+% \cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human supervisor
 % to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
@@
 % \cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
-% Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.
+% Search, which replaces the supervisor with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.
 
 % One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
-% provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
+% provide control inputs that the supervisor would have applied for every state encountered along a roll-out of a trajectory at every interation of the
 % algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
@@
 We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
-high-dimensional vectors corresponding to images from a camera, or joint angles and object poses in the environment.
+high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
 We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
-nature. The environment is
-modeled to have dynamics that are stationary and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
+nature\adnote{avoid filler words like in nature}. The environment is
+modeled\adnote{avoid passive voice; sidd always asked me whenever i wrote that "X is done": "done by who?
+by jesus?"} to have dynamics that are stationary\adnote{why stationary?
+what does this mean?} and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
 \mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
-so that $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
-When no confusion arises, we denote the probability density over the initial state also by $p:\mathcal{X}\to
-\mathbb{R}$. By a trajectory, we mean a finite series of pairs of $T$ states visited and corresponding
+so that\adnote{this sentence already contained a so that; break long sentences} $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
+When no confusion arises\adnote{what is confusion arising}, we denote the probability density over the initial state also by $p:\mathcal{X}\to
+\mathbb{R}$. By a trajectory, we mean \adnote{new par, a trajectory is a finite ...}a finite series of pairs of $T$ states visited and corresponding
 control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
 and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
-At times we will also consider trajectories in state space only, in which case a trajectory corresponds
+At times we will also consider trajectories in state space only\adnote{this makes you seem floppy; do we need this?
+if so maybe denot by something else, like $\bar{tau}$ and call it a full trajectory vs a state trajectory}, in which case a trajectory corresponds
 to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.
 
-By a policy, we mean a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
-We shall in particular consider classes of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
-parameter $\theta\in \mathbb{R}^d$ corresponding to support vectors of a Support Vector Machine (SVM).
-Any such policy, $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
+By a policy, we mean\adnote{a policy is a function} a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
+We shall\adnote{we search in a space of parametrized policies} in particular consider classes of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
+parameter $\theta\in \mathbb{R}^d$ corresponding to support vectors of a Support Vector Machine (SVM).\adnote{this is not a requirement that it's the svm necessarily, can be whatever estimator}
+Any such policy, $\pi_{\theta}$ \adnote{missing comma here?} in an environment with probabilistic initial state density and Markovian dynamics
 induces a density on state-space trajectories of length $T+1$: $p(\tau | \theta)=
@@
 
-$p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ for $t-1$ time steps which can be calculated by marginalization $p(\bx_t|\theta) =
+\adnote{Let} $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
+$\pi_{\theta}$ for $t-1$ time steps\adnote{break sentence. This can be computed by marginalizing ... (explain in words first)} which can be calculated by marginalization $p(\bx_t|\theta) =
 \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction},
@@
 While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
-\bx)$ or $p(\bx|\theta)$, but instead assume that we have a stochastic real robot or a simulator such that for any state
-$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ such that $\bx_{t+1}$ follows the distribution corresponding
-to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. In particular, when 'rolling out' trajectories under a policy
+\bx)$ or $p(\bx|\theta)$, but\adnote{while.., but..
+doesn't make sense; "We do not assume...
+Instead, we assume that..."} instead assume that we have a stochastic real robot or a simulator such that for any state
+$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ such that\adnote{redundant; we can sample b from $p(b......$"} $\bx_{t+1}$ follows the distribution corresponding
+to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$.
+In particular\adnote{this is not really in particular; I think you should just say therefore, when rolling out..}, when 'rolling out' trajectories under a policy
 $\pi_{\theta}$, we utilize the robot or simulator to 'sample' the resulting stochastic trajectories rather than
-estimating than estimating $p(\bx|\theta)$ itself.
+estimating $p(\bx|\theta)$ itself.
 
-Typically, the objective in policy learning can be framed as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$
+Typically, the objective in policy learning can be framed\adnote{can be framed by great justice; suggest: typically, the objective of policy learning is to find a policy that minimizes some known cost function:} as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$
 of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
@@
 For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
-be considered \cite{levine2015end}.  In our present setting, we do not know the cost function itself, but instead have access to a "supervisor", 
-an algorithm or human that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
+be considered \cite{levine2015end}.
+In our present setting\adnote{in lfd, the robot does not have access to the cost function itself.
+Instead, it only has access to a ...}, we do not know the cost function itself, but instead have access to a "supervisor",
+an algorithm or human\adnote{don't start the enumeration with algoirhtm and put human second in a paper motivated by reducing supervisory load, which is more important with human supervision} that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
 an initial set of $N$ stochastic demonstration trajectories $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
-which are the result of the supervisor applying this policy.
+which are the result of the supervisor applying this policy. \adnote{sentences too long, break them up}
 
@@
 rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined
-threshold $\gamma$ \footnote{In the orginal DAgger the policy rolled out was stochastically mixed with the expert, thus with probability $\beta$ it would either take the expert's action or the robots.
+threshold $\gamma$ \footnote{In the orginal DAgger the policy rolled out was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action or the robots.
 The use of this stochasitically mix policy was for theoretical analysis.
@@
 
-\includegraphics[width=16cm , height = 5cm]{figures/active_learning/Slide1.jpg}
+\includegraphics[width=\textwidth]{figures/active_learning.pdf}
 
@@
 We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV,  where the size of $\bx$ is $27926$.
-For both DAgger and SHIV, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our expert.
+For both DAgger and SHIV, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our supervisor.
 For the optimization of Eq.

### 2015-08-21 paper.tex
added figs and stuff

--- 2015-08-19 paper.tex
@@
 \begin{abstract}
-Algorithms such as DAgger for robot learning from demonstrations can be very effective for problems where system dynamics and reward functions are unknown, but can impose a burden on supervisors to provide labels (control signals) as states are encountered during policy rollouts.
-To reduce this burden we introduce a new query selection method for stream-based active learning.
-The SHIV algorithm (Svm-based reduction in Human InterVention) only requests supervision for risky stater.
-To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) multi-joint robot arm grasping in clutter simulation with Box2D, and 3) surgical needle insertion.
-Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of 3x to 5x).
+The SHIV algorithm proposes an alternative to previous query selection methods for stream-based active learning to the non-stationary distributions encountered in robot control.
+To reduce operator burden, the Svm-based reduction in Human InterVention (SHIV) algorithm only requests supervision for sufficiently risky or novel states.
 
-%In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
+In traditional imitation learning, a human expert provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
 One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
 
-%\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the expert for additional examples along the states visited by that policy.
+\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the expert for additional examples along the states visited by that policy.
 Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.
 
-%Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance.
+Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance.
 \emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}
 
-%We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
+We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
 Our algorithm, SHIV (SVM-Based Reduction in Human Intervention), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise.
+Our experiments with a toy car domain, as well as with non-prehensile grasping in clutter, suggest that our method can better utilize a human supervision budget, achieving higher success rates for the same number of queries to the expert.
 
@@
 \centering
-\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
+\includegraphics[width=\columnwidth]{figures/teaser.pdf}
 \caption{ 
@@
 \subsection{Notation and Background}
-{\color{blue} [-- TODO: SENSOR MODEL --]}
 We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
@@
 
-Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore
-has guarantees guarantees the convergence to the supervisor's policy {\color{blue} [-- F: ONLY AN ERROR BOUND, RIGHT? --]}. 
+Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore under the assumption of the policy being no regret has theoretical properties of being linearly in time horizon T to the supervisor's policy.
 However, policy rollouts can result in the robot entering dangerous states. For example, when DAgger was used on a
@@
 \subsection{Estimation of Quantile Level Sets}\label{sec:level}
-{\color{blue} [-- REVISED UP TO HERE --]}
 Support estimation can be defined as minimizing a function that contains the volume of a given probability distribution.
@@
 \centering
-\includegraphics[width=6cm, height=6cm]{figures/race_car.png}
-\caption{ An example image from the racing simulator of a sampled polygonal track..
-The car is meant to drive around an not fall off.
-It is placed back on the center if it does fall off.
-The supervisor drives around the track for 2 iterations and HOG features are extracted from the images to form a feature space of }
-
-\vspace*{-10pt}
-\label{fig:race_car}
-\end{figure}
-
-\begin{figure}[t!]
-\centering
 \includegraphics[width=8cm, height=6cm]{figures/dagger_shiv_one_class.eps}
@@
 In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV using only the traditional One-Class SVM without the modification.
+\ref{fig:car_cost}, we plot the performance of DAgger and SHIV.
 Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
@@
 
+\subsection{Surgical Experiment}
+\todo{Need help discussing this better}
+In this experiment, we look at the task of inserting a needle into tissue in preparation for suturing.
+Needle insertion can be a challenging task for surgeons and learning a controller to do so could alleviate some of the burden placed on surgeons.
+We collected data from a surgeon, Dr.
+Douglas Boyd, on the Da Vince Research Kit.
+
+Dr.
+Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose and applied the neccesary corrections to achieve a correct pose.
+We used three of these demonstrations as our initial dataset $\mathcal{D}_0$.
+Dr.
+Boyd couldn't be around for the interactive labeling of both SHIV and DAgger, so we had to hardcore and expert controller that computed the transformation between the desired insertion pose and the current pose.
+We did this by calculating the inverse of a transformation matrix.
+
 \begin{figure}[t!]
 \centering
-\includegraphics[width=6cm, height=6cm]{figures/box2D_arm.png}
-\caption{  The arm, modeled with Box2D, consists of 3 degrees of freedom and has a parallel jaw gripper.
-For input the human demonstrator provides controls through an XBox controller.
-The left and right joystick determined the x and y velocity of the center of the end effector.
-The left bumper of the controller provided a binary input for opening and closing the gripper.
-Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, 1 being opened and zero being closed.
-}
-
+\includegraphics[width=\columnwidth, height=6cm]{figures/needle_insertion_results.eps}
+\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
+In Fig.
+\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV using only the traditional One-Class SVM without the modification.
+Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig.
+\ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
 \vspace*{-10pt}
-\label{fig:box2D_arm.png}
+\label{fig:car_cost}
 \end{figure}
 
-\subsection{Surigcal Experiment}
+\section{Discussions and Future Work}
+SHIV currently provides a way to apply active learning to online imitation learning, however its use of level set estimation of the underlying distribution introduces several hyper parameters.
+As Fig.
+shown these can significantly effect performance if not tuned correctly.
+Future work will look at using cross validation on a hold out set of data to more effectively tune parameters.
 
-\section{Discussion and Future Work}
+Another potential issue is that each iteration of SHIV requires solving a quadratic program with the Gram matrix.
+As we scale to harder tasks that require significantly more data, this can become problematic.
+Future work will look at using techniques like PCA and random feature projections to scale efficiently \todo{cite something}.
+
+Lastly, our approach is promising in simulation.
+However we need to evaluate how our active learning method will work on a real robot with noisy sensor observations.
+Future work will be doing the grasping in clutter experiments on an actual robot.
+
+\section{Acknowledgments} 
+This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536 and NSF-Graduate Research Fellowship.. 
+We thank UC Berkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Siddarth Sen, Steve McKinley and Sergey Levine.
 

### 2015-08-21 paper.tex

--- 2015-08-21 paper.tex
@@
 \centering
-\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
+\includegraphics[width=\columnwidth]{figures/teaser.pdf}
 \caption{ 
-Conceptual illustration of robot states (projected onto the plane) with quantile levelset (shaded) for measuring the riskiness of
-executing the current policy as distance from the levelset boundary.  In SHIF, supervisor demonstrations are only requested when risky states are encountered. 
+Illustrations of the different examples we evaluated our algorithm, SHIV, on.
+A) Driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track.
+B) Grasping in clutter experiment in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not moving the red square objects off the gray boundary representing a table.
+C) A experiment on the Da Vince Research Kit to learn a controller from a surgeon's demonstrations of correcting a needle before suturing in surgery.
 }
@@
 
+\begin{figure*}[ht]
+\centering
+
+\includegraphics[width=\textwidth]{figures/active_learning.pdf}
+
+\caption{An illustrative example of different active learning techniques.
+The shaded and empty circles represent different labeled classes $0$ and $1$.
+The red empty circles represent label $1$, but are encountered on a different distribution then what was trained on.
+As illustrated, Confidence and Query by Committee methods measure states far away from the decision boundary of the estimator as low risk, however novelty detection methods measure the level of risk as how far a point is from the trained data.
+Our modified risk method attempts to measure risk both as a function of how far it is from data trained on and the decision boundary of the estimator.
+}
+\label{fig:support_example}
+\end{figure*}
+
 \section{Problem Statement}
 \subsection{Notation and Background}
-{\color{blue} [-- TODO: SENSOR MODEL --]}
 We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
@@
 Here $(w,\rho)$ are a weight vector and offset parameterizing a hyperplane in the feature space associated with a kernel.
-
-\begin{figure*}[ht]
-\centering
-
-\includegraphics[width=\textwidth]{figures/active_learning.pdf}
-
-\caption{Data is sampled from a Gaussian Mixture Model and in Fig.
-\ref{fig:subfigure1}, the red points are those that the trained policy, $\pi_{theta}$ will mis-predict.
-In Fig.
-\ref{fig:subfigure2} the One Class SVM is fit to the data and tries to estimate the areas of low risk (the light green region), while it is able to estimates the area where the majority of the data lies it also encloses the points the trained policy is mis-predicting.
-In Fig.
-\ref{fig:subfigure3}, the Risk Sensitive One Class SVM is able to effectively remove the red points from the region of low risk.}
-\label{fig:support_example}
-\end{figure*}
 

### 2015-08-21 paper.tex
.

@@
 
+\newcommand{\fpnote}[1]{\ifthenelse{\boolean{include-notes}}%
+ {\textcolor{blue}{\textbf{FP: #1}}}{}}
+
 \renewcommand{\baselinestretch}{.99}
@@
 \begin{abstract}
-Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system dynamics and reward functions are unknown.
-However, they impose a burden on supervisors to demonstrate labels (control signals) as the robot encounters new states when iteratively executing its new best policy.
-We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
+Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system
+dynamics and reward functions are unknown. However, they impose a burden on supervisors to demonstrate labels (control
+signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
+algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
 SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
@@
 
-\caption{An illustrative example of different active learning techniques.
-The shaded and empty circles represent different labeled classes $0$ and $1$.
-The red empty circles represent label $1$, but are encountered on a different distribution then what was trained on.
-As illustrated, Confidence and Query by Committee methods measure states far away from the decision boundary of the estimator as low risk, however novelty detection methods measure the level of risk as how far a point is from the trained data.
-Our modified risk method attempts to measure risk both as a function of how far it is from data trained on and the decision boundary of the estimator.
+\caption{An illustrative example of different active learning techniques. The shaded and empty circles represent
+different labeled classes $0$ and $1$. The red empty circles represent label $1$, but are encountered on a different
+distribution then what was trained on
+{\color{blue} FP:can we make this more formal sounding? Represent samples from a different distribution?} 
+As illustrated, Confidence and Query by Committee methods
+measure
+{\color{blue} FP:estimate} states far away from the decision boundary of the estimator as having low risk,
+however novelty detection methods measure {\color{blue} FP:estimate} the level of risk as
+{\color{blue}FP:by} how far a point is from the trained data. Our
+modified risk method attempts to measure risk both as a function of how far it
+{\color{blue}it gramatically refers to risk,
+but you mean sample "it$\mapsto$a sample"?} is from data trained on
+{\color{blue}grammatically strange$\mapsto$from the training data} and the decision boundary of the estimator. 
 }
@@
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
-We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
-nature\adnote{avoid filler words like in nature}. The environment is
-modeled\adnote{avoid passive voice; sidd always asked me whenever i wrote that "X is done": "done by who?
-by jesus?"} to have dynamics that are stationary\adnote{why stationary?
-what does this mean?} and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
-\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
-so that\adnote{this sentence already contained a so that; break long sentences} $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
-When no confusion arises\adnote{what is confusion arising}, we denote the probability density over the initial state also by $p:\mathcal{X}\to
-\mathbb{R}$. By a trajectory, we mean \adnote{new par, a trajectory is a finite ...}a finite series of pairs of $T$ states visited and corresponding
-control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
+We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or
+continuous. We assume that Markovian dynamics, such that the the probability of state $\mathbf{x_{t+1}}\in
+\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
+\mathcal{U}$. Under this assumption $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
+We denote the probability density over the initial state also by $p:\mathcal{X}\to
+\mathbb{R}$. By a trajectory, we mean a finite series of pairs of $T$ states visited and corresponding
+control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
 and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
-At times we will also consider trajectories in state space only\adnote{this makes you seem floppy; do we need this?
-if so maybe denot by something else, like $\bar{tau}$ and call it a full trajectory vs a state trajectory}, in which case a trajectory corresponds
-to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.
+For a given trajectory $\tau$ as above, we denote by $\hat{\tau}$ the corresponding trajectory in state space,
+$\hat{\tau} = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.
 
-By a policy, we mean\adnote{a policy is a function} a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
-We shall\adnote{we search in a space of parametrized policies} in particular consider classes of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
-parameter $\theta\in \mathbb{R}^d$ corresponding to support vectors of a Support Vector Machine (SVM).\adnote{this is not a requirement that it's the svm necessarily, can be whatever estimator}
-Any such policy, $\pi_{\theta}$ \adnote{missing comma here?} in an environment with probabilistic initial state density and Markovian dynamics
+A policy is a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
+We consider a space of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
+parameter $\theta\in \mathbb{R}^d$. Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
 induces a density on state-space trajectories of length $T+1$: $p(\tau | \theta)=
@@
 
-\adnote{Let} $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ for $t-1$ time steps\adnote{break sentence. This can be computed by marginalizing ... (explain in words first)} which can be calculated by marginalization $p(\bx_t|\theta) =
+Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
+$\pi_{\theta}$ for $t-1$ time steps. This density can be computed by marginalization: $p(\bx_t|\theta) =
 \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction},
@@
 While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
-\bx)$ or $p(\bx|\theta)$, but\adnote{while.., but..
-doesn't make sense; "We do not assume...
-Instead, we assume that..."} instead assume that we have a stochastic real robot or a simulator such that for any state
-$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ such that\adnote{redundant; we can sample b from $p(b......$"} $\bx_{t+1}$ follows the distribution corresponding
-to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$.
-In particular\adnote{this is not really in particular; I think you should just say therefore, when rolling out..}, when 'rolling out' trajectories under a policy
-$\pi_{\theta}$, we utilize the robot or simulator to 'sample' the resulting stochastic trajectories rather than
+\bx)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
+$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
+Therefore, when 'rolling out' trajectories under a policy
+$\pi_{\theta}$, we utilize the robot or a simulator to sample the resulting stochastic trajectories rather than
 estimating $p(\bx|\theta)$ itself.
 
-Typically, the objective in policy learning can be framed\adnote{can be framed by great justice; suggest: typically, the objective of policy learning is to find a policy that minimizes some known cost function:} as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$
-of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
+Typically, the objective of policy learning is to find a policy that minimizes some known cost function
+$C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
 \mathcal{U})^{T+1}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
@@
 be considered \cite{levine2015end}.  
-In our present setting\adnote{in lfd, the robot does not have access to the cost function itself.
-Instead, it only has access to a ...}, we do not know the cost function itself, but instead have access to a "supervisor",
-an algorithm or human\adnote{don't start the enumeration with algoirhtm and put human second in a paper motivated by reducing supervisory load, which is more important with human supervision} that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
+In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to a
+a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$. We are furthermore given
 an initial set of $N$ stochastic demonstration trajectories $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
-which are the result of the supervisor applying this policy. \adnote{sentences too long, break them up}
+which are the result of the supervisor applying this policy.
 
-Next, we define a ``surrogate'' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+Next, we define a `surrogate' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
 measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$,
@@
 of high probability under $\pi_\theta$ by sampling via policy `roll outs' from $p(\bx|\theta)$. 
-{\color{blue} [-- F: DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
-made more precise then and refer to the algorithm --]}
+\fpnote{DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
+made more precise then and refer to the algorithm}
 
 \subsubsection{Step 1}
+\fpnote{this is really start of iteration `i', as we circle back}
 At iteration $k=0$ an initial dataset $\mathcal{D}_0$ of $N_0$ supervisor demonstration trajectories 
@@
 
-This problem can be considered as a supervised learning problem in particular and can be solved using standard machine
+This problem can be considered as a supervised learning problem which can be solved using standard machine
 learning techniques, for example a support vector machine or a neural network.
@@
 To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
-{ \color{blue} [-- F: Make precise --]}
 can be considered as present in policy's output. We employ a regularization technique in the optimization which is
@@
 The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$. 
+\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
 
-Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss approaches zero. Since DAgger
-requires rolling out the policy at each iteration, one way to terminate the algorithm is when the performance of the
-rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined
-threshold $\gamma$ \footnote{In the orginal DAgger the policy rolled out was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action or the robots.
-The use of this stochasitically mix policy was for theoretical analysis.
-In practice, it is recommended to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}
+Steps 1 and 2 are repeated for $K$ iterations or until 
+the cumulative surrogate is smaller than some predefined threshold\footnote{In the orginal DAgger the policy rolled out
+was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
+or the robots. The use of this stochasitically mix policy was for theoretical analysis. In practice, it is recommended
+to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.
 
 Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore under the assumption of the policy being no regret has theoretical properties of being linearly in time horizon T to the supervisor's policy.
-However, policy rollouts can result in the robot entering dangerous states. For example, when DAgger was used on a
+\fpnote{How about: Dagger has been experimentally shown to perform well in both simulation and real world
+    experiments. Under a technical `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
+deduced error bounds on the expected loss which scale linearly in the time horizon $T$.}
+
+However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
 quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
 We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
-previously trained states, which potentially means our policy will mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so the state, although visited, does
+previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
+loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so that the state, although visited, does
 not model the supervisor's control inputs correctly. Furthermore providing correct control inputs or ``labeling'' at each
@@
 
-To address these limitations, we propose to 1) avoid highly risky states entirely by early termination the policy
-roll-out that enter these regions and 2) to recognize non-risky states and to not request human input for these,
+To address these limitations, we propose to 1) avoid highly risky states entirely by early termination of the policy
+roll-outs that enter these regions and 2) to recognize non-risky states and to not request supervisor input for these,
 thereby reducing the burden on the human trainer.
@@
 a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
+\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}
 
 \subsection{Estimation of Quantile Level Sets}\label{sec:level}
-Support estimation can be defined as minimizing a function that contains the volume of a given probability distribution.
-Formally we define it as follows let $\mathbf{x}_1,...,\mathbf{x}_n $ be i.i.d.
-random variables in a set $\mathcal{X}$ with distribution $P$.
-Let $\mathcal{G}$ be a class of measurable subsets of $\mathcal{X}$ and let $\lambda$ be a real function defined on $\mathcal{G}$.
-The quantile function with respect to $(P,\lambda,\mathcal{G})$ is
-
-\vspace{-2ex}
+\fpnote{my git commit on this section was overwritten by an old commit at version 10 - reintroduced modifications here,
+Michael, please check this is still accurate with recent modifications}
+We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
+independent and identically distributed samples $\mathbf{x}_1,...,\mathbf{x}_n\in \mathcal{X}$.
+In most general terms, the quantile function for $P$ and subject to a class of measurable subsets $\mathcal{G}$ of $\mathcal{X}$ is
+defined by
 \begin{align}\label{eq:quantile}
@@
 \end{align} 
+$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure which most commonly is given by the Lebesgue measure.
+Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
+measure (i.e. volume) for each $\gamma\in [0,1]$ (this set is in general not necessarily unique). 
+$G(\gamma)$ denotes a set of minimum measure $G \in \mathcal{G}$ with $P(G(\gamma))\ge \gamma$. Note in particular that $G(1)$ is the support of the density $p$ corresponding to $P$, if $p$ exists.
 
-We denote by $G(\gamma)$ the $G \in \mathcal{G}$ that attains the infinimum.
-The most common choice of $\lambda$ is Lebesgue measure, in which case $G(\gamma)$ is the minimum volume $G \in \mathcal{G}$ that contains at least a fraction $\gamma$ of the the probability mass.
-Thus, $G(1)$ is the support of the density $p$ corresponding to $P$, assuming it exists.
+To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al.
+looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}.
+By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
+derives an approximation of the quantile function described in Eq. \ref{eq:quantile}, which in particular has rigorous
+convergence guarantees asymptotically when a normalized Gaussian kernel $k$ is chosen and bandwidths decay at an
+appropriately chosen rate as the number of samples tends to infinity \cite{vert2006consistency}.
+This approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$,
+$f_w(\mathbf{x}) = \sum_i w_i k(\mathbf{x}_i, \mathbf{x})$
+and $(w,\rho)$ denote the weight vector and offset parameterizing a hyperplane in the feature space associated with a
+Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}$.
 
-To handle high dimensional densities $P$, work by Scholk{\"o}pf et al.
-looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}.
-They then minimize a SV  regularizer which, using a kernel, controls the smoothness of the estimated function describing $G$.
-In terms of the quantile function described in Eq.
-\ref{eq:quantile}, the approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$.
-Here $(w,\rho)$ are a weight vector and offset parameterizing a hyperplane in the feature space associated with a kernel.
+Let $\Phi:\mathcal{X}\to \mathcal{F}$ denote the feature map corresponding to our exponential kernel, mapping the
+observation space $\mathcal{X}$ into a Hilbert space $(\mathcal{F}, \langle, \rangle)$ such that $k(\bx, \bx') = \langle
+\Phi(\bx), \Phi(\bx')\rangle$.
 
-Let $\Phi$ be a feature map $\mathcal{X} \rightarrow \mathcal{F}$, i.e.
-a map into an inner product space $\mathcal{F}$ such that the inner product in the image of $\Phi$ can be computed by evaluating some  kernel
-
+The One Class SVM proposed by \cite{scholkopf2001estimating} determines a hyperplane in feature space $\mathcal{F}$
+maximally separating the input data from the origin:
 \vspace{-2ex}
-\begin{align}
-k(\bx_0,\bx_1) = \langle\Phi(\bx_0),\Phi(\bx_1)\rangle
+\begin{align}\label{eq:primal_sup}
+    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
+\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
 \end{align}
 
-such as the Gaussian kernel
-
-\vspace{-2ex}
-\begin{align}
-k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}
-\end{align}
-
-The main idea is to solve an optimization problem that separates the origin, we solve the following quadratic problem:
-
-\vspace{-2ex}
-\begin{align}\label{eq:primal_sup}
-\underset{w\in F, \mathbf{\xi} \in \mR, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag
-\end{align}
-
-The parameter $\nu$ controls the penalty on slack terms and asymptotically approaches is equivalent to $\gamma$ \cite{vert2006consistency}.  The decision function then becomes
+Here, the parameter $\nu$ controls the penalty or `slack term' and asymptotically approaches $\gamma$ \cite{vert2006consistency}
+in the quantile definition when bandwidths decay at appropriate rates as the number of samples increases. The decision
+function, determining point membership in the approximate quantile levelset is given by
 
@@
 \begin{align}\label{eq:primal_sup}
-\underset{w\in F, \mathbf{\xi} \in \mR^l, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}
+    \underset{w\in F, \mathbf{\xi} \in \mathbb{R}^l, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
+\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}.
 \end{align}
 
-Points that are mis-predicted are then enforced to lie on the opposite of the hyper-plane in the feature space $\phi(\bx)$, which carves out holes in the support region around them.
-The dual formulation, which is what is solved in practice, can be derived as
+States that incur loss above the $\varepsilon$ threshold are then enforced to lie on the opposite side of the
+hyper-plane separating the origin from the data in the feature space. Practically, this modification corresponds to
+`carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
+exluded from the super-levelset.
 
-\vspace{-2ex}
+The dual formulation to the modified optimization problem, which is solved in practice, is 
 \begin{align}\label{eq:dual_sup}
-\underset{\alpha\in \mathcal{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
-\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1 
+\underset{\alpha_i\in \mathbb{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
+\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1.
 \end{align}
 
-Our decision boundary function $g(\bx)$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n \alpha_i y_i k(\bx_i,\bx) - \rho$.
-To compute the $\rho$ term,we leverage the fact that for an optimal solution the inequalities in Eq.
-\ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$.
-Therefore we can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating}.
+Our corresponding decision function $g:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n
+\alpha_i y_i k(\bx_i,\bx) - \rho$. To compute the $\rho$ term, we leverage the fact that for an optimal solution the
+inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
+can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating} {\color{blue} [-- F:
+explain this more --]}.
 
-\subsection{SHIV: SVM-Based Reduction in Human Intervention}
+\subsection{The \acro~algorithm}
 
-Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the supervisor's control,which we define as the region of low risk.
-In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.
-Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the supervisor provide labels when the robot leaves this boundary.
-Furthermore to avoid entering pathological states that are far from the supervisor's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$.
-The risk threshold, $r_0$, is user defined based on the task.
+Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
+predict the supervisor's control, by means of the thresholded surrogate just discussed.  
+% Too vague:
+%In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
+%Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
+To reduce the burdon on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
+$\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
+above a threshold $\varepsilon$ chosen by the user.
+The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
+resulting risk-aware quantile super-levelset and we terminate roll-outs that are at a task-specific threshold $r(\bx) = \sum_i^n
+\alpha_i \bx_i k(\bx_i,\bx)-\rho>r_0$ away from the decision boundary $g$ corresponding to this modified super-levelset.
 
+{\color{blue} [-- F: use formal algorithm and explain here instead --]} 
 \subsubsection{Step 1}
-Similar to DAgger at iteration $k$ the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$ by solving Eq.
-\ref{eq:super_objj}.
-We then estimate the level set of the distribution being trained on by solving the optimization for the One Class SVM or $\ref{eq:primal_sup}$ on the dataset $\mathcal{D}_k$.
-We now have a decision boundary $g_k(\bx)$, which is $1$ if the region is in the low risk area and $-1$ otherwise .
-The parameter $\nu$ is an estimate of how much probability mass is contained in the level set and can be use to control the size of the low risk region.
+
+Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
+by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
+training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
+This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.
 
  \subsubsection{Step 2}
- In DAgger the policy that was rolled out is $\pi_{\theta_k}$, however this could potential encounter pathological states that are far from the initial set of demonstrations $\mathcal{D}_0$.
-To prevent this we terminate the rolled out policy if the risk, or distance from the support, is above some threshold $r(\bx_t) > r_0$.
-Furthermore, instead of labeling every state now the supervisor is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.
-These states are then added to the dataset $\mathcal{D}_{k}$
+ In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
+ robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
+ above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
+ provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
+ dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.
+
+We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
+between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
+supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
+incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
+areas and obtain more labels from the supervisor in those regions.
 
 \section{Experiments}
+\fpnote{Michael, please also compare my comments/changes git version 273ecde - all these changes got overwritten when merging}
 \subsection{Driving Example}
-A common benchmark in Reinforcement Learning  is a car driving around a track avoiding other cars \cite{argall2009survey}.
-To illustrate our methods ability in high dimensions, the car must follow a polygonal track using only HOG features extracted from images.
-If the car falls off the track, it is placed back on the center facing the angle of the polygonal track piece.
-We sample the polygonal track by drawing points from a Gaussian with a mean that is the centered of the video game work space.
-The convex hull of the sampled points is then computed.
-The car's control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
+%A common benchmark in Reinforcement Learning  is a car driving around a track avoiding other cars
+%\cite{argall2009survey}. To illustrate our methods ability in high dimensions, the car must follow a polygonal track
+%using only HOG features extracted from images. If the car falls off the track, it is placed back on the center facing
+%the angle of the polygonal track piece. We sample the polygonal track by drawing points from a Gaussian with a mean that
+%is the centered of the video game work space. The convex hull of the sampled points is then computed. The car's control
+%space $\mathcal{U} = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
 The internal state space of the car is xy-coordinates and the angle it is facing.
@@
 
-We have the supervisor drive around the track 2 times and then collect the raw images observed.
+\fpnote{Previous commit:
+A common benchmark in Reinforcement Learning is that of a car driving around a track while avoiding collisions with
+other cars \cite{argall2009survey}. We implemented a car simulator where the car must stay on a rectangular track and
+avoid autonomously controlled cars that drive on the same track. If the car accidentally leaves the track, it is placed
+back on the center of the track at a nearby position. The car's control input space is  $\mathcal{U} = \lbrace -15^\circ, 0, 15^\circ \rbrace$
+instantly changing the angle of the car that drives at a unit speed. The internal state space of the car is given by the
+xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
+state space search through the driving simulator to plan the next control {\color{blue} [-- F: be more precise --]}.
+    The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
+and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
+Oriented Gradients (HOG) features using OpenCV. These histograms serve as the \emph{observable state space}
+$\mathcal{X}$. For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
+policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
+validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
+exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution. 
+[what about $r_0$?] We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
+defined to be total number of times the car left the track or collided with the other cars on the track. We compare the
+cost to the number of control input demonstrations queried from the supervisor.
+Initial results over 1 level shown in Fig.
+suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
+}
+%We have the supervisor drive around the track 2 times and then collect the raw images observed.
 We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV,  where the size of $\bx$ is $27926$.
@@
 
-To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
+%To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
 The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
@@
 
-We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
+%We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
 In Fig.

### 2015-08-21 paper.tex
.

@@
 \section{Experiments}
-\fpnote{Michael, please also compare my comments/changes git version 273ecde - all these changes got overwritten when merging}
+\fpnote{Michael, please also compare my comments git version 273ecde - those changes got overwritten when merging and
+had some improvements in style}
 \subsection{Driving Example}
-%A common benchmark in Reinforcement Learning  is a car driving around a track avoiding other cars
-%\cite{argall2009survey}. To illustrate our methods ability in high dimensions, the car must follow a polygonal track
-%using only HOG features extracted from images. If the car falls off the track, it is placed back on the center facing
-%the angle of the polygonal track piece. We sample the polygonal track by drawing points from a Gaussian with a mean that
-%is the centered of the video game work space. The convex hull of the sampled points is then computed. The car's control
-%space $\mathcal{U} = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
+A common benchmark in Reinforcement Learning  is a car driving around a track avoiding other cars \cite{argall2009survey}.
+To illustrate our methods ability in high dimensions, the car must follow a polygonal track using only HOG features extracted from images.
+If the car falls off the track, it is placed back on the center facing the angle of the polygonal track piece.
+We sample the polygonal track by drawing points from a Gaussian with a mean that is the centered of the video game work space.
+The convex hull of the sampled points is then computed.
+The car's control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
 The internal state space of the car is xy-coordinates and the angle it is facing.
@@
 
-\fpnote{Previous commit:
-A common benchmark in Reinforcement Learning is that of a car driving around a track while avoiding collisions with
-other cars \cite{argall2009survey}. We implemented a car simulator where the car must stay on a rectangular track and
-avoid autonomously controlled cars that drive on the same track. If the car accidentally leaves the track, it is placed
-back on the center of the track at a nearby position. The car's control input space is  $\mathcal{U} = \lbrace -15^\circ, 0, 15^\circ \rbrace$
-instantly changing the angle of the car that drives at a unit speed. The internal state space of the car is given by the
-xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
-state space search through the driving simulator to plan the next control {\color{blue} [-- F: be more precise --]}.
-    The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
-and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
-Oriented Gradients (HOG) features using OpenCV. These histograms serve as the \emph{observable state space}
-$\mathcal{X}$. For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
-policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
-validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
-exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution. 
-[what about $r_0$?] We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
-defined to be total number of times the car left the track or collided with the other cars on the track. We compare the
-cost to the number of control input demonstrations queried from the supervisor.
-Initial results over 1 level shown in Fig.
-suggest an $75\%$ reduction in the number of queries needed for SHEATH compared to DAgger.
-}
-%We have the supervisor drive around the track 2 times and then collect the raw images observed.
+We have the supervisor drive around the track 2 times and then collect the raw images observed.
 We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV,  where the size of $\bx$ is $27926$.
@@
 
-%To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
+To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
 The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
@@
 
-%We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
+We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
 In Fig.

### 2015-08-22 paper.tex
Anca and Florian's feedback

@@
 \includegraphics[width=\columnwidth]{figures/teaser.pdf}
-\caption{ 
-Illustrations of the different examples we evaluated our algorithm, SHIV, on.
-A) Driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track.
-B) Grasping in clutter experiment in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not moving the red square objects off the gray boundary representing a table.
-C) A experiment on the Da Vince Research Kit to learn a controller from a surgeon's demonstrations of correcting a needle before suturing in surgery.
+\caption{ \adnote{make this a 2 by 2 grid; a b c d, where d is the result; make the result graph more square}
+For a given budget of human supervision, SHIV improves performance (reduced policy cost) in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a surgeon's demonstrations of correcting a needle before suturing in surgery.
 }
@@
 \end{figure}
+
+\begin{figure*}[t]
+\centering
+
+\includegraphics[width=\textwidth]{figures/active_learning.pdf}
+
+\caption{\adnote{A comparison of different query selection strategies for active learning on a non-stationary distribution.
+The shaded and empty circles are training data from two classes, $0$ and $1$ respectively.
+The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $1$.
+Typical strategies assign high risk to states close the decision boundary (a), or for which a set of estimators disagree (b).
+Neither of these apply to our new samples in red.
+In contrast, we use a strategy that is amenable to non-stationary distributions by assigning high risk to novel states (c) and states in historically mislabeled regions.
+}
+%Confidence and Query by Committee methods measure
+%{\color{blue} FP:estimate} states far away from the decision boundary of the estimator as having low risk,
+%however novelty detection methods measure {\color{blue} FP:estimate} the level of risk as
+%{\color{blue}FP:by} how far a point is from the trained data. Our
+%modified risk method attempts to measure risk both as a function of how far it
+%{\color{blue}it gramatically refers to risk,
+%but you mean sample "it$\mapsto$a sample"?} is from data trained on
+%{\color{blue}grammatically strange$\mapsto$from the training data} and the decision boundary of the estimator. 
+}
+\label{fig:support_example}
+\end{figure*}
 
@@
 \section{Related Work}
-\adnote{stick to either learning from demonstration or imitation learning}
-Below we summarize related work in robot\adnote{robot learnign too broad, active approaches to learning from demonstration perhaps} learning and in risk evaluation.
+Below we summarize related work in active approaches to robot learning from demonstration, as well as in risk evaluation techniques that we build upon.
 
@@
 
-Stream-based active learning has two ingredients: a stream, given here by the policy, and a query selection method.
+Stream-based active learning has two ingredients: a stream, given here by executing the current best policy, and a query selection method deciding whether or not to query.
 Typical query selection methods are estimator-centric: they evaluate the estimator's confidence, e.g.
-distance from the classification hyperplane \cite{tong2002support}, implicitly assuming a stationary distribution --- that the new data is sampled from the same distribution as the previous training data.
-Although such methods have been proposed for online imitation learning (see dogged learning \cite{chernova2009interactive,grollman2007dogged}),
+distance from the classification hyperplane \cite{tong2002support}, as in Fig.
+\ref{fig:support_example}(a).
+An alternative to distance-based measures of confidence is query by committee \adnote{cite}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
+Confidence here is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig.
+\ref{fig:support_example}(b)).
+
+Both approaches implicitly assume a stationary state distribution --- that the new data is sampled from the same distribution as the previous training data.
+Although such methods have been previously proposed for online imitation learning (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
 online imitation learning violates the stationary distribution assumption because each new policy induces a new distribution of states.
-An alternative to distance-based measures of confidence is query by committee, which uses a committee of hypothesized classifiers\adnote{don't have to be classifiers, repalce with estimators maybe} that are trained on different subset of training data and only labels points for which they disagree\adnote{you evaluate confidence based on disagreement, not only label points for which they disagree; so rephrase to "..subsets of data.
-Confidence is based on the level of agreement or disagreement among these hypotheses."}.
-Judah et al.
-has proposed using this approach towards online imitation learning\cite{judah2011active,judah2012active}, however it has been shown when training and test distributions are different this can perform worse than randomly selecting points\adnote{points confusing; suggest: than randomly selecting which states to query} \cite{burbidge2007active}.
+This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.\adnote{merged the two types since they have the same problem, and references the figure}
 
-In SHIV, we use a query selection method that allows a non-stationary distribution, evaluating confidence based on novelty (is the state an outlier to the training distribution)
-and on historically mislabeled regions.
+In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating confidence based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig.
+\ref{fig:support_example}(c).
+Additionally, we also assign lower confidence to  historically \emph{mislabeled} regions, as in Fig.
+\ref{fig:support_example}(d).
 %Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.
-Our results suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (either distance or query by committee based).
+Our results in Sec.
+\ref{}\adnote{fill in} suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (be it distance or query by committee based).
 
@@
 
-\begin{figure*}[ht]
-\centering
-
-\includegraphics[width=\textwidth]{figures/active_learning.pdf}
-
-\caption{An illustrative example of different active learning techniques. The shaded and empty circles represent
-different labeled classes $0$ and $1$. The red empty circles represent label $1$, but are encountered on a different
-distribution then what was trained on
-{\color{blue} FP:can we make this more formal sounding? Represent samples from a different distribution?} 
-As illustrated, Confidence and Query by Committee methods
-measure
-{\color{blue} FP:estimate} states far away from the decision boundary of the estimator as having low risk,
-however novelty detection methods measure {\color{blue} FP:estimate} the level of risk as
-{\color{blue}FP:by} how far a point is from the trained data. Our
-modified risk method attempts to measure risk both as a function of how far it
-{\color{blue}it gramatically refers to risk,
-but you mean sample "it$\mapsto$a sample"?} is from data trained on
-{\color{blue}grammatically strange$\mapsto$from the training data} and the decision boundary of the estimator. 
-}
-\label{fig:support_example}
-\end{figure*}
-
 \section{Problem Statement}
-\subsection{Notation and Background}
-We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
+\noindent\textbf{Policies and State Densities.}
+We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example, of
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
 We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or
-continuous. We assume that Markovian dynamics, such that the the probability of state $\mathbf{x_{t+1}}\in
+continuous. We assume Markovian dynamics, such that the probability of state $\mathbf{x_{t+1}}\in
 \mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
-\mathcal{U}$. Under this assumption $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
-We denote the probability density over the initial state also by $p:\mathcal{X}\to
-\mathbb{R}$. By a trajectory, we mean a finite series of pairs of $T$ states visited and corresponding
-control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
-and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
-For a given trajectory $\tau$ as above, we denote by $\hat{\tau}$ the corresponding trajectory in state space,
-$\hat{\tau} = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.
+\mathcal{U}$. Thus, we assume that 
+$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
+We assume a probability density over initial states $p(\bx_0)$.
+%We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.
+
+A trajectory $\hat{\tau}$ is a finite series of $T+1$ pairs of states visited and corresponding
+control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
+and $\bu_t\in \mathcal{U}$ for $t\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
+For a given trajectory $\hat{\tau}$ as above, we denote by ${\tau}$ the corresponding trajectory in state space,
+${\tau} = (\bx_0,....,\bx_T)$.
 
 A policy is a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
-We consider a space of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
-parameter $\theta\in \mathbb{R}^d$. Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
-induces a density on state-space trajectories of length $T+1$: $p(\tau | \theta)=
-p(\bx_0)\prod_{i=0}^{T-1}p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$, for $\tau = (\bx_0, \bx_1, \ldots, \bx_N)\in
-\mathcal{X}^{N+1}$.
+We consider a space of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by some $\theta\in \mathbb{R}^d$.
+Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
+induces a density on state-space trajectories of length $T+1$: $$p(\tau | \theta)=
+p(\bx_0)\prod_{i=0}^{T-1}p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$$
 
 Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ for $t-1$ time steps. This density can be computed by marginalization: $p(\bx_t|\theta) =
-\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction},
-the average density on states is now defined as $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
+$\pi_{\theta}$ from time $0$ to time $t-1$.\adnote{shouldnt you then define this above insted of the probability of a trajectory?} This density can be computed by marginalization: $p(\bx_t|\theta) =
+\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
+the average density on states for \emph{any} timepoint by 
+\begin{equation}
+p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)
+\label{eq:density}
+\end{equation}
+
 While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
-\bx)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
+\bx)$\adnote{this is a typo} or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
 $\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
@@
 
-Typically, the objective of policy learning is to find a policy that minimizes some known cost function
-$C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
-\mathcal{U})^{T+1}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
+\noindent\textbf{Objective.} Typically, the objective of policy learning is to find a policy that minimizes some known cost function
+$C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\tau$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
 For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
 be considered \cite{levine2015end}.  
-In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to a
+In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
 a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$. We are furthermore given
-an initial set of $N$ stochastic demonstration trajectories $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
+an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
 which are the result of the supervisor applying this policy.
+This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
+The goal is to produce a low cost policy for the task based on these demonstrations.
 
-Next, we define a `surrogate' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+We define a `surrogate' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
 measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$,
@@
 Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how "close" the policy's
-returned control intput $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
+returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
 $\tilde{\pi}(\bx)\in \mathcal{U}$.
-Our objective then consists of determining a policy $\pi_{\theta}$ minimizing the expected surrogate loss where the expectation is taken over the distribution of states.
+
+Following \cite{ross2010reduction}, our objective then consists of determining a policy $\pi_{\theta}$ minimizing the expected surrogate loss, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
 
@@
 \end{align}
+with $p(\bx|\theta)$ from Eq. \ref{eq:density}.
 
-The optimization problem in Eq.
+If the robot could learn the policy perfectly, this state density would match the one encountered in the user examples.
+But any small error will make the state distribution deviate from the training one, and this the motivation for an iterative algorithm like DAgger and now SHIV.
+
+% The optimization problem in Eq.
 \ref{eq:LFD_obj} is  typically non-convex.
@@
 
- \subsection{DAgger: Dataset Aggregation}
-Note that Eq. \ref{eq:LFD_obj} involves both the parameterized policy $\pi_{\theta}$ and the average distribution of
-states with respect to the policy, $p(\bx|\theta)$.
+\section{SHIV}
+\adnote{putting shiv and dagger side by side.
+also, notice how I am setting up the rest of the section by explaining what will follow; also, avoid filler sentences like "note that ..." when you are not following that up with a point; avoid filler words like two "basic" steps -- it's just steps, why are they basic?}
+
+Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq.
+\ref{eq:LFD_obj} by iterating two steps: 1) find an optimal $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
+However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky enough to warrant a query, thereby reducing supervisory burden.
+
+%  \subsection{DAgger: Dataset Aggregation}
+% Note that Eq. \ref{eq:LFD_obj} involves both the parameterized policy $\pi_{\theta}$ and the average distribution of
+% states with respect to the policy, $p(\bx|\theta)$.
 Let us recall that Dataset Aggregation (DAgger) is an iterative algorithm developed by \cite{ross2010reduction} which iterates two basic steps for $K$ iterations to find an optimal policy under this objective.
-DAgger iteratively minimizes $\pi_{\theta}$ on the collected dataset of examples $\mathcal{D}$ and then adds new states
-of high probability under $\pi_\theta$ by sampling via policy `roll outs' from $p(\bx|\theta)$. 
-\fpnote{DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
-made more precise then and refer to the algorithm}
+%DAgger iteratively minimizes $\pi_{\theta}$ on the collected dataset of examples $\mathcal{D}$ and then adds new states
+%of high probability under $\pi_\theta$ by sampling via policy `roll outs' from $p(\bx|\theta)$. 
+%\fpnote{DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
+%made more precise then and refer to the algorithm}
 
-\subsubsection{Step 1}
-\fpnote{this is really start of iteration `i', as we circle back}
-At iteration $k=0$ an initial dataset $\mathcal{D}_0$ of $N_0$ supervisor demonstration trajectories 
-with $T+1$ time steps: $\tau^i=(\bx_0^i, \bu_0^i, \ldots, \bx_T^i, \bu_T^i)\in (\mathcal{X}\times\mathcal{U})^{T+1}$ for $i\in \{0, \ldots, N_0\}$
-mapping states to control
-inputs is provided. DAgger solves the following optimization problem with respect to the surrogate loss function:
+\subsection{Step 1.}
+The first step of any iteration $k$ is to find a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):
+% \fpnote{this is really start of iteration `i', as we circle back}
+% At iteration $k=0$ an initial dataset $\mathcal{D}_0$ of $N_0$ supervisor demonstration trajectories 
+% with $T+1$ time steps: $\tau^i=(\bx_0^i, \bu_0^i, \ldots, \bx_T^i, \bu_T^i)\in (\mathcal{X}\times\mathcal{U})^{T+1}$ for $i\in \{0, \ldots, N_0\}$
+% mapping states to control
+% inputs is provided. DAgger solves the following optimization problem with respect to the surrogate loss function:
 
@@
 \begin{align}\label{eq:super_objj}
-\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{N_0}\sum_{t=0}^T l(\pi_{\theta}(\bx_t^{i}),\bu_{t}^i).
+\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{M} l(\pi_{\theta}(\bx_i),\bu_i).
 \end{align}
 
-This problem can be considered as a supervised learning problem which can be solved using standard machine
+\adnote{simplified D above to just be pairs so that shiv makes sense too, as it doesnt add full trajectories}
+This problem can be treated as a supervised learning problem which can be solved using standard machine
 learning techniques, for example a support vector machine or a neural network.
@@
 used to control the smoothness of the function that is fit to the sampled data.
-In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.
+In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.\adnote{is this just us or also dagger?}
 
- \subsubsection{Step 2}
-DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\theta_{k=1}$.
+ \subsection{Step 2}
+The second step starts in boht SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.
+
+What happens next, however, differs.
 For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
-Formally, for a given sampled trajectory  $\tau = (\bx_0,\bu_0,...,\bx_T,\bu_T )$.
-The supervisor provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
-The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$. 
-\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
+Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \pi(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
+The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
+$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
+%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
+
+Providing correct control inputs or ``labeling'' at each
+iteration and each state in DAgger can be tedious, imposing a large burden on the supervisor.
+\adnote{add in the discussion that another advantage of measuring risk is the early termination which can avoid disaster}
+Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of \emph{risk} to actively \emph{decide} whether a label is necessary.
+For every state encountered $\bx_t$, it applies a \emph{decision function} $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which will capture how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.
+
+SHIV only asks for supervision on states for which $g(\bx)=-1$: \adnote{don't know what a good way to mention the termination condition is, maybe just a footnote or in discussion at the end as an advantage}
+$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$
 
 Steps 1 and 2 are repeated for $K$ iterations or until 
-the cumulative surrogate is smaller than some predefined threshold\footnote{In the orginal DAgger the policy rolled out
+the cumulative surrogate is smaller than some predefined threshold\footnote{In the original DAgger the policy rolled out
 was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
-or the robots. The use of this stochasitically mix policy was for theoretical analysis. In practice, it is recommended
+or the robots. The use of this stochastically mix policy was for theoretical analysis. In practice, it is recommended
 to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.
 
-Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore under the assumption of the policy being no regret has theoretical properties of being linearly in time horizon T to the supervisor's policy.
-\fpnote{How about: Dagger has been experimentally shown to perform well in both simulation and real world
-    experiments. Under a technical `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
-deduced error bounds on the expected loss which scale linearly in the time horizon $T$.}
+Dagger has been experimentally shown to perform well in both simulation and real world
+    experiments\cite{}\adnote{cite}. Under a `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
+deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically.
+For a conservative threshold $\rho$ on risk, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary.
+However, if $\rho$ is too high, then SHIV will not collect new that that is needed and revert back to the performance of offline methods.
+We analyze the dependence on $\rho$ in our experimental section.
+Our results suggest that SHIV is robust to this parameter selection.
+\adnote{must add this experiment!}
 
-However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
-quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
+\subsection{Measuring Risk}
+
+\adnote{somewhere in this section refer to the second figure}
+
+% However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
+% quad-copter, the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
 We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
 previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so that the state, although visited, does
-not model the supervisor's control inputs correctly. Furthermore providing correct control inputs or ``labeling'' at each
-iteration and each state in DAgger can be tedious or costly.
+loss \cite{tokdar2010importance}, or 2) the surrogate loss of the current policy at the current state is high, so that the state, although visited, does
+not model the supervisor's control inputs correctly.
 
-To address these limitations, we propose to 1) avoid highly risky states entirely by early termination of the policy
-roll-outs that enter these regions and 2) to recognize non-risky states and to not request supervisor input for these,
-thereby reducing the burden on the human trainer.
+% To address these limitations, we propose to 1) avoid highly risky states entirely by early termination of the policy
+% roll-outs that enter these regions and 2) to recognize non-risky states and to not request supervisor input for these,
+% thereby reducing the burden on the human trainer.
 
-One way to do this is to define risk in terms of distance to a nearest neighbor, but this approach is vulnerable to
-outliers in the known set of states. Another option is to fit a density to the known set of states, which requires an
-exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}. We propose using a
+%One way to do this is to define risk in terms of distance to a nearest neighbor, but this approach is vulnerable to
+%outliers in the known set of states. Another option is to fit a density to the known set of states, which requires an
+%exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}.\adnote{this stuff is in the related work too}
+
+To evaluate risk in high-dimensional state spaces (such as HOG features on images, like in our driving simulator testcase), we use
 modified version of the technique known as the One Class SVM that implicitly approximately estimates a boundary of a user defined quantile of
 a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
-\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}
+%\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}
 
-\subsection{Estimation of Quantile Level Sets}\label{sec:level}
+%\subsection{Estimation of Quantile Level Sets}\label{sec:level}
 \fpnote{my git commit on this section was overwritten by an old commit at version 10 - reintroduced modifications here,
@@
 
-Where, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
+Here, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
 $g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
@@
 
-Our corresponding decision function $g:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n
-\alpha_i y_i k(\bx_i,\bx) - \rho$. To compute the $\rho$ term, we leverage the fact that for an optimal solution the
+Our corresponding decision function $g:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $$g(\bx) = \sum_i^n
+\alpha_i y_i k(\bx_i,\bx) - \rho$$
+To compute the $\rho$ term, we leverage the fact that for an optimal solution the
 inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
@@
 explain this more --]}.
+
+Our experiments analyze the performance of risk as a query selection strategy, with our without the addition of the second risk criteria --- regions of space where the surrogate loss is high.
 
@@
 %Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
-To reduce the burdon on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
+To reduce the burden on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
 $\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
@@
 The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
-resulting risk-aware quantile super-levelset and we terminate roll-outs that are at a task-specific threshold $r(\bx) = \sum_i^n
-\alpha_i \bx_i k(\bx_i,\bx)-\rho>r_0$ away from the decision boundary $g$ corresponding to this modified super-levelset.
+resulting risk-aware quantile super-levelset.
 

### 2015-08-22 paper.tex
added experiments surgical, improved figure

--- 2015-08-21 paper.tex
@@
 
-\newcommand{\fpnote}[1]{\ifthenelse{\boolean{include-notes}}%
- {\textcolor{blue}{\textbf{FP: #1}}}{}}
-
 \renewcommand{\baselinestretch}{.99}
@@
 \begin{abstract}
-Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system
-dynamics and reward functions are unknown. However, they impose a burden on supervisors to demonstrate labels (control
-signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
-algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
+Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system dynamics and reward functions are unknown.
+However, they impose a burden on supervisors to demonstrate labels (control signals) as the robot encounters new states when iteratively executing its new best policy.
+We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
 SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
@@
 
-\caption{An illustrative example of different active learning techniques. The shaded and empty circles represent
-different labeled classes $0$ and $1$. The red empty circles represent label $1$, but are encountered on a different
-distribution then what was trained on
-{\color{blue} FP:can we make this more formal sounding? Represent samples from a different distribution?} 
-As illustrated, Confidence and Query by Committee methods
-measure
-{\color{blue} FP:estimate} states far away from the decision boundary of the estimator as having low risk,
-however novelty detection methods measure {\color{blue} FP:estimate} the level of risk as
-{\color{blue}FP:by} how far a point is from the trained data. Our
-modified risk method attempts to measure risk both as a function of how far it
-{\color{blue}it gramatically refers to risk,
-but you mean sample "it$\mapsto$a sample"?} is from data trained on
-{\color{blue}grammatically strange$\mapsto$from the training data} and the decision boundary of the estimator. 
+\caption{An illustrative example of different active learning techniques.
+The shaded and empty circles represent different labeled classes $0$ and $1$.
+The red empty circles represent label $1$, but are encountered on a different distribution then what was trained on.
+As illustrated, Confidence and Query by Committee methods measure states far away from the decision boundary of the estimator as low risk, however novelty detection methods measure the level of risk as how far a point is from the trained data.
+Our modified risk method attempts to measure risk both as a function of how far it is from data trained on and the decision boundary of the estimator.
 }
@@
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
-We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or
-continuous. We assume that Markovian dynamics, such that the the probability of state $\mathbf{x_{t+1}}\in
-\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
-\mathcal{U}$. Under this assumption $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
-We denote the probability density over the initial state also by $p:\mathcal{X}\to
-\mathbb{R}$. By a trajectory, we mean a finite series of pairs of $T$ states visited and corresponding
-control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
+We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
+nature\adnote{avoid filler words like in nature}. The environment is
+modeled\adnote{avoid passive voice; sidd always asked me whenever i wrote that "X is done": "done by who?
+by jesus?"} to have dynamics that are stationary\adnote{why stationary?
+what does this mean?} and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
+\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
+so that\adnote{this sentence already contained a so that; break long sentences} $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
+When no confusion arises\adnote{what is confusion arising}, we denote the probability density over the initial state also by $p:\mathcal{X}\to
+\mathbb{R}$. By a trajectory, we mean \adnote{new par, a trajectory is a finite ...}a finite series of pairs of $T$ states visited and corresponding
+control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
 and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
-For a given trajectory $\tau$ as above, we denote by $\hat{\tau}$ the corresponding trajectory in state space,
-$\hat{\tau} = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.
+At times we will also consider trajectories in state space only\adnote{this makes you seem floppy; do we need this?
+if so maybe denot by something else, like $\bar{tau}$ and call it a full trajectory vs a state trajectory}, in which case a trajectory corresponds
+to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.
 
-A policy is a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
-We consider a space of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
-parameter $\theta\in \mathbb{R}^d$. Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
+By a policy, we mean\adnote{a policy is a function} a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
+We shall\adnote{we search in a space of parametrized policies} in particular consider classes of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by a
+parameter $\theta\in \mathbb{R}^d$ corresponding to support vectors of a Support Vector Machine (SVM).\adnote{this is not a requirement that it's the svm necessarily, can be whatever estimator}
+Any such policy, $\pi_{\theta}$ \adnote{missing comma here?} in an environment with probabilistic initial state density and Markovian dynamics
 induces a density on state-space trajectories of length $T+1$: $p(\tau | \theta)=
@@
 
-Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ for $t-1$ time steps. This density can be computed by marginalization: $p(\bx_t|\theta) =
+\adnote{Let} $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
+$\pi_{\theta}$ for $t-1$ time steps\adnote{break sentence. This can be computed by marginalizing ... (explain in words first)} which can be calculated by marginalization $p(\bx_t|\theta) =
 \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction},
@@
 While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
-\bx)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
-$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
-Therefore, when 'rolling out' trajectories under a policy
-$\pi_{\theta}$, we utilize the robot or a simulator to sample the resulting stochastic trajectories rather than
+\bx)$ or $p(\bx|\theta)$, but\adnote{while.., but..
+doesn't make sense; "We do not assume...
+Instead, we assume that..."} instead assume that we have a stochastic real robot or a simulator such that for any state
+$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ such that\adnote{redundant; we can sample b from $p(b......$"} $\bx_{t+1}$ follows the distribution corresponding
+to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$.
+In particular\adnote{this is not really in particular; I think you should just say therefore, when rolling out..}, when 'rolling out' trajectories under a policy
+$\pi_{\theta}$, we utilize the robot or simulator to 'sample' the resulting stochastic trajectories rather than
 estimating $p(\bx|\theta)$ itself.
 
-Typically, the objective of policy learning is to find a policy that minimizes some known cost function
-$C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
+Typically, the objective in policy learning can be framed\adnote{can be framed by great justice; suggest: typically, the objective of policy learning is to find a policy that minimizes some known cost function:} as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$
+of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
 \mathcal{U})^{T+1}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
@@
 be considered \cite{levine2015end}.
-In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to a
-a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$. We are furthermore given
+In our present setting\adnote{in lfd, the robot does not have access to the cost function itself.
+Instead, it only has access to a ...}, we do not know the cost function itself, but instead have access to a "supervisor",
+an algorithm or human\adnote{don't start the enumeration with algoirhtm and put human second in a paper motivated by reducing supervisory load, which is more important with human supervision} that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
 an initial set of $N$ stochastic demonstration trajectories $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
-which are the result of the supervisor applying this policy.
+which are the result of the supervisor applying this policy. \adnote{sentences too long, break them up}
 
-Next, we define a `surrogate' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+Next, we define a ``surrogate'' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
 measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$,
@@
 of high probability under $\pi_\theta$ by sampling via policy `roll outs' from $p(\bx|\theta)$. 
-\fpnote{DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
-made more precise then and refer to the algorithm}
+{\color{blue} [-- F: DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
+made more precise then and refer to the algorithm --]}
 
 \subsubsection{Step 1}
-\fpnote{this is really start of iteration `i', as we circle back}
 At iteration $k=0$ an initial dataset $\mathcal{D}_0$ of $N_0$ supervisor demonstration trajectories 
@@
 
-This problem can be considered as a supervised learning problem which can be solved using standard machine
+This problem can be considered as a supervised learning problem in particular and can be solved using standard machine
 learning techniques, for example a support vector machine or a neural network.
@@
 To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
+{ \color{blue} [-- F: Make precise --]}
 can be considered as present in policy's output. We employ a regularization technique in the optimization which is
@@
 The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.
-\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
 
-Steps 1 and 2 are repeated for $K$ iterations or until 
-the cumulative surrogate is smaller than some predefined threshold\footnote{In the orginal DAgger the policy rolled out
-was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
-or the robots. The use of this stochasitically mix policy was for theoretical analysis. In practice, it is recommended
-to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.
+Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss approaches zero. Since DAgger
+requires rolling out the policy at each iteration, one way to terminate the algorithm is when the performance of the
+rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined
+threshold $\gamma$ \footnote{In the orginal DAgger the policy rolled out was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action or the robots.
+The use of this stochasitically mix policy was for theoretical analysis.
+In practice, it is recommended to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}
 
 Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore under the assumption of the policy being no regret has theoretical properties of being linearly in time horizon T to the supervisor's policy.
-\fpnote{How about: Dagger has been experimentally shown to perform well in both simulation and real world
-    experiments. Under a technical `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
-deduced error bounds on the expected loss which scale linearly in the time horizon $T$.}
-
-However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
+However, policy rollouts can result in the robot entering dangerous states. For example, when DAgger was used on a
 quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
 We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
-previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so that the state, although visited, does
+previously trained states, which potentially means our policy will mis-predict the supervisor and incur high surrogate
+loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so the state, although visited, does
 not model the supervisor's control inputs correctly. Furthermore providing correct control inputs or ``labeling'' at each
@@
 
-To address these limitations, we propose to 1) avoid highly risky states entirely by early termination of the policy
-roll-outs that enter these regions and 2) to recognize non-risky states and to not request supervisor input for these,
+To address these limitations, we propose to 1) avoid highly risky states entirely by early termination the policy
+roll-out that enter these regions and 2) to recognize non-risky states and to not request human input for these,
 thereby reducing the burden on the human trainer.
@@
 a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
-\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}
 
 \subsection{Estimation of Quantile Level Sets}\label{sec:level}
-\fpnote{my git commit on this section was overwritten by an old commit at version 10 - reintroduced modifications here,
-Michael, please check this is still accurate with recent modifications}
-We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
-independent and identically distributed samples $\mathbf{x}_1,...,\mathbf{x}_n\in \mathcal{X}$.
-In most general terms, the quantile function for $P$ and subject to a class of measurable subsets $\mathcal{G}$ of $\mathcal{X}$ is
-defined by
+Support estimation can be defined as minimizing a function that contains the volume of a given probability distribution.
+Formally we define it as follows let $\mathbf{x}_1,...,\mathbf{x}_n $ be i.i.d.
+random variables in a set $\mathcal{X}$ with distribution $P$.
+Let $\mathcal{G}$ be a class of measurable subsets of $\mathcal{X}$ and let $\lambda$ be a real function defined on $\mathcal{G}$.
+The quantile function with respect to $(P,\lambda,\mathcal{G})$ is
+
+\vspace{-2ex}
 \begin{align}\label{eq:quantile}
@@
 \end{align}
-$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure which most commonly is given by the Lebesgue measure.
-Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
-measure (i.e. volume) for each $\gamma\in [0,1]$ (this set is in general not necessarily unique). 
-$G(\gamma)$ denotes a set of minimum measure $G \in \mathcal{G}$ with $P(G(\gamma))\ge \gamma$. Note in particular that $G(1)$ is the support of the density $p$ corresponding to $P$, if $p$ exists.
 
-To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al.
+We denote by $G(\gamma)$ the $G \in \mathcal{G}$ that attains the infinimum.
+The most common choice of $\lambda$ is Lebesgue measure, in which case $G(\gamma)$ is the minimum volume $G \in \mathcal{G}$ that contains at least a fraction $\gamma$ of the the probability mass.
+Thus, $G(1)$ is the support of the density $p$ corresponding to $P$, assuming it exists.
+
+To handle high dimensional densities $P$, work by Scholk{\"o}pf et al.
 looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}.
-By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
-derives an approximation of the quantile function described in Eq. \ref{eq:quantile}, which in particular has rigorous
-convergence guarantees asymptotically when a normalized Gaussian kernel $k$ is chosen and bandwidths decay at an
-appropriately chosen rate as the number of samples tends to infinity \cite{vert2006consistency}.
-This approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$,
-$f_w(\mathbf{x}) = \sum_i w_i k(\mathbf{x}_i, \mathbf{x})$
-and $(w,\rho)$ denote the weight vector and offset parameterizing a hyperplane in the feature space associated with a
-Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}$.
+They then minimize a SV  regularizer which, using a kernel, controls the smoothness of the estimated function describing $G$.
+In terms of the quantile function described in Eq.
+\ref{eq:quantile}, the approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$.
+Here $(w,\rho)$ are a weight vector and offset parameterizing a hyperplane in the feature space associated with a kernel.
 
-Let $\Phi:\mathcal{X}\to \mathcal{F}$ denote the feature map corresponding to our exponential kernel, mapping the
-observation space $\mathcal{X}$ into a Hilbert space $(\mathcal{F}, \langle, \rangle)$ such that $k(\bx, \bx') = \langle
-\Phi(\bx), \Phi(\bx')\rangle$.
+Let $\Phi$ be a feature map $\mathcal{X} \rightarrow \mathcal{F}$, i.e.
+a map into an inner product space $\mathcal{F}$ such that the inner product in the image of $\Phi$ can be computed by evaluating some  kernel
 
-The One Class SVM proposed by \cite{scholkopf2001estimating} determines a hyperplane in feature space $\mathcal{F}$
-maximally separating the input data from the origin:
+\vspace{-2ex}
+\begin{align}
+k(\bx_0,\bx_1) = \langle\Phi(\bx_0),\Phi(\bx_1)\rangle
+\end{align}
+
+such as the Gaussian kernel
+
+\vspace{-2ex}
+\begin{align}
+k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}
+\end{align}
+
+The main idea is to solve an optimization problem that separates the origin, we solve the following quadratic problem:
+
 \vspace{-2ex}
 \begin{align}\label{eq:primal_sup}
-    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
+\underset{w\in F, \mathbf{\xi} \in \mR, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
+\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag
 \end{align}
 
-Here, the parameter $\nu$ controls the penalty or `slack term' and asymptotically approaches $\gamma$ \cite{vert2006consistency}
-in the quantile definition when bandwidths decay at appropriate rates as the number of samples increases. The decision
-function, determining point membership in the approximate quantile levelset is given by
+The parameter $\nu$ controls the penalty on slack terms and asymptotically approaches is equivalent to $\gamma$ \cite{vert2006consistency}.  The decision function then becomes
 
@@
 \begin{align}\label{eq:decision_func}
-g(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
+g(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho)
 \end{align}
 
-Where, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
-$g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
-if $x$ lies strictly in the quantile sub-levelset. The dual form of the optimization yields a Quadratic Program 
-that can be solved efficiently \cite{scholkopf2001estimating}.
+Where $g(x) = 1$ indicates in the support region and $(g) = -1$ denotes being outside the support region.
+The dual form of the optimization takes the form of a Quadratic Program with respect to the Gram Matrix \cite{scholkopf2001estimating}.
 
-For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
-a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available.
-However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
-optimizing Eq. \ref{eq:super_objj} may still incur a large surrogate loss. To account for this, we propose a
-modification to the One Class SVM:
+Estimating the level set of a distribution can be a measure of the generalization ability of $\pi_{\theta}$ to points not within $\mathcal{D}$.
+However, it does not account for the fact that for a given $\theta$ or  solution to Eq.
+\ref{eq:super_objj}.
+$\pi_\theta$ may not correctly match the supervisor's controls for all points train on.
+To account for this, we propose a modification to the One Class SVM denote:
 
@@
      \begin{array}{lr}
-         1 & : l(\pi_{\theta}(\bx_i),\bu_i)\le \varepsilon\\
-         -1 & : l(\pi_{\theta}(\bx_i),\bu_i)>\varepsilon
+       1 & : \pi_{\theta}(\bx_i) =\bu_i\\
+       -1 & : \pi_{\theta}(\bx_i) \neq \bu_i
      \end{array}
@@
 \end{align}
-Where, in the case when $l$ denotes discrete $0-1$ loss, we set $\varepsilon = 0$, while in the continuous $L_2$ loss
-case, $\varepsilon$ is a user defined threshold specifying allowable surrogate loss.
-We use $y_i$ to modify the One Class SVM optimization objective as follows:
+
+or $y_i$ is $1$ if the control applied matches the supervisor and $-1$ if it differs.
+In the regression case the decision between $1$ and $-1$ can be set by a some threshold on a L2-norm or $||\pi_{\theta}(\bx_i)-\bu_i||$.
+We use $y_i$ to modify the optimization as follows:
 
@@
 \begin{align}\label{eq:primal_sup}
-    \underset{w\in F, \mathbf{\xi} \in \mathbb{R}^l, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}.
+\underset{w\in F, \mathbf{\xi} \in \mR^l, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
+\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}
 \end{align}
 
-States that incur loss above the $\varepsilon$ threshold are then enforced to lie on the opposite side of the
-hyper-plane separating the origin from the data in the feature space. Practically, this modification corresponds to
-`carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
-exluded from the super-levelset.
+Points that are mis-predicted are then enforced to lie on the opposite of the hyper-plane in the feature space $\phi(\bx)$, which carves out holes in the support region around them.
+The dual formulation, which is what is solved in practice, can be derived as
 
-The dual formulation to the modified optimization problem, which is solved in practice, is 
+\vspace{-2ex}
 \begin{align}\label{eq:dual_sup}
-\underset{\alpha_i\in \mathbb{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
-\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1.
+\underset{\alpha\in \mathcal{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
+\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1 
 \end{align}
 
-Our corresponding decision function $g:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n
-\alpha_i y_i k(\bx_i,\bx) - \rho$. To compute the $\rho$ term, we leverage the fact that for an optimal solution the
-inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
-can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating} {\color{blue} [-- F:
-explain this more --]}.
+Our decision boundary function $g(\bx)$ is then derived in terms of the support vectors as $g(\bx) = \sum_i^n \alpha_i y_i k(\bx_i,\bx) - \rho$.
+To compute the $\rho$ term,we leverage the fact that for an optimal solution the inequalities in Eq.
+\ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$.
+Therefore we can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating}.
 
-\subsection{The \acro~algorithm}
+\subsection{SHIV: SVM-Based Reduction in Human Intervention}
 
-Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
-predict the supervisor's control, by means of the thresholded surrogate just discussed.  
-% Too vague:
-%In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
-%Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
-To reduce the burdon on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
-$\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
-above a threshold $\varepsilon$ chosen by the user.
-The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
-resulting risk-aware quantile super-levelset and we terminate roll-outs that are at a task-specific threshold $r(\bx) = \sum_i^n
-\alpha_i \bx_i k(\bx_i,\bx)-\rho>r_0$ away from the decision boundary $g$ corresponding to this modified super-levelset.
+Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the supervisor's control,which we define as the region of low risk.
+In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.
+Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the supervisor provide labels when the robot leaves this boundary.
+Furthermore to avoid entering pathological states that are far from the supervisor's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$.
+The risk threshold, $r_0$, is user defined based on the task.
 
-{\color{blue} [-- F: use formal algorithm and explain here instead --]} 
 \subsubsection{Step 1}
-
-Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
-by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
-training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
-This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.
+Similar to DAgger at iteration $k$ the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$ by solving Eq.
+\ref{eq:super_objj}.
+We then estimate the level set of the distribution being trained on by solving the optimization for the One Class SVM or $\ref{eq:primal_sup}$ on the dataset $\mathcal{D}_k$.
+We now have a decision boundary $g_k(\bx)$, which is $1$ if the region is in the low risk area and $-1$ otherwise .
+The parameter $\nu$ is an estimate of how much probability mass is contained in the level set and can be use to control the size of the low risk region.
 
  \subsubsection{Step 2}
- In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
- robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
- above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
- provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
- dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.
-
-We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
-between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
-supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
-incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
-areas and obtain more labels from the supervisor in those regions.
+ In DAgger the policy that was rolled out is $\pi_{\theta_k}$, however this could potential encounter pathological states that are far from the initial set of demonstrations $\mathcal{D}_0$.
+To prevent this we terminate the rolled out policy if the risk, or distance from the support, is above some threshold $r(\bx_t) > r_0$.
+Furthermore, instead of labeling every state now the supervisor is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.
+These states are then added to the dataset $\mathcal{D}_{k}$
 
 \section{Experiments}
-\fpnote{Michael, please also compare my comments git version 273ecde - those changes got overwritten when merging and
-had some improvements in style}
+All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
+1600 MHz memory in Python 2.7. The policies, $\pi_\theta$ were represented using either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
+
 \subsection{Driving Example}
@@
 
-To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
+To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane \cite{tong2002support}.
 The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-We measured the performance of our modified One Class SVM to the confidence measure, in terms of how many states are estimated to be of low risk (i.e.
+We further compared against Query By Committee, which was trained via bagging \cite{}.
+Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on.
+If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
+We finally compared our combined risk approach against the traditional One Class SVM without the "hole-punching".
+We measured the performance in terms of how many states are estimated to be of low risk (i.e.
 correctly classified) and are of actually high risk on the first policy roll out.
-Results  are averaged over 50 tracks and shown in Table \ref{table:active_comp}.
+Results  are averaged over 50 tracks and shown in Fig.
+\ref{fig:active_comp}.
 
@@
 \includegraphics[width=9cm, height=8cm]{figures/risk_bar.eps}
-   \caption { \footnotesize  To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane.
-The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-We measured the performance of our modified One Class SVM to the confidence measure, in terms of how many states are estimated to be of low risk (i.e.
+   \caption { \footnotesize To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyper plane \cite{tong2002support}.
+The threshold was set to the average distance from the hyper plane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
+We further compared against Query By Committee, which was trained via bagging \cite{}.
+Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on.
+If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
+We finally compared our combined risk approach against the traditional One Class SVM without the "hole-punching".
+We measured the performance in terms of how many states are estimated to be of low risk (i.e.
 correctly classified) and are of actually high risk on the first policy roll out.
-Results  are averaged over 50 randomly generated tracks.
+Results  are averaged over 50 tracks.
    }
@@
 We look at having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
+Grasping in clutter can be a challenging task because as shown in Kiteav et al.
+traditional motion planning techniques require knowledge of how the objects will behave when in contact.
+They used iLQR with a hand tuned cost function and dynamics given by a physics simulator to successfully grab an object without displacing the other movable objects on the table off \cite{kitaevphysics}.
+We are interested in learning such a policy via human demonstrations.
 We used Box2D a physics simulator to model the virtual world.
@@
 For input the human demonstrator provides controls through an XBox controller.
-The left and right joystick determined the x and y velocity of the center of the end effector.
-The left bumper of the controller provided a binary input for opening and closing the gripper.
+The right joystick contains two principle components that determine the x and y velocity of the center of the end effector.
+The left bumper is a binary value for opening the gripper and the right bumper is a binary value for closing the gripper.
+Thus, the set of controls is the following tuple $\mathcal{U} = \lbrace [-1,1],[-1,1],\lbrace 0,1 \rbrace, \lbrace 0, 1\rbrace \rbrace$.
 
-\todo{double check this section with Sammy}
-Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, 1 being opened and zero being closed.
-For our representation of $\pi_{\theta}$, we used linear ridge regression.
-We defined two cost functions, $C(\bx,\bu)$, as the sum of the number of objects knocked off the table and 1 for not successfully grasping the target object.
+Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, $1$ being fully closed and $0$ being opened.
+For our representation of $\pi_{\theta}$, we used kernelized ridge regression with the radial basis function as the kernel with the default Sci-Kit learn parameters.
+We defined the cost functions, $C(\bx,\bu)$, as the sum of the number of objects knocked off the table plus $10$ times the binary value indicating if the object is grasped or not.
+The order of magnitude difference in cost for grasping the object is to place emphasize on that portion of the task.
 
-In experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out.
+In our experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out.
 At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
@@
 
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth, height=6cm]{figures/grasp_clutter.eps}
+\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
+In Fig.
+\ref{fig:car_cost}, we plot the performance of DAgger and SHIV without the modification.
+Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig.
+\ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
+\vspace*{-10pt}
+\label{fig:car_cost}
+\end{figure}
+
 \subsection{Surgical Experiment}
-\todo{Need help discussing this better}
+\todo{Getting a paper from Animesh to motivate this}
 In this experiment, we look at the task of inserting a needle into tissue in preparation for suturing.
@@
 Dr.
-Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose and applied the neccesary corrections to achieve a correct pose.
+Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose $P_0$ and applied the necessary corrections to achieve a goal pose $P_G$.
 We used three of these demonstrations as our initial dataset $\mathcal{D}_0$.
 Dr.
-Boyd couldn't be around for the interactive labeling of both SHIV and DAgger, so we had to hardcore and expert controller that computed the transformation between the desired insertion pose and the current pose.
-We did this by calculating the inverse of a transformation matrix.
+Boyd couldn't be around for the interactive labeling of both SHIV and DAgger, so we had to hand design an expert controller that computed the transformation between the desired insertion pose and the current pose.
+We did this by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
+We then converted $C$ to the associated lie algebra vector $c \in \mathcal{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control $c_D$ Doug Boyd applied to the robot.
+
+For trials we sample a start position from a Gaussian on the translational component of $P_0$ with isotropic variance of  $0.1$ cm.
+The distance between initial $P_0$ and $P_G$ is roughly $3$ cm.
+Our cost function $c(\bx,\bu)$ is measured in terms of Euclidean distance in translational component, which is in centimeters.
+We run DAgger and SHIV both for 20 iterations and average over 40 rounds.
+Initial results show in Fig.
+\ref{figures/needle_insertion_results.eps} suggest a reduction $67\%$ in the amount of human inquiries needed.
 
@@
 In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger, SHIV and SHIV using only the traditional One-Class SVM without the modification.
+\ref{fig:car_cost}, we plot the performance of DAgger and SHIV without the modification.
 Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig.
@@
 \vspace*{-10pt}
-\label{fig:car_cost}
+\label{fig:needle}
 \end{figure}
@@
 This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536 and NSF-Graduate Research Fellowship.. 
-We thank UC Berkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Siddarth Sen, Steve McKinley and Sergey Levine.
+We thank UC Berkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Siddarth Sen, Steve McKinley, Sachin Patil and Sergey Levine.
 

### 2015-08-22 paper.tex

--- 2015-08-22 paper.tex
@@
 \includegraphics[width=\columnwidth]{figures/teaser.pdf}
-\caption{ \adnote{make this a 2 by 2 grid; a b c d, where d is the result; make the result graph more square}
+\caption{ 
 For a given budget of human supervision, SHIV improves performance (reduced policy cost) in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a surgeon's demonstrations of correcting a needle before suturing in surgery.
@@
 \vspace*{-10pt}
-\label{fig:dis_traveled}
+\label{fig:teaser}
 \end{figure}
@@
 
-\caption{\adnote{A comparison of different query selection strategies for active learning on a non-stationary distribution.
+\caption{A comparison of different query selection strategies for active learning on a non-stationary distribution.
 The shaded and empty circles are training data from two classes, $0$ and $1$ respectively.
@@
 In contrast, we use a strategy that is amenable to non-stationary distributions by assigning high risk to novel states (c) and states in historically mislabeled regions.
-}
 %Confidence and Query by Committee methods measure
@@
 \section{Experiments}
-\fpnote{Michael, please also compare my comments git version 273ecde - those changes got overwritten when merging and
-had some improvements in style}
+All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
+1600 MHz memory in Python 2.7. The policies, $\pi_\theta$ were represented using either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
+
 \subsection{Driving Example}
-A common benchmark in Reinforcement Learning  is a car driving around a track avoiding other cars \cite{argall2009survey}.
+A common benchmark in Reinforcement Learning  is a car learning to drive around a track  \cite{argall2009survey}.
 To illustrate our methods ability in high dimensions, the car must follow a polygonal track using only HOG features extracted from images.
@@
 For input the human demonstrator provides controls through an XBox controller.
-The left and right joystick determined the x and y velocity of the center of the end effector.
-The left bumper of the controller provided a binary input for opening and closing the gripper.
+The right joystick contains two principle components that determine the x and y velocity of the center of the end effector.
+The left bumper is a binary value for opening the gripper and the right bumper is a binary value for closing the gripper.
+Thus, the set of controls is the following tuple $\mathcal{U} = \lbrace [-1,1],[-1,1],\lbrace 0,1 \rbrace, \lbrace 0, 1\rbrace \rbrace$.
 
-\todo{double check this section with Sammy}
-Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, 1 being opened and zero being closed.
-For our representation of $\pi_{\theta}$, we used linear ridge regression.
-We defined two cost functions, $C(\bx,\bu)$, as the sum of the number of objects knocked off the table and 1 for not successfully grasping the target object.
+Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, $1$ being fully closed and $0$ being opened.
+For our representation of $\pi_{\theta}$, we used kernelized ridge regression with the radial basis function as the kernel with the default Sci-Kit learn parameters.
+We defined the cost functions, $C(\bx,\bu)$, as the sum of the number of objects knocked off the table plus $10$ times the binary value indicating if the object is grasped or not.
+The order of magnitude difference in cost for grasping the object is to place emphasize on that portion of the task.
 
-In experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out.
+In our experiment, we had our human demonstrator provide one demonstration and then iterated until the cost function was zero during the policy roll out.
 At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
 
-In Figure , we show both the cost function associated with knocking an object off the table and the one associated with being able to successfully grasp an object or not.
-\todo{Finalize results then discuss them}
+In Fig.
+\ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 trials for SHIV and DAgger.
+Initial results suggest we are able to achieve an approximate $70\%$ reduction in data.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth, height=6cm]{figures/grasp_clutter.eps}
+\caption{\todo{Might get more trials from Sammy tomorrow as well}We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
+In Fig.
+\ref{fig:car_cost}, we plot the performance of DAgger and SHIV without the modification.
+Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig.
+\ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
+\vspace*{-10pt}
+\label{fig:grasp_cost}
+\end{figure}
 
 \subsection{Surgical Experiment}
-\todo{Need help discussing this better}
-In this experiment, we look at the task of inserting a needle into tissue in preparation for suturing.
-Needle insertion can be a challenging task for surgeons and learning a controller to do so could alleviate some of the burden placed on surgeons.
-We collected data from a surgeon, Dr.
-Douglas Boyd, on the Da Vince Research Kit.
+Robotic Surgical Assistants (RSAs) are frequently used for procedures such as: prostectomy, uterectomy, and tumorectomies within the abdominal and thoracic cavities with high success rates~\cite{van2013laparoscopic,darzi2004impact} .
+Intuitive Surgical’s da Vinci Robotic Surgical Assistant, a type of RSA, facilitated over 570,000 procedures worldwide in 2014 across 3000 devices [5].
+Currently, these devices are controlled by surgeons via physical tele-operation at all times; introducing autonomy of surgical sub-tasks has the potential to reduce cognitive load
+and facilitate supervised autonomy for remote tele-surgerical procedures.
+
+Suture tying in surgery is a manually intensive task that can occur frequently through out a surgery.
+One important step in suture tying is properly placing a needle in an initial configuration for insertion.
+Misplacement of this the needle can lead to suture failure and potentially rupture the surrounding tissue \cite{liu2015optimal}.
+In this experiment, we are interested in learning a policy to correct bad initial poses to the proper insertion pose as shown in Fig.
+\ref{fig:support_example}.
+We had a surgeon, Dr.
+Douglas Boyd, demonstrate via tele-operation the correction strategies.
 
 Dr.
-Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose and applied the neccesary corrections to achieve a correct pose.
+Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose $P_0$ and applied the necessary corrections to achieve a goal pose $P_G$.
 We used three of these demonstrations as our initial dataset $\mathcal{D}_0$.
 Dr.
-Boyd couldn't be around for the interactive labeling of both SHIV and DAgger, so we had to hardcore and expert controller that computed the transformation between the desired insertion pose and the current pose.
-We did this by calculating the inverse of a transformation matrix.
+Boyd couldn't be around for the interactive labeling of both SHIV and DAgger, so we had to hand design an expert controller that computed the transformation between the desired insertion pose and the current pose.
+We did this by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
+Then converted $C$ to the associated lie algebra vector $c \in \mathcal{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control $c_D$ Doug Boyd applied to the robot.
+
+The policy $\pi_{\theta}$ was represented as kernel ridge regression with the default values given in Sci-Kit learn.
+The state $\mathcal{X}$ was  a 16 dimensional vector consisting of the elements in the pose $P$ vector.
+The control space $\mathcal{U}$ was a $\mathcal{R}^6$ vector representing the lie algebra group.
+The
+
+For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's label.
+The two $nu$ parameters where set to $0.1$ and $0.001$ for the good and bad support regions respectively.
+The sigma bandwidths, $\sigma$, in the rbf kernel were set to $2$ and $0.25$.
+
+For trials we sample a start position from a Gaussian on the translational component of $P_0$ with isotropic variance of  $0.1$ cm.
+The distance between initial $P_0$ and $P_G$ is roughly $3$ cm.
+Our cost function $c(\bx,\bu)$ is measured in terms of Euclidean distance in translational component, which is in centimeters.
+We run DAgger and SHIV both for 20 iterations and average over 40 rounds.
+Initial results show in Fig.
+\ref{figures/needle_insertion_results.eps} suggest a reduction $67\%$ in the amount of human inquiries needed.
 

### 2015-08-22 paper.tex
Updates from ShareLaTeX

--- 2015-08-22 paper.tex
@@
  \subsection{Step 2}
-The second step starts in boht SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.
+The second step starts in both SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.
 
@@
 deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically.
-For a conservative threshold $\rho$ on risk, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary.
-However, if $\rho$ is too high, then SHIV will not collect new that that is needed and revert back to the performance of offline methods.
-We analyze the dependence on $\rho$ in our experimental section.
+For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary.
+However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods.
+We analyze the dependence on $\sigma$ in our experimental section.
 Our results suggest that SHIV is robust to this parameter selection.
@@
 \begin{align}\label{eq:decision_func}
-g(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
+g_{\sigma}(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
 \end{align}
+\adnote{let's make sure we define $\sigma$ above}
 
@@
 
-Our corresponding decision function $g:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $$g(\bx) = \sum_i^n
+Our corresponding decision function $g_{\sigma}:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $$g_{\sigma}(\bx) = \sum_i^n
 \alpha_i y_i k(\bx_i,\bx) - \rho$$
@@
 
-\subsection{The \acro~algorithm}
+% \subsection{The \acro~algorithm}
 
-Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
-predict the supervisor's control, by means of the thresholded surrogate just discussed.  
-% Too vague:
-%In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
-%Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
-To reduce the burden on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
-$\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
-above a threshold $\varepsilon$ chosen by the user.
-The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
-resulting risk-aware quantile super-levelset.
+% Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
+% predict the supervisor's control, by means of the thresholded surrogate just discussed.  
+% % Too vague:
+% %In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
+% %Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
+% To reduce the burden on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
+% $\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
+% above a threshold $\varepsilon$ chosen by the user.
+% The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
+% resulting risk-aware quantile super-levelset.
 
-{\color{blue} [-- F: use formal algorithm and explain here instead --]} 
-\subsubsection{Step 1}
+% {\color{blue} [-- F: use formal algorithm and explain here instead --]} 
+% \subsubsection{Step 1}
 
-Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
-by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
-training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
-This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.
+% Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
+% by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
+% training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
+% This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.
 
- \subsubsection{Step 2}
- In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
- robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
- above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
- provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
- dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.
+%  \subsubsection{Step 2}
+%  In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
+%  robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
+%  above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
+%  provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
+%  dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.
 
-We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
-between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
-supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
-incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
-areas and obtain more labels from the supervisor in those regions.
+% We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
+% between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
+% supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
+% incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
+% areas and obtain more labels from the supervisor in those regions.
 

### 2015-08-22 paper.tex
.

@@
 
-\subsection{Driving Example}
-A common benchmark in Reinforcement Learning  is a car learning to drive around a track  \cite{argall2009survey}.
-To illustrate our methods ability in high dimensions, the car must follow a polygonal track using only HOG features extracted from images.
-If the car falls off the track, it is placed back on the center facing the angle of the polygonal track piece.
-We sample the polygonal track by drawing points from a Gaussian with a mean that is the centered of the video game work space.
-The convex hull of the sampled points is then computed.
-The car's control space $u = \lbrace -15^\circ, 0, 15^\circ \rbrace$ or 3 discrete commands that change the angle of the car.
-The internal state space of the car is xy-coordinates and the angle it is facing.
-Our supervisor is a solver that uses state space search through the driving simulator to plan the next control.
+\subsection{Car Simulator}
+A common benchmark in Reinforcement Learning is the problem of learning a policy for a car to drive around a track
+\cite{argall2009survey}. To illustrate our method's ability to scale to high dimensions we use high dimensional HOG features extracted from images
+as a state representation.
 
-We have the supervisor drive around the track 2 times and then collect the raw images observed.
-We use a Gaussian Pyramids to down sample the images to $125 \times 125$ RGB pixels and then extract Histogram of Oriented Gradients (HOG) features using OpenCV,  where the size of $\bx$ is $27926$.
-For both DAgger and SHIV, we use a Linear Support Vector Machine (SVM) as the policy representation, with the regularization term on the slack variable $\gamma=0.01$, which was set via cross validation on the initial training examples from our supervisor.
-For the optimization of Eq.
-\ref{eq:dual_sup} in SHIV we used a radial basis function as well for the kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
+We implemented a car simulator where the car must follow a polygonal track. If the car accidentally leaves the track, it is placed
+back on the center of the track at a nearby position. The car's control input space is given by  $\mathcal{U} = \lbrace
+-15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle of the car which drives at a unit speed. 
+The internal state space of the car is given by the
+xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
+state space search through the driving simulator to plan the next control .
+
+The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
+and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
+Oriented Gradients (HOG) features using OpenCV. This results in a $27926$ dimensional state space description.
+For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
+policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
+validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
+exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution. 
+{\color{blue} [-- F: what about $r_0$? --]}
 
@@
 
-We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
-In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger and SHIV.
-Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
-\ref{fig:car_cost} suggest a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
+defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
+In Fig. \ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.  We run 6 \fpnote{do we
+have large numbers of iterations in the final version, or is this the final one?} iterations \fpnote{define "iteration"
+how many simulation cycles/size of $T$?} of each algorithm over 40 different
+randomized polygonal tracks \fpnote{describe how you generated the tracks}. Figure \ref{fig:car_cost} presents averaged
+results from these experiments, suggesting a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger. 
+\fpnote{don't use "initial results" when talking about your main experiment - makes it sound too weak}
+
+\textbf{Comparison to active learning approaches:}
+\fpnote{Refer to figure 3 here and explain, also explain "prediction error" do you mean mean total surrogate loss,
+explain that you are using the scaled confidence intervals}
 
@@
 \centering
-\includegraphics[width=9cm, height=8cm]{figures/risk_bar.eps}
-   \caption { \footnotesize To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyper plane \cite{tong2002support}.
+\includegraphics[width=9cm, height=4cm]{figures/risk_bar.eps}
+\caption { \footnotesize {\color{blue}make this caption smaller, move discussion to main text} To compare our method against a traditional confidence based active learning approach, we
+       implemented a confidence measure based on the distance from the SVM hyper plane \cite{tong2002support}.
 The threshold was set to the average distance from the hyper plane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
@@
 \subsection{Grasping In Clutter}
-To illustrate how our technique can be used in the continuous case and with a human demonstrator. 
+To illustrate how our technique can be used the continuous case and with a human demonstrator. 
+\fpnote{avoid "look at" sound too informal and try to be as factual as possible - use investigate, consider}
 We look at having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
@@
 We are interested in learning such a policy via human demonstrations.
-We used Box2D a physics simulator to model the virtual world.
-The arm, shown in Fig.
-\ref{fig:box2d_arm}, consists of 3 degrees of freedom and has a parallel jaw gripper.
-For input the human demonstrator provides controls through an XBox controller.
-The right joystick contains two principle components that determine the x and y velocity of the center of the end effector.
+
+We used Box2D a physics simulator to model a virtual world. The arm, shown in Fig. \ref{fig:box2d_arm}, consists of 3
+degrees of freedom and has a parallel jaw gripper. \fpnote{the arm does not consist of kDOF - it has kdof, also add the
+    gripper - so it is 4dof: e.g.: We simulated a 4 DOF robot arm with three main joints and a parralel jaw gripper as
+displayed in Fig.X}
+
+For input the human demonstrator provides controls through an XBox controller. The right joystick contains two principle
+components that determine the x and y velocity of the center of the end effector. \fpnote{The right joystick was used to
+    provide horizontal and vertical velocity inputs for the center of the end-effector which were then translated into
+robot arm motions by means of a Jacobian transpose controller for the 3 main joint angles (was it?)}.
 The left bumper is a binary value for opening the gripper and the right bumper is a binary value for closing the gripper.
-Thus, the set of controls is the following tuple $\mathcal{U} = \lbrace [-1,1],[-1,1],\lbrace 0,1 \rbrace, \lbrace 0, 1\rbrace \rbrace$.
+\fpnote{The left `bumper' button on the joystic was used to provide a binary control signal to close the parralel jaw
+gripper} The control inputs are hence modelled by the set $\mathcal{U} = \lbrace [-1,1],[-1,1],\lbrace 0,1 \rbrace, \lbrace 0, 1\rbrace \rbrace$.
 
-Our state $\bx$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, $1$ being fully closed and $0$ being opened.
+A state $\bx\in \mathcal{X}$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, $1$ being fully closed and $0$ being opened.
 For our representation of $\pi_{\theta}$, we used kernelized ridge regression with the radial basis function as the kernel with the default Sci-Kit learn parameters.
@@
 
-In our experiment, we had our human demonstrator provide one demonstration and then iterated until the cost function was zero during the policy roll out.
+In our experiment, a human demonstrator provided one demonstration and then iterated until the cost function was zero during the policy roll out.
 At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
 
-In Fig.
-\ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 trials for SHIV and DAgger.
-Initial results suggest we are able to achieve an approximate $70\%$ reduction in data.
+In Fig. \ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 trials for SHIV and DAgger.
+Initial results suggest we are able to achieve an approximate $70\%$ reduction in data. \fpnote{instead of initial
+results suggest, say "in our experiment, ..." if you don't want to make the claim too strong. initial results sounds
+like the paper is not finnished}
 
@@
 
-Suture tying in surgery is a manually intensive task that can occur frequently through out a surgery.
-One important step in suture tying is properly placing a needle in an initial configuration for insertion.
-Misplacement of this the needle can lead to suture failure and potentially rupture the surrounding tissue \cite{liu2015optimal}.
-In this experiment, we are interested in learning a policy to correct bad initial poses to the proper insertion pose as shown in Fig.
-\ref{fig:support_example}.
-We had a surgeon, Dr.
-Douglas Boyd, demonstrate via tele-operation the correction strategies.
+Suture tying in surgery is a manually intensive task that can occur frequently through out a surgery. One important step
+in suture tying is properly placing a needle in an initial configuration for insertion. Misplacement of this the needle
+can lead to suture failure and potentially rupture the surrounding tissue \cite{liu2015optimal}. In this experiment, we
+are interested in learning a policy to correct bad initial poses to the proper insertion pose as shown in Fig.
+\ref{fig:support_example}. We had a surgeon, Dr. Douglas Boyd, demonstrate via tele-operation the correction strategies.
+\textbf{Sounds bossy - how about Dr. Douglas Boys, a surgeon at UCSF Medical XYZ, provided us with a collection of ...}
 
-Dr.
-Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose $P_0$ and applied the necessary corrections to achieve a goal pose $P_G$.
-We used three of these demonstrations as our initial dataset $\mathcal{D}_0$.
-Dr.
-Boyd couldn't be around for the interactive labeling of both SHIV and DAgger, so we had to hand design an expert controller that computed the transformation between the desired insertion pose and the current pose.
+Dr. Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose $P_0$ and
+applied the necessary corrections to achieve a goal pose $P_G$. We used three of these demonstrations as our initial
+dataset $\mathcal{D}_0$. Dr. Boyd couldn't be around \fpnote{too informal! also makes us sound weak. Since we were
+    limited to this dataset, and in order to study the convergence of our approach, we trained a synthetic
+... instead of executing ...}
+
+for the interactive labeling of both SHIV and DAgger, so we had to hand design \fpnote{aaa!
+- we chose...} an expert controller that computed the transformation between the desired insertion pose and the current pose.
 We did this by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
@@
 The state $\mathcal{X}$ was  a 16 dimensional vector consisting of the elements in the pose $P$ vector.
-The control space $\mathcal{U}$ was a $\mathcal{R}^6$ vector representing the lie algebra group.
-The
+The control space $\mathcal{U}$ was a $\mathcal{R}^6$ vector representing the Lie algebra.
 
 For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's label.
-The two $nu$ parameters where set to $0.1$ and $0.001$ for the good and bad support regions respectively.
-The sigma bandwidths, $\sigma$, in the rbf kernel were set to $2$ and $0.25$.
+The two $nu$ parameters where set to $0.1$ and $0.001$ for the good and bad support
+\fpnote{I don't think we introduced a notion of good and bad support regions - use formal language}
+regions respectively. The sigma bandwidths, $\sigma$, in the rbf kernel were set to $2$ and $0.25$.
 
-For trials we sample a start position from a Gaussian on the translational component of $P_0$ with isotropic variance of  $0.1$ cm.
-The distance between initial $P_0$ and $P_G$ is roughly $3$ cm.
-Our cost function $c(\bx,\bu)$ is measured in terms of Euclidean distance in translational component, which is in centimeters.
-We run DAgger and SHIV both for 20 iterations and average over 40 rounds.
-Initial results show in Fig.
-\ref{figures/needle_insertion_results.eps} suggest a reduction $67\%$ in the amount of human inquiries needed.
+For trials we sample a start position from a Gaussian on the translational component of $P_0$ with isotropic variance of
+$0.1$ cm. The distance between initial $P_0$ and $P_G$ \fpnote{earlier when you introduce $P_0$, $P_G$ describe how many
+and introduce a set- just 3 pairs, one per trajectory?} is roughly $3$ cm. Our cost function $c(\bx,\bu)$ is measured in
+terms of Euclidean distance in translational component, which is in centimeters. \fpnote{no notion of cost on
+rotations??} We run DAgger and SHIV both for 20 iterations and average over 40 rounds \fpnote{what's a 'round'?}.
+Initial results \fpnote{they are not initial if you submit them...} shown in Fig. \ref{figures/needle_insertion_results.eps} suggest a reduction $67\%$ in the amount of human inquiries needed.
 
@@
 \section{Discussions and Future Work}
+\fpnote{we'll need to work on this}
 SHIV currently provides a way to apply active learning to online imitation learning, however its use of level set estimation of the underlying distribution introduces several hyper parameters.
@@
 \section{Acknowledgments} 
+\fpnote{remove in the initial submission if we are pressed for space}
 This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536 and NSF-Graduate Research Fellowship.. 

### 2015-08-23 paper.tex
added Florian and Anca's comments, sensitivity analysis and final grasping in clutter results

@@
 
+  \newcommand{\mlnote}[1]{\ifthenelse{\boolean{include-notes}}%
+ {\textcolor{purple}{\textbf{ML: #1}}}{}}
+
 \renewcommand{\baselinestretch}{.99}
@@
 To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) 6DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
-Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of \adnote{fill in}).%[I hope more!
-- ken]
+We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
+Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of 70$\%$).
 
@@
 
-In \emph{model-free} robot learning from demonstration, a robot learns to perform a task, such as driving or grasping \adnote{we need to put this in fig 1 and refer to it here}, from examples provided by a competent \emph{supervisor}, usually a human.
-The problem is model-free\adnote{no dynamics model makes it model free, no reward is independent from that; suggest: in such problems, both the ...} if both the system dynamics and the reward function are unspecified, eg.
-dynamics model may be highly non-linear or noisy and the reward function may trade-off multiple factors and/or depend on future states.
-The robot must learn a policy mapping states to actions as it explores new states \adnote{not typical of model free lfd, instead the robot must learn a policy mapping states to actions from the demonstrated examples.}\cite{argall2009survey}.
+In \emph{model-free} robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig.
+\ref{fig:teaser}, from examples provided by a competent \emph{supervisor}, usually a human.
+The problem is model-free if  the system dynamics are unspecified, eg.
+dynamics model may be highly non-linear or noisy.
+In learning from demonstration, the cost function is usually unknown or non-continuous and difficult to learn with.
+The robot must learn a policy mapping states to controls as it observes the supervisor perform a task\cite{argall2009survey}.
 
@@
 
-\emph{On-line}\adnote{inconsistency here beetween offline and on-line instead of online} imitation learning approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+\emph{On-line} imitation learning approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
 In DAgger, a series of policies are learned.
-In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for the  new stats, which are then aggregated with the previous examples for the next iteration.
-The number of mistakes in DAgger scales linearly with the time horizon \cite{ross2010efficient}.
+In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for the  new states, which are then aggregated with the previous examples for the next iteration.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
+Theoretical analysis of DAgger have shown the number of mistakes to scale linearly for strongly convex loss functions.
 
@@
 
-Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that  has been historically misclassified.
+Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that  has been historically misclassified, which we know from our training data.
 %\adnote{Ken's version below does not seem to represent what we actually do.}
@@
 
-We compare SHIV with DAgger in three experiments: 1) a driving simulator, 2) 6DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
+We compare SHIV with DAgger in three experiments: 1) a driving simulator, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
 Our analysis suggests that compared to DAgger, SHIV learns a policy that performs significantly better given the same amount of human supervision.
-Conversely, SHIV significantly reduces supervisory burden (by a factor of \adnote{fill in}) while achieving the same performance.
+Conversely, SHIV significantly reduces supervisory burden (by a factor of $70\%$) while achieving the same performance.
 
@@
 \ref{fig:support_example}(a).
-An alternative to distance-based measures of confidence is query by committee \adnote{cite}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
+An alternative to distance-based measures of confidence is query by committee  \cite{breiman1996bagging}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
 Confidence here is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig.
@@
 online imitation learning violates the stationary distribution assumption because each new policy induces a new distribution of states.
-This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.\adnote{merged the two types since they have the same problem, and references the figure}
+This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.
 
@@
 Our results in Sec.
-\ref{}\adnote{fill in} suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (be it distance or query by committee based).
+\ref{sec:car} suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (be it distance or query by committee based).
 
@@
 Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ from time $0$ to time $t-1$.\adnote{shouldnt you then define this above insted of the probability of a trajectory?} This density can be computed by marginalization: $p(\bx_t|\theta) =
+$\pi_{\theta}$ from time $0$ to time $t-1$. This density can be computed by marginalization: $p(\bx_t|\theta) =
 \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
@@
 
-While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
-\bx)$\adnote{this is a typo} or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
+While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
+\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
 $\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
@@
 \noindent\textbf{Objective.} Typically, the objective of policy learning is to find a policy that minimizes some known cost function
-$C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\tau$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
+$C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
 For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
@@
 In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
-a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$. We are furthermore given
+a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\hat{\tau})$. We are furthermore given
 an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
@@
 
-\section{SHIV}
-\adnote{putting shiv and dagger side by side.
-also, notice how I am setting up the rest of the section by explaining what will follow; also, avoid filler sentences like "note that ..." when you are not following that up with a point; avoid filler words like two "basic" steps -- it's just steps, why are they basic?}
+\section{SHIV} \label{sec:SHIV}
 
 Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq.
-\ref{eq:LFD_obj} by iterating two steps: 1) find an optimal $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
+\ref{eq:LFD_obj} by iterating two steps: 1) find a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
 However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky enough to warrant a query, thereby reducing supervisory burden.
-
-%  \subsection{DAgger: Dataset Aggregation}
-% Note that Eq. \ref{eq:LFD_obj} involves both the parameterized policy $\pi_{\theta}$ and the average distribution of
-% states with respect to the policy, $p(\bx|\theta)$.
-Let us recall that Dataset Aggregation (DAgger) is an iterative algorithm developed by \cite{ross2010reduction} which iterates two basic steps for $K$ iterations to find an optimal policy under this objective.
-%DAgger iteratively minimizes $\pi_{\theta}$ on the collected dataset of examples $\mathcal{D}$ and then adds new states
-%of high probability under $\pi_\theta$ by sampling via policy `roll outs' from $p(\bx|\theta)$. 
-%\fpnote{DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
-%made more precise then and refer to the algorithm}
 
@@
 The first step of any iteration $k$ is to find a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):
-% \fpnote{this is really start of iteration `i', as we circle back}
-% At iteration $k=0$ an initial dataset $\mathcal{D}_0$ of $N_0$ supervisor demonstration trajectories 
-% with $T+1$ time steps: $\tau^i=(\bx_0^i, \bu_0^i, \ldots, \bx_T^i, \bu_T^i)\in (\mathcal{X}\times\mathcal{U})^{T+1}$ for $i\in \{0, \ldots, N_0\}$
-% mapping states to control
-% inputs is provided. DAgger solves the following optimization problem with respect to the surrogate loss function:
 
@@
 
-\adnote{simplified D above to just be pairs so that shiv makes sense too, as it doesnt add full trajectories}
 This problem can be treated as a supervised learning problem which can be solved using standard machine
@@
 To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
-can be considered as present in policy's output. We employ a regularization technique in the optimization which is
+can be considered as present in policy's output.  A regularization technique in the optimization is
 used to control the smoothness of the function that is fit to the sampled data.
-In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.\adnote{is this just us or also dagger?}
-
+In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.
  \subsection{Step 2}
@@
 iteration and each state in DAgger can be tedious, imposing a large burden on the supervisor.
-\adnote{add in the discussion that another advantage of measuring risk is the early termination which can avoid disaster}
 Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of \emph{risk} to actively \emph{decide} whether a label is necessary.
@@
 
-SHIV only asks for supervision on states for which $g(\bx)=-1$: \adnote{don't know what a good way to mention the termination condition is, maybe just a footnote or in discussion at the end as an advantage}
+SHIV only asks for supervision on states for which $g(\bx)=-1$:
+
 $$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$
@@
 Dagger has been experimentally shown to perform well in both simulation and real world
-    experiments\cite{}\adnote{cite}. Under a `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
+    experiments\cite{NIPS2014_5421,ross2010reduction,ross2013learning}. Under a `no regret' assumption, Ross et al.\cite{ross2010reduction} furthermore
 deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically.
@@
 However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods.
-We analyze the dependence on $\sigma$ in our experimental section.
+We analyze the dependence on $\sigma$ in Sec.
+\ref{sec:car}.
 Our results suggest that SHIV is robust to this parameter selection.
-\adnote{must add this experiment!}
 
 \subsection{Measuring Risk}
-
-\adnote{somewhere in this section refer to the second figure}
-
 % However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
@@
 previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance}, or 2) the surrogate loss of the current policy at the current state is high, so that the state, although visited, does
+loss \cite{tokdar2010importance}, or 2) the surrogate loss of the current policy at a state in $\mathcal{D}$ is high, so that the state, although visited, does
 not model the supervisor's control inputs correctly.
 
-% To address these limitations, we propose to 1) avoid highly risky states entirely by early termination of the policy
-% roll-outs that enter these regions and 2) to recognize non-risky states and to not request supervisor input for these,
-% thereby reducing the burden on the human trainer.
-
-%One way to do this is to define risk in terms of distance to a nearest neighbor, but this approach is vulnerable to
-%outliers in the known set of states. Another option is to fit a density to the known set of states, which requires an
-%exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}.\adnote{this stuff is in the related work too}
-
 To evaluate risk in high-dimensional state spaces (such as HOG features on images, like in our driving simulator testcase), we use
-modified version of the technique known as the One Class SVM that implicitly approximately estimates a boundary of a user defined quantile of
+a modified version of the technique known as the One Class SVM that  approximately estimates a boundary of a user defined quantile of
 a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
@@
 %\subsection{Estimation of Quantile Level Sets}\label{sec:level}
-\fpnote{my git commit on this section was overwritten by an old commit at version 10 - reintroduced modifications here,
-Michael, please check this is still accurate with recent modifications}
 We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
@@
 and $(w,\rho)$ denote the weight vector and offset parameterizing a hyperplane in the feature space associated with a
-Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}$.
+Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/2\sigma^2}$.
 
@@
 \end{align}
-\adnote{let's make sure we define $\sigma$ above}
 
@@
 
-\subsection{Car Simulator}
+\subsection{Driving Simulator} \label{sec:car}
 A common benchmark in Reinforcement Learning is the problem of learning a policy for a car to drive around a track
@@
 
-We implemented a car simulator where the car must follow a polygonal track. If the car accidentally leaves the track, it is placed
+We implemented a driving simulator where the car must follow a polygonal track.
+The polygonal tracks are randomly created by sampling from a Gaussian with mean that is the center of the video game workspace.Then a convex hull is computed on the sampled points.
+In general this produces tracks composed of five to seven edges, an example is shown in Fig.
+\ref{fig:teaser}(a).
+If the car accidentally leaves the track, it is placed
 back on the center of the track at a nearby position. The car's control input space is given by  $\mathcal{U} = \lbrace
@@
 exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
-{\color{blue} [-- F: what about $r_0$? --]}
 
+We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
+defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
+In Fig.
+\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
+We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
+randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
+results from these experiments, suggesting a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+
+\textbf{Comparison to active learning approaches:}
 To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane \cite{tong2002support}.
 The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-We further compared against Query By Committee, which was trained via bagging \cite{}.
+We further compared against Query By Committee, which was trained via bagging \cite{breiman1996bagging}.
 Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on.
@@
 
-We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
-defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
-In Fig. \ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.  We run 6 \fpnote{do we
-have large numbers of iterations in the final version, or is this the final one?} iterations \fpnote{define "iteration"
-how many simulation cycles/size of $T$?} of each algorithm over 40 different
-randomized polygonal tracks \fpnote{describe how you generated the tracks}. Figure \ref{fig:car_cost} presents averaged
-results from these experiments, suggesting a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger. 
-\fpnote{don't use "initial results" when talking about your main experiment - makes it sound too weak}
+\textbf{Sensitivity Analysis}. 
+To analyze the sensitivity of our method we varied the $\sigma$ parameter of the risk estimation function $g_{\sigma}$.
+SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
+As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to  less data being used, but worst performance similar to the traditional supervise learning approach.
 
-\textbf{Comparison to active learning approaches:}
-\fpnote{Refer to figure 3 here and explain, also explain "prediction error" do you mean mean total surrogate loss,
-explain that you are using the scaled confidence intervals}
+\begin{table}[t]
+\centering
+\begin{tabular}{ R{2.5cm}||R{1.65cm}|R{1.65cm} }
+ %\hline
+ %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
+ %\hline 
+ \hline
+\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Final  Cost} & \specialcell{\bf States  Labeled} \\
+ \hline
+350 & 13 & 521\\
+250 & 6 & 1536 \\
+200 & 6 & 1524 \\
+150& 6 &  1859 \\
+50 & 6 &  3864 \\
+1 & 6 & 4122 \\
+ %\hline
+\end{tabular}
+   \caption { \footnotesize  An analysis of the sensitivity of $\sigma$.
+SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
+As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach.
+   }
+		\tablabel{opt-p-comparison}
+		\label{tab:sens}
+
+\end{table}
 
@@
 \includegraphics[width=9cm, height=4cm]{figures/risk_bar.eps}
-\caption { \footnotesize {\color{blue}make this caption smaller, move discussion to main text} To compare our method against a traditional confidence based active learning approach, we
-       implemented a confidence measure based on the distance from the SVM hyper plane \cite{tong2002support}.
-The threshold was set to the average distance from the hyper plane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-We further compared against Query By Committee, which was trained via bagging \cite{}.
-Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on.
-If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
-We finally compared our combined risk approach against the traditional One Class SVM without the "hole-punching".
-We measured the performance in terms of how many states are estimated to be of low risk (i.e.
-correctly classified) and are of actually high risk on the first policy roll out.
-Results  are averaged over 50 tracks.
+\caption {  A comparison of different active learning approaches in correctly classifying states to be of high risk during the initial policy roll out in the driving experiment .
+We compare against a confidence estimate of distance to hyperplane, query by committee for 3 hypothesis classifiers, the One Class SVM, and our modified One Class SVM.
+Results  are averaged over 50 tracks and the policy $\pi_\theta$ is represented as a Linear SVM.
    }
@@
 To illustrate how our technique can be used the continuous case and with a human demonstrator. 
-\fpnote{avoid "look at" sound too informal and try to be as factual as possible - use investigate, consider}
-We look at having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
+We investigate having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
 Grasping in clutter can be a challenging task because as shown in Kiteav et al.
@@
 
-We used Box2D a physics simulator to model a virtual world. The arm, shown in Fig. \ref{fig:box2d_arm}, consists of 3
-degrees of freedom and has a parallel jaw gripper. \fpnote{the arm does not consist of kDOF - it has kdof, also add the
-    gripper - so it is 4dof: e.g.: We simulated a 4 DOF robot arm with three main joints and a parralel jaw gripper as
-displayed in Fig.X}
+We used Box2D a physics simulator to model a virtual world. We simulated a 4 DOF robot arm with three main joints and a parallel jaw gripper as
+displayed in Fig. \ref{fig:teaser}(b).
 
-For input the human demonstrator provides controls through an XBox controller. The right joystick contains two principle
-components that determine the x and y velocity of the center of the end effector. \fpnote{The right joystick was used to
+For input the human demonstrator provides controls through an XBox controller. The right joystick was used to
     provide horizontal and vertical velocity inputs for the center of the end-effector which were then translated into
-robot arm motions by means of a Jacobian transpose controller for the 3 main joint angles (was it?)}.
-The left bumper is a binary value for opening the gripper and the right bumper is a binary value for closing the gripper.
-\fpnote{The left `bumper' button on the joystic was used to provide a binary control signal to close the parralel jaw
-gripper} The control inputs are hence modelled by the set $\mathcal{U} = \lbrace [-1,1],[-1,1],\lbrace 0,1 \rbrace, \lbrace 0, 1\rbrace \rbrace$.
+robot arm motions by means of a Jacobian transpose controller for the 3 main joint angles.
+The left `bumper' button on the joystick was used to provide a binary control signal to close the parallel jaw
+gripper. The control inputs are hence modeled by the set $\mathcal{U} = \lbrace [-1,1],[-1,1],\lbrace 0,1 \rbrace \rbrace$.
 
@@
 
-In Fig. \ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 trials for SHIV and DAgger.
-Initial results suggest we are able to achieve an approximate $70\%$ reduction in data. \fpnote{instead of initial
-results suggest, say "in our experiment, ..." if you don't want to make the claim too strong. initial results sounds
-like the paper is not finnished}
+In Fig. \ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 rounds for SHIV and DAgger.
+Our experiment suggest we are able to achieve an approximate $70\%$ reduction in data.
 
@@
 \includegraphics[width=\columnwidth, height=6cm]{figures/grasp_clutter.eps}
-\caption{\todo{Might get more trials from Sammy tomorrow as well}We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
+\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
 In Fig.
@@
 \subsection{Surgical Experiment}
-Robotic Surgical Assistants (RSAs) are frequently used for procedures such as: prostectomy, uterectomy, and tumorectomies within the abdominal and thoracic cavities with high success rates~\cite{van2013laparoscopic,darzi2004impact} .
-Intuitive Surgical’s da Vinci Robotic Surgical Assistant, a type of RSA, facilitated over 570,000 procedures worldwide in 2014 across 3000 devices [5].
-Currently, these devices are controlled by surgeons via physical tele-operation at all times; introducing autonomy of surgical sub-tasks has the potential to reduce cognitive load
-and facilitate supervised autonomy for remote tele-surgerical procedures.
+Robotic Surgical Assistants (RSAs) are frequently used for procedures such as: prostectomy, uterectomy, and tumorectomies within the abdominal and thoracic cavities with high success rates~\cite{van2013laparoscopic,darzi2004impact}.
+Currently, these devices are controlled by surgeons via physical tele-operation at all times; introducing autonomy of surgical sub-tasks has the potential to reduce cognitive load and facilitate supervised autonomy for remote tele-surgerical procedures.
 
@@
 are interested in learning a policy to correct bad initial poses to the proper insertion pose as shown in Fig.
-\ref{fig:support_example}. We had a surgeon, Dr. Douglas Boyd, demonstrate via tele-operation the correction strategies.
-\textbf{Sounds bossy - how about Dr. Douglas Boys, a surgeon at UCSF Medical XYZ, provided us with a collection of ...}
+\ref{fig:support_example}. Dr. Douglas Boyd, a surgeon at UC Davis, provided us with a collection of demonstrations on a Intuitive Surgical Da Vince Research Kit \cite{AnnualReport2014}.
 
-Dr. Boyd demonstrated a series of trajectories that started at an initial attempted needle insertion pose $P_0$ and
-applied the necessary corrections to achieve a goal pose $P_G$. We used three of these demonstrations as our initial
-dataset $\mathcal{D}_0$. Dr. Boyd couldn't be around \fpnote{too informal! also makes us sound weak. Since we were
-    limited to this dataset, and in order to study the convergence of our approach, we trained a synthetic
-... instead of executing ...}
-
-for the interactive labeling of both SHIV and DAgger, so we had to hand design \fpnote{aaa!
-- we chose...} an expert controller that computed the transformation between the desired insertion pose and the current pose.
-We did this by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
+Dr. Boyd demonstrated a series of trajectories that each started at an initial attempted needle insertion pose $P_0$ and
+applied the necessary corrections to achieve a goal pose $P_G$. The time horizon, $T$ of each trajectory was on average 80.  We used three of these demonstrations as our initial
+dataset $\mathcal{D}_0$, thus $|\mathcal{D}_0| = 240$.
+In order to study convergence of both SHIV and DAgger, we chose to create a synthetic expert for online learning part.
+The expert controller computed the transformation between the desired insertion pose and the current pose  by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
 Then converted $C$ to the associated lie algebra vector $c \in \mathcal{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control $c_D$ Doug Boyd applied to the robot.
@@
 For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's label.
-The two $nu$ parameters where set to $0.1$ and $0.001$ for the good and bad support
-\fpnote{I don't think we introduced a notion of good and bad support regions - use formal language}
-regions respectively. The sigma bandwidths, $\sigma$, in the rbf kernel were set to $2$ and $0.25$.
+The  $\nu$ parameters was set to $0.1$.
+regions respectively. The bandwidth, $\sigma$, in the rbf kernel was set to $2$.
 
 For trials we sample a start position from a Gaussian on the translational component of $P_0$ with isotropic variance of
-$0.1$ cm. The distance between initial $P_0$ and $P_G$ \fpnote{earlier when you introduce $P_0$, $P_G$ describe how many
-and introduce a set- just 3 pairs, one per trajectory?} is roughly $3$ cm. Our cost function $c(\bx,\bu)$ is measured in
-terms of Euclidean distance in translational component, which is in centimeters. \fpnote{no notion of cost on
-rotations??} We run DAgger and SHIV both for 20 iterations and average over 40 rounds \fpnote{what's a 'round'?}.
-Initial results \fpnote{they are not initial if you submit them...} shown in Fig. \ref{figures/needle_insertion_results.eps} suggest a reduction $67\%$ in the amount of human inquiries needed.
+$0.1$ cm. The distance between initial $P_0$ and $P_G$ is roughly $3$ cm. Our cost function $c(\bx,\bu)$ is measured in
+terms of Euclidean distance in translational component, which is in centimeters.
+\mlnote{We can do Frobenius norm on transformation matrix, wanted to double check if that was accurate though} We run DAgger and SHIV both for 20 iterations and average over 40 different starting positions.
+Results shown in Fig. \ref{fig:needle} suggest a reduction $67\%$ in the amount of human inquiries needed.
 

### 2015-08-28 paper.tex
Prof. G's comments

@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations}
+\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v15]}
 
@@
 \begin{abstract}
-Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system
-dynamics and reward functions are unknown. However, they impose a burden on supervisors to demonstrate labels (control
+Online algorithms for robot model-free learning from demonstration (such as DAgger) can learn policies for problems where system
+dynamics and cost function are unknown. However, they impose a burden on supervisors to demonstrate labels (control
 signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
@@
 To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
-Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of 70$\%$).
+We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation of consisting of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented as a transformation matrix .
+Results suggest that SHIV can learn policies and reduce operator burden significantly  up to 70$\%$.
 
@@
 dynamics model may be highly non-linear or noisy.
-In learning from demonstration, the cost function is usually unknown or non-continuous and difficult to learn with.
-The robot must learn a policy mapping states to controls as it observes the supervisor perform a task\cite{argall2009survey}.
+In learning from demonstration, the cost function, which is the negative of the reward function, is usually unknown or significantly delayed.
+In the grasping for clutter example, shown in Fig.
+\ref{fig:teaser}(b) the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback.
+To avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls by observing \cite{argall2009survey}.
 
@@
 The learned policy is not helpful in unfamiliar states, leading to robot failures (crashes or dropping objects).
-For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states on the side of the road where it has not encountered before, so its policy quickly fails \cite{pomerleau1989alvinn}.
-Theoretically, the number of mistakes made by the robot in such cases  can scale quadratically with the time horizon of the task \cite{ross2010efficient}.
+For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states on the side of the road where it has not encountered before, where its policy could  fail \cite{pomerleau1989alvinn}.
+Theoretically, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task \cite{ross2010efficient}.
 
@@
 \caption{ 
+\todo{update figure}
 For a given budget of human supervision, SHIV improves performance (reduced policy cost) in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a surgeon's demonstrations of correcting a needle before suturing in surgery.
@@
 
-\begin{figure*}[t]
-\centering
-
-\includegraphics[width=\textwidth]{figures/active_learning.pdf}
-
-\caption{A comparison of different query selection strategies for active learning on a non-stationary distribution.
-The shaded and empty circles are training data from two classes, $0$ and $1$ respectively.
-The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $1$.
-Typical strategies assign high risk to states close the decision boundary (a), or for which a set of estimators disagree (b).
-Neither of these apply to our new samples in red.
-In contrast, we use a strategy that is amenable to non-stationary distributions by assigning high risk to novel states (c) and states in historically mislabeled regions.
-%Confidence and Query by Committee methods measure
-%{\color{blue} FP:estimate} states far away from the decision boundary of the estimator as having low risk,
-%however novelty detection methods measure {\color{blue} FP:estimate} the level of risk as
-%{\color{blue}FP:by} how far a point is from the trained data. Our
-%modified risk method attempts to measure risk both as a function of how far it
-%{\color{blue}it gramatically refers to risk,
-%but you mean sample "it$\mapsto$a sample"?} is from data trained on
-%{\color{blue}grammatically strange$\mapsto$from the training data} and the decision boundary of the estimator. 
-}
-\label{fig:support_example}
-\end{figure*}
-
-\emph{On-line} imitation learning approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+\emph{On-line} learning from demonstration approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
 In DAgger, a series of policies are learned.
@@
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-Theoretical analysis of DAgger have shown the number of mistakes to scale linearly for strongly convex loss functions.
+Theoretical analysis of DAgger have shown the number of errors to scale linearly for strongly convex loss functions.
 
@@
 
-Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that  has been historically misclassified, which we know from our training data.
+Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that have been misclassified, in previous training data.
 %\adnote{Ken's version below does not seem to represent what we actually do.}
@@
 
-We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which reduces supervisor burden by enabling the robot to only request supervision for risky states.
-SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions (like those encountered when executing a new policy at each iteration).
-It builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating}.
+We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which can reduce supervisor burden by only requesting supervision for risky states.
+SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions..
+It builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
 
@@
 \section{Related Work}
-Below we summarize related work in active approaches to robot learning from demonstration, as well as in risk evaluation techniques that we build upon.
+Below we summarize related work in active approaches to robot learning from demonstration and risk evaluation techniques..
 
-\noindent\textbf{Active Imitation Learning.}
-SHIV instantiates \emph{stream-based} active learning ~\cite{atlas1990training,cohn1994improving}.
-It iteratively receives the stream of states induced by executing the current best policy estimate, and actively decides for each state whether to query the supervisor or not.
+\noindent\textbf{Active Learning from Demonstration}
+Online learning from demonstration can be formulated as a \emph{stream-based} active learning problem ~\cite{atlas1990training,cohn1994improving}.
+In stream based active learning, the decision of whether to query the supervisor (for a control signal or not) is not over the entire state space (like in traditional pool-based active learning), but only on the states encountered during learning.
 
 Stream-based active learning has two ingredients: a stream, given here by executing the current best policy, and a query selection method deciding whether or not to query.
-Typical query selection methods are estimator-centric: they evaluate the estimator's confidence, e.g.
+Typical query selection methods are estimator-centric:  evaluating risk using the estimator, e.g.
 distance from the classification hyperplane \cite{tong2002support}, as in Fig.
 \ref{fig:support_example}(a).
-An alternative to distance-based measures of confidence is query by committee  \cite{breiman1996bagging}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
-Confidence here is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig.
+An alternative to distance-based measures of  risk is query by committee  \cite{breiman1996bagging}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
+Risk here is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig.
 \ref{fig:support_example}(b)).
@@
 Both approaches implicitly assume a stationary state distribution --- that the new data is sampled from the same distribution as the previous training data.
-Although such methods have been previously proposed for online imitation learning (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
-online imitation learning violates the stationary distribution assumption because each new policy induces a new distribution of states.
+Although such methods have been previously proposed for online learning from demonstration (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
+online learning from demonstration violates the stationary distribution assumption because each new policy induces a new distribution of states.
 This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.
 
-In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating confidence based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig.
+In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig.
 \ref{fig:support_example}(c).
-Additionally, we also assign lower confidence to  historically \emph{mislabeled} regions, as in Fig.
+Additionally, we also assign higher risk to  historically \emph{mislabeled} regions, as in Fig.
 \ref{fig:support_example}(d).
-%Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.
-Our results in Sec.
-\ref{sec:car} suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (be it distance or query by committee based).
+We then use a classification method based on the One Class SVM \cite{scholkopf2001estimating} to predict if a state is risky or not risky, which we we define as safe.%Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.
 
@@
 One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
-trained on \cite{tokdar2010importance}.
-Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution, making it difficult for a model to correctly predict its label.
+trained on \cite{tokdar2010importance}. Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution.
 One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled.
+The if the probability of that point is low with respect to the underlying density, it will be marked as novel.
 However, the amount of data needed to accurately do so scales exponentially in the number of dimensions \cite{nadaraya1964estimating}.
@@
 An alternative to evaluating the probability of a data point is to measure distance to its nearest neighbors \cite{knox1998algorithms}. However, this approach was shown to be
-susceptible to outliers since nearest neighbors mostly incorporate local information about the data \cite{hodge2004survey}.
+susceptible to outliers since nearest neighbors  incorporates only local information about the data.
+Thus, a group of outliers can be close together, but significantly far from the majority of the data and nearest neighbors would mark them as not novel \cite{hodge2004survey}.
 
 Our approach is based on the One Class SVM proposed by Scholk{\"o}pf et al., which estimates a particular quantile level set for the training data by solving a convex quadratic program  to find support
-vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
+vectors~\cite{scholkopf2001estimating}. The method has been theoretically shown to approximate the quantile levelset of a density estimate
 asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
-In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for novelty detection in high-dimensional 
-image data.
+In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for novelty detection in high-dimensional image data.
+To our knowledge the use of One Class SVM to online learning from demonstration has never been done before.
+\begin{figure*}[t]
+\centering
+
+\includegraphics[width=\textwidth]{figures/active_learning.pdf}
+
+\caption{\todo{update figure with elipse} A comparison of different query selection strategies for active learning on a non-stationary distribution.
+The shaded and empty circles are training data from two classes, $0$ and $1$ respectively.
+The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $1$.
+Typical strategies assign high risk to states close the decision boundary (a), or for which a set of estimators disagree (b).
+Neither of these apply to our new samples in red.
+In contrast, we use a strategy that is amenable to non-stationary distributions by assigning high risk to novel states (c) and states in historically mislabeled regions.
+%Confidence and Query by Committee methods measure
+%{\color{blue} FP:estimate} states far away from the decision boundary of the estimator as having low risk,
+%however novelty detection methods measure {\color{blue} FP:estimate} the level of risk as
+%{\color{blue}FP:by} how far a point is from the trained data. Our
+%modified risk method attempts to measure risk both as a function of how far it
+%{\color{blue}it gramatically refers to risk,
+%but you mean sample "it$\mapsto$a sample"?} is from data trained on
+%{\color{blue}grammatically strange$\mapsto$from the training data} and the decision boundary of the estimator. 
+}
+\label{fig:support_example}
+\end{figure*}
 
@@
 \section{Problem Statement}
+The goal of this work is to learn a policy such that it becomes close or identical to a supervisor's policy, such that for states visited after completion of training the action taken by the robot is similar to that of the supervisor.
+
+\noindent\textbf{Assumptions} We assume a system that has a known markovian state space and set of controls.
+We assume stochastic dynamics of the environment, that are stationary (i.e.
+the underlying distribution doesn't change over time).
+We assume access to a robot or simulator, such that we can start in some initial state and apply a series of controls and observe the following states that occur.
+We assume the initial state must be sampled from some unknown distribution over the state space.
+Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories initially and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.
+
 \noindent\textbf{Policies and State Densities.}
-We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example, of
+We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
@@
 \mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
-\mathcal{U}$. Thus, we assume that 
+\mathcal{U}$: 
 $$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
@@
 Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
-induces a density on state-space trajectories of length $T+1$: $$p(\tau | \theta)=
+induces a density on trajectories of length $T+1$: $$p(\tau | \theta)=
 p(\bx_0)\prod_{i=0}^{T-1}p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$$
@@
 
-\noindent\textbf{Objective.} Typically, the objective of policy learning is to find a policy that minimizes some known cost function
+\noindent\textbf{Objective.} The objective of policy learning is to find a policy that minimizes some known cost function
 $C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
@@
 In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
-a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\hat{\tau})$. We are furthermore given
+a `supervisor' that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level.
+\mlnote{the last statement is intended to mean implementors of this algorithm have agreed that the supervisor may not be optimal, but has a level of performance that is worth automating} We are furthermore given
 an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
-which are the result of the supervisor applying this policy.
-This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
-The goal is to produce a low cost policy for the task based on these demonstrations.
+which are the result of the supervisor applying this policy. This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
 
@@
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
-$\tilde{\pi}(\bx)\in \mathcal{U}$.
+$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a that minimizes the surrgoate loss between relative to the supervisor's policy.
 
@@
  If the robot could learn the policy  perfectly, this state density would match the one encountered in the user examples.
-But any small error will make the state distribution deviate from the training one, and this the motivation for an iterative algorithm like DAgger and now SHIV.
+But if the robot to makes an error, it changes the distribution of states over which it visits, which in practice can lead it to encounter states in which it has no labels from the expert and can't generalize too \cite{pomerleau1989alvinn}.
+Thus, the motivation for iterative algorithms like DAgger and now SHIV, which iterate between learning a policy and then the supervisor providing feedback.
+The feedback is in the form of control signals on states sampled from the robot's new distribution of states.
 
@@
 Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq.
-\ref{eq:LFD_obj} by iterating two steps: 1) find a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
-However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky enough to warrant a query, thereby reducing supervisory burden.
+\ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
+However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky to warrant a query.
 
 \subsection{Step 1.}
-The first step of any iteration $k$ is to find a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):
+The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):
 
@@
 
-This problem can be treated as a supervised learning problem which can be solved using standard machine
-learning techniques, for example a support vector machine or a neural network.
+This problem is a supervised learning problem that can be solved using machine learning techniques, for example a support vector machine or a neural network.
+Finding the right function representation and optimization method for a given problem is still an open question in machine learning, however a large number of advances have been made that make the use of these techniques very feasible \cite{scholkopf2002learning}
 
@@
 \fpnote{we'll need to work on this}
-SHIV currently provides a way to apply active learning to online imitation learning, however its use of level set estimation of the underlying distribution introduces several hyper parameters.
+SHIV currently provides a way to apply active learning to online learning from demonstration, however its use of level set estimation of the underlying distribution introduces several hyper parameters.
 As Fig.

### 2015-09-01 paper.tex
added Ken's feedback, changed One Class SVM, added discussion on hyperparameters

@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v15]}
+\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v16]}
 
-\author{Michael Laskey$^1$, Sam Staszak, Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^2$% <-this % stops a space
-\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny, anca\}@berkeley.edu}}%
-\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
+\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^{1-2}$% <-this % stops a space
+\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh, ftpokorny, anca\}@berkeley.edu}}%
+\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
 \thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
 }
-
 \begin{document}
@@
 Online algorithms for robot model-free learning from demonstration (such as DAgger) can learn policies for problems where system
-dynamics and cost function are unknown. However, they impose a burden on supervisors to demonstrate labels (control
+dynamics and cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
 signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
 algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
-SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
+SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.
 To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation of consisting of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented as a transformation matrix .
-Results suggest that SHIV can learn policies and reduce operator burden significantly  up to 70$\%$.
+We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented spatial transform.
+Results suggest that SHIV can reduce the number of queries up to 70$\%$.
 
@@
 
-In \emph{model-free} robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig.
-\ref{fig:teaser}, from examples provided by a competent \emph{supervisor}, usually a human.
-The problem is model-free if  the system dynamics are unspecified, eg.
+In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig.
+\ref{fig:teaser}, from examples provided by a competent supervisor, usually a human.
+The problem is model-free if  the system dynamics are unknown, eg.
 dynamics model may be highly non-linear or noisy.
@@
 \ref{fig:teaser}(b) the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback.
-To avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls by observing \cite{argall2009survey}.
+To avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls by observing~\cite{argall2009survey}.
 
-In the standard supervised setting, a policy is learned offline from a fixed set of examples.
-When the robot executes this policy, the sequential process can quickly evolve away from the initial set of states.
-The learned policy is not helpful in unfamiliar states, leading to robot failures (crashes or dropping objects).
-For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states on the side of the road where it has not encountered before, where its policy could  fail \cite{pomerleau1989alvinn}.
-Theoretically, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task \cite{ross2010efficient}.
+In the supervised setting, a policy is learned offline from a fixed set of examples.
+When the robot executes this policy, the sequential process can quickly evolve away from the previously explored set of states.
+The learned policy might not be helpful in unfamiliar states, leading to unrecoverable failures.
+For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where it has not encountered before, where its policy could  fail~\cite{pomerleau1989alvinn}.
+It has been shown, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
 
@@
 \todo{update figure}
-For a given budget of human supervision, SHIV improves performance (reduced policy cost) in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a surgeon's demonstrations of correcting a needle before suturing in surgery.
+SHIV reduces the number of queries to the supervisor in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery.
 }
@@
 
-\emph{On-line} learning from demonstration approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+On-line learning from demonstration approaches such as DAgger iteratively gather more examples from the supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
 In DAgger, a series of policies are learned.
-In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for the  new states, which are then aggregated with the previous examples for the next iteration.
+In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for all  new states, which are then aggregated with the previous examples for the next iteration.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-Theoretical analysis of DAgger have shown the number of errors to scale linearly for strongly convex loss functions.
+It has been shown for DAgger, the number of errors to scale linearly for strongly convex loss functions.
 
 One drawback is that such online algorithms increase the burden on the supervisor.
-Our goal is to reduce supervisor burden without degrading robot performance, \emph{by only requesting demonstrations for risky states.
-}
+Our goal is to reduce supervisor burden without degrading robot performance, by only requesting demonstrations for risky states.
 
-Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that have been misclassified, in previous training data.
+Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that have been misclassified, in previous training data.
 %\adnote{Ken's version below does not seem to represent what we actually do.}
@@
 It builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
-
-We compare SHIV with DAgger in three experiments: 1) a driving simulator, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.
-Our analysis suggests that compared to DAgger, SHIV learns a policy that performs significantly better given the same amount of human supervision.
-Conversely, SHIV significantly reduces supervisory burden (by a factor of $70\%$) while achieving the same performance.
 
@@
 \noindent\textbf{Active Learning from Demonstration}
-Online learning from demonstration can be formulated as a \emph{stream-based} active learning problem ~\cite{atlas1990training,cohn1994improving}.
+Online learning from demonstration can be formulated as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
 In stream based active learning, the decision of whether to query the supervisor (for a control signal or not) is not over the entire state space (like in traditional pool-based active learning), but only on the states encountered during learning.
@@
 \ref{fig:support_example}(c).
-Additionally, we also assign higher risk to  historically \emph{mislabeled} regions, as in Fig.
+Additionally, we also assign higher risk to  historically mislabeled regions, as in Fig.
 \ref{fig:support_example}(d).
@@
 One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled.
-The if the probability of that point is low with respect to the underlying density, it will be marked as novel.
+If the probability of that point is low with respect to the underlying density, it will be marked as novel.
 However, the amount of data needed to accurately do so scales exponentially in the number of dimensions \cite{nadaraya1964estimating}.
@@
 \section{Problem Statement}
-The goal of this work is to learn a policy such that it becomes close or identical to a supervisor's policy, such that for states visited after completion of training the action taken by the robot is similar to that of the supervisor.
+The goal of this work is to 1)learn a policy, such that for states visited after completion of training the difference in controls taken by the robot is as small as possible to that of the supervisor 2)the supervisor is only requested for a query in states, which the robot is mis-predicting the supervisor's control.
 
-\noindent\textbf{Assumptions} We assume a system that has a known markovian state space and set of controls.
-We assume stochastic dynamics of the environment, that are stationary (i.e.
-the underlying distribution doesn't change over time).
+\noindent\textbf{Modeling Choices and Assumptions} We model the system dynamics as markovian and stochastic.
+The system dynamics are model to be stationary (i.e.
+given a state and a control the probability of the next state doesn't change over time).
+We model the initial state as sampled from a distribution over the state space.
+
+We assume a known state space and set of controls.
 We assume access to a robot or simulator, such that we can start in some initial state and apply a series of controls and observe the following states that occur.
-We assume the initial state must be sampled from some unknown distribution over the state space.
 Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories initially and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.
@@
 \noindent\textbf{Policies and State Densities.}
-We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
+We denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
-We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or
+We furthermore consider a set $\mathcal{U}$ of allowable control inputs for the robot, which can be discrete or
 continuous. We assume Markovian dynamics, such that the probability of state $\mathbf{x_{t+1}}\in
@@
 \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
-the average density on states for \emph{any} timepoint by 
+the average density on states for any timepoint by 
 \begin{equation}
@@
 $C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
-For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
+For example, in task of inserting a peg into a hole, a function on distance between the peg's current and desired final state can
 be considered \cite{levine2015end}.  
@@
 \ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
-However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky to warrant a query.
+However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky to warrant a query.
 
@@
 
-SHIV only asks for supervision on states for which $g(\bx)=-1$:
+SHIV only asks for supervision on states for which $g_{\sigma}(\bx)=-1$:
 
@@
 Dagger has been experimentally shown to perform well in both simulation and real world
-    experiments\cite{NIPS2014_5421,ross2010reduction,ross2013learning}. Under a `no regret' assumption, Ross et al.\cite{ross2010reduction} furthermore
+    experiments~\cite{NIPS2014_5421,ross2010reduction,ross2013learning}. Under a `no regret' assumption, Ross et al.\cite{ross2010reduction} furthermore
 deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically.
@@
 \begin{align}\label{eq:primal_sup}
-    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
+    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{minimize}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
 \mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
@@
 
-Here, the parameter $\nu$ controls the penalty or `slack term' and asymptotically approaches $\gamma$ \cite{vert2006consistency}
+Here, the parameter $\nu$ controls the penalty or `slack term' and is equivalent to $\gamma$ \cite{vert2006consistency}
 in the quantile definition when bandwidths decay at appropriate rates as the number of samples increases. The decision
@@
 \begin{align}\label{eq:decision_func}
-g_{\sigma}(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
+g_{\sigma}(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
 \end{align}
@@
 if $x$ lies strictly in the quantile sub-levelset. The dual form of the optimization yields a Quadratic Program 
-that can be solved efficiently \cite{scholkopf2001estimating}.
+that can be solved efficiently \cite{scholkopf2001estimating}. In the dual the decision function is given by
 
-For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
+\vspace{-2ex}
+\begin{align}\label{eq:decision_func}
+g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho).
+\end{align}
+
+where $\alpha_i$ corresponds to the dual variables.    For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
 a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available.
@@
 \end{align}
+
 Where, in the case when $l$ denotes discrete $0-1$ loss, we set $\varepsilon = 0$, while in the continuous $L_2$ loss
 case, $\varepsilon$ is a user defined threshold specifying allowable surrogate loss.
-We use $y_i$ to modify the One Class SVM optimization objective as follows:
+We use $y_i$ to modify the One Class SVM decision function as follows:
 
-\vspace{-2ex}
-\begin{align}\label{eq:primal_sup}
-    \underset{w\in F, \mathbf{\xi} \in \mathbb{R}^l, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}.
-\end{align}
+We then divide up our data in two sets those correctly classified:
+$$D_{g}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=1\}$$
+and those states incorrectly classified: 
+$$D_{b}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=-1\}$$
+A separate One-Class SVM is then trained on each set of states, ($D_{g}$ and $D_{b}$) and providing measures of the level sets, $g_{\sigma_g}$ and $g_{\sigma_b}$.
 
-States that incur loss above the $\varepsilon$ threshold are then enforced to lie on the opposite side of the
-hyper-plane separating the origin from the data in the feature space. Practically, this modification corresponds to
+We then define the overall decision function as:
+$$g_{\sigma}(\bx) = g_{\sigma_g} (\bx)+ g_{\sigma_b}(\bx)$$
+points are deemed risky if $g_{\sigma}(\bx) \neq 0$.  Practically, this modification corresponds to
 `carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
-exluded from the super-levelset.
-
-The dual formulation to the modified optimization problem, which is solved in practice, is 
-\begin{align}\label{eq:dual_sup}
-\underset{\alpha_i\in \mathbb{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
-\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1.
-\end{align}
-
-Our corresponding decision function $g_{\sigma}:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $$g_{\sigma}(\bx) = \sum_i^n
-\alpha_i y_i k(\bx_i,\bx) - \rho$$
-To compute the $\rho$ term, we leverage the fact that for an optimal solution the
-inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
-can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating} {\color{blue} [-- F:
-explain this more --]}.
+excluded from the super-levelset.
 
@@
 
+Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_g$.
+We set $\nu = 1e-3$ and $\nu_g = 1e-1$ for all experiments.
+The intuition for this is that 'hole-punching' One Class SVM, $g_{\sigma_b}$, should treat all points as inliers, to be conservative.
+The level set estimation should be robust to outliers in the dataset thus only looks at $90\%$ of points.
+We tuned $\sigma$ and $\sigma_b$ by doing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each example.
+\mlnote{we start the grid search with a rule of thumb that it should scale with feature size, hence the car example is 200 while the grasping is 5 and the needle is 2, looking for a citation on this though.
+Scikit learn does the same thing for kenerlized regression}
+
 \subsection{Driving Simulator} \label{sec:car}
@@
 validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
-exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.
+exponential kernel with a bandwidth of $\sigma_g = 200$ and $\sigma_b = 200$ to account for $95\%$ of the training distribution.
 
@@
  \hline
+ 1 & 6 & 4122 \\
+ 50 & 6 &  3864 \\
+ 150& 6 &  1859 \\
+200 & 6 & 1524 \\
+250 & 6 & 1536 \\
 350 & 13 & 521\\
-250 & 6 & 1536 \\
-200 & 6 & 1524 \\
-150& 6 &  1859 \\
-50 & 6 &  3864 \\
-1 & 6 & 4122 \\
+
  %\hline
@@
 The order of magnitude difference in cost for grasping the object is to place emphasize on that portion of the task.
+The bandwidth parameters for SHIV were set to $\sigma_b = 5$ and $\sigma = 6$.
+For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's control.
 
@@
 are interested in learning a policy to correct bad initial poses to the proper insertion pose as shown in Fig.
-\ref{fig:support_example}. Dr. Douglas Boyd, a surgeon at UC Davis, provided us with a collection of demonstrations on a Intuitive Surgical Da Vince Research Kit \cite{AnnualReport2014}.
+\ref{fig:support_example}. Dr. Douglas Boyd, a surgeon at UC Davis, provided us with a collection of demonstrations on a Intuitive Surgical Da Vinci Research Kit \cite{AnnualReport2014}.
 
@@
 The expert controller computed the transformation between the desired insertion pose and the current pose  by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
-Then converted $C$ to the associated lie algebra vector $c \in \mathcal{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control $c_D$ Doug Boyd applied to the robot.
+Then converted $C$ to the associated lie algebra vector $c \in \mathbb{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control,  $||\bar{c}_D||$, Doug Boyd applied to the robot.
 
@@
 The state $\mathcal{X}$ was  a 16 dimensional vector consisting of the elements in the pose $P$ vector.
-The control space $\mathcal{U}$ was a $\mathcal{R}^6$ vector representing the Lie algebra.
+The control space $\mathcal{U}$ was a $\mathbb{R}^6$ vector representing the Lie algebra.
 
-For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's label.
-The  $\nu$ parameters was set to $0.1$.
-regions respectively. The bandwidth, $\sigma$, in the rbf kernel was set to $2$.
+For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's control. 
+regions respectively. The bandwidth, $\sigma$, in the rbf kernel was set to $2$ and $\sigma_b = 1$.
 

### 2015-09-01 paper.tex
added Florian's comments

@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v16]}
+\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v17]}
 
-\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^{1-2}$% <-this % stops a space
+\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^{1,2}$% <-this % stops a space
 \thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh, ftpokorny, anca\}@berkeley.edu}}%
@@
 \ref{fig:teaser}(b) the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback.
-To avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls by observing~\cite{argall2009survey}.
+To potentially avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls~\cite{argall2009survey}.
 
@@
 
-In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig.
+In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on novelty (is the state an outlier to the training distribution), as in Fig.
 \ref{fig:support_example}(c).
@@
 We assume access to a robot or simulator, such that we can start in some initial state and apply a series of controls and observe the following states that occur.
-Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories initially and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.
+Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.
 
@@
 iteration and each state in DAgger can be tedious, imposing a large burden on the supervisor.
-Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of \emph{risk} to actively \emph{decide} whether a label is necessary.
-For every state encountered $\bx_t$, it applies a \emph{decision function} $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which will capture how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.
+Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of risk to actively decide whether a label is necessary.
+For every state encountered $\bx_t$, it applies a decision function $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which will capture how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.
 
-SHIV only asks for supervision on states for which $g_{\sigma}(\bx)=-1$:
+SHIV only asks for supervision on states for which $g_{\sigma}(\bx) \neq 0$:
 
@@
 \begin{align}\label{eq:decision_func}
-g_{\sigma}(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
+g(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
 \end{align}
@@
 where $\alpha_i$ corresponds to the dual variables.    For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
-a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available.
+a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available. The novelty detection method can be visualized in Fig. \ref{fig:support_example}(c). 
 However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
@@
 
-We then divide up our data in two sets those correctly classified:
-$$D_{g}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=1\}$$
+We divide up our data in to two sets those correctly classified:
+$$\mathcal{D}_{s}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=1\}$$
 and those states incorrectly classified: 
-$$D_{b}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=-1\}$$
-A separate One-Class SVM is then trained on each set of states, ($D_{g}$ and $D_{b}$) and providing measures of the level sets, $g_{\sigma_g}$ and $g_{\sigma_b}$.
+$$\mathcal{D}_{r}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=-1\}$$
+A separate One-Class SVM is then trained on each set of states, ($D_{s}$ and $D_{r}$) and providing measures of the level sets, $g_{s}$ and $g_{r}$.
+Specified by parameters $(\nu,\sigma)$ and $(\nu_r,\sigma_r)$, respectively.
 
 We then define the overall decision function as:
-$$g_{\sigma}(\bx) = g_{\sigma_g} (\bx)+ g_{\sigma_b}(\bx)$$
+$$g_{\sigma}(\bx) = g_{r} (\bx)+ g_{s}(\bx)$$
 points are deemed risky if $g_{\sigma}(\bx) \neq 0$.  Practically, this modification corresponds to
 `carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
-excluded from the super-levelset.
+excluded from the super-levelset. An illustration of this can be seen in Fig. \ref{fig:support_example}(d).
 
@@
 
-Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_g$.
-We set $\nu = 1e-3$ and $\nu_g = 1e-1$ for all experiments.
-The intuition for this is that 'hole-punching' One Class SVM, $g_{\sigma_b}$, should treat all points as inliers, to be conservative.
-The level set estimation should be robust to outliers in the dataset thus only looks at $90\%$ of points.
-We tuned $\sigma$ and $\sigma_b$ by doing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each example.
-\mlnote{we start the grid search with a rule of thumb that it should scale with feature size, hence the car example is 200 while the grasping is 5 and the needle is 2, looking for a citation on this though.
-Scikit learn does the same thing for kenerlized regression}
+Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_r$.
+We set $\nu = 10^{-3}$ and $\nu_r = 0.1$ for all experiments.
+$\nu = 0.1$ corresponds to looking at most $90\%$ of the data, which can make it robust to outliers.
+We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each example.
+Since the Driving Simulator worked with a much larger feature space the grid search started at 200, the Grasping and Surgical experiments started at 5.
 
@@
 validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
-exponential kernel with a bandwidth of $\sigma_g = 200$ and $\sigma_b = 200$ to account for $95\%$ of the training distribution.
+exponential kernel with a bandwidth of $\sigma = 200$ and $\sigma_r = 200$.
 
@@
 If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
-We finally compared our combined risk approach against the traditional One Class SVM without the "hole-punching".
-We measured the performance in terms of how many states are estimated to be of low risk (i.e.
-correctly classified) and are of actually high risk on the first policy roll out.
+We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
+We measured the performance in terms of the percentage of risky states that  are estimated to be safe by the active learning technique roll out.
 Results  are averaged over 50 tracks and shown in Fig.
@@
 \includegraphics[width=9cm, height=4cm]{figures/risk_bar.eps}
-\caption {  A comparison of different active learning approaches in correctly classifying states to be of high risk during the initial policy roll out in the driving experiment .
+\caption {  A comparison of different active learning approaches in terms of the percentage of risky states that are estimated to be safe by the active learning technique during the first policy roll out.
 We compare against a confidence estimate of distance to hyperplane, query by committee for 3 hypothesis classifiers, the One Class SVM, and our modified One Class SVM.
@@
 \includegraphics[width=8cm, height=6cm]{figures/dagger_shiv_one_class.eps}
-\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
+\caption{We compare performance for the Driving Simulator in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
 In Fig.
@@
 The order of magnitude difference in cost for grasping the object is to place emphasize on that portion of the task.
-The bandwidth parameters for SHIV were set to $\sigma_b = 5$ and $\sigma = 6$.
+The bandwidth parameters for SHIV were set to $\sigma_r = 5$ and $\sigma = 6$.
 For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's control.
@@
 \includegraphics[width=\columnwidth, height=6cm]{figures/grasp_clutter.eps}
-\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
-In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger and SHIV without the modification.
-Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig.
-\ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
+\caption{We compare performance for Grasping in Clutter in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
+Initial results, which are averaged over 8 different trials suggest a $65\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
 \vspace*{-10pt}
@@
 $0.1$ cm. The distance between initial $P_0$ and $P_G$ is roughly $3$ cm. Our cost function $c(\bx,\bu)$ is measured in
-terms of Euclidean distance in translational component, which is in centimeters.
-\mlnote{We can do Frobenius norm on transformation matrix, wanted to double check if that was accurate though} We run DAgger and SHIV both for 20 iterations and average over 40 different starting positions.
-Results shown in Fig. \ref{fig:needle} suggest a reduction $67\%$ in the amount of human inquiries needed.
+terms of Euclidean distance in translational component, which is in centimeters. We run DAgger and SHIV both for 20 iterations and average over 40 different starting positions.
+Results shown in Fig. \ref{fig:needle} suggest a reduction $67\%$ in the amount of supervisor queries needed.
 

### 2015-09-02 paper.tex
Anca's comments

@@
 \newcommand{\adnote}[1]{\ifthenelse{\boolean{include-notes}}%
- {\textcolor{green}{\textbf{AD: #1}}}{}}
+ {\textcolor{blue}{\textbf{AD: #1}}}{}}
 
@@
 
-\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^{1,2}$% <-this % stops a space
+\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeff Mahler$^1$, \\ Florian T. Pokorny$^1$, Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
 \thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh, ftpokorny, anca\}@berkeley.edu}}%
@@
 \begin{abstract}
-Online algorithms for robot model-free learning from demonstration (such as DAgger) can learn policies for problems where system
-dynamics and cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
+Online algorithms for robot model-free\adnote{model-free robot} learning from demonstration (such as DAgger) can learn policies for problems where \adnote{the} system
+dynamics and \adnote{the} cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
 signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
-algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
+algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to \emph{only request supervision for risky states}.
 SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.
@@
 We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented spatial transform.
-Results suggest that SHIV can reduce the number of queries up to 70$\%$.
+Results suggest that SHIV can reduce the number of queries up to 70$\%$\adnote{double check this}.
 
@@
 
-In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig.
-\ref{fig:teaser}, from examples provided by a competent supervisor, usually a human.
-The problem is model-free if  the system dynamics are unknown, eg.
-dynamics model may be highly non-linear or noisy.
-In learning from demonstration, the cost function, which is the negative of the reward function, is usually unknown or significantly delayed.
+In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment (Fig.
+\ref{fig:teaser}), from examples provided by a competent\adnote{why competent?
+called expert in the literature; either stick to that or simplify to just supervisor} supervisor, usually a human.
+The problem is model-free if  the system dynamics are unknown, e.g.
+dynamics model may be highly non-linear or noisy.\adnote{the problem isn't model free, the approach is; when the dynamics are not known, you can explicitly learn them, or learn a policy; that's the difference between model based and model free} In learning from demonstration, the cost function, which is the negative of the reward function, is usually unknown or significantly delayed\adnote{confusing; in learning from demonstration it is always unknown.
+unclear what significantly delayed means and it feels like you are confusing reinforcement with imitation learning}.
 In the grasping for clutter example, shown in Fig.
-\ref{fig:teaser}(b) the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback.
-To potentially avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls~\cite{argall2009survey}.
+\ref{fig:teaser}(b)\adnote{missing comma} the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback.\adnote{this is a reinforcement learning problem then, not a learning from demonstration problem} To potentially\adnote{potentially?
+sounds like a filler word} avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls~\cite{argall2009survey}.
+\adnote{Maybe keep first sentence and replace the rest with: In such problems, the robot does not have access to neither the cost function that it should optimize, nor the dynamics model.
+The former happens when it is difficult for a human to specify how to trade-off various aspects that matter, like [fill in and refer to driving].
+The latter happens when either the system of the interaction with the world is difficulty to characterize, like when the robot is pushing obstacles out of the way while reaching for a goal object (Fig.
+\ref{fig:teaser}(b).
+Rather than learning the cost function and the dynamics model, and then using optimization to produce a policy for the task, the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.}
 
-In the supervised setting, a policy is learned offline from a fixed set of examples.
-When the robot executes this policy, the sequential process can quickly evolve away from the previously explored set of states.
+In the supervised\adnote{all of them are the supervised setting} setting, a policy is \adnote{avoid passive voice} learned offline from a fixed set of examples.\adnote{In the offline setting, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.} When the robot executes this policy\adnote{During execution,}, the sequential process\adnote{what sequential process?
+you haven't said anything about sequential yet.
+During execution, a small error can accumulate and push the robot away from the region of the state space where it has seen examples.} can quickly evolve away from the previously explored set of states.
 The learned policy might not be helpful in unfamiliar states, leading to unrecoverable failures.
 For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where it has not encountered before, where its policy could  fail~\cite{pomerleau1989alvinn}.
-It has been shown, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
+It has been shown\adnote{by jesus}, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.\adnote{avoid passive, replace with "The number of errors made by the robot can, in the worst case, scale linearly..."}
 
@@
 \caption{ 
-\todo{update figure}
-SHIV reduces the number of queries to the supervisor in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery.
+\todo{update figure}\adnote{make everything flush in a grid, add caption to graph, increase font size in graph labels so that it is the same as the caption}
+SHIV \\adnote[(orange in the graph in d)} reduces the number of queries to the supervisor \adnote{compared to the state of the art?} in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery.
 }
@@
 
-On-line learning from demonstration approaches such as DAgger iteratively gather more examples from the supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
-In DAgger, a series of policies are learned.
-In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for all  new states, which are then aggregated with the previous examples for the next iteration.
+On-line\adnote{online;it's how you spell it in the rest of the document, and you don't spell offline off-line, so I don't get the reason for this inconsistency} learning from demonstration approaches such as DAgger \adnote{address this issue by }iteratively gather more examples from the supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+In DAgger, a series of policies are learned\adnote{DAgger learns a series of policies}.
+In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for all  new states, which are then aggregated with the previous examples for the next iteration\adnote{the learning step is missing here; At each itteration, the robot trains a policy based on the existing examples, then rolls out (executes) that policy and ....}.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-It has been shown for DAgger, the number of errors to scale linearly for strongly convex loss functions.
+It has been shown for DAgger, the number of errors to scale linearly for strongly convex loss functions.\adnote{clunky sentence.
+how about In DAgger, the number of errors scales only linearly with the time horizon of the task.
+-- also too early to talk about loss functions; note also the "only", because we use this to contrast with the end of the last paragraph, where it was quadratically}
 
-One drawback is that such online algorithms increase the burden on the supervisor.
-Our goal is to reduce supervisor burden without degrading robot performance, by only requesting demonstrations for risky states.
+One drawback is that\adnote{perhaps too weak of a statement; maybe "To achieve better performance guarantees, online algorithms singificatonly increase the burden on the supervisor, who now iteratively labels all states that the robot visits during training.} such online algorithms increase the burden on the supervisor.
+Our goal is to reduce supervisor burden without degrading robot performance,\adnote{performance.} \adnote{check spelling, there are many typos in this text}
+\begin{quote}
+\adnote{\emph{Our key insight is that the robot only needs to request demonstrations for risky states.}}
+\end{quote}
 
-Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that have been misclassified, in previous training data.
+Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that have\adnote{grammar:the region has, not have} been misclassified, in previous training data.
 %\adnote{Ken's version below does not seem to represent what we actually do.}
@@
 
+\adnote{We contribute an algorithm for online learning from demonstration that can actively decide whether it is necessary to ask the supervisor to label the new states that the robot encounters.
+Our algorithm, SHIV (...), reduced supervisor burden by..}
 We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which can reduce supervisor burden by only requesting supervision for risky states.
-SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions..
-It builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
+SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to \adnote{the} \emph{non-stationary} state distributions \adnote{the robot encounters as it iteratively executes learned policies}.
+It\adnote{I think we should say we here: we build on..} builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
+
+\adnote{we need results here; both the highlights of the analysis we do (so that people don;t think we are blindly comparing it to dagger without asking if all these changes are necessary), as well as the main point, that shiv is better for the same budget, and refer to fig 1}
 
@@
 Online learning from demonstration can be formulated as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
-In stream based active learning, the decision of whether to query the supervisor (for a control signal or not) is not over the entire state space (like in traditional pool-based active learning), but only on the states encountered during learning.
+In stream based active learning, the decision of whether to query the supervisor (for a control signal or not)\adnote{(for a label or control signal) or not -- note also where the ) ends} is not over the entire state space (like in traditional pool-based active learning), but only on the states encountered during learning.
+\adnote{I think streambased is more general then that, where the stream can come from some oracle and not from any learning process.}
 
@@
 We then use a classification method based on the One Class SVM \cite{scholkopf2001estimating} to predict if a state is risky or not risky, which we we define as safe.%Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.
+\adnote{we need more here on why this is good for a nonstationary distribution; michael, give it a try and send me a paragraph via email, i;ll help edit it}
 
@@
 One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
-trained on \cite{tokdar2010importance}. Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution.
+trained on \cite{tokdar2010importance}\adnote{,making states outside of this distribution risky}.
+Novelty detection \cite{hodge2004survey} is concerned with recognizing \adnote{when this happens: recognizing }that a sample is outside of this distribution.
+
 One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled.
@@
 To our knowledge the use of One Class SVM to online learning from demonstration has never been done before.
+\adnote{you can say this to me, but not really write it in a paper; I think that perhaps you want to say, and in a new paragraph so that it stands out, "Our contribution is the addition of stream-based active learning to online learning from demonstration.
+To do so, we use a query selection method based on the One Class SVM.}
+
 \begin{figure*}[t]
@@
 \section{Problem Statement}
-The goal of this work is to 1)learn a policy, such that for states visited after completion of training the difference in controls taken by the robot is as small as possible to that of the supervisor 2)the supervisor is only requested for a query in states, which the robot is mis-predicting the supervisor's control.
+The goal of this work is to 1) learn a policy, such that for states visited after completion of training the difference in controls taken by the robot is as small as possible to that of the supervisor\adnote{very complicated, could we simplify to "learn a policy that matches that of the supervisor's?} 2)the supervisor is only requested for a query in states, which the robot is mis-predicting the supervisor's control.\adnote{gramma weird here; the robot only asks the supervisor for an example for states in which it would have mis-predicted the supervisor's control.; but this is a bit strong, as we don't achieve this goal; maybe we want to learn a policy that matches that of the supervisor's while asking the supervisor for as few examples as possible?}
 
 \noindent\textbf{Modeling Choices and Assumptions} We model the system dynamics as markovian and stochastic.
-The system dynamics are model to be stationary (i.e.
+The system dynamics are model\adnote{first, you mean modeled; second, by jesus?
+:-) if it's we, say we.
+We model the system dynamics ad markovian, stochastic, and stationary.} to be stationary (i.e.
 given a state and a control the probability of the next state doesn't change over time).
@@
 We assume a known state space and set of controls.
-We assume access to a robot or simulator, such that we can start in some initial state and apply a series of controls and observe the following states that occur.
-Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.
+We assume access to a robot or simulator\adnote{simulator when you don't knowo the dynamics is weird; maybe say access to a robot (or a computatonally expensive simulator)}, such that we can start in some initial state and apply a series of controls and observe the following states that occur.\adnote{too coloquial; that can sample from the state sequences induced by a sequence of controls.} \adnote{I feel like this is a very weak assumption and we should not even bother mentioning that there is a robot -- of course there is, otherwise how are you even getting demonstrations..
+hmm..
+and it shows up later as well} Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.
+\adnote{clunky; Lastly, we assume access to a supervisor who can, given a state, provide the desired control signal label.
+(note that doing this also means you can do trajectories, so that's redundant}
+
+\adnote{weird that this subsection comes before some of the math, I keep wanting to refer to the math symbols and write the right equations for these things, like markovian and probability over the initial state and so on..}
 
@@
 We furthermore consider a set $\mathcal{U}$ of allowable control inputs for the robot, which can be discrete or
-continuous. We assume Markovian dynamics, such that the probability of state $\mathbf{x_{t+1}}\in
+continuous.
+We assume Markovian dynamics\adnote{see, this shows up again, and much better here when I know what the notation is and I can write it in math as well}, such that the probability of state $\mathbf{x_{t+1}}\in
 \mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
@@
 \int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
-the average density on states for any timepoint by 
+the average density on states \emph{for any timepoint} by 
 \begin{equation}
@@
 
-\noindent\textbf{Objective.} The objective of policy learning is to find a policy that minimizes some known cost function
+\noindent\textbf{Objective.} The objective of \adnote{typical (you want to not make the person think that this is our objective too)} policy learning is to find a policy that minimizes some known cost function
 $C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
@@
 be considered \cite{levine2015end}.
-In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
-a `supervisor' that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level.
+
+In our learning from demonstration setup, \adnote{however,}the robot does not have access to the cost function itself. Instead, it only has access to 
+a `supervisor'\adnote{why quotes all of the sudden?} that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level.
 \mlnote{the last statement is intended to mean implementors of this algorithm have agreed that the supervisor may not be optimal, but has a level of performance that is worth automating} We are furthermore given
@@
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
-$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a that minimizes the surrgoate loss between relative to the supervisor's policy.
+$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a \adnote{policy}that minimizes the surrgoate loss between relative to the supervisor's policy.
 
@@
 \begin{align}\label{eq:LFD_obj}
-\underset{\theta}{\min} \: E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}(\bx))].
+\underset{\theta}{\min} \: E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}(\bx))]
 \end{align}
@@
  If the robot could learn the policy  perfectly, this state density would match the one encountered in the user examples.
-But if the robot to makes an error, it changes the distribution of states over which it visits, which in practice can lead it to encounter states in which it has no labels from the expert and can't generalize too \cite{pomerleau1989alvinn}.
-Thus, the motivation for iterative algorithms like DAgger and now SHIV, which iterate between learning a policy and then the supervisor providing feedback.
+But if the robot to\adnote{delete to} makes an error, it changes the distribution of states over\adnote{delete over..} which it visits, which in practice can lead it to encounter states in which it has no labels from the expert and can't generalize too \cite{pomerleau1989alvinn}.\adnote{clunky: But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to.} Thus,\adnote{this sentence has no verb.
+maybe "this is the motivation.."} the motivation for iterative algorithms like DAgger and now SHIV, which iterate between learning a policy and then the supervisor providing feedback.
 The feedback is in the form of control signals on states sampled from the robot's new distribution of states.
@@
 \ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
-However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky to warrant a query.
+However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky \adnote{enough }to warrant a query.
 
 \subsection{Step 1.}
-The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):
+The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D}_k=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $\mathcal{D}$ of initial trajectory demonstrations):
 
@@
 
-This problem is a supervised learning problem that can be solved using machine learning techniques, for example a support vector machine or a neural network.
-Finding the right function representation and optimization method for a given problem is still an open question in machine learning, however a large number of advances have been made that make the use of these techniques very feasible \cite{scholkopf2002learning}
+This problem is a supervised learning problem that can be solved using machine learning techniques\adnote{this sentence makes use seem like we don't know machine learning; it's subtle but could hurt us; how about this is a standard supervised learning problem, solvable by estimators like a support vector machine or a neural net.}, for example a support vector machine or a neural network.
+Finding the right function representation and optimization method for a given problem is still an open question in machine learning, however a large number of advances have been made that make the use of these techniques very feasible \cite{scholkopf2002learning}\adnote{is this really needed?
+what does it add?
+it basically says figuring out what method to use is hard; maybe say: performance will vary with the selection of a particular estimator \cite{}}
 
 To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
-can be considered as present in policy's output.  A regularization technique in the optimization is
+can be considered as present in \adnote{the} policy's output\adnote{does espilon show up anywhere?
+do we need to say this?
+maybe a footnote instead?}.
+A regularization technique in the optimization is
 used to control the smoothness of the function that is fit to the sampled data.
@@
 We analyze the dependence on $\sigma$ in Sec.
-\ref{sec:car}.
-Our results suggest that SHIV is robust to this parameter selection.
+\ref{sec:car}, and our results suggest that SHIV is robust to this parameter selection.
 
@@
 \end{align}
+\adnote{we need $\sigma$ showing up here as $g_{\sigma}$ and remind the reader that the that inner product is a function of $\sigma$.
+might also be good to add a sentence or two on the intuitive role of sigma in this decision -- it caputures how much we expect states to generalize, i.e.
+how smooth the policy function is}
 
@@
 
-Our experiments analyze the performance of risk as a query selection strategy, with our without the addition of the second risk criteria --- regions of space where the surrogate loss is high.
+Our experiments analyze the performance of risk as a query selection strategy, with or without the addition of the second risk criteria, i.e. regions of space where the surrogate loss is high.
 
@@
 \section{Experiments}
+
+\adnote{We begin our experiments in an in-depth analysis of SHIV with a driving simulator.
+Here, we compare our query selection method with those typically used in active learning.
+We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than a confidence and query-by-committee based methods.
+We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from (refer to the right equation where we first introduce $g_{\sigma}$)).}
+
+\adnote{We then compare SHIV and DAgger on three domains: the driving simulator, push-grasping in clutter with a 4DOF arm, and surgery needle insertion using demonstrations from Dr.
+Douglas Boyd, surgeon as UC Davis.
+}
+
 All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
-1600 MHz memory in Python 2.7. The policies, $\pi_\theta$ were represented using either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
+1600 MHz memory in Python 2.7.
+The policies, $\pi_\theta$ were represented \adnote{by jesus; avoid passive :-)}using either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
 
@@
 $\nu = 0.1$ corresponds to looking at most $90\%$ of the data, which can make it robust to outliers.
-We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each example.
-Since the Driving Simulator worked with a much larger feature space the grid search started at 200, the Grasping and Surgical experiments started at 5.
+We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each example\adnote{example used to mean state-action pair; no idea what it means here}.
+Since the Driving Simulator worked with a much larger feature space the grid search started at 200, the Grasping and Surgical experiments started at 5.\adnote{no idea what any of this means; too detailed for here, move down to wherever it actually makes sense}
 
-\subsection{Driving Simulator} \label{sec:car}
-A common benchmark in Reinforcement Learning is the problem of learning a policy for a car to drive around a track
-\cite{argall2009survey}. To illustrate our method's ability to scale to high dimensions we use high dimensional HOG features extracted from images
+\adnote{breaking this into analysis and comparison}
+
+\subsection{SHIV Analysis}\label{sec:car}
+We analyze our algorithm in a driving domain.
+
+\noindent\textbf{Driving Simulator Domain.}
+\adnote{Our first domain is a common benchmark in Reinforcement Learning: learning a policy for a car to drive around a track \cite{}.}A common benchmark in Reinforcement Learning is the problem of learning a policy for a car to drive around a track
+\cite{argall2009survey}. To illustrate our method's ability to scale to high dimensions\adnote{missing comma} we use high dimensional HOG features extracted from images
 as a state representation.
+\adnote{we represent states via ?how many?
+HOG features extracted from images taken directly from the a driving simulator.
+(and move this sentence a bit down where it actually fits in, now it comes out of nowhere since I don't even know the problem yet}
 
 We implemented a driving simulator where the car must follow a polygonal track.
-The polygonal tracks are randomly created by sampling from a Gaussian with mean that is the center of the video game workspace.Then a convex hull is computed on the sampled points.
+The polygonal tracks are randomly created \adnote{We generated polygonal tracks }by \adnote{repeatedly }sampling from a Gaussian with mean that is the center of the video game workspace\adnote{centered in the middle of the workspace, and computing the convex hull of the sampled points.}.Then a convex hull is computed on the sampled points.
 In general this produces tracks composed of five to seven edges, an example is shown in Fig.
@@
 xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
-state space search through the driving simulator to plan the next control .
+state space search through the driving simulator to plan the next control.
 
@@
 validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
-exponential kernel with a bandwidth of $\sigma = 200$ and $\sigma_r = 200$.
+exponential kernel with a bandwidth of $\sigma = 200$ and $\sigma_r = 200$.\adnote{fix passive voice}
 
-We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
-defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
-In Fig.
-\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
-We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
-randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
-results from these experiments, suggesting a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+\subsubsection{Comparison to active learning approaches.}
+\adnote{breaking this up into factors and measures and results}
 
-\textbf{Comparison to active learning approaches:}
-To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane \cite{tong2002support}.
-The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-We further compared against Query By Committee, which was trained via bagging \cite{breiman1996bagging}.
-Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on.
+\noindent\textbf{Independent Variables:} We compare four query selection methods.
+We compare our combined notion of risk \adnote{refer to the right figure from back in related work part d}, with risk based on novelty alone \adnote{refer to fig c}  in order to test whether carving out regions that have been misclassified previously is valuable.
+
+We also compare against two baselines, typically used in active learning.
+The first is confidence based on distance from the classification hyperplane \cite{tong2002support} \adnote{refer to fig a}.
+We set the threshold distance to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
+
+The second baseline is Query By Committee \adnote{refer to fig b}, which was trained via bagging \cite{breiman1996bagging}.
+Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on\adnote{bad grammar, complex sentence structure; To obtain a committe, we divided the training data into 3 overlapping subsets, each with 80\% of the data.
+We trained a Linear SVM on each subset.}.
 If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
-We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
-We measured the performance in terms of the percentage of risky states that  are estimated to be safe by the active learning technique roll out.
-Results  are averaged over 50 tracks and shown in Fig.
+%We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
+
+We run each query selection method over 50 different car tracks.
+
+\noindent\textbf{Dependent Measures.
+}We measured the percentage of trully risky states that  are estimated to be safe by the active learning technique roll out\adnote{by the query selection method} \adnote{when you get new data from rolling out the trained policy, right?
+not on the old data, since the whole pointis to test this using a nonstationary distribution and that's supposed to be the reason it works better}.
+
+\noindent\textbf{Results.
+} Results  are averaged over 50 tracks and shown in Fig.
 \ref{fig:active_comp}.
+\adnote{Fig.
+x plots the performance for each query selection method, averaged over 50 tracks.
+We observe a significant performance improvement with methods based on novelty compared to confidence and query by committee.
+Furthermore, using the combined measure of risk performs better than relying solely on novelty.
+(is this significant?
+we should run at least a t test)}
 
-\textbf{Sensitivity Analysis}. 
-To analyze the sensitivity of our method we varied the $\sigma$ parameter of the risk estimation function $g_{\sigma}$.
-SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
-As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to  less data being used, but worst performance similar to the traditional supervise learning approach.
+\subsubsection{Sensitivity Analysis}.
+
+\noindent\textbf{Independent Variables.} To analyze the sensitivity of our method we varied the $\sigma$ parameter of the risk estimation function $g_{\sigma}$.
+\adnote{$\sigma$ is a measure of how much risk we allow, with smaller $\sigma$s leading to more risk-adverse behavior.} SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
+
+\noindent\textbf{Dependent Measures. } \adnote{fill in}
+
+\noindent\textbf{Results.
+} As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help (many states labeled) and very large sigma, $\sigma = 350$, relates to  less data being used, but worse performance similar to the traditional (offline) supervised learning approaches.
+\adnote{However, $\sigma$ values between $150$ and $250$ all achieve similarly good performance, suggesting that SHIV is robust to the choice of a particular $\sigma$.}
 
@@
 SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
-As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach.
+As shown in Table \ref{tab:sens},\adnote{dont refer to the table in its own caption} small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach.
+\adnote{fix this caption; it just repeats the text; use shorter captions, like "risk sensitivity analysis"}
    }
@@
 
-\subsection{Grasping In Clutter}
-To illustrate how our technique can be used the continuous case and with a human demonstrator. 
+\subsection{Comparing SHIV with DAgger}
+We compare SHIV with DAgger on three domains: the driving simulator from above, push-grasping in clutter, and needle insertion.
+
+\noindent\textbf{Independent Variables.} \adnote{We manipulate two variables.
+First, we manipulate the online learning from demonstration algorithm we use: SHIV vs.
+DAgger.
+Second, we manipulate how many examples the algorithms are allowed to ask for: we set a budget of labeled states, and analyze performance as this budget increases.}
+
+\noindent\textbf{Dependent Measures.} \adnote{For each algorithm and budget of states labeled, we measure the real cost that the learned policy attains (e.g. number of crashes in the driving domain).}
+
+\noindent\textbf{Hypothesis: } \adnote{We expect SHIV to consistently achieve a lower cost that DAgger for the same budget of supervisor examples.
+Equivalently, we expect that SHIV achives the same performance as DAgger, but by asking for fewer examples and thus reducing supervisor burden.}
+
+\subsubsection{Driving.}
+
+\noindent\textbf{Domain.} Our first domain is the driving domain described above.
+We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
+defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
+
+\noindent\textbf{Results.} 
+In Fig.
+\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
+We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
+randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
+results from these experiments, suggesting a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+
+\subsubsection{Grasping In Clutter}
+
+\noindent\textbf{Domain.}
+To illustrate how our technique can be used the continuous case and with a human demonstrator.\adnote{this sentence does not have a verb} 
 We investigate having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
-Grasping in clutter can be a challenging task because as shown in Kiteav et al.
-traditional motion planning techniques require knowledge of how the objects will behave when in contact.
-They used iLQR with a hand tuned cost function and dynamics given by a physics simulator to successfully grab an object without displacing the other movable objects on the table off \cite{kitaevphysics}.
+Grasping in clutter can be a challenging task because as shown in Kiteav et al.\adnote{need some commas here} traditional motion planning techniques require knowledge of how the objects will behave when in contact.
+They\adnote{never say they; either cite and say Kiteav et al use, or [12] uses (meaning the paper), or the method uses, but never they use} used iLQR with a hand tuned cost function and dynamics given by a physics simulator to successfully grab an object without displacing the other movable objects on the table off \cite{kitaevphysics}.
 We are interested in learning such a policy via human demonstrations.
+\adnote{need better motivation here; cite kiteav and king/sidd in a sentence that says that this type of task is important and has been used as a manipulation benchmark.
+then say it is difficult because modeling the physics of pushing is nontrivial, and relies on knowing many paramteres such as the coefficient of fricition between the objects and the table, etc.}
 
 We used Box2D a physics simulator to model a virtual world. We simulated a 4 DOF robot arm with three main joints and a parallel jaw gripper as
-displayed in Fig. \ref{fig:teaser}(b).
+displayed in Fig.
+\ref{fig:teaser}(b).
+\adnote{here we need to make it clear that we only use box2d in lieu of giving a robot real demonstratons; our algorithm shiv does not have access to box 2d, and instead learns a policy that is implicitly mindful of the physics effects}
 
@@
 
-In Fig. \ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 rounds for SHIV and DAgger.
-Our experiment suggest we are able to achieve an approximate $70\%$ reduction in data.
+\noindent\textbf{Results.} In Fig. \ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 rounds for SHIV and DAgger.
+Our experiment suggests that we are able to achieve an approximate $70\%$ reduction in data.
+\adnote{again?
+please check these numbers, is it a typo or is it 70\% every time; and be more specific -- supporting our hypothesis, our results suggests that SHIV can achieve the same performance with a 70\% reduction in the number of examples needed.}
 
@@
 
-\subsection{Surgical Experiment}
+\subsubsection{Surgical Experiment}
+
+\noindent\textbf{Domain.}
 Robotic Surgical Assistants (RSAs) are frequently used for procedures such as: prostectomy, uterectomy, and tumorectomies within the abdominal and thoracic cavities with high success rates~\cite{van2013laparoscopic,darzi2004impact}.
@@
 terms of Euclidean distance in translational component, which is in centimeters. We run DAgger and SHIV both for 20 iterations and average over 40 different starting positions.
-Results shown in Fig. \ref{fig:needle} suggest a reduction $67\%$ in the amount of supervisor queries needed.
+
+\noindent\textbf{Results. }
+Results shown in Fig. \ref{fig:needle} suggest a reduction $67\%$ in the amount of supervisor queries needed. \adnote{remarkable that it is so consitent over all domains, if that is really the case!}
 
@@
 \section{Discussions and Future Work}
+\adnote{as florian says, this needs a lot of work; it needs to start by summarizing the key contribution and results, and it needs to state the limitations clearly -- we've talked a lot about limitations during out in person meetings, hopefully michael took notes; only then you can point to some big areas of future work that actually sounds exciting}
 \fpnote{we'll need to work on this}

### 2015-09-03 paper.tex
Anca's comments

--- 2015-09-01 paper.tex
@@
 
-\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^{1,2}$% <-this % stops a space
+\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeffrey Mahler$^1$, \\ Florian T. Pokorny$^1$, Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
 \thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh, ftpokorny, anca\}@berkeley.edu}}%
@@
 \begin{abstract}
-Online algorithms for robot model-free learning from demonstration (such as DAgger) can learn policies for problems where system
-dynamics and cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
+Online algorithms for robot model-free robot learning from demonstration (such as DAgger) can learn policies for problems where the system
+dynamics and the cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
 signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
-algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states.
+algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to \emph{only request supervision for risky states}.
 SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.
@@
 
-In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig.
-\ref{fig:teaser}, from examples provided by a competent supervisor, usually a human.
-The problem is model-free if  the system dynamics are unknown, eg.
-dynamics model may be highly non-linear or noisy.
-In learning from demonstration, the cost function, which is the negative of the reward function, is usually unknown or significantly delayed.
-In the grasping for clutter example, shown in Fig.
-\ref{fig:teaser}(b) the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback.
-To potentially avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls~\cite{argall2009survey}.
+In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment (Fig.
+\ref{fig:teaser}), from examples provided by a  supervisor, usually a human.
+In such problems, the robot does not have access to neither the cost function that it should optimize, nor the dynamics model.
+The former happens when it is difficult for a human to specify how to trade-off various aspects that matter, like when the robot is reaching for a goal object while not pushing objects off a table(Fig.
+\ref{fig:teaser}(b).
+The latter happens when either the system or the interaction with the world is difficult to characterize with the given observations, like in Fig.
+\ref{fig:teaser}(a) the robot must stay on the track but only has access to visual information from a bird's eye view.
 
-In the supervised setting, a policy is learned offline from a fixed set of examples.
-When the robot executes this policy, the sequential process can quickly evolve away from the previously explored set of states.
+Rather than learning the cost function and the dynamics model, and then using optimization to produce a policy for the task, the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
+
+In the offline learning from demonstration setting, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
+During execution, a small error can accumulate and push the robot away from the region of the state space where it has seen examples.
 The learned policy might not be helpful in unfamiliar states, leading to unrecoverable failures.
-For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where it has not encountered before, where its policy could  fail~\cite{pomerleau1989alvinn}.
-It has been shown, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
+For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
+The number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
 
@@
 \caption{ 
-\todo{update figure}
-SHIV reduces the number of queries to the supervisor in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery.
+SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) cost of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
 }
@@
 
-On-line learning from demonstration approaches such as DAgger iteratively gather more examples from the supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
-In DAgger, a series of policies are learned.
-In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for all  new states, which are then aggregated with the previous examples for the next iteration.
+Online learning from demonstration approaches such as DAgger address this issue by iteratively gathering more examples from the supervisor in states the robot is likely to visit~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+DAgger learns a series of policies.
+At each iteration, the robot trains a policy based on the existing examples, then rolls out (executes) that policy and the supervisor provides demonstrations for all states the robot visits.
+The new examples are aggregated with the old examples for the next iteration.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-It has been shown for DAgger, the number of errors to scale linearly for strongly convex loss functions.
+In DAgger, the number of errors scales only linearly with the time horizon of the task.
 
-One drawback is that such online algorithms increase the burden on the supervisor.
-Our goal is to reduce supervisor burden without degrading robot performance, by only requesting demonstrations for risky states.
+To achieve better performance guarantees, online algorithms can significantly increase the burden on the supervisor, who now labels all states that the robot visits during training.
+Our goal is to reduce supervisor burden without degrading robot performance.
 
-Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that have been misclassified, in previous training data.
+Our key insight, to reduce burden, is that the robot only needs to request demonstrations for risky states.
+Risk arises because:  (1) states are different than the states previously encountered and used to train the current policy, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that has been misclassified, in previous training data.
 %\adnote{Ken's version below does not seem to represent what we actually do.}
@@
 
-We introduce the SHIV algorithm (Svm-based reduction in Human InterVention), which can reduce supervisor burden by only requesting supervision for risky states.
-SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions..
-It builds on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
+We contribute an algorithm for online learning from demonstration that can actively decide whether it is necessary to ask the supervisor to label the new states that the robot encounters.
+Our algorithm, SHIV  (Svm-based reduction in Human InterVention), reduces supervisor burden by only requesting supervision for risky states.
+SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to the non-stationary state distributions the robot encounters as it iteratively executes learned policies.
+We build on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
 
-% \adnote{Old intro:}
-
-% Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
-% against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
-% underlying cost function describing the task, traditional model based control approaches are often not applicable. In
-% these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching a robot how to
-% accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.\adnote{these are very random things to cite for LfD, FYI - there is a survey by Argall that usually gets cited}
-
-% One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
-% supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
-% while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
-% of states encountered during the execution of a policy are not independent random variables, thus making statistical
-% inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
-% time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
-% behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
-% distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
-% presenting an iterative method that first trains a policy on the data observed using standard supervised learning
-% techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
-% the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
-% and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
-% robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
-% through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-
-% During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
-% should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
-% human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
-% reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
-% executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
-% required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
-% training data in its vicinity, which potentially means our policy will mis-predict the supervisor
-% \cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
-% nonetheless. If an accurate density estimation corresponding to
-% the pairs of visited states and control signals is available, the first scenario can be captured by regions of
-% state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
-% is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
-% model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
-% machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with supervisor
-% demonstrations.
-% %
-% %Vague!!!
-% %This property can be seen used in importance sampling when data is collected from one distribution, but tested on
-% %another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
-% %
-% While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
-% space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
-% representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
-% SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
-% \cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
-% image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
-% estimate where the local policy estimate is inconsistent with the supervisor demonstrations.
-
-% To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
-% where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
-% and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
-% inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
-% able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
-% analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
-% the Markovian assumption).
-
-% Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
-% demonstrations and reduces supervisor
-% burdon by asking for supervisor demonstrations only in `risky' states. 
-% We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
-% of the distribution of states with demonstrations and additionally
-% and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
-% risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
-% peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
-% averaged over 20 levels.
-% {\color{blue}[-- FINALIZE --]}
+\mlnote{Ken didn't want to repeat the abstract here, so we removed this section}
+\adnote{we need results here; both the highlights of the analysis we do (so that people don;t think we are blindly comparing it to dagger without asking if all these changes are necessary), as well as the main point, that shiv is better for the same budget, and refer to fig 1}
 
@@
 Online learning from demonstration can be formulated as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
-In stream based active learning, the decision of whether to query the supervisor (for a control signal or not) is not over the entire state space (like in traditional pool-based active learning), but only on the states encountered during learning.
+In stream based active learning, the decision of whether to query the supervisor (for a label or control signal) or not is not over the entire state space (like in traditional pool-based active learning), but on states drawn one at a time from some data source.
+In  online learning  from demonstration, the data source is the states encountered during learning.
 
@@
 
-In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on novelty (is the state an outlier to the training distribution), as in Fig.
+The  estimator is a function of the current distribution.
+Therefore, it no longer provides a good measure of confidence when that distribution changes, as it does when the robot is rolling out a learned policy and starts encountering further away states.
+Instead of relying on the estimator, our measure of risk explicitly identifies when states are drawn from a different distribution, i.e.
+when they are novel.
+
+%%In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on novelty (is the state an outlier to the training distribution), as in Fig.
 \ref{fig:support_example}(c).
@@
 One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
-trained on \cite{tokdar2010importance}. Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution.
+trained on \cite{tokdar2010importance}, making states outside of this distribution risky.
+Novelty detection \cite{hodge2004survey} is concerned with recognizing when this happens: recognizing that a sample is outside of this distribution.
+
 One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled.
@@
 An alternative to evaluating the probability of a data point is to measure distance to its nearest neighbors \cite{knox1998algorithms}. However, this approach was shown to be
-susceptible to outliers since nearest neighbors  incorporates only local information about the data.
-Thus, a group of outliers can be close together, but significantly far from the majority of the data and nearest neighbors would mark them as not novel \cite{hodge2004survey}.
+susceptible to issues, since nearest neighbors  incorporates only local information about the data.
+For example, a group of outliers can be close together, but significantly far from the majority of the data and nearest neighbors would mark them as not novel \cite{hodge2004survey}.
 
-Our approach is based on the One Class SVM proposed by Scholk{\"o}pf et al., which estimates a particular quantile level set for the training data by solving a convex quadratic program  to find support
+Our approach is based on the One Class SVM proposed by Scholk{\"o}pf et al., which estimates a particular quantile level set for the training data by solving a convex quadratic program  to the find support
 vectors~\cite{scholkopf2001estimating}. The method has been theoretically shown to approximate the quantile levelset of a density estimate
@@
 To our knowledge the use of One Class SVM to online learning from demonstration has never been done before.
+\mlnote{Ken, wanted to our knowledge in the last part} \adnote{you can say this to me, but not really write it in a paper; I think that perhaps you want to say, and in a new paragraph so that it stands out, "Our contribution is the addition of stream-based active learning to online learning from demonstration.
+To do so, we use a query selection method based on the One Class SVM.}
+
 \begin{figure*}[t]
@@
 
-\caption{\todo{update figure with elipse} A comparison of different query selection strategies for active learning on a non-stationary distribution.
-The shaded and empty circles are training data from two classes, $0$ and $1$ respectively.
-The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $1$.
-Typical strategies assign high risk to states close the decision boundary (a), or for which a set of estimators disagree (b).
+\caption{A comparison of different query selection strategies for active learning on a non-stationary distribution.
+The shaded and empty circles are training data from two classes, $1$ and $0$ respectively.
+The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $0$.
+Typical strategies classify states close the decision boundary as risky(a), or for which a set of estimators disagree (b).
 Neither of these apply to our new samples in red.
-In contrast, we use a strategy that is amenable to non-stationary distributions by assigning high risk to novel states (c) and states in historically mislabeled regions.
-%Confidence and Query by Committee methods measure
-%{\color{blue} FP:estimate} states far away from the decision boundary of the estimator as having low risk,
-%however novelty detection methods measure {\color{blue} FP:estimate} the level of risk as
-%{\color{blue}FP:by} how far a point is from the trained data. Our
-%modified risk method attempts to measure risk both as a function of how far it
-%{\color{blue}it gramatically refers to risk,
-%but you mean sample "it$\mapsto$a sample"?} is from data trained on
-%{\color{blue}grammatically strange$\mapsto$from the training data} and the decision boundary of the estimator. 
+In contrast, we use a strategy that is amenable to non-stationary distributions by classifying  novel states as safe (i.e not risky) (c) and states in historically mislabeled regions.
 }
@@
 
-% The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
-% \cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human supervisor
-% to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
-% neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
-% robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
-% to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
-% configurations of the~\cite{schulman2013case}.
+\section{Problem Statement}
+The goal of this work is to learn a policy that matches that of the supervisor's while asking the supervisor for as few examples as possible.
 
-% A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
-% the robot and the environment are not known and that no access to a cost function describing a given task is available.
-% Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
-% problem can be treated as a supervised learning problem that determines a function from state space to
-% controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
-% associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
-% travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
-% not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
-% demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
-% rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
-% stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
-% robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.
+\mlnote{Ken is a big fan of  discussing the assumptions and model choices without notation before everything else, so a reader can quickly determine if this method suits there problem}
 
-% Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
-% policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
-% the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
-% controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
-% before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
-% \cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
-% (HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
-% methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
-% \cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
-% to move sematically in a building with a training set consisting of of humans following similar verbal instructions
-% \cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
-% Search, which replaces the supervisor with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.
-
-% One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
-% provide control inputs that the supervisor would have applied for every state encountered along a roll-out of a trajectory at every interation of the
-% algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
-% human or an algorithm with a high computational demand.
-
-% In prior work, Judah et al. proposed applying active learning techniques to improve the learninng ability of an algorithm given a fixed budget. 
-% \cite{judah2011active,judah2012active}. A drawback of this approach is that it requires us to estimate a complete
-% density of states from the samples, which can be difficult especially in high dimensions. Furthermore, the  
-% at each iteration only one labeled state was given. Thus, the robot could potentially be required to try out many more iterations of learning in order to successfully accomplished the task.
-
-% \begin{enumerate}
-% \item Our work is different than traditional pool base active learning for two reasons 1) the data comes in as a stream (i.e.
-we decided whether to label or not label the sample vs.
-using a pool base methods) 2) the estimator being trained is part of the parametrization of the distribution of states being encountered at run time, thus violating the i.i.d assumption common in these methods.
-% \item Some techniques that can handle these approaches are 1) uncertainty sampling , or measuring some confidence level in a classifier and deciding whether to label or not.
-2) Query by committee, which involves sampling a committee of hypothesises from a version space of consistent classifiers 3) Density weighted model, which fitting a density to the unlabeled pool and then using a technique such as uncertainty sampling or query by committee to chose the label with the highest uncertainity times the density under the model.
-The reason for density weighted model is because the previous approaches are prone to labeling outliers \cite{settles2008analysis}.
-% \item Our approach can be considered a query selective strategy that uses the ideas of density weighted models.
-The level set estimation of the One Class SVM is a binary decision metric of how close a point is to the global support points that define its neighbors.
-Then our hole punching technique places a "prior" on points that are likely to be misclassified condition on the fact that points nearby are misclassified.
-Thus, encapsulating both a notion of uncertainity and distance to relative points.
-% \item One point that I've been thinking about is that traditional active learning is about training an estimator on some fix distribution and then trying to predict how the estimator will change given new points sampled from the same distribution.
-Thus most approaches work on the estimator themselves (query by committee sampling different hypotheses or uncertainty sampling measuring confidence).
-This assumption is violated in DAgger because you are sampling from a new distribution each iteration different from what is trained on.
-Thus, a confidence threshold such as (distance to hyperplane for an svm) would be misleading because if the point was drawn from a different distribution it could be very far from the hyperplane, but have a different label than that side of the hyperplane.
-Thus, we purpose not looking at the estimator but at the data itself.
-We make an assumption that points close to other points in our feature space will have similar labels, but the outliers are unknown and will need new labels.
-I suggest we run a uncertainty sampling technique vs.
-SHIV to verify all this.
-
-% \end{enumerate}
-
-% %[Let's discuss this part]
-% {\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
-% an incorrect control input, we leverage a
-% property in statistical machine learning that a trained model will be able to generalize within the distribution it is
-% trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
-% distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
-% approach is to estimate the probability density of states the policy is trained on.
-However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.
-
-% Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
-% to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
-% neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
-% susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
-% \cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
-% at a point was high, the point was considered as likely to be outside of the estimators domain within which
-% generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
-% and might require a large amount of hyperparameter tuning.
-
-% Our approach is in particular based on the One Class SVM proposed by Scholk{\"o}pf et al. which estimates a user
-% defined quantile level set for a collection of training data by solving a convex quadratic program  to find support
-% vectors. The method has been theoretically shown to approximate the quantile levelset of a density estimate
-% asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
-% In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for outlier detection of high-dimensional 
-% image data.
-
-\section{Problem Statement}
-The goal of this work is to 1)learn a policy, such that for states visited after completion of training the difference in controls taken by the robot is as small as possible to that of the supervisor 2)the supervisor is only requested for a query in states, which the robot is mis-predicting the supervisor's control.
-
-\noindent\textbf{Modeling Choices and Assumptions} We model the system dynamics as markovian and stochastic.
-The system dynamics are model to be stationary (i.e.
-given a state and a control the probability of the next state doesn't change over time).
+\noindent\textbf{Modeling Choices and Assumptions}  We model the system dynamics as markovian, stochastic, and stationary.
+Stationary meaning  given a state and a control the probability of the next state doesn't change over time.
 We model the initial state as sampled from a distribution over the state space.
@@
 We assume a known state space and set of controls.
-We assume access to a robot or simulator, such that we can start in some initial state and apply a series of controls and observe the following states that occur.
-Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.
+We assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.
+Lastly, we assume access to a supervisor who can, given a state, provide the desired control signal label.
 
@@
 We furthermore consider a set $\mathcal{U}$ of allowable control inputs for the robot, which can be discrete or
-continuous. We assume Markovian dynamics, such that the probability of state $\mathbf{x_{t+1}}\in
+continuous. We model dynamics, as Markovian, such that the probability of state $\mathbf{x_{t+1}}\in
 \mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
@@
 
-\noindent\textbf{Objective.} The objective of policy learning is to find a policy that minimizes some known cost function
-$C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
-For example, in task of inserting a peg into a hole, a function on distance between the peg's current and desired final state can
+\noindent\textbf{Objective.} The objective of  policy learning is to find a policy that minimizes some known cost function $C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$.
+The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific.
+For example, in the task of inserting a peg into a hole, a function on the distance between the peg's current and desired final state can
 be considered \cite{levine2015end}.
-In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
-a `supervisor' that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level.
+
+However in our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
+a supervisor that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level.
 \mlnote{the last statement is intended to mean implementors of this algorithm have agreed that the supervisor may not be optimal, but has a level of performance that is worth automating} We are furthermore given
@@
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
-$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a that minimizes the surrgoate loss between relative to the supervisor's policy.
+$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrgoate loss between relative to the supervisor's policy.
 
@@
  If the robot could learn the policy  perfectly, this state density would match the one encountered in the user examples.
-But if the robot to makes an error, it changes the distribution of states over which it visits, which in practice can lead it to encounter states in which it has no labels from the expert and can't generalize too \cite{pomerleau1989alvinn}.
-Thus, the motivation for iterative algorithms like DAgger and now SHIV, which iterate between learning a policy and then the supervisor providing feedback.
+But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to \cite{pomerleau1989alvinn}.Thus, motivating iterative algorithms like DAgger and now SHIV, which iterate between learning a policy and then the supervisor providing feedback.
 The feedback is in the form of control signals on states sampled from the robot's new distribution of states.
@@
 \ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
-However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky to warrant a query.
+However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky enough to warrant a query.
 
 \subsection{Step 1.}
-The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):
+The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D}_k=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $\mathcal{D}$ of initial trajectory demonstrations):
 
@@
 
-This problem is a supervised learning problem that can be solved using machine learning techniques, for example a support vector machine or a neural network.
-Finding the right function representation and optimization method for a given problem is still an open question in machine learning, however a large number of advances have been made that make the use of these techniques very feasible \cite{scholkopf2002learning}
+This problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net \footnote{To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$
+can be considered as present in the policy's output.  A regularization technique in the optimization is
+used to control the smoothness of the function that is fit to the sampled data.
+In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.}.
+Finding the right function representation and optimization method for a given problem is still an open question in machine learning.
+However a large number of advances have been made that make the use of these techniques very feasible \cite{scholkopf2002learning} \mlnote{The point was to acknowledge to traditional machine learning people that the problem is still hard and not solved.
+Ken didn't want to offend them}\adnote{is this really needed?
+what does it add?
+it basically says figuring out what method to use is hard; maybe say: performance will vary with the selection of a particular estimator \cite{}}
 
-To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
-can be considered as present in policy's output.  A regularization technique in the optimization is
-used to control the smoothness of the function that is fit to the sampled data.
-In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.
  \subsection{Step 2}
-The second step starts in both SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.
+The second step starts in both SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely under $p(\bx|\theta_{k})$.
 
@@
 
-Providing correct control inputs or ``labeling'' at each
-iteration and each state in DAgger can be tedious, imposing a large burden on the supervisor.
+Providing correct control inputs or ``labeling'' for all states encountered at each
+iteration can impose a large burden on the supervisor.
 Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of risk to actively decide whether a label is necessary.
-For every state encountered $\bx_t$, it applies a decision function $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which will capture how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.
+For every state encountered $\bx_t$, it applies a decision function $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which captures how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.
 
@@
 
-Dagger has been experimentally shown to perform well in both simulation and real world
-    experiments~\cite{NIPS2014_5421,ross2010reduction,ross2013learning}. Under a `no regret' assumption, Ross et al.\cite{ross2010reduction} furthermore
-deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically.
  For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary.
@@
 previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance}, or 2) the surrogate loss of the current policy at a state in $\mathcal{D}$ is high, so that the state, although visited, does
-not model the supervisor's control inputs correctly.
+loss \cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at a state in $\mathcal{D}$ is high, so that the state does not model the supervisor's control inputs correctly.
 
-To evaluate risk in high-dimensional state spaces (such as HOG features on images, like in our driving simulator testcase), we use
+To evaluate risk in high-dimensional state spaces (such as HOG features on images, like in our driving simulator, Fig. \ref{fig:teaser}(a)), we use
 a modified version of the technique known as the One Class SVM that  approximately estimates a boundary of a user defined quantile of
@@
 Here, the parameter $\nu$ controls the penalty or `slack term' and is equivalent to $\gamma$ \cite{vert2006consistency}
-in the quantile definition when bandwidths decay at appropriate rates as the number of samples increases. The decision
+in the quantile definition, Eq. \ref{eq:quantile}, as the number of samples increases. The decision
 function, determining point membership in the approximate quantile levelset is given by
@@
 \end{align}
+\mlnote{The decison function actually used is not till the end, this is just a piece of it}
+\adnote{we need $\sigma$ showing up here as $g_{\sigma}$ and remind the reader that the that inner product is a function of $\sigma$.
+might also be good to add a sentence or two on the intuitive role of sigma in this decision -- it captures how much we expect states to generalize, i.e.
+how smooth the policy function is}
 
@@
 \vspace{-2ex}
-\begin{align}\label{eq:decision_func}
+\begin{align}
 g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho).
@@
 
-where $\alpha_i$ corresponds to the dual variables.    For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
-a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available. The novelty detection method can be visualized in Fig. \ref{fig:support_example}(c). 
+where $\alpha_i$ corresponds to the dual variables.  The novelty detection method can be visualized in Fig. \ref{fig:support_example}(c). 
 However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
@@
 We then define the overall decision function as:
-$$g_{\sigma}(\bx) = g_{r} (\bx)+ g_{s}(\bx)$$
+
+\vspace{-2ex}
+\begin{align}\label{eq:decision_func}
+g_{\sigma}(\bx) = g_{r} (\bx)+ g_{s}(\bx)
+\end{align}
+
 points are deemed risky if $g_{\sigma}(\bx) \neq 0$.  Practically, this modification corresponds to
@@
 
-Our experiments analyze the performance of risk as a query selection strategy, with our without the addition of the second risk criteria --- regions of space where the surrogate loss is high.
+The decision function parametrization consists of the kernel bandwidth $\sigma$ in $g_s$.
+Changing sigma corresponds to how much influence each point in the training set has on the measure of risk.
+Large $\sigma$ corresponds to points nearby being safe.
 
-% \subsection{The \acro~algorithm}
-
-% Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately
-% predict the supervisor's control, by means of the thresholded surrogate just discussed.  
-% % Too vague:
-% %In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.
-% %Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  
-% To reduce the burden on the supervisor, we estimate the training data's quantile level-set for a user-defined threshold
-% $\nu$ and further modify the corresponding super-levelset estimate by excluding neighborhoods of states that incur a loss
-% above a threshold $\varepsilon$ chosen by the user.
-% The user then only provides control input demonstrations for states of trajectory roll-outs that lie outside the
-% resulting risk-aware quantile super-levelset.
-
-% {\color{blue} [-- F: use formal algorithm and explain here instead --]} 
-% \subsubsection{Step 1}
-
-% Similar to DAgger, at iteration $k$, the algorithm estimates a policy, $\pi_{\theta_k}$ on the dataset $\mathcal{D}_k$
-% by solving the optimization problem in Eq. \ref{eq:super_objj}. We then estimate the quantile super-levelset of the
-% training data state-distribution solving the optimization for the modified One Class SVM using the dataset $\mathcal{D}_k$. 
-% This yields a decision boundary $g_k(\bx)$, where is $g(\bx)\ge 0$ if a state $\bx$ is to be considered of `low risk' and $-1$ otherwise.
-
-%  \subsubsection{Step 2}
-%  In DAgger, the policy $\pi_{\theta_k}$ is rolled out for a fixed number of time steps, however this could lead to the
-%  robot entering pathological states that are risky. To prevent this, we terminate the rolled out policy if the risk, is
-%  above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of providing control inputs for every state, the supervisor is only required to 
-%  provide demonstrations of control inputs for states for which $g(\bx)=-1$.  These demonstrations are then added to the
-%  dataset $\mathcal{D}_{k+1}$ and the algorithm returns to Step 1.
-
-% We note that the choise of user-defined thresholds $\nu$, $\epsilon$, $r_0$ yield an implicit trade-off
-% between exploration and exploitation. For large quantile super-levelsets, the robot is confident and asks the
-% supervisor only rarely for demonstrations. Similarly, large $\varepsilon$ values allow the robot to be tolerant to
-% incorrectly trained policies with large surrogate loss, while large $r_0$ settings allow the robot to explore risky
-% areas and obtain more labels from the supervisor in those regions.
+Our experiments analyze the performance of risk as a query selection strategy, with or without the addition of the second risk criteria, i.e. regions of space where the surrogate loss is high.
 
 \section{Experiments}
+
+We begin our experiments in an in-depth analysis of SHIV with a driving simulator.
+Here, we compare our query selection method with those typically used in active learning.
+We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than a confidence and query-by-committee based methods.
+We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from Eq.
+\ref{eq:decision_func}).
+
+We then compare SHIV and DAgger on three domains: a driving simulator, push-grasping in clutter with a 4DOF arm, and surgery needle insertion using demonstrations from Dr.
+Douglas Boyd, a master surgeon at UC Davis.
+
 All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
-1600 MHz memory in Python 2.7. The policies, $\pi_\theta$ were represented using either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
+1600 MHz memory in Python 2.7. The policies, $\pi_\theta$ are either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
 
 Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_r$.
-We set $\nu = 10^{-3}$ and $\nu_r = 0.1$ for all experiments.
-$\nu = 0.1$ corresponds to looking at most $90\%$ of the data, which can make it robust to outliers.
-We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each example.
-Since the Driving Simulator worked with a much larger feature space the grid search started at 200, the Grasping and Surgical experiments started at 5.
+We set $\nu = 0.1$ and $\nu_r =10^{-3}$ for all experiments.
+We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each domain.
 
-\subsection{Driving Simulator} \label{sec:car}
-A common benchmark in Reinforcement Learning is the problem of learning a policy for a car to drive around a track
-\cite{argall2009survey}. To illustrate our method's ability to scale to high dimensions we use high dimensional HOG features extracted from images
-as a state representation.
+\subsection{SHIV Analysis}\label{sec:car}
+We analyze our algorithm in a driving domain.
 
+\noindent\textbf{Driving Simulator Domain.}
+Our first domain is a common benchmark in Reinforcement Learning: learning a policy for a car to drive around a track~\cite{argall2009survey,ross2010efficient,ross2011reduction}.
 We implemented a driving simulator where the car must follow a polygonal track.
-The polygonal tracks are randomly created by sampling from a Gaussian with mean that is the center of the video game workspace.Then a convex hull is computed on the sampled points.
+We generated polygonal tracks by repeatedly sampling from a Gaussian with mean that is the center of the video game workspace centered in the middle of the workspace, and computing the convex hull of the sampled points.Then a convex hull is computed on the sampled points.
 In general this produces tracks composed of five to seven edges, an example is shown in Fig.
@@
 policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
-validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
-exponential kernel with a bandwidth of $\sigma = 200$ and $\sigma_r = 200$.
+validation on the initial training examples. We set SHIV's parameters  of the exponential kernel's bandwidth as $\sigma = 200$ and $\sigma_r = 200$.
 
-We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
-defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
-In Fig.
-\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
-We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
-randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
-results from these experiments, suggesting a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+\subsubsection{Comparison to active learning approaches.}\
 
-\textbf{Comparison to active learning approaches:}
-To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane \cite{tong2002support}.
-The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-We further compared against Query By Committee, which was trained via bagging \cite{breiman1996bagging}.
-Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on.
+\noindent\textbf{Independent Variables:} We compare four query selection methods.
+We compare our combined notion of risk (Fig.
+\ref{fig:support_example}(d)), with risk based on novelty alone (Fig.
+\ref{fig:support_example}(c)) in order to test whether carving out regions that have been misclassified previously is valuable.
+
+We also compare against two baselines, typically used in active learning.
+The first is confidence based on distance from the classification hyperplane \cite{tong2002support} (Fig.
+\ref{fig:support_example}(a)).
+We set the threshold distance to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
+
+The second baseline is Query By Committee (Fig.
+\ref{fig:support_example}(d)), which was trained via bagging \cite{breiman1996bagging}.
+To obtain a committe, we divided the training data into 3 overlapping subsets, each with 80\% of the data.
+We trained a Linear SVM on each subset.
 If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
-We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
-We measured the performance in terms of the percentage of risky states that  are estimated to be safe by the active learning technique roll out.
-Results  are averaged over 50 tracks and shown in Fig.
-\ref{fig:active_comp}.
+%We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
 
-\textbf{Sensitivity Analysis}. 
-To analyze the sensitivity of our method we varied the $\sigma$ parameter of the risk estimation function $g_{\sigma}$.
+We run each query selection method over 50 different car tracks.
+
+\noindent\textbf{Dependent Measures.
+}We measured the percentage of truly risky states, encountered during the first policy roll out, that  are estimated to be safe by the active learning technique.
+The active learning techniques are trained on the initial demonstrations $\mathcal{D}_0$, which is different then the distribution being sampled from, $p(\bx|\theta_0)$, in this experiment.
+
+\noindent\textbf{Results.
+} Fig.
+\ref{fig:active_comp}  plots the performance for each query selection method, averaged over 50 tracks.
+We observe a significant performance improvement with methods based on novelty compared to confidence and query by committee.
+Furthermore, using the combined measure of risk performs better than relying solely on novelty.
+
+\subsubsection{Sensitivity Analysis}.
+
+\noindent\textbf{Independent Variables.} To analyze the sensitivity of our method we varied the $\sigma$ parameter of the risk estimation function $g_{\sigma}$.
+$\sigma$ is a measure of how much risk we allow, with smaller $\sigma$s leading to more risk-adverse behavior.
 SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
-As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to  less data being used, but worst performance similar to the traditional supervise learning approach.
+
+\noindent\textbf{Dependent Measures.
+} For each  $\sigma$, we measure the final cost function for the policy $\pi_{\theta}$ after 6 iterations and the number of examples SHIV requested from the supervisor.
+
+\noindent\textbf{Results.
+} As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help (many states labeled) and very large sigma, $\sigma = 350$, relates to  less data being used, but worse performance similar to the traditional (offline) supervised learning approaches.
+However, $\sigma$ values between $150$ and $250$ all achieve similarly good performance, suggesting that SHIV is robust to the choice of a particular $\sigma$.
 
@@
 SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
-As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach.
+Small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach.
    }
@@
 \centering
-\includegraphics[width=9cm, height=4cm]{figures/risk_bar.eps}
+\includegraphics[width=\columnwidth, height=4cm]{figures/risk_bar.eps}
 \caption {  A comparison of different active learning approaches in terms of the percentage of risky states that are estimated to be safe by the active learning technique during the first policy roll out.
@@
 \centering
-\includegraphics[width=8cm, height=6cm]{figures/dagger_shiv_one_class.eps}
+\includegraphics[width=\columnwidth, height=6cm]{figures/dagger_shiv_one_class.eps}
 \caption{We compare performance for the Driving Simulator in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
@@
 Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
-\ref{fig:car_cost} suggest an $70\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
+\ref{fig:car_cost} suggest an $71\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
 \vspace*{-10pt}
@@
 
-\subsection{Grasping In Clutter}
-To illustrate how our technique can be used the continuous case and with a human demonstrator. 
+\subsection{Comparing SHIV with DAgger}
+We compare SHIV with DAgger on three domains: the driving simulator from above, push-grasping in clutter, and needle insertion.
+
+\noindent\textbf{Independent Variables.} We manipulate two variables.
+First, we manipulate the online learning from demonstration algorithm we use: SHIV vs.
+DAgger.
+Second, we manipulate how many examples the algorithms are allowed to ask for: we set a budget of labeled states, and analyze performance as this budget increases.
+
+\noindent\textbf{Dependent Measures.}For each algorithm and budget of states labeled, we measure the real cost that the learned policy attains (e.g. number of crashes in the driving domain).
+
+\noindent\textbf{Hypothesis: } We expect SHIV to consistently achieve a lower cost that DAgger for the same budget of supervisor examples.
+Equivalently, we expect that SHIV achieves the same performance as DAgger, but by asking for fewer examples and thus reducing supervisor burden.
+
+\subsubsection{Driving.}
+
+\noindent\textbf{Domain.} Our first domain is the driving domain described above and illustrates SHIV's performance in high dimensions. 
+We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
+defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
+
+\noindent\textbf{Results.} 
+In Fig.
+\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
+We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
+randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
+results from these experiments, suggesting a $71\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+
+\subsubsection{Grasping In Clutter}
+
+\noindent\textbf{Domain.}
 We investigate having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
-Grasping in clutter can be a challenging task because as shown in Kiteav et al.
-traditional motion planning techniques require knowledge of how the objects will behave when in contact.
-They used iLQR with a hand tuned cost function and dynamics given by a physics simulator to successfully grab an object without displacing the other movable objects on the table off \cite{kitaevphysics}.
+Grasping an object in a cluttered environment is a common task for a robot in an unstructured environment and has been considered a benchmark for robotic manipulation~ \cite{kitaevphysics,kingnonprehensile}.
+The task is difficult because modeling the physics of pushing an object is non-trivial and requires knowing the shape, mass distribution and friction coefficient of all objects on the table.
 We are interested in learning such a policy via human demonstrations.
 
-We used Box2D a physics simulator to model a virtual world. We simulated a 4 DOF robot arm with three main joints and a parallel jaw gripper as
-displayed in Fig. \ref{fig:teaser}(b).
+In lieu of real robot demonstrations, we used Box2D a physics simulator to model a virtual world. We simulate a 4 DOF robot arm with three main joints and a parallel jaw gripper as
+displayed in Fig. \ref{fig:teaser}(b). SHIV and DAgger do not have access to the underlying dynamics of the simulator and must learn a policy from only demonstrations.
 
@@
 
-In Fig. \ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 rounds for SHIV and DAgger.
-Our experiment suggest we are able to achieve an approximate $70\%$ reduction in data.
+\noindent\textbf{Results.} In Fig.
+\ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 rounds for SHIV and DAgger.
+Supporting our hypothesis, our results suggests that SHIV can achieve the same performance with a 64\% reduction in the number of examples needed.
 
@@
 \caption{We compare performance for Grasping in Clutter in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
-Initial results, which are averaged over 8 different trials suggest a $65\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
+Initial results, which are averaged over 8 different trials suggest a $64\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
 \vspace*{-10pt}
@@
 terms of Euclidean distance in translational component, which is in centimeters. We run DAgger and SHIV both for 20 iterations and average over 40 different starting positions.
-Results shown in Fig. \ref{fig:needle} suggest a reduction $67\%$ in the amount of supervisor queries needed.
+
+\noindent\textbf{Results. }
+ In Fig.
+\ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 40 rounds for SHIV and DAgger.
+Supporting our hypothesis, our results suggests that SHIV can achieve the same performance with a $67\%$ reduction in the number of examples needed.
 

### 2015-09-07 paper.tex
updated figures, added limitations

@@
 \setboolean{include-notes}{true}
-\newcommand{\adnote}[1]{\ifthenelse{\boolean{include-notes}}%
+\newcommand{\adnote}[1]{\ifthenelse{ \boolean{include-notes}}%
  {\textcolor{blue}{\textbf{AD: #1}}}{}}
 
- \newcommand{\fpnote}[1]{\ifthenelse{\boolean{include-notes}}%
+ \newcommand{\fpnote}[1]{\ifthenelse{ \boolean{include-notes}}%
  {\textcolor{blue}{\textbf{FP: #1}}}{}}
 
-  \newcommand{\mlnote}[1]{\ifthenelse{\boolean{include-notes}}%
+  \newcommand{\mlnote}[1]{\ifthenelse{ \boolean{include-notes}}%
  {\textcolor{purple}{\textbf{ML: #1}}}{}}
@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v17]}
+\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v19]}
 
@@
 We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented spatial transform.
-Results suggest that SHIV can reduce the number of queries up to 70$\%$\adnote{double check this}.
+Results suggest that SHIV can reduce the number of queries up to 70$\%$.
 
@@
 
-In the offline learning from demonstration setting, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
-During execution, a small error can accumulate and push the robot away from the region of the state space where it has seen examples.
-The learned policy might not be helpful in unfamiliar states, leading to unrecoverable failures.
-For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
-The number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
+\begin{figure}[ht]
+\centering
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth]{figures/teaser.pdf}
+\includegraphics[width=0.5\textwidth]{figures/teaser.pdf}
 \caption{ 
@@
 \end{figure}
+
+In the offline learning from demonstration setting, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
+During execution, a small error can accumulate and push the robot away from the region of the state space where it has seen examples.
+The learned policy might not be helpful in unfamiliar states, leading to unrecoverable failures.
+For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
+The number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
 
@@
 We assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.
-Lastly, we assume access to a supervisor who can, given a state, provide the desired control signal label.
+Lastly, we assume access to a supervisor who can, given a state, provide a control signal label.
+We assume the supervisor the supervisor can be noisy and imperfect, but also that the robot can at best reach the same level of performance of the supervisor after learning.
 
@@
 Large $\sigma$ corresponds to points nearby being safe.
+For a policy that is a smooth function $\sigma$ should be large.
 
@@
 Douglas Boyd, a master surgeon at UC Davis.
+Each domain test different aspects of our algorithm: the driving simulator has a high dimensional visual state space, grasping in clutter has a human demonstrator provide the labels and is a challenging manipulation problem, surgical needle insertion uses data from a real robot and has an expert demonstrator.
 
@@
 state space search through the driving simulator to plan the next control.
+The algorithm is only allowed to search a finite amount a time ahead in the game and is prone to error, thus on averages crashes 5 times per lap.
 
@@
 \centering
-\includegraphics[width=\columnwidth, height=6cm]{figures/grasp_clutter.eps}
+\includegraphics[width=\columnwidth, height=2in]{figures/grasp_clutter.eps}
 \caption{We compare performance for Grasping in Clutter in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
@@
 \centering
-\includegraphics[width=\columnwidth, height=6cm]{figures/needle_insertion_results.eps}
+\includegraphics[width=\columnwidth, height=2in]{figures/needle_insertion_results.eps}
 \caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
@@
 \section{Discussions and Future Work}
-\adnote{as florian says, this needs a lot of work; it needs to start by summarizing the key contribution and results, and it needs to state the limitations clearly -- we've talked a lot about limitations during out in person meetings, hopefully michael took notes; only then you can point to some big areas of future work that actually sounds exciting}
-\fpnote{we'll need to work on this}
-SHIV currently provides a way to apply active learning to online learning from demonstration, however its use of level set estimation of the underlying distribution introduces several hyper parameters.
-As Fig.
-shown these can significantly effect performance if not tuned correctly.
-Future work will look at using cross validation on a hold out set of data to more effectively tune parameters.
+Online imitation learning algorithms have been successful on array of task~\cite{NIPS2014_5421,ross2010reduction}, however can significantly increase the burden on a supervisor.
+Our algorithm, SHIV, implements stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
+We empirically evaluated our method on three different domains: a driving simulator, grasping in clutter and surgical needle insertion.
+Results suggest a $70\%$ reduction in the number of queries to the supervisor needed.
 
-Another potential issue is that each iteration of SHIV requires solving a quadratic program with the Gram matrix.
-As we scale to harder tasks that require significantly more data, this can become problematic.
-Future work will look at using techniques like PCA and random feature projections to scale efficiently \todo{cite something}.
+While achieving a high level of performance, SHIV has several limitations.
+For instance, the selection of the value of $\sigma$ can affect performance and a poor choice could result in the algorithm becoming offline imitation learning, as shown in Table \ref{tab:sens}.
+Future work will look at better understanding the relationship of $\sigma$ to the function $\pi_{\theta}$ and how to automatically select it.
 
-Lastly, our approach is promising in simulation.
-However we need to evaluate how our active learning method will work on a real robot with noisy sensor observations.
-Future work will be doing the grasping in clutter experiments on an actual robot.
+ Furthermore, to update the decision function $g_{\sigma}$ requires solving a quadratic program, which has an upper bound computationally complexity of $O(n^3)$ in the number of data points.
+This can effect the ability of using our modified One Class SVM for larger problems.
+Future work will look at using techniques such as random features or PCA on the kernel Gram matrix to allow for better scaling~\cite{scholkopf2002learning}.
+
+ Lastly, online imitation learning only allows a policy to learn to be as good as the supervisor.
+If the supervisor is imperfect then the robot will be as well.
+Future work will look at combining techniques from inverse reinforcment learning\cite{argall2009survey} with online imitation learning to allow the robot to improve upon it's policy after supervision is done.
 

### 2015-09-10 paper.tex
added Ken's comments ...v20

@@
 \usepackage{benktools}
+\usepackage{bbm}
 
@@
 \newboolean{include-notes}
-\setboolean{include-notes}{true}
+\setboolean{include-notes}{false}
 \newcommand{\adnote}[1]{\ifthenelse{ \boolean{include-notes}}%
@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v19]}
+\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v20]}
 
@@
 \begin{abstract}
-Online algorithms for robot model-free robot learning from demonstration (such as DAgger) can learn policies for problems where the system
+Online learning from demonstration algorithms, such as DAgger, can learn policies for problems where the system
 dynamics and the cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
-signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
-algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to \emph{only request supervision for risky states}.
+signals) as the robot encounters new states when executing its current best policy. We introduce the SHIV
+algorithm (Svm-based reduction in Human InterVention), which reduces this burden by only requesting supervision for risky states.
 SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.
 To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented spatial transform.
-Results suggest that SHIV can reduce the number of queries up to 70$\%$.
+We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936 dimension visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter simulation with Box2D with a 22 dimension state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16 dimension state represented spatial transform.
+Results suggest that SHIV can learn equivalent policies with up to $70\%$ fewer queries.
 
-%In traditional imitation learning, a human supervisor provides a few demonstrations to the robot, which then \emph{offline} learns a policy to extrapolate these examples to new situations.
-One challenge is that during execution of the learned policy, a small but inevitable error will amplify, taking the robot further and further away from the regions of state space for which it has seen examples.
-
-%\emph{Online} imitation learning algorithms such as DAgger address this challenge by iteratively executing a trained policy, and asking the supervisor for additional examples along the states visited by that policy.
-Such algorithms perform well in new situations, but rely much more heavily on extensive human supervision.
-
-%Our goal is to reduce the amount of human supervision required in imitation learning, without sacrificing performance.
-\emph{Our key insight is that the robot should ask for supervision only when its current trained policy has high risk.}
-
-%We introduce a method for online imitation learning that evaluates risk based on novelty of a state, as well as prior difficulty in labeling a nearby states.
-Our algorithm, SHIV (SVM-Based Reduction in Human Intervention), follows the trained policy when evaluated risk is low, and asks for human supervision otherwise.
-
-%A trained policy can have a high risk of predicting the wrong action for a state for two reasons: 1) the state is too far away from the training states, and 2) the state is in an area in which the learner has historically struggled.
-We introduce a method for iterative imitation learning that estimates regions of high risk based on these two criteria, and limits queries to the supervisor to only high risk states.
-Our method instantiates stream based active learning, with a query selection strategy that generalizes novelty detection to querying in areas that are inherently difficult to correctly label.
-
-% \adnote{Old abstract:}
-
-% For robot control problems where the reward function  and the dynamics of the environment are not specified, the
-% learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
-% demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
-% the problem of determining a policy as an iterative supervised learning problem which alternates between executing a
-% trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. In this
-% work, we propose a novel algorithm, \acro~which is based on DAgger and which estimates the riskiness of states
-% encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
-% states used for training the current policy. Since learning a quantile function for high-dimensional input data is
-% challenging, we instead modify an SVM-based approach to quantile estimation that employs regularization to solve this
-% problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
-% user-defined quantile super-levelset is encountered. Our approach furthermore reduces the amount of neccessary
-% supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
-% In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
-% DAgger, our approach results in similar performance levels as DAgger while reducing the amount of required supervisor
-% control inputs by more than {\color{blue}[-- TODO --]} percent.
  \end{abstract}
@@
 
-In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment (Fig.
-\ref{fig:teaser}), from examples provided by a  supervisor, usually a human.
-In such problems, the robot does not have access to neither the cost function that it should optimize, nor the dynamics model.
-The former happens when it is difficult for a human to specify how to trade-off various aspects that matter, like when the robot is reaching for a goal object while not pushing objects off a table(Fig.
-\ref{fig:teaser}(b).
-The latter happens when either the system or the interaction with the world is difficult to characterize with the given observations, like in Fig.
-\ref{fig:teaser}(a) the robot must stay on the track but only has access to visual information from a bird's eye view.
+In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment, from examples provided by a  supervisor, usually a human.
+In such problems, the robot does not have access to either the cost function that it should optimize, nor the dynamics model.
+The former occurs when it is difficult to specify how to trade-off various aspects that matter, like when the robot is reaching for a goal object while not pushing objects off a table.
+The latter occurs when either the system or the interaction with the world is difficult to characterize based on observations, as in Fig.
+\ref{fig:teaser}(a) the robot drives on the track but only has access to visual information from a bird's eye view.
 
-Rather than learning the cost function and the dynamics model, and then using optimization to produce a policy for the task, the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
+Rather than explicitly learning the cost function, like in inverse reinforcement learning, and the dynamics model, and then using optimization to produce a policy for the task, the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
+Learning from demonstrations algorithms can be categorized as offline, where the robot only observes demonstrations, or online, where the robot interacts with the world and receives feedback from the supervisor.
 
@@
 
-In the offline learning from demonstration setting, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
-During execution, a small error can accumulate and push the robot away from the region of the state space where it has seen examples.
-The learned policy might not be helpful in unfamiliar states, leading to unrecoverable failures.
+In offline learning from demonstration, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
+During execution, a small error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.
 For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
-The number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
+Ross and Bagnell showed the number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
 
-Online learning from demonstration approaches such as DAgger address this issue by iteratively gathering more examples from the supervisor in states the robot is likely to visit~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
-DAgger learns a series of policies.
+Online learning from demonstration addresses this issue by iteratively gathering more examples from the supervisor in states the robot encounters~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+One such algorithm, DAgger learns a series of policies.
 At each iteration, the robot trains a policy based on the existing examples, then rolls out (executes) that policy and the supervisor provides demonstrations for all states the robot visits.
-The new examples are aggregated with the old examples for the next iteration.
+The new state/control examples are aggregated with the old examples for the next iteration.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-In DAgger, the number of errors scales only linearly with the time horizon of the task.
+In DAgger, it was proved under certain conditions, the number of errors scales only linearly with the time horizon of the task.
 
-To achieve better performance guarantees, online algorithms can significantly increase the burden on the supervisor, who now labels all states that the robot visits during training.
+DAgger significantly increases the burden on the supervisor, who now labels all states that the robot visits during training.
 Our goal is to reduce supervisor burden without degrading robot performance.
 
-Our key insight, to reduce burden, is that the robot only needs to request demonstrations for risky states.
-Risk arises because:  (1) states are different than the states previously encountered and used to train the current policy, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that has been misclassified, in previous training data.
+Our key insight is that the robot only needs to request demonstrations for risky states.
+Risk arises because:  (1) states are sufficiently different than the states previously encountered, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that has been misclassified in previous training data.
 %\adnote{Ken's version below does not seem to represent what we actually do.}
@@
 
-We contribute an algorithm for online learning from demonstration that can actively decide whether it is necessary to ask the supervisor to label the new states that the robot encounters.
-Our algorithm, SHIV  (Svm-based reduction in Human InterVention), reduces supervisor burden by only requesting supervision for risky states.
+We present an algorithm for online learning from demonstration that can actively decide whether it is necessary to ask the supervisor to label the new states that the robot encounters.
+SHIV  (Svm-based reduction in Human InterVention) reduces supervisor burden by only requesting supervision for risky states.
 SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to the non-stationary state distributions the robot encounters as it iteratively executes learned policies.
 We build on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
-
-\mlnote{Ken didn't want to repeat the abstract here, so we removed this section}
-\adnote{we need results here; both the highlights of the analysis we do (so that people don;t think we are blindly comparing it to dagger without asking if all these changes are necessary), as well as the main point, that shiv is better for the same budget, and refer to fig 1}
 
@@
 
-\begin{figure*}[t]
-\centering
-
-\includegraphics[width=\textwidth]{figures/active_learning.pdf}
-
-\caption{A comparison of different query selection strategies for active learning on a non-stationary distribution.
-The shaded and empty circles are training data from two classes, $1$ and $0$ respectively.
-The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $0$.
-Typical strategies classify states close the decision boundary as risky(a), or for which a set of estimators disagree (b).
-Neither of these apply to our new samples in red.
-In contrast, we use a strategy that is amenable to non-stationary distributions by classifying  novel states as safe (i.e not risky) (c) and states in historically mislabeled regions.
-}
-\label{fig:support_example}
-\end{figure*}
-
 \section{Problem Statement}
@@
 
-\mlnote{Ken is a big fan of  discussing the assumptions and model choices without notation before everything else, so a reader can quickly determine if this method suits there problem}
-
-\noindent\textbf{Modeling Choices and Assumptions}  We model the system dynamics as markovian, stochastic, and stationary.
-Stationary meaning  given a state and a control the probability of the next state doesn't change over time.
+\noindent\textbf{Modeling Choices and Assumptions}  We model the system dynamics as Markovian, stochastic, and stationary.
+Stationary dynamics meaning  given a state and a control the probability of the next state doesn't change over time.
+Note this is different then the non-stationary distribution over the states the robot encounters during learning.
 We model the initial state as sampled from a distribution over the state space.
@@
 Lastly, we assume access to a supervisor who can, given a state, provide a control signal label.
-We assume the supervisor the supervisor can be noisy and imperfect, but also that the robot can at best reach the same level of performance of the supervisor after learning.
+We assume the supervisor can be noisy and imperfect.
+Noting that the robot cannot surpass the level of performance of the supervisor.
 
 \noindent\textbf{Policies and State Densities.}
-We denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
+Following conventions from control theory, we denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
@@
 Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ from time $0$ to time $t-1$. This density can be computed by marginalization: $p(\bx_t|\theta) =
-\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
-the average density on states \emph{for any timepoint} by 
-\begin{equation}
-p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)
-\label{eq:density}
-\end{equation}
+$\pi_{\theta}$ from time $0$ to time $t-1$.  Following \cite{ross2010reduction}, we can compute
+the average density on states for any timepoint by $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
 
-While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
+While we do not assume knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
 \theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
@@
 
-However in our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
-a supervisor that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level.
-\mlnote{the last statement is intended to mean implementors of this algorithm have agreed that the supervisor may not be optimal, but has a level of performance that is worth automating} We are furthermore given
+However in this case, we do not have access to the cost function itself. Instead, we only have access to 
+a supervisor that can achieve a desire level of performance on the task.  We are furthermore given
 an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
@@
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
-$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrgoate loss between relative to the supervisor's policy.
+$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrogate loss relative to the supervisor's policy.
 
-Following \cite{ross2010reduction}, our objective then consists of determining a policy $\pi_{\theta}$ minimizing the expected surrogate loss, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
+Following \cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
 
@@
 
- If the robot could learn the policy  perfectly, this state density would match the one encountered in the user examples.
-But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to \cite{pomerleau1989alvinn}.Thus, motivating iterative algorithms like DAgger and now SHIV, which iterate between learning a policy and then the supervisor providing feedback.
+ If the robot could learn the policy  perfectly, this state density would match the one encountered in user examples.
+But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to \cite{pomerleau1989alvinn}.This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing feedback.
 The feedback is in the form of control signals on states sampled from the robot's new distribution of states.
 
-% The optimization problem in Eq.
-\ref{eq:LFD_obj} is  typically non-convex.
-It can also be difficult to solve, since we only have access to samples from the supervisor's policy $\tilde{\pi}$ arising from the demonstration trajectories $\mathcal{D}$.
-To address these issues Stephane and Ross proposed an iterative method known as DAgger \cite{ross2010reduction}.
+\section{Risky and Safe States}
 
-\section{SHIV} \label{sec:SHIV}
+\begin{figure*}[t]
+\centering
 
-Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq.
-\ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
-However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky enough to warrant a query.
+\includegraphics[width=\textwidth]{figures/active_learning.pdf}
 
-\subsection{Step 1.}
-The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D}_k=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $\mathcal{D}$ of initial trajectory demonstrations):
-
- \vspace{-2ex}
-\begin{align}\label{eq:super_objj}
-\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{M} l(\pi_{\theta}(\bx_i),\bu_i).
-\end{align}
-
-This problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net \footnote{To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$
-can be considered as present in the policy's output.  A regularization technique in the optimization is
-used to control the smoothness of the function that is fit to the sampled data.
-In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.}.
-Finding the right function representation and optimization method for a given problem is still an open question in machine learning.
-However a large number of advances have been made that make the use of these techniques very feasible \cite{scholkopf2002learning} \mlnote{The point was to acknowledge to traditional machine learning people that the problem is still hard and not solved.
-Ken didn't want to offend them}\adnote{is this really needed?
-what does it add?
-it basically says figuring out what method to use is hard; maybe say: performance will vary with the selection of a particular estimator \cite{}}
-
- \subsection{Step 2}
-The second step starts in both SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely under $p(\bx|\theta_{k})$.
-
-What happens next, however, differs.
-For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
-Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \pi(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
-The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
-$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
-%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
+\caption{A comparison of different query selection strategies for active learning on a non-stationary distribution.
+The shaded and empty circles are training data from two classes, $1$ and $0$ respectively.
+The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $0$.
+Typical strategies classify states close the decision boundary as risky(a), or for which a set of estimators disagree (b).
+Neither of these apply to our new samples in red.
+In contrast, we use a strategy that is amenable to non-stationary distributions by classifying  novel states as safe (i.e not risky) (c) and states in historically mislabeled regions.
+}
+\label{fig:support_example}
+\end{figure*}
 
@@
 iteration can impose a large burden on the supervisor.
-Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of risk to actively decide whether a label is necessary.
-For every state encountered $\bx_t$, it applies a decision function $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which captures how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.
+Instead of asking the supervisor for labels at all visited states, SHIV uses a measure of risk to actively decide whether a label is necessary.
 
-SHIV only asks for supervision on states for which $g_{\sigma}(\bx) \neq 0$:
+We define a state as "risky" for 2 reasons: 1) it lies in an area with a low density of
+previously trained states, which can cause the current policy to mis-predict the supervisor and incur high surrogate
+loss \cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at the state  is high, so that the state is unlikely to model the supervisor's control inputs correctly.
+States that are not classified as "risky" are deemed "safe".
 
-$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$
-
-Steps 1 and 2 are repeated for $K$ iterations or until 
-the cumulative surrogate is smaller than some predefined threshold\footnote{In the original DAgger the policy rolled out
-was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
-or the robots. The use of this stochastically mix policy was for theoretical analysis. In practice, it is recommended
-to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.
-
- For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary.
-However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods.
-We analyze the dependence on $\sigma$ in Sec.
-\ref{sec:car}, and our results suggest that SHIV is robust to this parameter selection.
-
-\subsection{Measuring Risk}
-% However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
-% quad-copter, the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
-We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
-previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at a state in $\mathcal{D}$ is high, so that the state does not model the supervisor's control inputs correctly.
-
-To evaluate risk in high-dimensional state spaces (such as HOG features on images, like in our driving simulator, Fig. \ref{fig:teaser}(a)), we use
-a modified version of the technique known as the One Class SVM that  approximately estimates a boundary of a user defined quantile of
-a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
+The amount of data needed to estimate the density, scales exponentially in the dimension of the state space \cite{nadaraya1964estimating}. 
+Thus, to evaluate risk in high-dimensional state spaces , such as the HOG features in our driving simulator, Fig. \ref{fig:teaser}(a), we use
+a modified version of the technique known as the One Class SVM that  estimates a regularized boundary of a user defined quantile on the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
 %\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}
@@
 defined by
+\vspace{-2ex}
 \begin{align}\label{eq:quantile}
@@
 \end{align} 
-$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure which most commonly is given by the Lebesgue measure.
+$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure.
 Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
@@
 To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al.
-looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}.
+represents the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}.
 By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
-derives an approximation of the quantile function described in Eq. \ref{eq:quantile}, which in particular has rigorous
-convergence guarantees asymptotically when a normalized Gaussian kernel $k$ is chosen and bandwidths decay at an
-appropriately chosen rate as the number of samples tends to infinity \cite{vert2006consistency}.
+derives an approximation of the quantile function described in Eq. \ref{eq:quantile}.
 This approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$,
@@
 in the quantile definition, Eq. \ref{eq:quantile}, as the number of samples increases. The decision
-function, determining point membership in the approximate quantile levelset is given by
-
-\vspace{-2ex}
-\begin{align}\label{eq:decision_func}
-g(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
-\end{align}
-\mlnote{The decison function actually used is not till the end, this is just a piece of it}
-\adnote{we need $\sigma$ showing up here as $g_{\sigma}$ and remind the reader that the that inner product is a function of $\sigma$.
-might also be good to add a sentence or two on the intuitive role of sigma in this decision -- it captures how much we expect states to generalize, i.e.
-how smooth the policy function is}
-
+function, determining point membership in the approximate quantile levelset is given by $g(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho)$.
 Here, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
 $g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
-if $x$ lies strictly in the quantile sub-levelset. The dual form of the optimization yields a Quadratic Program 
-that can be solved efficiently \cite{scholkopf2001estimating}. In the dual the decision function is given by
+if $x$ lies strictly in the quantile sub-levelset.
 
-\vspace{-2ex}
-\begin{align}
-g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho).
-\end{align}
-
-where $\alpha_i$ corresponds to the dual variables.  The novelty detection method can be visualized in Fig. \ref{fig:support_example}(c). 
+The dual form of the optimization yields a Quadratic Program 
+that has worst case computational complexity of $O(n^3)$.
+However, Sch{\"o}lkopf et al.
+developed an improved optimization method that has empirically been shown to be as low as $O(n^2)$ \cite{scholkopf2001estimating}.
+In the dual, the decision function is given by $g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho)$ where $\alpha_i$ corresponds to the dual variables.
+The novelty detection method can be visualized in Fig.
+\ref{fig:support_example}(c).
 However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
@@
 
+\vspace{-2ex}
 \begin{align}
@@
 
-We divide up our data in to two sets those correctly classified:
-$$\mathcal{D}_{s}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=1\}$$
-and those states incorrectly classified: 
-$$\mathcal{D}_{r}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=-1\}$$
+We divide up our data in to two sets those correctly classified: $\mathcal{D}_{s}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=1\}$ and those states incorrectly classified: $\mathcal{D}_{r}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=-1\}$
 A separate One-Class SVM is then trained on each set of states, ($D_{s}$ and $D_{r}$) and providing measures of the level sets, $g_{s}$ and $g_{r}$.
@@
 \end{align}
-
 points are deemed risky if $g_{\sigma}(\bx) \neq 0$.  Practically, this modification corresponds to
@@
 The decision function parametrization consists of the kernel bandwidth $\sigma$ in $g_s$.
-Changing sigma corresponds to how much influence each point in the training set has on the measure of risk.
-Large $\sigma$ corresponds to points nearby being safe.
-For a policy that is a smooth function $\sigma$ should be large.
+We treat $\sigma$ as a "risk sensitivity" parameter.
+For two reasons: 1)The expected number of examples, after a policy roll out, the supervisor can be asked is  $T*\int_\bx \mathbbm{1}(g_{\sigma}(\bx) == 0) p(\bx|\theta)d\bx$.
+Thus, smaller $\sigma$ corresponds to asking for more examples.
+2) A relation exists between how smooth the supervisor's poilcy, $\tilde{\pi}$ and how many examples are needed to learn it.
+Thus, a large $\sigma$ can be dangerous for policies with sharp variation because it will treat points as safe that are really risky.
 
-Our experiments analyze the performance of risk as a query selection strategy, with or without the addition of the second risk criteria, i.e. regions of space where the surrogate loss is high.
+\section{SHIV} \label{sec:SHIV}
+
+Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq.
+\ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
+However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky enough to warrant a query.
+
+\subsection{Step 1}
+The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D}_k=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $\mathcal{D}$ of initial trajectory demonstrations):
+
+ \vspace{-2ex}
+\begin{align}\label{eq:super_objj}
+\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{M} l(\pi_{\theta}(\bx_i),\bu_i).
+\end{align}
+
+This sub-problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net \footnote{To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$
+can be considered as present in the policy's output.  A regularization technique in the optimization is
+used to control the smoothness of the function that is fit to the sampled data.
+In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.}.
+Performance can vary though with the selection of a the estimator \cite{scholkopf2002learning}
+
+ \subsection{Step 2}
+The second step SHIV and DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.
+
+What happens next, however, differs between SHIV and DAgger.
+For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
+Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
+The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
+$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
+%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
+
+SHIV only asks for supervision on states for which are risky, or $g_{\sigma}(\bx) \neq 0$: 
+$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$
+Steps 1 and 2 are repeated for $K$ iterations or until 
+the robot has achieved sufficient performance on the task\footnote{In the original DAgger the policy rolled out
+was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
+or the robots. The use of this stochastically mix policy was for theoretical analysis. In practice, it is recommended
+to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.
 
@@
 
-We begin our experiments in an in-depth analysis of SHIV with a driving simulator.
-Here, we compare our query selection method with those typically used in active learning.
+All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
+1600 MHz memory in Python 2.7.
+The policies, $\pi_\theta$ are either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
+Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_r$.
+We set $\nu = 0.1$ and $\nu_r =10^{-3}$ for all experiments.
+We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each domain.
+
+We compare SHIV and DAgger in three domains: a driving simulator, push-grasping in clutter with a 4DOF arm, and surgical needle insertion using demonstrations from Dr.
+Douglas Boyd, a surgeon and professor at UC Davis.
+Each domain test different aspects of our algorithm: the driving simulator has a high dimensional visual state space, grasping in clutter has a human demonstrator provide the labels and is a challenging manipulation problem, surgical needle insertion uses data from a real robot and has an expert demonstrator.
+
+We then  compare our query selection method with those typically used in active learning.
 We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than a confidence and query-by-committee based methods.
@@
 
-We then compare SHIV and DAgger on three domains: a driving simulator, push-grasping in clutter with a 4DOF arm, and surgery needle insertion using demonstrations from Dr.
-Douglas Boyd, a master surgeon at UC Davis.
-Each domain test different aspects of our algorithm: the driving simulator has a high dimensional visual state space, grasping in clutter has a human demonstrator provide the labels and is a challenging manipulation problem, surgical needle insertion uses data from a real robot and has an expert demonstrator.
+\subsection{Comparing SHIV with DAgger}
+We compare SHIV with DAgger on three domains: the driving simulator from above, push-grasping in clutter, and needle insertion.
+We hypothesize that SHIV achieves the same performance as DAgger, but by asking for fewer examples and thus reducing supervisor burden.
 
-All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
-1600 MHz memory in Python 2.7. The policies, $\pi_\theta$ are either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
+The independent variables are two variables.
+First, we manipulate the online learning from demonstration algorithm we use: SHIV vs.
+DAgger.
+Second, we manipulate how many examples the algorithms are allowed to ask for: we set a budget of labeled states, and analyze performance as this budget increases.
 
-Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_r$.
-We set $\nu = 0.1$ and $\nu_r =10^{-3}$ for all experiments.
-We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each domain.
+For each algorithm and budget of states labeled, we measure the real cost that the learned policy attains (e.g. number of crashes in the driving domain).
 
-\subsection{SHIV Analysis}\label{sec:car}
-We analyze our algorithm in a driving domain.
+\subsubsection{Driving Simulator}
 
-\noindent\textbf{Driving Simulator Domain.}
 Our first domain is a common benchmark in Reinforcement Learning: learning a policy for a car to drive around a track~\cite{argall2009survey,ross2010efficient,ross2011reduction}.
 We implemented a driving simulator where the car must follow a polygonal track.
-We generated polygonal tracks by repeatedly sampling from a Gaussian with mean that is the center of the video game workspace centered in the middle of the workspace, and computing the convex hull of the sampled points.Then a convex hull is computed on the sampled points.
-In general this produces tracks composed of five to seven edges, an example is shown in Fig.
+We generate a polygonal track by repeatedly sampling from a Gaussian with mean that is the center of the video game workspace centered in the middle of the workspace, and computing the convex hull of the sampled points.
+Then a convex hull is computed on the sampled points.
+This produces tracks composed of five to seven edges, an example is shown in Fig.
 \ref{fig:teaser}(a).
 If the car accidentally leaves the track, it is placed
-back on the center of the track at a nearby position. The car's control input space is given by  $\mathcal{U} = \lbrace
--15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle of the car which drives at a unit speed. 
+back on the center of the track at a nearby position. The car's steering is  $\mathcal{U} = \lbrace
+-15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle at a unit speed. 
 The internal state space of the car is given by the
@@
 state space search through the driving simulator to plan the next control.
-The algorithm is only allowed to search a finite amount a time ahead in the game and is prone to error, thus on averages crashes 5 times per lap.
+The supervisor is only allowed to search a finite amount a time ahead in the game and is prone to error, thus on averages crashes 5.4 times per lap.
 
@@
 policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
-validation on the initial training examples. We set SHIV's parameters  of the exponential kernel's bandwidth as $\sigma = 200$ and $\sigma_r = 200$.
+validation on the initial training examples. We set SHIV's parameters  of the exponential kernel's bandwidth as $\sigma = 200$ and $\sigma_r = 200$, which are set via the grid search defined above.
 
-\subsubsection{Comparison to active learning approaches.}\
-
-\noindent\textbf{Independent Variables:} We compare four query selection methods.
-We compare our combined notion of risk (Fig.
-\ref{fig:support_example}(d)), with risk based on novelty alone (Fig.
-\ref{fig:support_example}(c)) in order to test whether carving out regions that have been misclassified previously is valuable.
-
-We also compare against two baselines, typically used in active learning.
-The first is confidence based on distance from the classification hyperplane \cite{tong2002support} (Fig.
-\ref{fig:support_example}(a)).
-We set the threshold distance to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-
-The second baseline is Query By Committee (Fig.
-\ref{fig:support_example}(d)), which was trained via bagging \cite{breiman1996bagging}.
-To obtain a committe, we divided the training data into 3 overlapping subsets, each with 80\% of the data.
-We trained a Linear SVM on each subset.
-If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
-%We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
-
-We run each query selection method over 50 different car tracks.
-
-\noindent\textbf{Dependent Measures.
-}We measured the percentage of truly risky states, encountered during the first policy roll out, that  are estimated to be safe by the active learning technique.
-The active learning techniques are trained on the initial demonstrations $\mathcal{D}_0$, which is different then the distribution being sampled from, $p(\bx|\theta_0)$, in this experiment.
-
-\noindent\textbf{Results.
-} Fig.
-\ref{fig:active_comp}  plots the performance for each query selection method, averaged over 50 tracks.
-We observe a significant performance improvement with methods based on novelty compared to confidence and query by committee.
-Furthermore, using the combined measure of risk performs better than relying solely on novelty.
-
-\subsubsection{Sensitivity Analysis}.
-
-\noindent\textbf{Independent Variables.} To analyze the sensitivity of our method we varied the $\sigma$ parameter of the risk estimation function $g_{\sigma}$.
-$\sigma$ is a measure of how much risk we allow, with smaller $\sigma$s leading to more risk-adverse behavior.
-SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
-
-\noindent\textbf{Dependent Measures.
-} For each  $\sigma$, we measure the final cost function for the policy $\pi_{\theta}$ after 6 iterations and the number of examples SHIV requested from the supervisor.
-
-\noindent\textbf{Results.
-} As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help (many states labeled) and very large sigma, $\sigma = 350$, relates to  less data being used, but worse performance similar to the traditional (offline) supervised learning approaches.
-However, $\sigma$ values between $150$ and $250$ all achieve similarly good performance, suggesting that SHIV is robust to the choice of a particular $\sigma$.
-
-\begin{table}[t]
-\centering
-\begin{tabular}{ R{2.5cm}||R{1.65cm}|R{1.65cm} }
- %\hline
- %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
- %\hline 
- \hline
-\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Final  Cost} & \specialcell{\bf States  Labeled} \\
- \hline
- 1 & 6 & 4122 \\
- 50 & 6 &  3864 \\
- 150& 6 &  1859 \\
-200 & 6 & 1524 \\
-250 & 6 & 1536 \\
-350 & 13 & 521\\
-
- %\hline
-\end{tabular}
-   \caption { \footnotesize  An analysis of the sensitivity of $\sigma$.
-SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
-Small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach.
-   }
-		\tablabel{opt-p-comparison}
-		\label{tab:sens}
-
-\end{table}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=\columnwidth, height=4cm]{figures/risk_bar.eps}
-\caption {  A comparison of different active learning approaches in terms of the percentage of risky states that are estimated to be safe by the active learning technique during the first policy roll out.
-We compare against a confidence estimate of distance to hyperplane, query by committee for 3 hypothesis classifiers, the One Class SVM, and our modified One Class SVM.
-Results  are averaged over 50 tracks and the policy $\pi_\theta$ is represented as a Linear SVM.
-   }
-
-\label{fig:active_comp}
-\end{figure}
+In Fig.
+\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
+We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
+randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
+results from these experiments, suggesting a $71\%$ reduction in the number of queries needed for SHIV compared to DAgger, in order to reach approximately the same performance as our non-optimal supervisor.
 
@@
 \centering
-\includegraphics[width=\columnwidth, height=6cm]{figures/dagger_shiv_one_class.eps}
+\includegraphics[width=\columnwidth, height=4cm]{figures/dagger_shiv_one_class.eps}
 \caption{We compare performance for the Driving Simulator in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
-In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger and SHIV.
+We plot the performance of DAgger and SHIV, the teal and orange lines.
+We also plot the performance of our supervisor, who makes non-optimal decisions and has an average performance of 5.4 crashes.
 Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
-\ref{fig:car_cost} suggest an $71\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
+\ref{fig:car_cost} suggest an $71\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+Error bars in grey measure the standard error on the mean}
 \vspace*{-10pt}
@@
 
-\subsection{Comparing SHIV with DAgger}
-We compare SHIV with DAgger on three domains: the driving simulator from above, push-grasping in clutter, and needle insertion.
+\subsubsection{Grasping In Clutter in Box2D}
 
-\noindent\textbf{Independent Variables.} We manipulate two variables.
-First, we manipulate the online learning from demonstration algorithm we use: SHIV vs.
-DAgger.
-Second, we manipulate how many examples the algorithms are allowed to ask for: we set a budget of labeled states, and analyze performance as this budget increases.
-
-\noindent\textbf{Dependent Measures.}For each algorithm and budget of states labeled, we measure the real cost that the learned policy attains (e.g. number of crashes in the driving domain).
-
-\noindent\textbf{Hypothesis: } We expect SHIV to consistently achieve a lower cost that DAgger for the same budget of supervisor examples.
-Equivalently, we expect that SHIV achieves the same performance as DAgger, but by asking for fewer examples and thus reducing supervisor burden.
-
-\subsubsection{Driving.}
-
-\noindent\textbf{Domain.} Our first domain is the driving domain described above and illustrates SHIV's performance in high dimensions. 
-We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
-defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
-
-\noindent\textbf{Results.} 
-In Fig.
-\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
-We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
-randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
-results from these experiments, suggesting a $71\%$ reduction in the number of queries needed for SHIV compared to DAgger.
-
-\subsubsection{Grasping In Clutter}
-
-\noindent\textbf{Domain.}
-We investigate having a human demonstrator control a robot arm in 2D to reach a target object with out knocking other objects off a table.
+We investigate having a human demonstrator control a simulated robot arm in 2D to reach a target object with out knocking other objects off a table.
 Grasping an object in a cluttered environment is a common task for a robot in an unstructured environment and has been considered a benchmark for robotic manipulation~ \cite{kitaevphysics,kingnonprehensile}.
@@
 
-In lieu of real robot demonstrations, we used Box2D a physics simulator to model a virtual world. We simulate a 4 DOF robot arm with three main joints and a parallel jaw gripper as
+We used Box2D a physics simulator to model a virtual world. We simulate a 4 DOF robot arm with three main joints and a parallel jaw gripper as
 displayed in Fig. \ref{fig:teaser}(b). SHIV and DAgger do not have access to the underlying dynamics of the simulator and must learn a policy from only demonstrations.
 
-For input the human demonstrator provides controls through an XBox controller. The right joystick was used to
+For input the human demonstrator provides controls through an XBox game controller. The right joystick was used to
     provide horizontal and vertical velocity inputs for the center of the end-effector which were then translated into
@@
 
-\noindent\textbf{Results.} In Fig.
+ In Fig.
 \ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 rounds for SHIV and DAgger.
@@
 \centering
-\includegraphics[width=\columnwidth, height=2in]{figures/grasp_clutter.eps}
+\includegraphics[width=\columnwidth, height=4cm]{figures/grasp_clutter.eps}
 \caption{We compare performance for Grasping in Clutter in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
@@
 
-\subsubsection{Surgical Experiment}
+\subsubsection{Surgical Needle Insertion}
 
-\noindent\textbf{Domain.}
 Robotic Surgical Assistants (RSAs) are frequently used for procedures such as: prostectomy, uterectomy, and tumorectomies within the abdominal and thoracic cavities with high success rates~\cite{van2013laparoscopic,darzi2004impact}.
@@
 are interested in learning a policy to correct bad initial poses to the proper insertion pose as shown in Fig.
-\ref{fig:support_example}. Dr. Douglas Boyd, a surgeon at UC Davis, provided us with a collection of demonstrations on a Intuitive Surgical Da Vinci Research Kit \cite{AnnualReport2014}.
+\ref{fig:support_example}. Dr. Douglas Boyd, a surgeon and professor at UC Davis, provided us with a collection of demonstrations on a Intuitive Surgical Da Vinci Research Kit \cite{AnnualReport2014}.
 
-Dr. Boyd demonstrated a series of trajectories that each started at an initial attempted needle insertion pose $P_0$ and
+Dr. Boyd demonstrated a set of trajectories that each started at an initial attempted needle insertion pose $P_0$ and
 applied the necessary corrections to achieve a goal pose $P_G$. The time horizon, $T$ of each trajectory was on average 80.  We used three of these demonstrations as our initial
@@
 The expert controller computed the transformation between the desired insertion pose and the current pose  by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
-Then converted $C$ to the associated lie algebra vector $c \in \mathbb{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control,  $||\bar{c}_D||$, Doug Boyd applied to the robot.
+Then converted $C$ to the associated lie algebra vector $c \in \mathbb{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control,  $||\bar{c}_D||$, Dr.
+Boyd applied to the robot.
 
@@
 
-\noindent\textbf{Results. }
  In Fig.
@@
 \centering
-\includegraphics[width=\columnwidth, height=2in]{figures/needle_insertion_results.eps}
+\includegraphics[width=\columnwidth, height=4cm]{figures/needle_insertion_results.eps}
 \caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
 In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger and SHIV without the modification.
+\ref{fig:car_cost}, we plot the performance of DAgger and SHIV.
 Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig.
-\ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
+\ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger.
+Error bars in grey measure the standard error on the mean}
 \vspace*{-10pt}
@@
 
+\subsection{SHIV Analysis}\label{sec:car}
+
+\subsubsection{Comparison to active learning approaches.}\
+
+ We compare four active learning methods.
+We compare our combined notion of risk (Fig.
+\ref{fig:support_example}(d)), with risk based on novelty alone (Fig.
+\ref{fig:support_example}(c)) in order to test whether carving out regions that have been misclassified previously is valuable.
+
+We also compare against two baselines typically used in active learning.
+The first is confidence based on distance from the classification hyperplane \cite{tong2002support} (Fig.
+\ref{fig:support_example}(a)).
+We set the threshold distance to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
+
+The second baseline is Query By Committee (Fig.
+\ref{fig:support_example}(d)), which has a committee of different hypothesis estimators and points are marked risky if the committee disagrees.
+Our committee which was trained via bagging \cite{breiman1996bagging}.
+To obtain a committee, we divided the training data into 3 overlapping subsets, each with 80\% of the data.
+We trained a Linear SVM on each subset.
+If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
+%We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
+
+We run each query selection method over 50 different car tracks in the driving simulator domain.
+
+We measured the percentage of truly risky states, encountered during the first policy roll out, that  are estimated to be safe by the active learning technique.
+The active learning techniques are trained on the initial demonstrations $\mathcal{D}_0$, which is different then the distribution being sampled from, $p(\bx|\theta_0)$, in this experiment.
+
+ Fig.
+\ref{fig:active_comp}  plots the performance for each query selection method, averaged over 50 tracks.
+We observe a significant performance improvement with methods based on novelty compared to confidence and query by committee.
+Furthermore, using the combined measure of risk performs better than relying solely on novelty.
+
+\subsubsection{Sensitivity Analysis to Risk Sensitivity Parameter}
+
+ To analyze the sensitivity of our method we varied the risk sensitivity  parameter or $\sigma$ of the decision function $g_{\sigma}$, or Eq.
+$\ref{eq:decision_func}$.
+$\sigma$ is a measure of how much risk we allow, with smaller $\sigma$s leading to more risk-adverse behavior.
+SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
+
+ For each  $\sigma$, we measure the final cost function for the policy $\pi_{\theta}$ after 6 iterations and the number of examples SHIV requested from the supervisor.
+
+ As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help (many states labeled) and very large sigma, $\sigma = 350$, relates to  less data being used, but worse performance.
+However, $\sigma$ values between $150$ and $250$ all achieve similarly good performance, suggesting that SHIV is robust to the choice of a particular $\sigma$.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{ R{2.5cm}||R{1.65cm}|R{1.65cm} }
+ %\hline
+ %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
+ %\hline 
+ \hline
+\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Final  Cost} & \specialcell{\bf States  Labeled} \\
+ \hline
+ 1 & 5.8 & 4122 \\
+ 50 & 5.7&  3864 \\
+ 150& 5.9 &  1859 \\
+200 & 6.1 & 1524 \\
+250 & 6.3 & 1536 \\
+350 & 13.2 & 521\\
+
+ %\hline
+\end{tabular}
+   \caption { \footnotesize  An analysis of the sensitivity risk sensitivity parameter,$\sigma$, of Eq.
+\ref{eq:decision_func}, or the decision function for risky or safe.
+SHIV was run for 6 iterations and averaged over 40 different randomized polygonal tracks.
+Small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but decreased performance.
+   }
+		\tablabel{opt-p-comparison}
+		\label{tab:sens}
+
+\end{table}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\columnwidth, height=4cm]{figures/risk_bar.eps}
+\caption {  A comparison of different active learning approaches in terms of the percentage of risky states that are estimated to be safe by the active learning technique during the first policy roll out.
+We compare against a confidence estimate of distance to hyperplane, query by committee for 3 hypothesis classifiers, the One Class SVM, and our modified One Class SVM, marked as SHIV.
+Results  are averaged over 50 tracks and the policy $\pi_\theta$ is represented as a Linear SVM.
+Error bars measure the standard error on the mean.
+   }
+
+\label{fig:active_comp}
+\end{figure}
+
 \section{Discussions and Future Work}
-Online imitation learning algorithms have been successful on array of task~\cite{NIPS2014_5421,ross2010reduction}, however can significantly increase the burden on a supervisor.
+Online imitation learning algorithms have been successful on array of tasks~\cite{NIPS2014_5421,ross2010reduction}, however can place significant burden on a supervisor.
 Our algorithm, SHIV, implements stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
 We empirically evaluated our method on three different domains: a driving simulator, grasping in clutter and surgical needle insertion.
-Results suggest a $70\%$ reduction in the number of queries to the supervisor needed.
+Results suggests up to a $70\%$ reduction in the number of queries to the supervisor.
 
-While achieving a high level of performance, SHIV has several limitations.
+SHIV has several limitations.
 For instance, the selection of the value of $\sigma$ can affect performance and a poor choice could result in the algorithm becoming offline imitation learning, as shown in Table \ref{tab:sens}.
@@
 
- Furthermore, to update the decision function $g_{\sigma}$ requires solving a quadratic program, which has an upper bound computationally complexity of $O(n^3)$ in the number of data points.
-This can effect the ability of using our modified One Class SVM for larger problems.
-Future work will look at using techniques such as random features or PCA on the kernel Gram matrix to allow for better scaling~\cite{scholkopf2002learning}.
-
  Lastly, online imitation learning only allows a policy to learn to be as good as the supervisor.
 If the supervisor is imperfect then the robot will be as well.
-Future work will look at combining techniques from inverse reinforcment learning\cite{argall2009survey} with online imitation learning to allow the robot to improve upon it's policy after supervision is done.
-
-\section{Acknowledgments} 
-\fpnote{remove in the initial submission if we are pressed for space}
-This work is supported in part by the U.S. National Science Foundation under Award IIS-1227536 and NSF-Graduate Research Fellowship.. 
-We thank UC Berkeley and our colleagues who gave feedback and suggestions, in particular Sanjay Krishnan, Siddarth Sen, Steve McKinley, Sachin Patil and Sergey Levine.
+Future work will look at combining techniques from inverse reinforcment learning\cite{argall2009survey} with online imitation learning to allow the robot to further fine-tune the policies.
 

### 2015-09-11 paper.tex
v21, flipped plotsto performance

@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v20]}
+\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v21]}
 
@@
 
-We define a state as "risky" for 2 reasons: 1) it lies in an area with a low density of
+In contrast to the standard measure risk based purely on variance, we define a state as "risky" for 2 reasons: 1) it lies in an area with a low density of
 previously trained states, which can cause the current policy to mis-predict the supervisor and incur high surrogate
 loss \cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at the state  is high, so that the state is unlikely to model the supervisor's control inputs correctly.
-States that are not classified as "risky" are deemed "safe".
+States that are not classified as "risky" are deemed "safe" .Our definition of risk can be visualized in Fig.
+\ref{fig:support_example}(d).
 
@@
 
-For each algorithm and budget of states labeled, we measure the real cost that the learned policy attains (e.g. number of crashes in the driving domain).
+For each algorithm and budget of states labeled, we measure the normalized performance (e.g.
+1 corresponds to matching the supervisor's performance on a task).
+Performance is a domain specific term, such as number of times the car crashes in the driving simulator.
 
@@
 \includegraphics[width=\columnwidth, height=4cm]{figures/dagger_shiv_one_class.eps}
-\caption{We compare performance for the Driving Simulator in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the  number of times the car left the track versus the number of queries made to the supervisor.
+\caption{We compare normalized performance (i.e.
+matching the performance of the supervisor) for the Driving Simulator , performance is defined as the number of times the car left the track versus the number of queries made to the supervisor.
 We plot the performance of DAgger and SHIV, the teal and orange lines.
@@
 For our representation of $\pi_{\theta}$, we used kernelized ridge regression with the radial basis function as the kernel with the default Sci-Kit learn parameters.
-We defined the cost functions, $C(\bx,\bu)$, as the sum of the number of objects knocked off the table plus $10$ times the binary value indicating if the object is grasped or not.
+We defined performance as the sum of the number of objects knocked off the table plus $10$ times the binary value indicating if the object is grasped or not.
 The order of magnitude difference in cost for grasping the object is to place emphasize on that portion of the task.
@@
 
-In our experiment, a human demonstrator provided one demonstration and then iterated until the cost function was zero during the policy roll out.
+In our experiment, a human demonstrator provided one demonstration and then iterated until the performance was zero during the policy roll out.
 At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
@@
  In Fig.
-\ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 8 rounds for SHIV and DAgger.
+\ref{fig:grasp_cost} , we show the normalized performance averaged over 8 rounds for SHIV and DAgger.
 Supporting our hypothesis, our results suggests that SHIV can achieve the same performance with a 64\% reduction in the number of examples needed.
@@
 \includegraphics[width=\columnwidth, height=4cm]{figures/grasp_clutter.eps}
-\caption{We compare performance for Grasping in Clutter in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
+\caption{We compare normalize performance (i.e.
+mathcing the performance of the supervisor) for Grasping in Clutter domain, performance is defined as the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
 Initial results, which are averaged over 8 different trials suggest a $64\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
@@
 For trials we sample a start position from a Gaussian on the translational component of $P_0$ with isotropic variance of
-$0.1$ cm. The distance between initial $P_0$ and $P_G$ is roughly $3$ cm. Our cost function $c(\bx,\bu)$ is measured in
+$0.1$ cm. The distance between initial $P_0$ and $P_G$ is roughly $3$ cm. Performance is measured in
 terms of Euclidean distance in translational component, which is in centimeters. We run DAgger and SHIV both for 20 iterations and average over 40 different starting positions.
@@
  In Fig.
-\ref{fig:grasp_cost} , we show the cost function $c(\bx,\bu)$ averaged over 40 rounds for SHIV and DAgger.
+\ref{fig:grasp_cost} , we show the normalized performance (i.e.
+1 corresponds to matching the supervisor) averaged over 40 rounds for SHIV and DAgger.
 Supporting our hypothesis, our results suggests that SHIV can achieve the same performance with a $67\%$ reduction in the number of examples needed.
@@
 \includegraphics[width=\columnwidth, height=4cm]{figures/needle_insertion_results.eps}
-\caption{We compare performance in terms of minimization of the underlying cost function $c(\bx,\bu)$, which is euclidean distance between translation in centimeters.
+\caption{We compare normalized performance (i.e.
+matching the performance of the supervisor), performance is defined as the euclidean distance between translation in centimeters.
 In Fig.
@@
 
- For each  $\sigma$, we measure the final cost function for the policy $\pi_{\theta}$ after 6 iterations and the number of examples SHIV requested from the supervisor.
+ For each  $\sigma$, we measure the final cost performance of the policy $\pi_{\theta}$ after 6 iterations and the number of examples SHIV requested from the supervisor.
 
@@
  \hline
-\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Final  Cost} & \specialcell{\bf States  Labeled} \\
+\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Performance} & \specialcell{\bf States  Labeled} \\
  \hline

### 2015-09-11 paper.tex
updated teaser photo

@@
 \caption{ 
-SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) cost of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
+SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) normalized performance of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
 }

### 2015-09-14 paper.tex
Anca's comments

--- 2015-09-11 paper.tex
@@
 \newboolean{include-notes}
-\setboolean{include-notes}{false}
+\setboolean{include-notes}{true}
 \newcommand{\adnote}[1]{\ifthenelse{ \boolean{include-notes}}%
@@
 Online learning from demonstration algorithms, such as DAgger, can learn policies for problems where the system
-dynamics and the cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
-signals) as the robot encounters new states when executing its current best policy. We introduce the SHIV
+dynamics and the cost function are unknown. However, during learning, they impose a burden on supervisors to provide labels (control
+signals) as the robot encounters new states while executing its current best policy. We introduce the SHIV
 algorithm (Svm-based reduction in Human InterVention), which reduces this burden by only requesting supervision for risky states.
@@
 To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936 dimension visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter simulation with Box2D with a 22 dimension state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16 dimension state represented spatial transform.
-Results suggest that SHIV can learn equivalent policies with up to $70\%$ fewer queries.
+We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936 dimension visual HOG feature state representation, 2) a push-grasping in clutter simulation for a 4DOF robot arm, using Box2D, with a 22 dimension state representation  of joint angles and the pose of each object, and 3) a surgical needle insertion task with a 16 dimension state represented spatial transform.
+Results suggest that SHIV can learn equivalent policies with up to 70\% fewer queries.
 
@@
 
-In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment, from examples provided by a  supervisor, usually a human.
+In model-free robot Learning from Demonstration (LfD), a robot learns to perform a task, such as driving or grasping an object in a cluttered environment, from examples provided by a  supervisor, usually a human.
 In such problems, the robot does not have access to either the cost function that it should optimize, nor the dynamics model.
@@
 The latter occurs when either the system or the interaction with the world is difficult to characterize based on observations, as in Fig.
-\ref{fig:teaser}(a) the robot drives on the track but only has access to visual information from a bird's eye view.
+\ref{fig:teaser}(a) the robot drives on the track but only has access to visual information from a bird's eye view.\adnote{these are both pretty bad examples; i'd use the typical driving example for the first point, taken from abeeel and ng, and i'd use the pushing for the second point, because it is very hard to write down accurate dynamics models for pushing -- took Mehmet 3 years to do push grasping with a single object, still can't do with arbitrary objects; Jen uses Box2d but the real world is uncertain; it's a perfect example in whihc writing down the dynamics model is very difficult;}
 
-Rather than explicitly learning the cost function, like in inverse reinforcement learning, and the dynamics model, and then using optimization to produce a policy for the task, the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
-Learning from demonstrations algorithms can be categorized as offline, where the robot only observes demonstrations, or online, where the robot interacts with the world and receives feedback from the supervisor.
+Rather than explicitly learning the cost function, like in Inverse Reinforcement Learning\adnote{cite}, and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
 
@@
 \caption{ 
-SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) cost of SHIV and DAgger's policy on the grasping in clutter example versus states labeled.
+SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) normalized performance of SHIV and DAgger's policy on the grasping in clutter example versus states labeled \adbote{by the supervisor}.
 }
@@
 
-In offline learning from demonstration, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
+LfD algorithms can be categorized as offline, where the robot only observes demonstrations, or online, where the robot interacts with the world and receives feedback from the supervisor.
+In offline LfD, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
 During execution, a small error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.
-For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
+For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will \adnote{eventually} put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
 Ross and Bagnell showed the number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
 
-Online learning from demonstration addresses this issue by iteratively gathering more examples from the supervisor in states the robot encounters~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
-One such algorithm, DAgger learns a series of policies.
-At each iteration, the robot trains a policy based on the existing examples, then rolls out (executes) that policy and the supervisor provides demonstrations for all states the robot visits.
+Online LfD addresses this issue by iteratively gathering more examples from the supervisor in states the robot encounters~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+One such algorithm, DAgger, learns a series of policies.
+At each iteration, the robot trains a policy based on the existing examples, then rolls out (executes) that policy, and the supervisor provides demonstrations for all states the robot visits.
 The new state/control examples are aggregated with the old examples for the next iteration.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-In DAgger, it was proved under certain conditions, the number of errors scales only linearly with the time horizon of the task.
+In DAgger, \adnote{delted it was proved, unnecessary} under certain conditions, the number of errors scales only linearly with the time horizon of the task\adnote{cite}.
 
-DAgger significantly increases the burden on the supervisor, who now labels all states that the robot visits during training.
+\adnote{there needs to be a lead up to this, like yay dagger is cool.
+however, }DAgger significantly increases the burden on the supervisor, who now labels all states that the robot visits during training.
 Our goal is to reduce supervisor burden without degrading robot performance.
@@
 
+\adnote{nothing about experiements and resutls?
+how do i know if it worked?
+also how do i know that you didn;t just compare to dagger, but ran an indepth analysis of the algorithm?
+i thought i put a paragraph like that here at some point}
+
 \section{Related Work}
-Below we summarize related work in active approaches to robot learning from demonstration and risk evaluation techniques..
+Below we summarize related work in active approaches to robot learning from demonstration and risk evaluation techniques.
 
 \noindent\textbf{Active Learning from Demonstration}
-Online learning from demonstration can be formulated as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
-In stream based active learning, the decision of whether to query the supervisor (for a label or control signal) or not is not over the entire state space (like in traditional pool-based active learning), but on states drawn one at a time from some data source.
-In  online learning  from demonstration, the data source is the states encountered during learning.
+Online LfD\adnote{been replacing with "LfD" for simplicity, no need to say the same expression 100 times in the paper especially since everyone calls it that} can be formulated as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}\adnote{NO!!
+Your approach of asking only when risky instantiates stream based active learning.
+In general, online lfd is NOT an active learning problem, that is the proble we are fixing here!
+sorry for the "!!" but this is crucial}.
+In stream based active learning, the decision of whether to query the supervisor (for a label or control signal) or not is not over the entire state space (like in traditional pool-based active learning), but on states drawn one at a time from some data stream.
+In  online LfD, the\adnote{this} data stream is the states encountered during learning\adnote{encountered when the robot is executing the current best policy.}
 
-Stream-based active learning has two ingredients: a stream, given here by executing the current best policy, and a query selection method deciding whether or not to query.
-Typical query selection methods are estimator-centric:  evaluating risk using the estimator, e.g.
+Stream-based active learning has two ingredients: a stream, given here by executing the current best policy,\adnote{Aside from the data strea, stream-based active learning has another ingredient: a query selection method.} and a query selection method deciding whether or not to query.
+Typical query selection methods are estimator-centric, evaluating risk using the estimator, e.g.
 distance from the classification hyperplane \cite{tong2002support}, as in Fig.
-\ref{fig:support_example}(a).
-An alternative to distance-based measures of  risk is query by committee  \cite{breiman1996bagging}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
-Risk here is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig.
+\ref{fig:support_example}(a); or query by committee  \cite{breiman1996bagging}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
+Risk in query by committee is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig.
 \ref{fig:support_example}(b)).
@@
 Both approaches implicitly assume a stationary state distribution --- that the new data is sampled from the same distribution as the previous training data.
-Although such methods have been previously proposed for online learning from demonstration (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
-online learning from demonstration violates the stationary distribution assumption because each new policy induces a new distribution of states.
+Although such methods have been previously proposed for online LfD (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
+online LfD violates the stationary distribution assumption because each new policy induces a new distribution of states.
 This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.
 
+The problem lies in being estimator-centric.
 The  estimator is a function of the current distribution.
@@
 
+\adnote{replace learning from demonstration with LfD from here onwards}
+
 \noindent\textbf{Risk via Novelty Detection.}
-One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
+The main motivation for our risk definition is the notion that a trained model will be able to generalize within the distribution it is
 trained on \cite{tokdar2010importance}, making states outside of this distribution risky.
@@
 
+\adnote{OK fiiiiiine. Then maybe To our knowledge, incorporating a query selection method for nonstationary distributions, such as the One Class SVM, into online LfD is a novel contribution.}
+
 \section{Problem Statement}
@@
 \noindent\textbf{Modeling Choices and Assumptions}  We model the system dynamics as Markovian, stochastic, and stationary.
-Stationary dynamics meaning  given a state and a control the probability of the next state doesn't change over time.
-Note this is different then the non-stationary distribution over the states the robot encounters during learning.
+Stationary dynamics meaning\adnote{this sentence is missing a predicate; Stationary dynamics occur when, given..}  given a state and a control, the probability of the next state doesn't\adnote{does not} change over time.
+Note this is different then\adnote{from} the non-stationary distribution over the states the robot encounters during learning.
+\adnote{very good addition here!}
+
 We model the initial state as sampled from a distribution over the state space.
+We assume a known state space and set of controls.
+We also assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.
+Lastly, we assume access to a supervisor who can, given a state, provide a control signal label.
+We assume the supervisor can be noisy and imperfect, noting that the robot cannot surpass the level of performance of the supervisor.
+\adnote{not in general just in our work}
 
-We assume a known state space and set of controls.
-We assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.
-Lastly, we assume access to a supervisor who can, given a state, provide a control signal label.
-We assume the supervisor can be noisy and imperfect.
-Noting that the robot cannot surpass the level of performance of the supervisor.
+\adnote{again, this would be better at the same time with introducing the basic notation, like states and controls, so that you can state mathematically what these mean; for instance, you restate the markovian modelling anyway}
 
@@
 We furthermore consider a set $\mathcal{U}$ of allowable control inputs for the robot, which can be discrete or
-continuous. We model dynamics, as Markovian, such that the probability of state $\mathbf{x_{t+1}}\in
+continuous. We model dynamics as Markovian, such that the probability of state $\mathbf{x_{t+1}}\in
 \mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
@@
 \noindent\textbf{Objective.} The objective of  policy learning is to find a policy that minimizes some known cost function $C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$.
-The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific.
+The cost $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific.
 For example, in the task of inserting a peg into a hole, a function on the distance between the peg's current and desired final state can
-be considered \cite{levine2015end}.
+be considered \cite{levine2015end}.  \adnote{can be considered? like you'll allow it? maybe For example, in the task... , the cost function could be ...}
 
-However in this case, we do not have access to the cost function itself. Instead, we only have access to 
-a supervisor that can achieve a desire level of performance on the task.  We are furthermore given
+In our problem, we do not have access to the cost function itself. Instead, we only have access to 
+a supervisor that can achieve a desire\adnote{d} level of performance on the task.
+\adnote{furthermore doesnt make sense here because the supervisor is providing these; say instead The supervisor provides the robot an initial set..} We are furthermore given
 an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
-which are the result of the supervisor applying this policy. This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
+which are the result of the supervisor applying this policy. This induces a training data set $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
 
-We define a `surrogate' loss function $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+We define a `surrogate' loss function \adnote{as in \cite{ross2010reduction}, }$l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
 measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$,
@@
 \end{align}
-with $p(\bx|\theta)$ from Eq. \ref{eq:density}.
+with $p(\bx|\theta)$ from Eq. \ref{eq:density}.\adnote{fix}
 
@@
 \section{Risky and Safe States}
-
+\adnote{I don't like the flow of this coming before the algorithm.
+You can understand the algorithm without understanding the specifics of risk, but here I read this and still don't know how the algorithm is going to work and it's like keeping me in (bad) suspense until the next section.
+It also breaks flow because the last section set up the optimization problem that shiv and dagger are solving}
 \begin{figure*}[t]
@@
 
-Providing correct control inputs or ``labeling'' for all states encountered at each
-iteration can impose a large burden on the supervisor.
+Providing correct control inputs for (or ``labeling'')  all states encountered at each
+iteration can impose a large burden on the supervisor.\adnote{but you haven't described the algorithm yet so how am i supposed to know what that means; this is no longer intro land so stuff should be precise not handwavy; that is why this section doesnt fit here}
 Instead of asking the supervisor for labels at all visited states, SHIV uses a measure of risk to actively decide whether a label is necessary.
@@
 We then  compare our query selection method with those typically used in active learning.
-We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than a confidence and query-by-committee based methods.
-We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from Eq.
+We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than a confidence and query-by-committee based methods.\adnote{also: We also test whether SHIV actually benefits from measuring both forms of risk (novelty and ???).} We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from Eq.
 \ref{eq:decision_func}).
@@
 
-\subsubsection{Comparison to active learning approaches.}\
+\subsubsection{Comparison to active learning approaches.}
 

### 2015-09-14 paper.tex
Incoporated Anca's feedback

@@
 
-Rather than explicitly learning the cost function, like in Inverse Reinforcement Learning\adnote{cite}, and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
+Rather than explicitly learning the cost function, like in Inverse Reinforcement Learning \cite{ng2000algorithms}, and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
 
@@
 \caption{ 
-SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) normalized performance of SHIV and DAgger's policy on the grasping in clutter example versus states labeled \adbote{by the supervisor}.
+SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) normalized performance of SHIV and DAgger's policy on the grasping in clutter example versus states labeled by the supervisor.
 }
@@
 During execution, a small error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.
-For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will \adnote{eventually} put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
+For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will eventually put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
 Ross and Bagnell showed the number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
@@
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-In DAgger, \adnote{delted it was proved, unnecessary} under certain conditions, the number of errors scales only linearly with the time horizon of the task\adnote{cite}.
+In DAgger, under certain conditions, the number of errors scales only linearly with the time horizon of the task\cite{ross2010reduction}.
 
-\adnote{there needs to be a lead up to this, like yay dagger is cool.
-however, }DAgger significantly increases the burden on the supervisor, who now labels all states that the robot visits during training.
+However one drawback is that DAgger significantly increases the burden on the supervisor, who now labels all states that the robot visits during training.
 Our goal is to reduce supervisor burden without degrading robot performance.
@@
 \noindent\textbf{Active Learning from Demonstration}
-Online LfD\adnote{been replacing with "LfD" for simplicity, no need to say the same expression 100 times in the paper especially since everyone calls it that} can be formulated as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}\adnote{NO!!
-Your approach of asking only when risky instantiates stream based active learning.
-In general, online lfd is NOT an active learning problem, that is the proble we are fixing here!
-sorry for the "!!" but this is crucial}.
+We formulate applying active learning to Online Lfd as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
 In stream based active learning, the decision of whether to query the supervisor (for a label or control signal) or not is not over the entire state space (like in traditional pool-based active learning), but on states drawn one at a time from some data stream.
-In  online LfD, the\adnote{this} data stream is the states encountered during learning\adnote{encountered when the robot is executing the current best policy.}
+In  online LfD, this data stream is the states encountered when the robot is executing the current best policy.
 
-Stream-based active learning has two ingredients: a stream, given here by executing the current best policy,\adnote{Aside from the data strea, stream-based active learning has another ingredient: a query selection method.} and a query selection method deciding whether or not to query.
+Aside from the data stream, stream-based active learning has another ingredient: a query selection method.
+A query selection method is deciding whether or not to query.
 Typical query selection methods are estimator-centric, evaluating risk using the estimator, e.g.
@@
 In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for novelty detection in high-dimensional image data.
-To our knowledge the use of One Class SVM to online learning from demonstration has never been done before.
-\mlnote{Ken, wanted to our knowledge in the last part} \adnote{you can say this to me, but not really write it in a paper; I think that perhaps you want to say, and in a new paragraph so that it stands out, "Our contribution is the addition of stream-based active learning to online learning from demonstration.
-To do so, we use a query selection method based on the One Class SVM.}
-
-\adnote{OK fiiiiiine. Then maybe To our knowledge, incorporating a query selection method for nonstationary distributions, such as the One Class SVM, into online LfD is a novel contribution.}
+To our knowledge, incorporating a query selection method for nonstationary distributions, such as the One Class SVM, into online LfD is a novel contribution.
 
@@
 \noindent\textbf{Modeling Choices and Assumptions}  We model the system dynamics as Markovian, stochastic, and stationary.
-Stationary dynamics meaning\adnote{this sentence is missing a predicate; Stationary dynamics occur when, given..}  given a state and a control, the probability of the next state doesn't\adnote{does not} change over time.
-Note this is different then\adnote{from} the non-stationary distribution over the states the robot encounters during learning.
-\adnote{very good addition here!}
+Stationary dynamics occur when, given a state and a control, the probability of the next state does not change over time.
+Note this is different from the non-stationary distribution over the states the robot encounters during learning.
 
@@
 Lastly, we assume access to a supervisor who can, given a state, provide a control signal label.
-We assume the supervisor can be noisy and imperfect, noting that the robot cannot surpass the level of performance of the supervisor.
-\adnote{not in general just in our work}
-
-\adnote{again, this would be better at the same time with introducing the basic notation, like states and controls, so that you can state mathematically what these mean; for instance, you restate the markovian modelling anyway}
+We additionally assume the supervisor can be noisy and imperfect, noting that the robot cannot surpass the level of performance of the supervisor.
 
 \noindent\textbf{Policies and State Densities.}
-Following conventions from control theory, we denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
+Following conventions from control theory, we denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of 
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
@@
 For example, in the task of inserting a peg into a hole, a function on the distance between the peg's current and desired final state can
-be considered \cite{levine2015end}.  \adnote{can be considered? like you'll allow it? maybe For example, in the task... , the cost function could be ...}
+be used \cite{levine2015end}.
 
 In our problem, we do not have access to the cost function itself. Instead, we only have access to 
-a supervisor that can achieve a desire\adnote{d} level of performance on the task.
-\adnote{furthermore doesnt make sense here because the supervisor is providing these; say instead The supervisor provides the robot an initial set..} We are furthermore given
+a supervisor that can achieve a desired} level of performance on the task. The supervisor provides the robot an initial set
 an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
@@
 
-We define a `surrogate' loss function \adnote{as in \cite{ross2010reduction}, }$l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+We define a `surrogate' loss function as in \cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
 measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$,
@@
 \end{align}
-with $p(\bx|\theta)$ from Eq. \ref{eq:density}.\adnote{fix}
+with $p(\bx|\theta)$ from Eq. \ref{eq:density}.
 
@@
 \section{Risky and Safe States}
-\adnote{I don't like the flow of this coming before the algorithm.
-You can understand the algorithm without understanding the specifics of risk, but here I read this and still don't know how the algorithm is going to work and it's like keeping me in (bad) suspense until the next section.
-It also breaks flow because the last section set up the optimization problem that shiv and dagger are solving}
+
 \begin{figure*}[t]
@@
 Providing correct control inputs for (or ``labeling'')  all states encountered at each
-iteration can impose a large burden on the supervisor.\adnote{but you haven't described the algorithm yet so how am i supposed to know what that means; this is no longer intro land so stuff should be precise not handwavy; that is why this section doesnt fit here}
+iteration can impose a large burden on the supervisor.
 Instead of asking the supervisor for labels at all visited states, SHIV uses a measure of risk to actively decide whether a label is necessary.
@@
 We then  compare our query selection method with those typically used in active learning.
-We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than a confidence and query-by-committee based methods.\adnote{also: We also test whether SHIV actually benefits from measuring both forms of risk (novelty and ???).} We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from Eq.
+We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than confidence, query-by-committee based methods and the One Class SVM with out the hole carving out modification.
+We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from Eq.
 \ref{eq:decision_func}).

### 2015-09-16 paper.tex
Intial submitted version

@@
 \usepackage{bbm}
+\renewcommand{\baselinestretch}{.5}
 
@@
 
-\renewcommand{\baselinestretch}{.99}
+\renewcommand{\baselinestretch}{.92}
 
@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v21]}
+\title{SHIV: Reducing Supervisor Burden using Support Vectors for Efficient
+Learning from Demonstrations in High Dimensional State Spaces }
 
-\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeffrey Mahler$^1$, \\ Florian T. Pokorny$^1$, Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
-\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh, ftpokorny, anca\}@berkeley.edu}}%
+\author{Michael Laskey$^1$, Sam Staszak$^1$, Wesley Yu-Shu Hsieh$^1$, Jeffrey Mahler$^1$, \\ Florian T. Pokorny$^1$, Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
+\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu, \small staszass@rose-hulman.edu} }%
 \thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
@@
 In such problems, the robot does not have access to either the cost function that it should optimize, nor the dynamics model.
-The former occurs when it is difficult to specify how to trade-off various aspects that matter, like when the robot is reaching for a goal object while not pushing objects off a table.
-The latter occurs when either the system or the interaction with the world is difficult to characterize based on observations, as in Fig.
-\ref{fig:teaser}(a) the robot drives on the track but only has access to visual information from a bird's eye view.\adnote{these are both pretty bad examples; i'd use the typical driving example for the first point, taken from abeeel and ng, and i'd use the pushing for the second point, because it is very hard to write down accurate dynamics models for pushing -- took Mehmet 3 years to do push grasping with a single object, still can't do with arbitrary objects; Jen uses Box2d but the real world is uncertain; it's a perfect example in whihc writing down the dynamics model is very difficult;}
+The former occurs when it is difficult to specify how to trade-off various aspects that matter, like a car trying to drive on the road and dodge other cars \cite{abbeel2004apprenticeship}.
+The latter occurs when either the system or the interaction with the world is difficult to characterize like when a robot is trying to grasp an object in clutter and doesn't have an accurate model of the objects dynamics.
 
 Rather than explicitly learning the cost function, like in Inverse Reinforcement Learning \cite{ng2000algorithms}, and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
+Learning from demonstration has been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering \cite{abbeel2007application},car parking \cite{abbeel2008apprenticeship},  and robotic surgery \cite{van2010superhuman}.
 
@@
 \includegraphics[width=0.5\textwidth]{figures/teaser.pdf}
-\caption{ 
+\caption{ \footnotesize
 SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) normalized performance of SHIV and DAgger's policy on the grasping in clutter example versus states labeled by the supervisor.
 }
-\vspace*{-10pt}
+\vspace*{-20pt}
 \label{fig:teaser}
@@
 However one drawback is that DAgger significantly increases the burden on the supervisor, who now labels all states that the robot visits during training.
-Our goal is to reduce supervisor burden without degrading robot performance.
+Our goal is to reduce supervisor burden without degrading performance.
 
@@
 
-We present an algorithm for online learning from demonstration that can actively decide whether it is necessary to ask the supervisor to label the new states that the robot encounters.
+We present an algorithm for online LfD that can actively decide whether it is necessary to ask the supervisor to label the new states that the robot encounters.
 SHIV  (Svm-based reduction in Human InterVention) reduces supervisor burden by only requesting supervision for risky states.
@@
 \section{Related Work}
-Below we summarize related work in active approaches to robot learning from demonstration and risk evaluation techniques.
+Below we summarize related work in active approaches to robot LfD and risk evaluation techniques.
 
@@
 
-\adnote{replace learning from demonstration with LfD from here onwards}
-
-\noindent\textbf{Risk via Novelty Detection.}
+\noindent\textbf{Risk via Novelty Detection}
 The main motivation for our risk definition is the notion that a trained model will be able to generalize within the distribution it is
@@
 
-One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled.
-If the probability of that point is low with respect to the underlying density, it will be marked as novel.
-However, the amount of data needed to accurately do so scales exponentially in the number of dimensions \cite{nadaraya1964estimating}.
+Our work builds on Kim et al.
+\cite{kim2013maximum} who apply novelty detection for safe online learning from demonstrations to enable a supervisor to take over and prevent unsafe states.
+In their MMD-LI algorithm, risk is evaluated with Maximal Mean Discrepancy, which for a single point is the sum of a kernel density estimate and variance on the dataset, which works well in low dimensional state spaces.
+MMD-LI also reduces supervisor burden because the supervisor only takes control and provides demonstrations in risky states.
+However, having the supervisor take over can bias the states sampled, which can in practice lead to a loss in performance \cite{ross2010reduction}.
+In contrast, we focus on active learning for online LfD for high-dimensional state spaces, do not assume the supervisor is always available, and propose an alternative to non-parametric density estimation which can require data exponential in the dimension of the state-space
+\cite{nadaraya1964estimating}.
 
@@
 The cost $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific.
-For example, in the task of inserting a peg into a hole, a function on the distance between the peg's current and desired final state can
-be used \cite{levine2015end}.
+For example, in the task of inserting a peg into a hole, a function on distance between the peg's current and desired final state is used \cite{levine2015end}.
 
 In our problem, we do not have access to the cost function itself. Instead, we only have access to 
-a supervisor that can achieve a desired} level of performance on the task. The supervisor provides the robot an initial set
+a supervisor that can achieve a desired level of performance on the task. The supervisor provides the robot an initial set
 an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
@@
 We define a `surrogate' loss function as in \cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
-measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2$,
+measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2_2$,
 while in the discrete case $l(\bu_0,\bu_1) = 1$ if $\bu_0 \neq \bu_1$ and $l(\bu_0, \bu_1)=0$ otherwise.
 
-Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how "close" the policy's
+Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how `close' the policy's
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
@@
 \end{align}
-with $p(\bx|\theta)$ from Eq. \ref{eq:density}.
 
  If the robot could learn the policy  perfectly, this state density would match the one encountered in user examples.
-But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to \cite{pomerleau1989alvinn}.This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing feedback.
+But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to ~\cite{pomerleau1989alvinn}.This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing feedback.
 The feedback is in the form of control signals on states sampled from the robot's new distribution of states.
@@
 
-\caption{A comparison of different query selection strategies for active learning on a non-stationary distribution.
+\caption{\footnotesize A comparison of different query selection strategies for active learning on a non-stationary distribution.
 The shaded and empty circles are training data from two classes, $1$ and $0$ respectively.
@@
 }
+\vspace*{-20pt}
 \label{fig:support_example}
@@
 previously trained states, which can cause the current policy to mis-predict the supervisor and incur high surrogate
-loss \cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at the state  is high, so that the state is unlikely to model the supervisor's control inputs correctly.
+loss~\cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at the state  is high, so that the state is unlikely to model the supervisor's control inputs correctly.
 States that are not classified as "risky" are deemed "safe" .Our definition of risk can be visualized in Fig.
@@
 
-The amount of data needed to estimate the density, scales exponentially in the dimension of the state space \cite{nadaraya1964estimating}. 
-Thus, to evaluate risk in high-dimensional state spaces , such as the HOG features in our driving simulator, Fig. \ref{fig:teaser}(a), we use
-a modified version of the technique known as the One Class SVM that  estimates a regularized boundary of a user defined quantile on the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
+The amount of data needed to estimate the density, scales exponentially in the dimension of the state space~\cite{nadaraya1964estimating}. 
+Thus, to evaluate risk in high-dimensional state spaces, such as the HOG features in our driving simulator, Fig. \ref{fig:teaser}(a), we use
+a modified version of the technique known as the One Class SVM that  estimates a regularized boundary of a user defined quantile on the training data in $\mathcal{X}$~\cite{scholkopf2001estimating}.
 %\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}
@@
 However, Sch{\"o}lkopf et al.
-developed an improved optimization method that has empirically been shown to be as low as $O(n^2)$ \cite{scholkopf2001estimating}.
+developed an improved optimization method that has empirically been shown to scale quadratically \cite{scholkopf2001estimating}.
 In the dual, the decision function is given by $g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho)$ where $\alpha_i$ corresponds to the dual variables.
@@
 
-We divide up our data in to two sets those correctly classified: $\mathcal{D}_{s}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=1\}$ and those states incorrectly classified: $\mathcal{D}_{r}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=-1\}$
+We divide up our data in to two sets those correctly classified: $\mathcal{D}_{s}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y_i=1\}$ and those states incorrectly classified: $\mathcal{D}_{r}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y_i=-1\}$
 A separate One-Class SVM is then trained on each set of states, ($D_{s}$ and $D_{r}$) and providing measures of the level sets, $g_{s}$ and $g_{r}$.
@@
 \begin{align}\label{eq:decision_func}
-g_{\sigma}(\bx) = g_{r} (\bx)+ g_{s}(\bx)
+g_{\sigma}(\bx) = \left\{
+     \begin{array}{ll}
+         0 & : g_s(\bx) == 1 \: \mbox{and} \: g_r(\bx) == -1\\
+         -1 & : \mbox{otherwise}
+     \end{array}
+   \right.
 \end{align}
@@
 We treat $\sigma$ as a "risk sensitivity" parameter.
-For two reasons: 1)The expected number of examples, after a policy roll out, the supervisor can be asked is  $T*\int_\bx \mathbbm{1}(g_{\sigma}(\bx) == 0) p(\bx|\theta)d\bx$.
+For two reasons: 1)The expected number of examples, after a policy roll out, the supervisor can be asked is  $T*\int_\bx \mathbf{1}(g_{\sigma}(\bx) == 0) p(\bx|\theta)d\bx$.
 Thus, smaller $\sigma$ corresponds to asking for more examples.
-2) A relation exists between how smooth the supervisor's poilcy, $\tilde{\pi}$ and how many examples are needed to learn it.
+2) A relation exists between how smooth the supervisor's policy, $\tilde{\pi}$ and how many examples are needed to learn it.
 Thus, a large $\sigma$ can be dangerous for policies with sharp variation because it will treat points as safe that are really risky.
 
-\section{SHIV} \label{sec:SHIV}
+\section{SHIV:Svm-based reduction in Human InterVention} \label{sec:SHIV}
 
@@
 1600 MHz memory in Python 2.7.
-The policies, $\pi_\theta$ are either the linear SVM or  kernelized ridge regression classes in Scikit-Learn~\cite{scikit-learn}.
+The policies, $\pi_\theta$ are trained using Scikit-Learn~\cite{scikit-learn}.
 Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_r$.
 We set $\nu = 0.1$ and $\nu_r =10^{-3}$ for all experiments.
-We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each domain.
+We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations.
 
@@
 Douglas Boyd, a surgeon and professor at UC Davis.
-Each domain test different aspects of our algorithm: the driving simulator has a high dimensional visual state space, grasping in clutter has a human demonstrator provide the labels and is a challenging manipulation problem, surgical needle insertion uses data from a real robot and has an expert demonstrator.
+Each domain test different aspects of our algorithm: the driving simulator has a high dimensional visual state space, grasping in clutter has a human demonstrator provide the labels and is a challenging manipulation problem, surgical needle insertion uses data from a real robot.
 
@@
 The independent variables are two variables.
-First, we manipulate the online learning from demonstration algorithm we use: SHIV vs.
+First, we manipulate the online LfD algorithm we use: SHIV vs.
 DAgger.
@@
 \includegraphics[width=\columnwidth, height=4cm]{figures/dagger_shiv_one_class.eps}
-\caption{We compare normalized performance (i.e.
+\caption{ \footnotesize We compare normalized performance (i.e.
 matching the performance of the supervisor) for the Driving Simulator , performance is defined as the number of times the car left the track versus the number of queries made to the supervisor.
@@
 Error bars in grey measure the standard error on the mean}
-\vspace*{-10pt}
+\vspace*{-20pt}
 \label{fig:car_cost}
@@
 In our experiment, a human demonstrator provided one demonstration and then iterated until the performance was zero during the policy roll out.
-At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
+At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is  $3\%$ of the width of the table.
 
@@
 \includegraphics[width=\columnwidth, height=4cm]{figures/grasp_clutter.eps}
-\caption{We compare normalize performance (i.e.
+\caption{ \footnotesize We compare normalize performance (i.e.
 mathcing the performance of the supervisor) for Grasping in Clutter domain, performance is defined as the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
 Initial results, which are averaged over 8 different trials suggest a $64\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
-\vspace*{-10pt}
+\vspace*{-20pt}
 \label{fig:grasp_cost}
@@
 Robotic Surgical Assistants (RSAs) are frequently used for procedures such as: prostectomy, uterectomy, and tumorectomies within the abdominal and thoracic cavities with high success rates~\cite{van2013laparoscopic,darzi2004impact}.
-Currently, these devices are controlled by surgeons via physical tele-operation at all times; introducing autonomy of surgical sub-tasks has the potential to reduce cognitive load and facilitate supervised autonomy for remote tele-surgerical procedures.
+Introducing autonomy of surgical sub-tasks has the potential to reduce cognitive load and facilitate supervised autonomy for remote tele-surgerical procedures.
 
@@
 can lead to suture failure and potentially rupture the surrounding tissue \cite{liu2015optimal}. In this experiment, we
-are interested in learning a policy to correct bad initial poses to the proper insertion pose as shown in Fig.
+are interested in learning to correct bad initial poses to the proper pose as shown in Fig.
 \ref{fig:support_example}. Dr. Douglas Boyd, a surgeon and professor at UC Davis, provided us with a collection of demonstrations on a Intuitive Surgical Da Vinci Research Kit \cite{AnnualReport2014}.
@@
 Then converted $C$ to the associated lie algebra vector $c \in \mathbb{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control,  $||\bar{c}_D||$, Dr.
-Boyd applied to the robot.
+Boyd applied.
 
@@
 \includegraphics[width=\columnwidth, height=4cm]{figures/needle_insertion_results.eps}
-\caption{We compare normalized performance (i.e.
+\caption{ \footnotesize We compare normalized performance (i.e.
 matching the performance of the supervisor), performance is defined as the euclidean distance between translation in centimeters.
@@
 Error bars in grey measure the standard error on the mean}
-\vspace*{-10pt}
+\vspace*{-20pt}
 \label{fig:needle}
@@
 \ref{fig:support_example}(d)), which has a committee of different hypothesis estimators and points are marked risky if the committee disagrees.
-Our committee which was trained via bagging \cite{breiman1996bagging}.
+Our committee which was trained via bagging~\cite{breiman1996bagging}.
 To obtain a committee, we divided the training data into 3 overlapping subsets, each with 80\% of the data.
@@
 
+We compare against another novelty detection method as well called Maximal Mean Discrepancy (MMD), which evaluates how close a point is to the distribution using kernel density estimate and adds the variance of the distribution in the dataset $\mathcal{D}$~\cite{kim2013maximum}.
+We set bandwidth of the kernel as the same as our modified One Class SVM and the $\alpha$ decision boundary is set by sorting the MMD value of the states and picking an $\alpha$ such that the lowest $10\%$ are marked as risky.
+This is in similar spirit to $\nu = 0.1$.
+
 We run each query selection method over 50 different car tracks in the driving simulator domain.
-
 We measured the percentage of truly risky states, encountered during the first policy roll out, that  are estimated to be safe by the active learning technique.
@@
 \ref{fig:active_comp}  plots the performance for each query selection method, averaged over 50 tracks.
-We observe a significant performance improvement with methods based on novelty compared to confidence and query by committee.
-Furthermore, using the combined measure of risk performs better than relying solely on novelty.
+We observe a significant performance improvement with methods based on classification based novelty detection compared to confidence,query by committee and MMD.
+Furthermore, using the combined measure of risk performs better than relying solely on the One Class SVM.
 
@@
 		\label{tab:sens}
-
+\vspace*{-10pt}
 \end{table}
@@
 \includegraphics[width=\columnwidth, height=4cm]{figures/risk_bar.eps}
-\caption {  A comparison of different active learning approaches in terms of the percentage of risky states that are estimated to be safe by the active learning technique during the first policy roll out.
-We compare against a confidence estimate of distance to hyperplane, query by committee for 3 hypothesis classifiers, the One Class SVM, and our modified One Class SVM, marked as SHIV.
+\caption {  \footnotesize A comparison of different active learning approaches in terms of the percentage of risky states that are estimated to be safe by the active learning technique during the first policy roll out.
+We compare against a confidence estimate of distance to hyperplane,Maximal Mean Discrepancy, query by committee for 3 hypothesis classifiers, the One Class SVM, and our modified One Class SVM, marked as SHIV.
 Results  are averaged over 50 tracks and the policy $\pi_\theta$ is represented as a Linear SVM.
@@
    }
-
+\vspace*{-20pt}
 \label{fig:active_comp}
@@
 \section{Discussions and Future Work}
-Online imitation learning algorithms have been successful on array of tasks~\cite{NIPS2014_5421,ross2010reduction}, however can place significant burden on a supervisor.
+Online LfD have been successful on array of tasks~\cite{NIPS2014_5421,ross2010reduction}, however can place significant burden on a supervisor.
 Our algorithm, SHIV, implements stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
@@
 
- Lastly, online imitation learning only allows a policy to learn to be as good as the supervisor.
-If the supervisor is imperfect then the robot will be as well.
-Future work will look at combining techniques from inverse reinforcment learning\cite{argall2009survey} with online imitation learning to allow the robot to further fine-tune the policies.
+Furthermore, to update the decision function $g_{\sigma}$ requires solving a quadratic program, which has an upper bound computationally complexity of $O(n^3)$ in the number of data points.
+This can effect the ability of using our modified One Class SVM for larger problems.
+While, Scholk{\"o}pf et al.
+provides an efficient optimization that empirically scale quadratically \cite{scholkopf2001estimating} for very large datasets this can still be burdensome.
+Future work will look at using techniques such as random features or PCA on the kernel Gram matrix to allow for better scaling \cite{scholkopf2002learning}.
 

### 2015-09-16 paper.tex
Updates from ShareLaTeX
Anca's edits

@@
 The former occurs when it is difficult to specify how to trade-off various aspects that matter, like a car trying to drive on the road and dodge other cars \cite{abbeel2004apprenticeship}.
-The latter occurs when either the system or the interaction with the world is difficult to characterize like when a robot is trying to grasp an object in clutter and doesn't have an accurate model of the objects dynamics.
+The latter occurs when either the system or the interaction with the world is difficult to characterize, like when a robot is trying to grasp an object in clutter and does not have an accurate model of the objects dynamics.
 
-Rather than explicitly learning the cost function, like in Inverse Reinforcement Learning \cite{ng2000algorithms}, and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
+Rather than explicitly learning the cost function (like in Inverse Reinforcement Learning \cite{ng2000algorithms}) and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns the policy directly from supervisor examples, mapping states to controls~\cite{argall2009survey}.
 Learning from demonstration has been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering \cite{abbeel2007application},car parking \cite{abbeel2008apprenticeship},  and robotic surgery \cite{van2010superhuman}.
@@
 SHIV  (Svm-based reduction in Human InterVention) reduces supervisor burden by only requesting supervision for risky states.
-SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to the non-stationary state distributions the robot encounters as it iteratively executes learned policies.
+SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to the non-stationary state distributions the robot encounters as it iteratively executes learned policies, and tailored to high dimensional state spaces.
 We build on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
@@
 \noindent\textbf{Active Learning from Demonstration}
-We formulate applying active learning to Online Lfd as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
+We formulate reducing supervisor burden in nnline Lfd as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
 In stream based active learning, the decision of whether to query the supervisor (for a label or control signal) or not is not over the entire state space (like in traditional pool-based active learning), but on states drawn one at a time from some data stream.
@@
 
-Aside from the data stream, stream-based active learning has another ingredient: a query selection method.
-A query selection method is deciding whether or not to query.
+Aside from the data stream, stream-based active learning has another ingredient: a query selection method, deciding whether or not to query.
 Typical query selection methods are estimator-centric, evaluating risk using the estimator, e.g.
@@
 The  estimator is a function of the current distribution.
-Therefore, it no longer provides a good measure of confidence when that distribution changes, as it does when the robot is rolling out a learned policy and starts encountering further away states.
+Therefore, it no longer provides a good measure of confidence when that distribution changes.
+And the distribution does change when the robot is rolling out a learned policy and starts encountering further away states.
 Instead of relying on the estimator, our measure of risk explicitly identifies when states are drawn from a different distribution, i.e.
 when they are novel.
+Our experiments in Section \ref{sec:experiments} suggest that our measure of risk is more accurate in online LfD problems than estimator-centric measures.
 
@@
 Our work builds on Kim et al.
-\cite{kim2013maximum} who apply novelty detection for safe online learning from demonstrations to enable a supervisor to take over and prevent unsafe states.
-In their MMD-LI algorithm, risk is evaluated with Maximal Mean Discrepancy, which for a single point is the sum of a kernel density estimate and variance on the dataset, which works well in low dimensional state spaces.
-MMD-LI also reduces supervisor burden because the supervisor only takes control and provides demonstrations in risky states.
-However, having the supervisor take over can bias the states sampled, which can in practice lead to a loss in performance \cite{ross2010reduction}.
-In contrast, we focus on active learning for online LfD for high-dimensional state spaces, do not assume the supervisor is always available, and propose an alternative to non-parametric density estimation which can require data exponential in the dimension of the state-space
-\cite{nadaraya1964estimating}.
+\cite{kim2013maximum} who apply novelty detection to safe online LfD to enable a supervisor to take over and prevent unsafe states.
+In their MMD-LI algorithm, risk is evaluated with Maximal Mean Discrepancy.
+For a single state, this is the sum of a kernel density estimate and the variance of the dataset, which works well in low dimensional state spaces.
+MMD-LI also reduces supervisor burden because the supervisor only takes over in risky states, as opposed to providing labels for all new states.
+In contrast, we focus on active learning for online LfD in high-dimensional state spaces.
+Unlike safe learning, our problem does not require the supervisor to take over.
+This enables us to avoid the supervisor biasing the states sampled (which can in practice lead to a loss in performance \cite{ross2010reduction}), and also avoid assuming the supervisor is always available.
+On the other hand, our problem does require novelty detection in high dimensional state spaces, where non-parametric density estimation does not scale very well: it can require data exponential in the dimension of the state space \cite{nadaraya1964estimating}.
+Our results (Section \ref{sec:experiments}) suggests that in our high dimensional state spaces, SHIV achieves an error rate half of that of kernel density estimate-bases techniques like MMD.
+%However, having the supervisor take over can bias the states sampled, which can in practice lead to a loss in performance \cite{ross2010reduction}.
+In contrast, we focus on active learning for online LfD for high-dimensional state spaces, do not assume the supervisor is always available, and propose an alternative to non-parametric density estimation which can require data exponential in the dimension of the state-space \cite{nadaraya1964estimating}.
 
-An alternative to evaluating the probability of a data point is to measure distance to its nearest neighbors \cite{knox1998algorithms}. However, this approach was shown to be
+An alternative to kernel density estimates is to measure distance to its nearest neighbors \cite{knox1998algorithms}. However, this approach was shown to be
 susceptible to issues, since nearest neighbors  incorporates only local information about the data.
@@
 In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for novelty detection in high-dimensional image data.
-To our knowledge, incorporating a query selection method for nonstationary distributions, such as the One Class SVM, into online LfD is a novel contribution.
+To our knowledge, incorporating a query selection method for high-dimensional spaces and nonstationary distributions, such as the One Class SVM, into online LfD is a novel contribution.
 
@@
 The decision function parametrization consists of the kernel bandwidth $\sigma$ in $g_s$.
-We treat $\sigma$ as a "risk sensitivity" parameter.
+We treat $\sigma$ as a "risk sensitivity" parameter (and study its implications in Section \ref{sec:experiments}).
 For two reasons: 1)The expected number of examples, after a policy roll out, the supervisor can be asked is  $T*\int_\bx \mathbf{1}(g_{\sigma}(\bx) == 0) p(\bx|\theta)d\bx$.
@@
 
-\section{Experiments}
+\section{Experiments}\label{sec:experiments}
 
@@
 We then  compare our query selection method with those typically used in active learning.
-We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than confidence, query-by-committee based methods and the One Class SVM with out the hole carving out modification.
+We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than confidence, query-by-committee based methods, Maximum Mean Discrepancy, and the One Class SVM without the carving out misclassified holes modification.
 We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from Eq.
@@
 
- We compare four active learning methods.
+ We compare five active learning methods.
 We compare our combined notion of risk (Fig.
@@
 \section{Discussions and Future Work}
-Online LfD have been successful on array of tasks~\cite{NIPS2014_5421,ross2010reduction}, however can place significant burden on a supervisor.
-Our algorithm, SHIV, implements stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
+Online LfD has been successful on an array of tasks~\cite{NIPS2014_5421,ross2010reduction}, however it can place significant burden on a supervisor.
+Our algorithm, SHIV, implements stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary and high-dimensional state distributions.
 We empirically evaluated our method on three different domains: a driving simulator, grasping in clutter and surgical needle insertion.

### 2016-02-22 paper.tex
change stuff

--- 2015-09-16 paper.tex
@@
 \usepackage[ruled,vlined]{algorithm2e}
+\usepackage{url}
+\newenvironment{definition}[1][Definition]{\begin{trivlist}
+\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
 
@@
 
-\renewcommand{\baselinestretch}{.92}
-
+\renewcommand{\baselinestretch}{.95}
+\usepackage{times}
+\usepackage{microtype}
 %\title{Iterative Imitation Learning with Reduced Human Supervision [v11]}
@@
 
-\title{SHIV: Reducing Supervisor Burden using Support Vectors for Efficient
-Learning from Demonstrations in High Dimensional State Spaces }
+\title{A Gambler's DAgger: Reducing Supervisor Burden in Online Learning From Demonstration Learning  Through Hierarchical Supervisors}
 
-\author{Michael Laskey$^1$, Sam Staszak$^1$, Wesley Yu-Shu Hsieh$^1$, Jeffrey Mahler$^1$, \\ Florian T. Pokorny$^1$, Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
+\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$,...,Florian T. Pokorny,\\
+ Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
 \thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu, \small staszass@rose-hulman.edu} }%
@@
 \begin{abstract}
-Online learning from demonstration algorithms, such as DAgger, can learn policies for problems where the system
-dynamics and the cost function are unknown. However, during learning, they impose a burden on supervisors to provide labels (control
-signals) as the robot encounters new states while executing its current best policy. We introduce the SHIV
-algorithm (Svm-based reduction in Human InterVention), which reduces this burden by only requesting supervision for risky states.
-SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.
-To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.
-We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936 dimension visual HOG feature state representation, 2) a push-grasping in clutter simulation for a 4DOF robot arm, using Box2D, with a 22 dimension state representation  of joint angles and the pose of each object, and 3) a surgical needle insertion task with a 16 dimension state represented spatial transform.
-Results suggest that SHIV can learn equivalent policies with up to 70\% fewer queries.
-
+Online learning from demonstration algorithms such as
+DAgger can learn policies for problems where the system dynamics and
+the cost function are unknown. However they impose a
+burden on supervisors to respond to queries each time the robot
+encounters new states while executing its current best policy.
+Traditionally there has only been one supervisor and it is deemed expert.
+However, an expert supervisor might not be needed for a large portion of the state space, which could be handled by less-skilled supervisors.
+We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, which first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy and then only consults an expert for harder to learn states.
+We demonstrate this approach in training a visuomotor deep network policy for 2D grasping in clutter on a 4-DOF Zymark Robot.
+We were able to reduce the number of queries to the final expert supervisor by $X$ and manage to collect $X$K examples by leveraging the hierarchical supervisor model.
  \end{abstract}
@@
 \section{Introduction} 
-
 In model-free robot Learning from Demonstration (LfD), a robot learns to perform a task, such as driving or grasping an object in a cluttered environment, from examples provided by a  supervisor, usually a human.
 In such problems, the robot does not have access to either the cost function that it should optimize, nor the dynamics model.
-The former occurs when it is difficult to specify how to trade-off various aspects that matter, like a car trying to drive on the road and dodge other cars \cite{abbeel2004apprenticeship}.
-The latter occurs when either the system or the interaction with the world is difficult to characterize like when a robot is trying to grasp an object in clutter and doesn't have an accurate model of the objects dynamics.
+The former  when it is difficult to specify how to trade-off various aspects that matter, like a car trying to drive on the road with other cars~\cite{abbeel2004apprenticeship}.
+The latter occurs when either the system or the interaction with the world is difficult to characterize, like when a robot is trying to grasp an object in clutter and does not have an accurate model of the object dynamics.
 
-Rather than explicitly learning the cost function, like in Inverse Reinforcement Learning \cite{ng2000algorithms}, and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns the policy directly from supervisor examples mapping states to controls~\cite{argall2009survey}.
-Learning from demonstration has been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering \cite{abbeel2007application},car parking \cite{abbeel2008apprenticeship},  and robotic surgery \cite{van2010superhuman}.
+Rather than explicitly learning the cost function as in Inverse Reinforcement Learning and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns a policy directly from supervisor examples, mapping states to controls~\cite{argall2009survey}.
+Learning from demonstration has been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering~\cite{abbeel2007application}, car parking~\cite{abbeel2008apprenticeship},  and robot surgery~\cite{van2010superhuman}.
 
-\begin{figure}[ht]
-\centering
-
-\includegraphics[width=0.5\textwidth]{figures/teaser.pdf}
-\caption{ \footnotesize
-SHIV  reduces the number of queries to the supervisor in our three test domains: a) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; b) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; c) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery; d) normalized performance of SHIV and DAgger's policy on the grasping in clutter example versus states labeled by the supervisor.
-}
+ \begin{figure}
+\includegraphics[width=0.5\textwidth]{f_figs/teaser.pdf}
+\caption{Typical Initial States for our grasping in clutter task with a Zymark Robot.
+Red shapes indicate the clutter objects and the yellow circle indicates the goal object.
+The robot learns from raw image date to push the shapes and reach the yellow circle through our algorithm A Gambler's DAgger.
+The inscribed circle in the workspace prevents the robot from learning the trivial solution of simply pushing the red objects off the table.}
 \vspace*{-20pt}
@@
 In offline LfD, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
-During execution, a small error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.
+During execution, a small control error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.
 For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will eventually put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
@@
 
-Online LfD addresses this issue by iteratively gathering more examples from the supervisor in states the robot encounters~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
+Online LfD addresses this issue by iteratively requesting more examples from the supervisor in states the robot encounters~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
 One such algorithm, DAgger, learns a series of policies.
-At each iteration, the robot trains a policy based on the existing examples, then rolls out (executes) that policy, and the supervisor provides demonstrations for all states the robot visits.
-The new state/control examples are aggregated with the old examples for the next iteration.
+At each iteration, the robot computes a policy based on the existing examples, then rolls out (executes) that policy, and the supervisor provides demonstrations for all states the robot visits.
+The new state/control examples are aggregated with the prior examples for the next iteration.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-In DAgger, under certain conditions, the number of errors scales only linearly with the time horizon of the task\cite{ross2010reduction}.
+In DAgger, under certain conditions, the number of errors scales only linearly with the time horizon of the task~\cite{ross2010reduction}.
 
-However one drawback is that DAgger significantly increases the burden on the supervisor, who now labels all states that the robot visits during training.
-Our goal is to reduce supervisor burden without degrading performance.
+One drawback is that DAgger significantly increases the burden on the supervisor, who must label all states that the robot visits during training.
+Traditionally there has only been one supervisor and it is deemed an expert ~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}.
+However, an expert supervisor might not be needed for a large portion of the state space, which could be handled by less-skilled supervisors.
 
-Our key insight is that the robot only needs to request demonstrations for risky states.
-Risk arises because:  (1) states are sufficiently different than the states previously encountered, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that has been misclassified in previous training data.
-%\adnote{Ken's version below does not seem to represent what we actually do.}
-%the action associated with a state under the current policy yield a resulting state that is inconsistent with the expected next state. [how do we measure 2? - Ken]
+Our key insight is that for a large portion of the task the supervisor's time is used teaching the robot something that a less costly supervisor could do.
+For instance in our grasping in clutter example, the robot spends a large portion of the time trying to learn how to go towards the goal object.
+Analytical techniques such as forward kinematics, template matching and motion planning are readily available to provide examples in these parts of the state space.
+However, traditional Online Lfd method exploit the expert supervisor for all parts of the state space.
 
-We present an algorithm for online LfD that can actively decide whether it is necessary to ask the supervisor to label the new states that the robot encounters.
-SHIV  (Svm-based reduction in Human InterVention) reduces supervisor burden by only requesting supervision for risky states.
-SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to the non-stationary state distributions the robot encounters as it iteratively executes learned policies.
-We build on the One Class SVM method for approximating quantile level sets \cite{scholkopf2001estimating} to provide a classification method for deciding if a state is risky or safe.
-
-\adnote{nothing about experiements and resutls?
-how do i know if it worked?
-also how do i know that you didn;t just compare to dagger, but ran an indepth analysis of the algorithm?
-i thought i put a paragraph like that here at some point}
+We propose bootstrapping a policy from a hierarchy of supervisors ranked by cost.
+Examples of such a hierarchy are analytical models with a simplified dynamics of the world, crowd-source Amazon Mechanical Turk workers and then finally an expert supervisor.
+We demonstrate this approach in training a deep neural network for the visuo-motor based task of 2D grasping in clutter on a Zymark Robot.
+Our robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the table.
+The objects dataset consists of 20 Medium Density Fiber extruded polygons taken from 2D projections of objects in the Dex-Net \cite{} database.
+Results show that by bootstrapping from less skilled experts, the total amount of burden on the expert supervisor is reduced and the task is successfully learned \mlnote{We need an objective measure of success}.
 
 \section{Related Work}
-Below we summarize related work in active approaches to robot LfD and risk evaluation techniques.
+Below we summarize related work in reducing the number of queries to an expert in the Online LfD setting.\mlnote{Still a work in progress}
 
-\noindent\textbf{Active Learning from Demonstration}
-We formulate applying active learning to Online Lfd as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}.
-In stream based active learning, the decision of whether to query the supervisor (for a label or control signal) or not is not over the entire state space (like in traditional pool-based active learning), but on states drawn one at a time from some data stream.
-In  online LfD, this data stream is the states encountered when the robot is executing the current best policy.
+\noindent \textbf{Online Lfd with an Expert Supervisor}
+Successful robotic examples of Online Learning From Demonstration where an expert have been employed have been in flying a quad-copter through a foster, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.
 
-Aside from the data stream, stream-based active learning has another ingredient: a query selection method.
-A query selection method is deciding whether or not to query.
-Typical query selection methods are estimator-centric, evaluating risk using the estimator, e.g.
-distance from the classification hyperplane \cite{tong2002support}, as in Fig.
-\ref{fig:support_example}(a); or query by committee  \cite{breiman1996bagging}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data.
-Risk in query by committee is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig.
-\ref{fig:support_example}(b)).
+However, to date these approaches have all used only an expert supervisor to label all parts of the state space.
+Our contribution consists of the use of a hierarchical structure of non-expert supervisors to reduce queries to the expert at the top of the hierarchy.
 
-Both approaches implicitly assume a stationary state distribution --- that the new data is sampled from the same distribution as the previous training data.
-Although such methods have been previously proposed for online LfD (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
-online LfD violates the stationary distribution assumption because each new policy induces a new distribution of states.
-This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.
+\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reducing supervisor burden is applying active learning to only ask for queries one the robot is uncertain about the correct control to apply.
+Traditional active learning techniques like query-by-committee and uncertainty sampling have been applied by \cite{chernova2009interactive,judah2011active,grollman2007dogged}
 
-The problem lies in being estimator-centric.
-The  estimator is a function of the current distribution.
-Therefore, it no longer provides a good measure of confidence when that distribution changes, as it does when the robot is rolling out a learned policy and starts encountering further away states.
-Instead of relying on the estimator, our measure of risk explicitly identifies when states are drawn from a different distribution, i.e.
-when they are novel.
+Kim et al.
+demonstrated that due to the non-stationarity of the problem traditional active learning techniques do not work because the underlying state distribution changes and thus the use of novelty detection is needed to be more conservative in determining uncertainty~\cite{kim2013maximum}.
 
-%%In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on novelty (is the state an outlier to the training distribution), as in Fig.
-\ref{fig:support_example}(c).
-Additionally, we also assign higher risk to  historically mislabeled regions, as in Fig.
-\ref{fig:support_example}(d).
-We then use a classification method based on the One Class SVM \cite{scholkopf2001estimating} to predict if a state is risky or not risky, which we we define as safe.%Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.
+Laskey et al.
+created an approach, known as SHIV, for using active learning tailored to high dimensional and non-stationarity state distributions and  provided a modified version One Class SVM to reduce the problem to regularized binary classification~\cite{laskey}.
+However, the result that novelty detection is needed to reduce supervisor burden via active learning implies that for problems with high stochasticity, such as grasping in clutter with a large number of objects, the expert would be queried a significant number.
+Furthermore, with the advent of deep learning where the feature space changes each iteration, it becomes unclear as to what feature space to provide novelty detection in.
 
-\noindent\textbf{Risk via Novelty Detection}
-The main motivation for our risk definition is the notion that a trained model will be able to generalize within the distribution it is
-trained on \cite{tokdar2010importance}, making states outside of this distribution risky.
-Novelty detection \cite{hodge2004survey} is concerned with recognizing when this happens: recognizing that a sample is outside of this distribution.
+\noindent\textbf{Training Policies Via Analytical Methods} Instead of relying on a costly human supervisor an alternative approach is to use knowledge of the underlying dynamics and train a policy via a computationally expensive analytical method such as a controller in a physics simulator~\cite{IGOR} or dynamic programming in a Atari video game~\cite{NIPS2014_5421}.
 
-Our work builds on Kim et al.
-\cite{kim2013maximum} who apply novelty detection for safe online learning from demonstrations to enable a supervisor to take over and prevent unsafe states.
-In their MMD-LI algorithm, risk is evaluated with Maximal Mean Discrepancy, which for a single point is the sum of a kernel density estimate and variance on the dataset, which works well in low dimensional state spaces.
-MMD-LI also reduces supervisor burden because the supervisor only takes control and provides demonstrations in risky states.
-However, having the supervisor take over can bias the states sampled, which can in practice lead to a loss in performance \cite{ross2010reduction}.
-In contrast, we focus on active learning for online LfD for high-dimensional state spaces, do not assume the supervisor is always available, and propose an alternative to non-parametric density estimation which can require data exponential in the dimension of the state-space
-\cite{nadaraya1964estimating}.
-
-An alternative to evaluating the probability of a data point is to measure distance to its nearest neighbors \cite{knox1998algorithms}. However, this approach was shown to be
-susceptible to issues, since nearest neighbors  incorporates only local information about the data.
-For example, a group of outliers can be close together, but significantly far from the majority of the data and nearest neighbors would mark them as not novel \cite{hodge2004survey}.
-
-Our approach is based on the One Class SVM proposed by Scholk{\"o}pf et al., which estimates a particular quantile level set for the training data by solving a convex quadratic program  to the find support
-vectors~\cite{scholkopf2001estimating}. The method has been theoretically shown to approximate the quantile levelset of a density estimate
-asymptotically for correctly chosen bandwidth settings and in the case of a normalized Gaussian kernel function \cite{vert2006consistency}. 
-In \cite{liu2014unsupervised}, the One Class SVM has furthermore been used for novelty detection in high-dimensional image data.
-To our knowledge, incorporating a query selection method for nonstationary distributions, such as the One Class SVM, into online LfD is a novel contribution.
+While this approach can "compile" the computationally expensive option into an quickly computed function, it can be limited when analytical models cannot explicitly model the environment.
+For instance in our grasping in clutter example, the robot has no knowledge of the mass or friction properties of the object, which would make this a challenging problem for such analytical methods.
+We thus propose using analytical methods not as the expert supervisor, but instead part of a hierarchy where they can be used to reduce the burden of the supervisors above them in the hierarchy.
 
 \section{Problem Statement}
-The goal of this work is to learn a policy that matches that of the supervisor's while asking the supervisor for as few examples as possible.
+The goal of this work is to learn a policy that matches that of an expert supervisor's while asking expert supervisor with fewer queries than DAgger.
 
@@
 We also assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.
-Lastly, we assume access to a supervisor who can, given a state, provide a control signal label.
-We additionally assume the supervisor can be noisy and imperfect, noting that the robot cannot surpass the level of performance of the supervisor.
+Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label.
+We additionally assume the supervisors can be noisy and imperfect, noting that the robot cannot surpass the level of performance of the current supervisor it is training with.
 
@@
 $$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
-We assume a probability density over initial states $p(\bx_0)$.
+We assume a probability density over initial states $p(\bx_0)$ that can be sampled from.
 %We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.
@@
 Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
-induces a density on trajectories of length $T+1$: $$p(\tau | \theta)=
-p(\bx_0)\prod_{i=0}^{T-1}p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$$
-
-Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ from time $0$ to time $t-1$.  Following \cite{ross2010reduction}, we can compute
+induces a density on trajectories. Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
+$\pi_{\theta}$ from time $0$ to time $t-1$.  Following~\cite{ross2010reduction}, we can compute
 the average density on states for any timepoint by $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
@@
 
-\noindent\textbf{Objective.} The objective of  policy learning is to find a policy that minimizes some known cost function $C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$.
-The cost $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific.
-For example, in the task of inserting a peg into a hole, a function on distance between the peg's current and desired final state is used \cite{levine2015end}.
+\noindent\textbf{Objective.} The objective of  policy learning is to find a policy that maximizes some known cumulative reward function $\sum^T_{t=1} r(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$.
+The reward $r:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific.
+For example, in the task of inserting a peg into a hole, a function on distance between the peg's current and desired final state is used~\cite{levine2015end}.
 
-In our problem, we do not have access to the cost function itself. Instead, we only have access to 
+While a reward function exists for a task like grasping in clutter, such as a positive value for successfully reaching the goal object.
+It is often too delayed to provide useful information for quickly learning \cite{kitaevphysics}.
+We thus assume access to
 a supervisor that can achieve a desired level of performance on the task. The supervisor provides the robot an initial set
-an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
-which are the result of the supervisor applying this policy. This induces a training data set $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
+ of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
+which are the result of the supervisor applying their policy. This induces a training data set $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
 
-We define a `surrogate' loss function as in \cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+We define a `surrogate' loss function as in~\cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
 measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2_2$,
@@
 
-Following \cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
+Following~\cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
 
@@
  If the robot could learn the policy  perfectly, this state density would match the one encountered in user examples.
-But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to ~\cite{pomerleau1989alvinn}.This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing feedback.
+But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to~\cite{pomerleau1989alvinn}.
+This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing feedback.
 The feedback is in the form of control signals on states sampled from the robot's new distribution of states.
 
-\section{Risky and Safe States}
+ \section{A Gambler's DAgger}
+ In this section, we first recall the original DAgger algorithm.
+Then introduce the notion and formal definition of a hierarchical supervisor and finally describe how to combine DAgger with a hierarchical supervisor to create a Gambler's DAgger.
 
-\begin{figure*}[t]
-\centering
+ \subsection{DAgger: Dataset Aggregation}
+ DAgger~\cite{ross2010reduction} solves the minimization in Eq.
+\ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
 
-\includegraphics[width=\textwidth]{figures/active_learning.pdf}
-
-\caption{\footnotesize A comparison of different query selection strategies for active learning on a non-stationary distribution.
-The shaded and empty circles are training data from two classes, $1$ and $0$ respectively.
-The red empty circles are samples from a new distribution (produced by executing the learned policy), and belong to class $0$.
-Typical strategies classify states close the decision boundary as risky(a), or for which a set of estimators disagree (b).
-Neither of these apply to our new samples in red.
-In contrast, we use a strategy that is amenable to non-stationary distributions by classifying  novel states as safe (i.e not risky) (c) and states in historically mislabeled regions.
-}
-\vspace*{-20pt}
-\label{fig:support_example}
-\end{figure*}
-
-Providing correct control inputs for (or ``labeling'')  all states encountered at each
-iteration can impose a large burden on the supervisor.
-Instead of asking the supervisor for labels at all visited states, SHIV uses a measure of risk to actively decide whether a label is necessary.
-
-In contrast to the standard measure risk based purely on variance, we define a state as "risky" for 2 reasons: 1) it lies in an area with a low density of
-previously trained states, which can cause the current policy to mis-predict the supervisor and incur high surrogate
-loss~\cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at the state  is high, so that the state is unlikely to model the supervisor's control inputs correctly.
-States that are not classified as "risky" are deemed "safe" .Our definition of risk can be visualized in Fig.
-\ref{fig:support_example}(d).
-
-The amount of data needed to estimate the density, scales exponentially in the dimension of the state space~\cite{nadaraya1964estimating}. 
-Thus, to evaluate risk in high-dimensional state spaces, such as the HOG features in our driving simulator, Fig. \ref{fig:teaser}(a), we use
-a modified version of the technique known as the One Class SVM that  estimates a regularized boundary of a user defined quantile on the training data in $\mathcal{X}$~\cite{scholkopf2001estimating}.
-%\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}
-
-%\subsection{Estimation of Quantile Level Sets}\label{sec:level}
-We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
-independent and identically distributed samples $\mathbf{x}_1,...,\mathbf{x}_n\in \mathcal{X}$.
-In most general terms, the quantile function for $P$ and subject to a class of measurable subsets $\mathcal{G}$ of $\mathcal{X}$ is
-defined by
-\vspace{-2ex}
-\begin{align}\label{eq:quantile}
-U(\gamma) = \mbox{inf} \lbrace \lambda(G):P(G) \geq \gamma, G \in \mathcal{G} \rbrace \: 0<\gamma \leq 1
-\end{align} 
-$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure.
-Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
-measure (i.e. volume) for each $\gamma\in [0,1]$ (this set is in general not necessarily unique). 
-$G(\gamma)$ denotes a set of minimum measure $G \in \mathcal{G}$ with $P(G(\gamma))\ge \gamma$. Note in particular that $G(1)$ is the support of the density $p$ corresponding to $P$, if $p$ exists.
-
-To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al.
-represents the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}.
-By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
-derives an approximation of the quantile function described in Eq. \ref{eq:quantile}.
-This approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$,
-$f_w(\mathbf{x}) = \sum_i w_i k(\mathbf{x}_i, \mathbf{x})$
-and $(w,\rho)$ denote the weight vector and offset parameterizing a hyperplane in the feature space associated with a
-Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/2\sigma^2}$.
-
-Let $\Phi:\mathcal{X}\to \mathcal{F}$ denote the feature map corresponding to our exponential kernel, mapping the
-observation space $\mathcal{X}$ into a Hilbert space $(\mathcal{F}, \langle, \rangle)$ such that $k(\bx, \bx') = \langle
-\Phi(\bx), \Phi(\bx')\rangle$.
-
-The One Class SVM proposed by \cite{scholkopf2001estimating} determines a hyperplane in feature space $\mathcal{F}$
-maximally separating the input data from the origin:
-\vspace{-2ex}
-\begin{align}\label{eq:primal_sup}
-    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{minimize}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
-\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
-\end{align}
-
-Here, the parameter $\nu$ controls the penalty or `slack term' and is equivalent to $\gamma$ \cite{vert2006consistency}
-in the quantile definition, Eq. \ref{eq:quantile}, as the number of samples increases. The decision
-function, determining point membership in the approximate quantile levelset is given by $g(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho)$.
-Here, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
-$g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
-if $x$ lies strictly in the quantile sub-levelset.
-
-The dual form of the optimization yields a Quadratic Program 
-that has worst case computational complexity of $O(n^3)$.
-However, Sch{\"o}lkopf et al.
-developed an improved optimization method that has empirically been shown to scale quadratically \cite{scholkopf2001estimating}.
-In the dual, the decision function is given by $g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho)$ where $\alpha_i$ corresponds to the dual variables.
-The novelty detection method can be visualized in Fig.
-\ref{fig:support_example}(c).
-However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
-optimizing Eq. \ref{eq:super_objj} may still incur a large surrogate loss. To account for this, we propose a
-modification to the One Class SVM:
-
-\vspace{-2ex}
-\begin{align}
-y_i = \left\{
-     \begin{array}{lr}
-         1 & : l(\pi_{\theta}(\bx_i),\bu_i)\le \varepsilon\\
-         -1 & : l(\pi_{\theta}(\bx_i),\bu_i)>\varepsilon
-     \end{array}
-   \right.
-\end{align}
-
-Where, in the case when $l$ denotes discrete $0-1$ loss, we set $\varepsilon = 0$, while in the continuous $L_2$ loss
-case, $\varepsilon$ is a user defined threshold specifying allowable surrogate loss.
-We use $y_i$ to modify the One Class SVM decision function as follows:
-
-We divide up our data in to two sets those correctly classified: $\mathcal{D}_{s}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y_i=1\}$ and those states incorrectly classified: $\mathcal{D}_{r}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y_i=-1\}$
-A separate One-Class SVM is then trained on each set of states, ($D_{s}$ and $D_{r}$) and providing measures of the level sets, $g_{s}$ and $g_{r}$.
-Specified by parameters $(\nu,\sigma)$ and $(\nu_r,\sigma_r)$, respectively.
-
-We then define the overall decision function as:
-
-\vspace{-2ex}
-\begin{align}\label{eq:decision_func}
-g_{\sigma}(\bx) = \left\{
-     \begin{array}{ll}
-         0 & : g_s(\bx) == 1 \: \mbox{and} \: g_r(\bx) == -1\\
-         -1 & : \mbox{otherwise}
-     \end{array}
-   \right.
-\end{align}
-points are deemed risky if $g_{\sigma}(\bx) \neq 0$.  Practically, this modification corresponds to
-`carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
-excluded from the super-levelset. An illustration of this can be seen in Fig. \ref{fig:support_example}(d).
-
-The decision function parametrization consists of the kernel bandwidth $\sigma$ in $g_s$.
-We treat $\sigma$ as a "risk sensitivity" parameter.
-For two reasons: 1)The expected number of examples, after a policy roll out, the supervisor can be asked is  $T*\int_\bx \mathbf{1}(g_{\sigma}(\bx) == 0) p(\bx|\theta)d\bx$.
-Thus, smaller $\sigma$ corresponds to asking for more examples.
-2) A relation exists between how smooth the supervisor's policy, $\tilde{\pi}$ and how many examples are needed to learn it.
-Thus, a large $\sigma$ can be dangerous for policies with sharp variation because it will treat points as safe that are really risky.
-
-\section{SHIV:Svm-based reduction in Human InterVention} \label{sec:SHIV}
-
-Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq.
-\ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
-However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky enough to warrant a query.
-
-\subsection{Step 1}
+\subsubsection{Step 1}
 The first step of any iteration $k$ is to compute a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D}_k=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $\mathcal{D}$ of initial trajectory demonstrations):
 
- \vspace{-2ex}
+ \vspace{-1ex}
 \begin{align}\label{eq:super_objj}
@@
 
-This sub-problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net \footnote{To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$
-can be considered as present in the policy's output.  A regularization technique in the optimization is
-used to control the smoothness of the function that is fit to the sampled data.
-In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.}.
-Performance can vary though with the selection of a the estimator \cite{scholkopf2002learning}
+This sub-problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net.
+Performance can vary though with the selection of a the estimator~ Selecting the correct function class depends on the task being consider and knowledge of the problem, see for a guide~\cite{scholkopf2002learning}.
 
- \subsection{Step 2}
-The second step SHIV and DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.
-
-What happens next, however, differs between SHIV and DAgger.
+ \subsubsection{Step 2}
+The second step  DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.
 For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
@@
 
-SHIV only asks for supervision on states for which are risky, or $g_{\sigma}(\bx) \neq 0$: 
-$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$
 Steps 1 and 2 are repeated for $K$ iterations or until 
@@
 
-\section{Experiments}
+\subsection{Hierarchy of Supervisors}
+Instead of one expert supervisor,we propose a hierarchy  of $M$ supervisors where for each supervisor $\tilde{\pi}_m$, there is an associated expected cumulative reward $R_m = \int \sum^T_{t=1} r(\mathbf{x}_t,\mathbf{u}_t) p(\mathbf{x}|\tilde{\pi}_m)d\mathbf{x})$, where $p(\mathbf{x}|\tilde{\pi}_m)$ denotes the average distribution of states the supervisor encounters.
+We also denote some measure of cost $C_m$ that is ascribed to the supervisor, such as computational time or monetary expense.
+We assume that the rank of supervisors in terms of cost is equivalent to the rank of supervisor in the terms of expected cumulative reward.
+Thus, the cheapest supervisor also receives the lowest expected cumulative reward.
 
-All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
-1600 MHz memory in Python 2.7.
-The policies, $\pi_\theta$ are trained using Scikit-Learn~\cite{scikit-learn}.
-Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_r$.
-We set $\nu = 0.1$ and $\nu_r =10^{-3}$ for all experiments.
-We tuned $\sigma$ and $\sigma_r$ by performing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations.
+Additionally for two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ to be in the hierarchy, they must only disagree in expectation on a subset of the work space to some precision $\tilde{\epsilon}$.
+Denote the set of states two supervisors disagree as $\mathcal{X}_{m,m+1} = \lbrace \mathbf{x} | ||\tilde{\pi}_m(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x}) ||^2_2 > \tilde{\epsilon} \rbrace$ .We make this condition because if two supervisors never provided the same examples then all states would have to be relabeled by the next supervisor in the hierarchy.
 
-We compare SHIV and DAgger in three domains: a driving simulator, push-grasping in clutter with a 4DOF arm, and surgical needle insertion using demonstrations from Dr.
-Douglas Boyd, a surgeon and professor at UC Davis.
-Each domain test different aspects of our algorithm: the driving simulator has a high dimensional visual state space, grasping in clutter has a human demonstrator provide the labels and is a challenging manipulation problem, surgical needle insertion uses data from a real robot.
+We formally define two supervisor's in a hierarchy as follows
 
-We then  compare our query selection method with those typically used in active learning.
-We show that for a non-stationary state distribution like ours, the notion of risk based on novelty and misclassified regions performs better than confidence, query-by-committee based methods and the One Class SVM with out the hole carving out modification.
-We continue with a sensitivity analysis, which suggests that the performance of SHIV is robust to the choice of how risky the robot is allowed to be (the $\sigma$ parameter from Eq.
-\ref{eq:decision_func}).
+\begin{definition} Two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ are in a hierarchy if  $C_m < C_{m+1}$ , $R_m < R_{m+1}$ and  $\mathcal{X}_{m,m+1} \subset \mathcal{X}$
+\end{definition}
 
-\subsection{Comparing SHIV with DAgger}
-We compare SHIV with DAgger on three domains: the driving simulator from above, push-grasping in clutter, and needle insertion.
-We hypothesize that SHIV achieves the same performance as DAgger, but by asking for fewer examples and thus reducing supervisor burden.
+We note that a two hierarchical supervisors according to this definition also implies that supervisor $\tilde{\pi}_{m+1}$ in the hierarchy is higher than the set of supervisors $\lbrace \tilde{\pi}_i | \forall i \in [0,m] \rbrace$.
 
-The independent variables are two variables.
-First, we manipulate the online LfD algorithm we use: SHIV vs.
-DAgger.
-Second, we manipulate how many examples the algorithms are allowed to ask for: we set a budget of labeled states, and analyze performance as this budget increases.
+\subsection{A Gambler's DAgger}
+Our algorithm is as follows: first iterate through Step 1 and 2 of DAgger for a given supervisor, however after iteration $K$ or when the current policy, $\pi_{\theta_{m,k}}$ is able to achieve a loss $\epsilon$ on the sampled $J$ states at that current iteration (i.e):
 
-For each algorithm and budget of states labeled, we measure the normalized performance (e.g.
-1 corresponds to matching the supervisor's performance on a task).
-Performance is a domain specific term, such as number of times the car crashes in the driving simulator.
+$$\frac{1}{J} \sum^J_{j=1} ||\pi_{\theta_{m,k}}(\mathbf{x}_j) - \tilde{\pi}_m(\mathbf{x}_j) ||^2_2 \leq \epsilon$$
 
-\subsubsection{Driving Simulator}
+Then iterate to the next supervisor in the hierarchy or $m = m+1$.
+An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_K$ has examples from a different supervisor that receives a smaller expected cumulative reward.
+This could cause a learning algorithm to try and regress to both labels and diverge from the intended performance \cite{scholkopf2002learning}.
 
-Our first domain is a common benchmark in Reinforcement Learning: learning a policy for a car to drive around a track~\cite{argall2009survey,ross2010efficient,ross2011reduction}.
-We implemented a driving simulator where the car must follow a polygonal track.
-We generate a polygonal track by repeatedly sampling from a Gaussian with mean that is the center of the video game workspace centered in the middle of the workspace, and computing the convex hull of the sampled points.
-Then a convex hull is computed on the sampled points.
-This produces tracks composed of five to seven edges, an example is shown in Fig.
-\ref{fig:teaser}(a).
-If the car accidentally leaves the track, it is placed
-back on the center of the track at a nearby position. The car's steering is  $\mathcal{U} = \lbrace
--15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle at a unit speed. 
-The internal state space of the car is given by the
-xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
-state space search through the driving simulator to plan the next control.
-The supervisor is only allowed to search a finite amount a time ahead in the game and is prone to error, thus on averages crashes 5.4 times per lap.
+We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the current $\theta_{m,K}$ weight parameters.
+Thus, we propose only performing DAgger for each individual supervisor in the hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor.
+\mlnote{the last step about the dataset is something I want to empirically validate}
 
-The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
-and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
-Oriented Gradients (HOG) features using OpenCV. This results in a $27926$ dimensional state space description.
-For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
-policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
-validation on the initial training examples. We set SHIV's parameters  of the exponential kernel's bandwidth as $\sigma = 200$ and $\sigma_r = 200$, which are set via the grid search defined above.
+\begin{figure*}[t]
+\centering
 
-In Fig.
-\ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.
-We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
-randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
-results from these experiments, suggesting a $71\%$ reduction in the number of queries needed for SHIV compared to DAgger, in order to reach approximately the same performance as our non-optimal supervisor.
+\includegraphics[width=\textwidth]{f_figs/Labeling_GUI.pdf}
+
+\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task.
+The pink overlay indicates the desire change in the robot position with respect to the current robot state.
+Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave.
+Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm c) is closing the gripper and d) is rotating the turn table}
+\vspace*{-20pt}
+\label{fig:overlays}
+\end{figure*}
+
+\section{System for Grasping in Clutter Task}
+We now detail or experimental system for testing A Gambler's DAgger.
+First we describe the task itself, then each supervisor in the hierarchy and finally our deep network representation of the policy trained.
+
+\subsection{Task}
+We are interested in training a Zymark \mlnote{need make and model} to perform a grasping in clutter task on image data taken from a Logitech 2000 camera.
+Examples of images from the camera can be seen in Fig.
+\ref{fig:teaser}.
+
+The objects in clutter are made Medium Density Fiberboard and each one is on average 4" in diameter.
+The objects deemed cluttered are painted Red and the goal object is painted yellow.
+There is an inscribed circle around the work space to keep the robot from pushing the objects outside of the work space.
+The inscribed circle makes the task more challenging because the robot cannot simply "sweep" the cluttered objects off the table.
+
+The robot, shown in Fig.
+\ref{fig:robot}, has a 4 dimensional internal state of base rotation, arm extension, gripper and turn table.
+The robot is commanded via state position requests, which are tracked by a tuned PID controller.
+The policy $\pi_\theta$ outputs delta positions that are bounded by $15\deg$ for the gripper and turntable, $1$ cm for the arm extension and $0.5$ cm for the gripper at each time step.
+There is $T=100$ time steps in a trajectory.
 
@@
 \centering
-\includegraphics[width=\columnwidth, height=4cm]{figures/dagger_shiv_one_class.eps}
-\caption{ \footnotesize We compare normalized performance (i.e.
-matching the performance of the supervisor) for the Driving Simulator , performance is defined as the number of times the car left the track versus the number of queries made to the supervisor.
-We plot the performance of DAgger and SHIV, the teal and orange lines.
-We also plot the performance of our supervisor, who makes non-optimal decisions and has an average performance of 5.4 crashes.
-Initial results, which are run for 6 iterations each and are averaged over 40 levels, shown in Fig.
-\ref{fig:car_cost} suggest an $71\%$ reduction in the number of queries needed for SHIV compared to DAgger.
-Error bars in grey measure the standard error on the mean}
-\vspace*{-20pt}
-\label{fig:car_cost}
+\includegraphics[width=\columnwidth, height=4cm]{f_figs/robot.pdf}
+\caption{ \footnotesize Shown above is a Zymark robot.
+The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table.
+The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}
+\vspace*{-10pt}
+\label{fig:robot}
 \end{figure}
 
-\subsubsection{Grasping In Clutter in Box2D}
+\subsection{Supervisor Hierarchy}
+In this section, we list each supervisor in the order they appear in our hierarchy. The first supervisor is deemed the least expensive.
 
-We investigate having a human demonstrator control a simulated robot arm in 2D to reach a target object with out knocking other objects off a table.
-Grasping an object in a cluttered environment is a common task for a robot in an unstructured environment and has been considered a benchmark for robotic manipulation~ \cite{kitaevphysics,kingnonprehensile}.
-The task is difficult because modeling the physics of pushing an object is non-trivial and requires knowing the shape, mass distribution and friction coefficient of all objects on the table.
-We are interested in learning such a policy via human demonstrations.
+\noindent \textbf{Analytical Supervisor} Our first supervisor is a an analytical method that computes the trajectory the robot should move in to reach the goal object, or yellow circle.
+Our method employs template matching to identify the goal object in the image and the using the forward dynamics of the robot to computes the relative change in direction the robot should apply as an control.
+The template matching is implemented in OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}.
 
-We used Box2D a physics simulator to model a virtual world. We simulate a 4 DOF robot arm with three main joints and a parallel jaw gripper as
-displayed in Fig. \ref{fig:teaser}(b). SHIV and DAgger do not have access to the underlying dynamics of the simulator and must learn a policy from only demonstrations.
+In this stage, the analytical supervisors only tries to teach the robot to move towards the goal.
+Note that the analytical supervisor's advice contains no information about how the cluttered objects will respond to the dynamics applied, which results in sub-optimal polices.
+However, our analytical supervisor is both computationally and monetarily inexpensive to run which allows us to provide a large number of examples.
 
-For input the human demonstrator provides controls through an XBox game controller. The right joystick was used to
-    provide horizontal and vertical velocity inputs for the center of the end-effector which were then translated into
-robot arm motions by means of a Jacobian transpose controller for the 3 main joint angles.
-The left `bumper' button on the joystick was used to provide a binary control signal to close the parallel jaw
-gripper. The control inputs are hence modeled by the set $\mathcal{U} = \lbrace [-1,1],[-1,1],\lbrace 0,1 \rbrace \rbrace$.
+\noindent \textbf{CrowdSourced Supervisor} Our next level of supervisor relies on a crowd source service, called Amazon Mechanical Turk (AMT).
+Chung et al.
+demonstrated the reliable data learning from demonstration data could be obtained from an AMT platform.
+The AMT platform makes readily available thousands of human workers that can perform remedial task for a price range of \$1-0.1\cite{chung2014accelerating}.
+Thus potentially providing a higher quality supervisor who has an intuition for how the cluttered objects interact with the world, but at a higher cost.
 
-A state $\bx\in \mathcal{X}$ consisted of the 3 dimensional pose of the six objects on the table (translation and rotation), the 3 joint angles of the arm and a scalar value in the range $[0,1]$ that measured the position of the gripper, $1$ being fully closed and $0$ being opened.
-For our representation of $\pi_{\theta}$, we used kernelized ridge regression with the radial basis function as the kernel with the default Sci-Kit learn parameters.
-We defined performance as the sum of the number of objects knocked off the table plus $10$ times the binary value indicating if the object is grasped or not.
-The order of magnitude difference in cost for grasping the object is to place emphasize on that portion of the task.
-The bandwidth parameters for SHIV were set to $\sigma_r = 5$ and $\sigma = 6$.
-For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's control.
+In order to get quality example from a CrowdSourced Supervisor, we designed an interface shown in Fig.
+\ref{fig:overlays}.
+The interface draws a transparent overlay that shows how the robot would respond provided the current control this allows for the AMT worker to see some of the effect of their control.
+We rely on their natural intuition for how objects to infer how the change in robot position will change the objects.
 
-In our experiment, a human demonstrator provided one demonstration and then iterated until the performance was zero during the policy roll out.
-At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is  $3\%$ of the width of the table.
+We also design a tutorial for the work that first has them perform designated motions on a virtual robot and introduces them to a problem.
+We additionally provide a video of an expert providing corrections on three robot trajectories.
 
- In Fig.
-\ref{fig:grasp_cost} , we show the normalized performance averaged over 8 rounds for SHIV and DAgger.
-Supporting our hypothesis, our results suggests that SHIV can achieve the same performance with a 64\% reduction in the number of examples needed.
+\noindent \textbf{Expert Supervisor} Finally after training with the Analytical and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource, to provide corrections for a problem that would be non-obvious for someone who doesn't understand the physical limiations of the problem.
+Examples of this could be joint limits of the robot or how some of the objects might respond in more advanced dynamics.
+\mlnote{After we run the AMT study it will become apparent where an expert is still needed}
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth, height=4cm]{figures/grasp_clutter.eps}
-\caption{ \footnotesize We compare normalize performance (i.e.
-mathcing the performance of the supervisor) for Grasping in Clutter domain, performance is defined as the sum of the number of objects knocked off the table plus 10 times the binary value indicating if the object is grasped or not.
-Initial results, which are averaged over 8 different trials suggest a $64\%$ reduction in the number of queries needed for SHIV compared to DAgger,}
-\vspace*{-20pt}
-\label{fig:grasp_cost}
-\end{figure}
+It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSource Supervisor.
 
-\subsubsection{Surgical Needle Insertion}
+\subsection{Deep Neural Network Policy Architecture}
+Our policy is represented as deep neural network, which was trained using TensorFlow~\cite{tensorflow2015-whitepaper}.
+Our network architecture consists of 1 convolutional layer with 5 channels, a fully connected layer with an output of 128 dimensions and a final layer that maps to a four dimensional control signal.
+We used ReLus to separate the different layers and a final tanh on the output to scale the output between -1 and 1.
 
-Robotic Surgical Assistants (RSAs) are frequently used for procedures such as: prostectomy, uterectomy, and tumorectomies within the abdominal and thoracic cavities with high success rates~\cite{van2013laparoscopic,darzi2004impact}.
-Introducing autonomy of surgical sub-tasks has the potential to reduce cognitive load and facilitate supervised autonomy for remote tele-surgerical procedures.
+To determine our architecture we created a set of 32,400 different architectures and then performed simulated annealing on the loss function trained after 400 iterations with a batch size of 200.
+The set of architectures consist of different network architectures as well as different momentum terms, and weight initialization schemes.
 
-Suture tying in surgery is a manually intensive task that can occur frequently through out a surgery. One important step
-in suture tying is properly placing a needle in an initial configuration for insertion. Misplacement of this the needle
-can lead to suture failure and potentially rupture the surrounding tissue \cite{liu2015optimal}. In this experiment, we
-are interested in learning to correct bad initial poses to the proper pose as shown in Fig.
-\ref{fig:support_example}. Dr. Douglas Boyd, a surgeon and professor at UC Davis, provided us with a collection of demonstrations on a Intuitive Surgical Da Vinci Research Kit \cite{AnnualReport2014}.
+We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
 
-Dr. Boyd demonstrated a set of trajectories that each started at an initial attempted needle insertion pose $P_0$ and
-applied the necessary corrections to achieve a goal pose $P_G$. The time horizon, $T$ of each trajectory was on average 80.  We used three of these demonstrations as our initial
-dataset $\mathcal{D}_0$, thus $|\mathcal{D}_0| = 240$.
-In order to study convergence of both SHIV and DAgger, we chose to create a synthetic expert for online learning part.
-The expert controller computed the transformation between the desired insertion pose and the current pose  by calculating the inverse of a transformation matrix, $C = P_0P_G^{-1}$.
-Then converted $C$ to the associated lie algebra vector $c \in \mathbb{R}^6$ for $SE(3)$ and normalize it to the average magnitude of the control,  $||\bar{c}_D||$, Dr.
-Boyd applied.
+\section{Experiments}
 
-The policy $\pi_{\theta}$ was represented as kernel ridge regression with the default values given in Sci-Kit learn.
-The state $\mathcal{X}$ was  a 16 dimensional vector consisting of the elements in the pose $P$ vector.
-The control space $\mathcal{U}$ was a $\mathbb{R}^6$ vector representing the Lie algebra.
-
-For the $\epsilon$ term in the our risk method, we used the median in regression error which was the L2 distance between the predicted control and the true supervisor's control. 
-regions respectively. The bandwidth, $\sigma$, in the rbf kernel was set to $2$ and $\sigma_b = 1$.
-
-For trials we sample a start position from a Gaussian on the translational component of $P_0$ with isotropic variance of
-$0.1$ cm. The distance between initial $P_0$ and $P_G$ is roughly $3$ cm. Performance is measured in
-terms of Euclidean distance in translational component, which is in centimeters. We run DAgger and SHIV both for 20 iterations and average over 40 different starting positions.
-
- In Fig.
-\ref{fig:grasp_cost} , we show the normalized performance (i.e.
-1 corresponds to matching the supervisor) averaged over 40 rounds for SHIV and DAgger.
-Supporting our hypothesis, our results suggests that SHIV can achieve the same performance with a $67\%$ reduction in the number of examples needed.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth, height=4cm]{figures/needle_insertion_results.eps}
-\caption{ \footnotesize We compare normalized performance (i.e.
-matching the performance of the supervisor), performance is defined as the euclidean distance between translation in centimeters.
-In Fig.
-\ref{fig:car_cost}, we plot the performance of DAgger and SHIV.
-Initial results, which are run for 20 iterations each and are averaged over 40 different initial starting positions, shown in Fig.
-\ref{fig:car_cost} suggest an $67\%$ reduction in the number of queries needed for SHIV compared to DAgger.
-Error bars in grey measure the standard error on the mean}
-\vspace*{-20pt}
-\label{fig:needle}
-\end{figure}
-
-\subsection{SHIV Analysis}\label{sec:car}
-
-\subsubsection{Comparison to active learning approaches.}
-
- We compare four active learning methods.
-We compare our combined notion of risk (Fig.
-\ref{fig:support_example}(d)), with risk based on novelty alone (Fig.
-\ref{fig:support_example}(c)) in order to test whether carving out regions that have been misclassified previously is valuable.
-
-We also compare against two baselines typically used in active learning.
-The first is confidence based on distance from the classification hyperplane \cite{tong2002support} (Fig.
-\ref{fig:support_example}(a)).
-We set the threshold distance to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver.
-
-The second baseline is Query By Committee (Fig.
-\ref{fig:support_example}(d)), which has a committee of different hypothesis estimators and points are marked risky if the committee disagrees.
-Our committee which was trained via bagging~\cite{breiman1996bagging}.
-To obtain a committee, we divided the training data into 3 overlapping subsets, each with 80\% of the data.
-We trained a Linear SVM on each subset.
-If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk.
-%We finally compared our combined risk approach against the traditional One Class SVM without the "carving out".
-
-We compare against another novelty detection method as well called Maximal Mean Discrepancy (MMD), which evaluates how close a point is to the distribution using kernel density estimate and adds the variance of the distribution in the dataset $\mathcal{D}$~\cite{kim2013maximum}.
-We set bandwidth of the kernel as the same as our modified One Class SVM and the $\alpha$ decision boundary is set by sorting the MMD value of the states and picking an $\alpha$ such that the lowest $10\%$ are marked as risky.
-This is in similar spirit to $\nu = 0.1$.
-
-We run each query selection method over 50 different car tracks in the driving simulator domain.
-We measured the percentage of truly risky states, encountered during the first policy roll out, that  are estimated to be safe by the active learning technique.
-The active learning techniques are trained on the initial demonstrations $\mathcal{D}_0$, which is different then the distribution being sampled from, $p(\bx|\theta_0)$, in this experiment.
-
- Fig.
-\ref{fig:active_comp}  plots the performance for each query selection method, averaged over 50 tracks.
-We observe a significant performance improvement with methods based on classification based novelty detection compared to confidence,query by committee and MMD.
-Furthermore, using the combined measure of risk performs better than relying solely on the One Class SVM.
-
-\subsubsection{Sensitivity Analysis to Risk Sensitivity Parameter}
-
- To analyze the sensitivity of our method we varied the risk sensitivity  parameter or $\sigma$ of the decision function $g_{\sigma}$, or Eq.
-$\ref{eq:decision_func}$.
-$\sigma$ is a measure of how much risk we allow, with smaller $\sigma$s leading to more risk-adverse behavior.
-SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks.
-
- For each  $\sigma$, we measure the final cost performance of the policy $\pi_{\theta}$ after 6 iterations and the number of examples SHIV requested from the supervisor.
-
- As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help (many states labeled) and very large sigma, $\sigma = 350$, relates to  less data being used, but worse performance.
-However, $\sigma$ values between $150$ and $250$ all achieve similarly good performance, suggesting that SHIV is robust to the choice of a particular $\sigma$.
-
-\begin{table}[t]
-\centering
-\begin{tabular}{ R{2.5cm}||R{1.65cm}|R{1.65cm} }
- %\hline
- %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
- %\hline 
- \hline
-\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Performance} & \specialcell{\bf States  Labeled} \\
- \hline
- 1 & 5.8 & 4122 \\
- 50 & 5.7&  3864 \\
- 150& 5.9 &  1859 \\
-200 & 6.1 & 1524 \\
-250 & 6.3 & 1536 \\
-350 & 13.2 & 521\\
-
- %\hline
-\end{tabular}
-   \caption { \footnotesize  An analysis of the sensitivity risk sensitivity parameter,$\sigma$, of Eq.
-\ref{eq:decision_func}, or the decision function for risky or safe.
-SHIV was run for 6 iterations and averaged over 40 different randomized polygonal tracks.
-Small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but decreased performance.
+\mlnote{We need to nail down exactly what experiments are important.
+I suggest 1) main one is to show expert time withouth bootstrapping vs.
+with 2) can be different forms of how to handle the dataset aggregation (i.e.
+full retrain or batch update etc.) 3) analysis of the crowd source system and how effective that was (this would be a secondary follow up experiment though, 4) Can be also comparison with a previous way to reduce supervisor burden in high dimensional states (i.e.
+SHIV).
 }
-		\tablabel{opt-p-comparison}
-		\label{tab:sens}
-\vspace*{-10pt}
-\end{table}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=\columnwidth, height=4cm]{figures/risk_bar.eps}
-\caption {  \footnotesize A comparison of different active learning approaches in terms of the percentage of risky states that are estimated to be safe by the active learning technique during the first policy roll out.
-We compare against a confidence estimate of distance to hyperplane,Maximal Mean Discrepancy, query by committee for 3 hypothesis classifiers, the One Class SVM, and our modified One Class SVM, marked as SHIV.
-Results  are averaged over 50 tracks and the policy $\pi_\theta$ is represented as a Linear SVM.
-Error bars measure the standard error on the mean.
-   }
-\vspace*{-20pt}
-\label{fig:active_comp}
-\end{figure}
 
 \section{Discussions and Future Work}
-Online LfD have been successful on array of tasks~\cite{NIPS2014_5421,ross2010reduction}, however can place significant burden on a supervisor.
-Our algorithm, SHIV, implements stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.
-We empirically evaluated our method on three different domains: a driving simulator, grasping in clutter and surgical needle insertion.
-Results suggests up to a $70\%$ reduction in the number of queries to the supervisor.
 
-SHIV has several limitations.
-For instance, the selection of the value of $\sigma$ can affect performance and a poor choice could result in the algorithm becoming offline imitation learning, as shown in Table \ref{tab:sens}.
-Future work will look at better understanding the relationship of $\sigma$ to the function $\pi_{\theta}$ and how to automatically select it.
-
-Furthermore, to update the decision function $g_{\sigma}$ requires solving a quadratic program, which has an upper bound computationally complexity of $O(n^3)$ in the number of data points.
-This can effect the ability of using our modified One Class SVM for larger problems.
-While, Scholk{\"o}pf et al.
-provides an efficient optimization that empirically scale quadratically \cite{scholkopf2001estimating} for very large datasets this can still be burdensome.
-Future work will look at using techniques such as random features or PCA on the kernel Gram matrix to allow for better scaling \cite{scholkopf2002learning}.
+ \section{Acknowledgments} 
+This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative.
+This work is supported in part by the U.S.
+National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, by the Knut and Alice Wallenberg Foundation and the National Defense Science and Engineering Graduate Fellowship Program.
+We thank Pieter Abbeel, Sergey Levine and Sanjay Krishnan for insightful feedback.
 

### 2016-02-22 theory_section.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

%\documentclass[journal,transmag]{IEEEtran}% Comment this line out if you need a4paper

\documentclass[10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{url}

\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}

\def\lc{\left\lfloor}   
\def\rc{\right\rfloor}

\usepackage{amsmath,amssymb}

\usepackage{tabularx}
\usepackage{tikz,hyperref,graphicx,units}
\usepackage{subfigure}
\usepackage{benktools}
\usepackage{bbm}
\renewcommand{\baselinestretch}{.5}

\usepackage{caption}
\usepackage{epstopdf}
\renewcommand{\captionfont}{\footnotesize}
\usepackage{sidecap,wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\abs}[1]{\lvert#1\rvert} 
\newcommand{\norm}[1]{\lVert#1\rVert}
%\newcommand{\suchthat}{\mid}
\newcommand{\suchthat}{\ \big|\ }
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bd}{\mathbf{d}}
\newcommand{\bg}{\mathbf{g}}
\newcommand{\bj}{\mathbf{j}}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bt}{\mathbf{t}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bbf}{\mathbf{f}}
\newcommand{\bzero}{\mathbf{0}}
\newcommand{\bG}{\mathbf{G}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\bW}{\mathbf{W}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mG}{\mathcal{G}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mF}{\mathcal{F}}
\newcommand{\bZ}{\mathbf{Z}}
\newcommand{\mR}{\mathcal{R}}

\newcommand{\bfc}{W}
\newcommand{\Qinf}{Q_{\infty}}
\newcommand{\st}[1]{_\text{#1}}
\newcommand{\rres}{r\st{res}}
\newcommand{\pos}[1]{(#1)^+}
\newcommand{\depth}{\operatorname{depth}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\convhull}{\operatorname{ConvexHull}}
\newcommand{\minksum}{\operatorname{MinkowskiSum}}

\newcommand{\specialcell}[2][c]{ \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
\newcommand{\acro}{SHIV}
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}

\newcolumntype{L}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\RaggedLeft\hspace{0pt}}p{#1}}

\newboolean{include-notes}
\setboolean{include-notes}{false}
\newcommand{\adnote}[1]{\ifthenelse{ \boolean{include-notes}}%
 {\textcolor{blue}{\textbf{AD: #1}}}{}}

 \newcommand{\fpnote}[1]{\ifthenelse{ \boolean{include-notes}}%
 {\textcolor{blue}{\textbf{FP: #1}}}{}}

  \newcommand{\mlnote}[1]{\ifthenelse{ \boolean{include-notes}}%
 {\textcolor{purple}{\textbf{ML: #1}}}{}}

\renewcommand{\baselinestretch}{.99}
\usepackage{times}
\usepackage{microtype}
%\title{Iterative Imitation Learning with Reduced Human Supervision [v11]}
%\title{SHIV:  Reducing Human Supervision for Robot Active Learning [v11]}

\title{Theoretical Analysis of SHIV }

\author{Michael Laskey$^1$, Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Anca D. Dragan$^1$ and Ken Goldberg$^{1,2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu, \small staszass@rose-hulman.edu} }%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:Intro}
In this report, we provide bound on the expected surrogate loss of SHIV similar to one shown earlier for DAgger. It can be shown that DAgger guarantees the expected surrogate loss is bounded linearly in terms of the task horizon $T$ as opposed to the supervisor learning approach, which is quadratic.

DAgger's analysis first introduces a policy that with some probability takes either the supervisor control or the robots, this is known as being a stochastically mixed policy. The stochastically mixed policy is then assumed to be a no regret learner (i.e. in the limit of infinite number of iterations the difference of the average expected surrogate loss compared to the expected surrogate loss of the best policy in hindsight goes to zero). A detailed analysis of when the no-regret assumption is valid can be found in \cite{ross2011stability}.

 In the case of a strongly convex loss function and bounded policy class, it has been shown for no-regret learners that the number of iterations needed for convergence is linear in iterations~\cite{shalev2009mind}. DAgger then shows that in $T$ iterations the robot policies, $\pi_\theta$, approaches that of the no-regret stochastically mixed policy and achieves similar error, which is bounded linearly in $T$~\cite{ross2010reduction}.

We show how the additional hyperparameters of SHIV ($\nu$ and $\sigma$) effect the guarantees of DAgger and that the expected surrogate loss is still linear in the time horizon but now has  an additional term dependent on the hyperparameters. The intuition of the result is that active learning techniques can reduce the amount of data needed to learn, however a relation exists between how "smooth" the supervisor's policy is and how the hyperparameters are chosen. Our results suggest the less smooth a supervisor's policy is the more examples are needed to learn it.

 We maintain the same assumptions as above plus two additional assumptions.  First, we assume that the supervisor policy $\tilde{\pi}$ and the learned policy $\pi_\theta$ is "smooth" in the sense that it is Lipschitz continuous: there exists a constant L bound on the derivative of $\tilde{\pi}$ and a separate bound on the derivative of $\pi_\theta$. Second, that a Radial Basis Function (RBF) kernel is used for the risk decision function $g_{\sigma}(\bx)$.

The smoothness assumption of both the learned and supervisor policy is necessary to bound the worst case surrogate loss of our modified one class SVM query selection method (i.e. the maximum error in regression from the closest example). In many continuous control cases, like tele-operated robotic surgery~\cite{AnnualReport2014} or kinesthetically controlling a robot arm~\cite{akgun2012trajectories}, this is a reasonable assumption. However this would not hold when there is discrete controls such as learning a video game controller~\cite{NIPS2014_5421} or predicting which lane for an autonomous car to drive in~\cite{abbeel2004apprenticeship}, since the control abruptly changes between states.  The assumption can also be violated if the control space is not bounded and the policy applies a control asymptotically.

The assumption of  smooth learned policy is common for any learned function that is differentiable everywhere and has derivative of bounded magnitude, common techniques like linear or kernelized regression are capable of producing such a function~\cite{scholkopf2002learning}. Learning a policy via regression of a piecewise function  could violate this assumption because it is possible to have an unbounded derivative.

The assumption of a known kernel is needed to relate the bandwidth parameter $\sigma$ to the effects it has on DAgger's original upper bound on the expected surrogate loss. We chose to study the RBF kernel's hyperparameter because it is widely used in practice and was shown to work well in our experiments. An RBF kernel can be a poor choice in situations where the underlying function is linear or polynomial, for which there exists more data efficient kernels~\cite{scholkopf2002learning}.

\section{Problem Statement}
The goal is to learn a policy that matches that of the supervisor's while asking the supervisor for as few examples as possible.

\noindent\textbf{Policies and State Densities.}
Following conventions from control theory, we denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of 
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We furthermore consider a set $\mathcal{U}$ of allowable control inputs for the robot, which can be discrete or
continuous. We model dynamics as Markovian, such that the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
\mathcal{U}$: 
$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
We assume a probability density over initial states $p(\bx_0)$.
%We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.

A trajectory $\hat{\tau}$ is a finite series of $T+1$ pairs of states visited and corresponding
control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
and $\bu_t\in \mathcal{U}$ for $t\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
For a given trajectory $\hat{\tau}$ as above, we denote by ${\tau}$ the corresponding trajectory in state space,
${\tau} = (\bx_0,....,\bx_T)$.

A policy is a function $\pi: \mathcal{X} \to \mathcal{U}$ from states to control inputs. 
We consider a space of policies $\pi_{\theta}:\mathcal{X}\to \mathcal{U}$ parameterized by some $\theta\in \mathbb{R}^d$. Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
induces a density on trajectories. Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
$\pi_{\theta}$ from time $0$ to time $t-1$.  Following~\cite{ross2010reduction}, we can compute
the average density on states for any timepoint by $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.

While we do not assume knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
Therefore, when 'rolling out' trajectories under a policy
$\pi_{\theta}$, we utilize the robot or a simulator to sample the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

\noindent\textbf{Objective.} The objective of  policy learning is to find a policy that minimizes some known cost function $C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of trajectory $\hat{\tau}$. The cost $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, in the task of inserting a peg into a hole, the distance between the peg's current and desired final state is often used~\cite{levine2015end}.

In our problem, we do not have access to the cost function itself. Instead, we only have access to 
a supervisor that can achieve a desired level of performance on the task. The supervisor provides the robot
an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
which are the result of the supervisor applying this policy. This induces a training data set $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.

We define a `surrogate' loss function as in~\cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2_2$,
while in the discrete case $l(\bu_0,\bu_1) = 1$ if $\bu_0 \neq \bu_1$ and $l(\bu_0, \bu_1)=0$ otherwise.

Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how `close' the policy's
returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrogate loss relative to the supervisor's policy.

Following~\cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:

 \vspace{-2ex}
\begin{align}\label{eq:LFD_obj}
\underset{\theta}{\min} \: E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}(\bx))]
\end{align}

 If the robot could learn the policy  perfectly, this state density would match the one encountered in user examples. But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to~\cite{pomerleau1989alvinn}. This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing feedback. The feedback is in the form of control signals on states sampled from the robot's new distribution of states.

\section{Risky and Safe States}

Providing correct control inputs for (or ``labeling'')  all states encountered at each
iteration can impose a large burden on the supervisor.
Instead of asking the supervisor for labels at all visited states, SHIV uses a measure of risk to actively decide whether a label is necessary.

In contrast to the standard measure risk based purely on variance, we define a state as "risky"  if: 1) it lies in an area with a low density of
previously trained states, which can cause the current policy to mis-predict the supervisor and incur high surrogate
loss~\cite{tokdar2010importance}, or 2) the surrogate loss, or training error, of the current policy at the state  is high, so that the policy does not  model the supervisor's control inputs correctly. States that are not classified as "risky" are deemed "safe" .

The amount of data needed to estimate the density, scales exponentially in the dimension of the state space~\cite{liu2007sparse}. 
Thus, to evaluate risk in high-dimensional state spaces we use
a modified version of the technique known as the One Class SVM that estimates a regularized boundary of a user defined quantile on the training data in $\mathcal{X}$~\cite{scholkopf2001estimating}.
%\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}

%\subsection{Estimation of Quantile Level Sets}\label{sec:level}
We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
independent and identically distributed samples $\mathbf{x}_1,...,\mathbf{x}_n\in \mathcal{X}$.
In most general terms, the quantile function for $P$ and subject to a class of measurable subsets $\mathcal{G}$ of $\mathcal{X}$ is
defined by
\vspace{-2ex}
\begin{align}\label{eq:quantile}
U(\gamma) = \mbox{inf} \lbrace \lambda(G):P(G) \geq \gamma, G \in \mathcal{G} \rbrace \: 0<\gamma \leq 1
\end{align} 
$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure.
Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
measure (i.e. volume) for each $\gamma\in [0,1]$ (this set is in general not necessarily unique). 
$G(\gamma)$ denotes a set of minimum measure $G \in \mathcal{G}$ with $P(G(\gamma))\ge \gamma$.

To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al. represents the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space~\cite{scholkopf2001estimating}. 
By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
derives an approximation of the quantile function described in Eq. \ref{eq:quantile}.

Let $\Phi:\mathcal{X}\to \mathcal{F}$ denote the feature map corresponding to our exponential kernel, $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/2\sigma^2}$, mapping the
observation space $\mathcal{X}$ into a Hilbert space $(\mathcal{F}, \langle, \rangle)$ such that $k(\bx, \bx') = \langle
\Phi(\bx), \Phi(\bx')\rangle$.

The One Class SVM proposed by~\cite{scholkopf2001estimating} determines a hyperplane in feature space $\mathcal{F}$
maximally separating the input data from the origin:
\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{minimize}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
\end{align}

Here, the parameter $\nu$ controls the penalty or `slack term' and $1-\nu$ is equivalent to $\gamma$~\cite{vert2006consistency}
in the quantile definition, Eq. \ref{eq:quantile}, as the number of samples increases. The decision
function, determining point membership in the approximate quantile levelset is given by $g(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho)$. Here, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
$g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
if $x$ lies strictly in the quantile sub-levelset.

The dual form of the optimization yields a Quadratic Program 
that has worst case computational complexity of $O(n^3)$. However, Sch{\"o}lkopf et al. developed an improved optimization method that has empirically been shown to scale quadratically~\cite{scholkopf2001estimating},which we use. In the dual, the decision function is given by $g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho)$ where $\alpha_i$ corresponds to the dual variables. 
However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
optimizing Eq. \ref{eq:super_objj} may still incur a large surrogate loss. To account for this, we propose a
modification to the One Class SVM:

\vspace{-2ex}
\begin{align}
y_i = \left\{
     \begin{array}{lr}
         1 & : l(\pi_{\theta}(\bx_i),\bu_i)\le \varepsilon\\
         -1 & : l(\pi_{\theta}(\bx_i),\bu_i)>\varepsilon
     \end{array}
   \right.
\end{align}

Where, in the case when $l$ denotes discrete $0-1$ loss, we set $\varepsilon = 0$, while in the continuous $L_2$ loss
case, $\varepsilon$ is a user defined threshold specifying allowable surrogate loss.
We use $y_i$ to modify the One Class SVM decision function as follows:

We divide up our data in to two sets those correctly classified: $\mathcal{D}_{s}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y_i=1\}$ and those states incorrectly classified: $\mathcal{D}_{r}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y_i=-1\}$
A separate One-Class SVM is then trained on each set of states, ($D_{s}$ and $D_{r}$) and providing measures of the level sets, $g_{s}$ and $g_{r}$. Specified by parameters $(\nu,\sigma)$ and $(\nu_r,\sigma_r)$, respectively.

We then define the overall decision function as:

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g_{\sigma}(\bx) = \left\{
     \begin{array}{ll}
         0 & : g_s(\bx) == 1 \: \mbox{and} \: g_r(\bx) == -1\\
         -1 & : \mbox{otherwise}
     \end{array}
   \right.
\end{align}
points are deemed risky if $g_{\sigma}(\bx) \neq 0$.  Practically, this modification corresponds to
`carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
excluded from the super-levelset.

The decision function parametrization consists of the kernel bandwidth $\sigma$ in $g_s$. We treat $\sigma$ as a "risk sensitivity" parameter (and study its implications in Section \ref{sec:experiments}). For two reasons: 1)The expected number of examples, after a policy roll out, the supervisor can be asked is  $T*\int_\bx \mathbf{1}(g_{\sigma}(\bx) == 0) p(\bx|\theta)d\bx$. Thus, smaller $\sigma$ corresponds to asking for more examples. 2) A relation exists between how smooth the supervisor's policy, $\tilde{\pi}$ and how many examples are needed to learn it. Thus, a large $\sigma$ can be dangerous for policies with sharp variation because it will treat points as safe that are really risky.

\section{SHIV:Svm-based reduction in Human InterVention} \label{sec:SHIV}

Both SHIV and DAgger~\cite{ross2010reduction} solve the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states. However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky enough to warrant a query after the policy roll out.

 \vspace{-2ex}

\subsection{Step 1}
The first step of each iteration $k$  computes $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D}_k=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $\mathcal{D}$ of initial trajectory demonstrations):

 \vspace{-1ex}
\begin{align}\label{eq:super_objj}
\theta_{k} = \underset{\theta}{\argmin} \: \sum_{i=1}^{M} l(\pi_{\theta}(\bx_i),\bu_i).
\end{align}

This sub-problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net. Performance can vary though with the selection of the estimator~\cite{scholkopf2002learning}

 \subsection{Step 2}
The second step SHIV and DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.

What happens next, however, differs between SHIV and DAgger. For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}

SHIV only asks for supervision on states for which are risky, or $g_{\sigma}(\bx) \neq 0$: 
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$
Steps 1 and 2 are repeated for $K$ iterations or until 
the robot has achieved sufficient performance on the task\footnote{In the original DAgger the policy rolled out
was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
or the robots. The use of this stochastically mix policy was for theoretical analysis. In practice, it is recommended
to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.

\section{Theoretical Analysis}\label{sec:theory_sec}
We recap the analysis of DAgger and state the main result and then introduce SHIV's analysis. Note, we denote a change in notation  $l_i(\bx) = l(\pi_{\theta_i}(\bx),\tilde{\pi}(\bx)) $ where $l_i(\bu): \mathcal{U} \rightarrow \mathbb{R}$. The change is for convenience, since the only time $l$ is used in the analysis is with respect to the supervisor.

\noindent \textbf{DAgger Analysis} Analysis of DAgger models the problem as online learning, where an algorithm must provide a policy $\pi_n$ at iteration $n$ which incurs loss $E_{p(\bx|\theta_n)}[l_n(\pi_n)]$. After observing this loss the algorithm can provide a different policy $\pi_{n+1}$ for the next iteration which will incur loss $E_{p(\bx|\theta_{n+1})}[l_{n+1}(\pi_{n+1})]$. The loss functions $E_{p(\bx|\theta_{n+1})}[l_{n+1}(\pi_{n+1})]$ may vary in an unknown fashion over time \cite{ross2010reduction}.

DAgger assumes a no-regret algorithm, i.e. an algorithm that produces a series of policies $\pi_1,\pi_2,...,\pi_N$ such that the average regret with respect to the best policy in hindsight goes to $0$ as $N$ goes to $\infty$.

$$\frac{1}{N}\sum^N_{i=1} E_{p(\bx|\theta_i)} [l_i(\pi_\theta(\bx))] - \underset{\pi \in \Pi}{\mbox{min}} \frac{1}{N} \sum^N_{i=1} E_{p(\bx|\theta_i)} [l(\pi(\bx))] \leq \gamma_N$$

for $\mbox{lim}_{N \rightarrow \infty} \gamma_N = 0$. Many no-regret algorithms guarantee that $\gamma_N$ is $\tilde{O}(\frac{1}{N})$ (e.g. when $l$ is strongly convex).

Assume $l(\bu)$ is strongly convex and bounded over $\Pi$. Let $\epsilon_N = \mbox{min}_{\pi\in \Pi} \frac{1}{N} \sum^N_{i=1} E_{p(\bx|\theta_i)} [l(\pi(\bx))]$ be the true loss of the best policy in hindsight. Then the following holds in the infinite sample case (infinite number of trajectories at each iteration):\\

\begin{theorem}\label{thm:Dagger}
For DAgger if N is $\tilde{O}(T)$ there exists a policy $\hat{\pi} \in \hat{\pi}_{1:N}$ such that $E_{p(\bx|\theta_N)}[l_N(\bx)] \leq \epsilon_N + O(1/T)$\\
\end{theorem}

Note, a bound on the total expected surrogate loss of a policy during roll out  can be computed by multiplying the right hand side by a factor of $T$.

\noindent \textbf{SHIV Analysis} In SHIV, a state is queried or not queried via a decision function $g_{\sigma}$ the boundaries of this decision function is parameterized by $\nu$ and $\sigma$. We are interested in bounding the worst case effect this has on the original DAgger analysis or Theorem \ref{thm:Dagger}.

For SHIV's analysis we make the additional assumptions of an $L_0$-Lipschitz supervisor policy, $\tilde{\pi}$ and a class of $L_1$-Lipschitz learned policy $\pi_\theta$.  We also assume a Radial Basis Function (RBF) kernel, $k(x_0,x_1) = \mbox{exp}(-||x_0-x_1||^2/\sigma^2)$, is used in the decision function $g_\sigma(\bx)$. The intuition behind these assumptions and examples of where they would and wouldn't hold is described in Sec. \ref{sec:Intro}.

We introduce the set of states inside the decision function as $\mathcal{Y} = \lbrace \bx | \bx \in \mathcal{X}, g_\sigma(\bx) = 0 \rbrace$ and the set of states outside as $\mathcal{Z} = \lbrace \bx | \bx \in \mathcal{X}, g_\sigma(\bx) = -1 \rbrace$.

 In order to prove the Theorem \ref{thm:main_thereom}, we need the following lemmas. \\

\begin{lemma} \label{lm:lipschitz}
Given an $L_0$-Lipschitz supervisor policy $\tilde{\pi}$ and $L_1$-Lipschitz learned policy $\pi_\theta$, define $L = \mbox{max}(L_0,L_1)$. With maximum regression error on the dataset $\eta_N$, where $\eta_N = \max_{\bx_i \in \mathcal{D}_N} ||\pi_\theta(\bx_i) - \tilde{\pi}(\bx_i)||^2_2$. Define $L_w: \mathcal{X} \rightarrow [0,\infty)$ as $L_w(\bx) =\mbox{min}_{\bx_i \in \mathcal{D}} ||\bx_i - \bx||_2^2$, which is the shortest Euclidean distance a point is to those in the dataset. The surrogate loss function $l(\pi_\theta(\bx),\tilde{\pi}(\bx)) = ||\pi_\theta(\bx) - \tilde{\pi}(\bx)||^2_2 $ is bounded as follows:

$$l(\pi_\theta(\bx),\tilde{\pi}(\bx)) \leq (2L)L_w(\bx) + \eta_N$$\\
\end{lemma}

\begin{proof}
 Given a point $\bx$, define $\bx_h = \mbox{argmin}_{\bx_i \in\mathcal{D}} \: ||\bx - \bx_i||$ or the point closest to it in the dataset.

 \begin{align*}
&||\pi_\theta(\bx) - \tilde{\pi}(\bx)||^2_2\\ 
& = || \pi_\theta(\bx) + (\tilde{\pi}(\bx_h) - \tilde{\pi}(\bx_h)) + (\pi_\theta(\bx_h) - \pi_\theta(\bx_h)) + \tilde{\pi}(\bx)||_2^2\\
& \leq ||\pi_\theta(\bx) - \pi_\theta(\bx_h)||^2_2 + ||\tilde{\pi}(\bx_h) - \pi_\theta(\bx_h)||^2_2+ ||\tilde{\pi}(\bx) - \tilde{\pi}(\bx_h)||^2_2\\
& \leq ||\pi_\theta(\bx) - \pi_\theta(\bx_h)||^2_2 + \eta_N + ||\tilde{\pi}(\bx) - \tilde{\pi}(\bx_h)||^2_2\\
& \leq (_{•}2L)L_w(\bx) + \eta_N
\end{align*}

Line two come from equality. The intuition behind this is to determine how far your estimate of the supervisor's policy can be when trying to generalize from the training example in the dataset. Line three is a result of the triangle inequality. Line four then applies the definition of $\eta_N$. Line five is applying the definition of Lipschitz continuity and the definition of $L$.

\end{proof}

\begin{lemma}\label{lm:F_bound}
Given a decision function $g_{\sigma}(\bx)$, parameterized by $\nu$ and $\sigma$ and an RBF kernel. Define the constant $F$ as the maximum squared Euclidean  distance of a point inside the decision boundary from the states $g_{\sigma}$ was trained on:

\vspace{-2ex}
\begin{align*}\label{eq:primal_sup}
   F = \underset{\bx \in \mathcal{X}}{\mbox{max}}\underset{\bx_i \in \mathcal{D} }{\mbox{min}}\: ||\bx_i-\bx||^2_2\\
\mbox{s.t.} \: \bx \in \mathcal{Y} \notag.
\end{align*}

We can bound $F$ by the following:

$$F \leq \sigma^2\mbox{log}(\frac{1}{\rho \nu})$$

\end{lemma}

\begin{proof}

We will   prove Lemma \ref{lm:F_bound} by increasing the set size of $g_{\sigma}(\bx)$ by a series of upper bounds and then bounding the increase set in terms of the hyper parameters $\nu$ and $\sigma$. \\

\begin{align}
   F = \underset{\bx \in \mathcal{X}}{\mbox{max}}\underset{\bx_i \in \mathcal{D} }{\mbox{min}}\: ||\bx_i-\bx||^2_2\\
\mbox{s.t.} \: \bx \in \mathcal{Y} \notag.
\end{align}

Define the solution to the problem  as $ \bx^* \in \mathcal{X}$ and $\bx_m \in \mathcal{D}$ (i.e.)

\begin{align}
   \big(\bx^*,\bx_m \big)= \big(\underset{\bx \in \mathcal{X}}{\mbox{argmax}}, \: \underset{\bx_i \in \mathcal{D} }{\mbox{argmin}}\: ||\bx_i-\bx||^2_2\big)\\
\mbox{s.t.} \: \bx \in \mathcal{Y} \notag.
\end{align}

We restate the definition of $g_{\sigma}(\bx) = \mbox{sgn}(\sum_i^n \alpha_i k(\bx,\bx_i) - \rho)$. Note we have removed the additional carving out term, since we are only interested in an upper bound on error induced.  We can increase the size of the set by noting that $0 \leq \alpha_i \leq \frac{1}{\nu n}$, which comes from the KKT conditions of the original optimization \cite{scholkopf2001estimating}.  Thus our increased set's decision boundary becomes $\mbox{sgn}(\frac{1}{\nu n}\sum_i^n  k(\bx,\bx_i) - \rho)$.

\begin{align*}
   F \leq \underset{\bx \in \mathcal{X}}{\mbox{max}}\underset{\bx_i \in \mathcal{D}}{\mbox{min}}\: ||\bx_i-\bx||^2_2\\
\mbox{s.t.} \: \frac{1}{\nu n}\sum_i^n  k(\bx,\bx_i) - \rho \geq 0 \notag.
\end{align*}

To further increase the size of the set around the point $\bx_m$, we change the boundary to  $\mbox{sgn}(\frac{1}{v}  k(\bx,\bx_m) - \rho)$.

\begin{align*}
    F \leq \underset{\bx \in \mathcal{X}}{\mbox{max}}\: ||\bx_m-\bx||^2_2\\
\mbox{s.t.} \: \frac{1}{\nu }  k(\bx,\bx_m) - \rho \geq 0 \notag.
\end{align*}

Now we can determine the distance to the boundary of this larger set by setting 
 \begin{align*}
&\frac{1}{\nu} k(\bx,\bx_m) = \rho\\
&\mbox{exp}(-||\bx-\bx_m||^2/\sigma^2)= \nu\rho\\
&||\bx-\bx_m|| = \sigma^2 \mbox{log}(\frac{1}{\nu\rho})\\
\end{align*}

This equality in the large set can then be used to upperbound the original term $F \leq \sigma^2 \mbox{log}(\frac{1}{\nu\rho})$.

\end{proof}

\begin{theorem}\label{thm:main_thereom}
For SHIV if N is $O(T)$ there exists a policy $\hat{\pi} \in \hat{\pi}_{1:N}$ such that $E_{p(\bx|\theta_N)}[l_N(\pi_\theta(\bx))] \leq \epsilon_N  + \eta_N+ O(1/T)+(2L)\mbox{log}(\frac{1}{\nu\rho})\sigma^2$\\
\end{theorem}

We note again to obtain the surrogate loss over an entire trajectory the right hand side is multiplied by $T$. \\

\begin{proof}
\begin{align*}
&\mbox{min}_{\pi\in \pi_{1:N}} E_{p(\bx|\theta_i)}[l_i(\pi_\theta(\bx))]\\
&\leq \frac{1}{N} \sum^N_{i=1} E_{p(\bx|\theta_i)}(l_i(\bx))\\
&=\frac{1}{N} \sum^N_{i=1} \int_{\mathcal{Y}} l_i(\pi_\theta(\bx)) p(\bx|\theta_i)d\bx+\int_{\mathcal{Z}}l_i(\pi_\theta(\bx)) p(\bx|\theta_i)d\bx\\
&\leq\frac{1}{N} \sum^N_{i=1}[ \int_{\mathcal{Y}}l_i(\pi_\theta(\bx))p(\bx|\theta_i)d\bx+ \int_{\mathcal{X}} l_i(\pi_\theta(\bx))p(\bx|\theta_i)d\bx]\\
&\leq\frac{1}{N} \sum^N_{i=1} \int_{\mathcal{Y}} l_i(\pi_\theta(\bx))p(\bx|\theta_i)d\bx+  \epsilon_N + O(1/T)\\
\end{align*}

Line three in the proof separates the integral over states inside the decision function $g_{\sigma}$ and outside the decision function. Line four  bounds the expectation over the states outside the decision boundary by replacing the integral back to original density for the second term. The intuition for these steps is to separate the problem between what states are predicted to be safe and what ones are deemed risky.

The last line bounds the second term by the original results of DAgger because these are on the distributions of states outside of the decision function $g_{\sigma}$, where SHIV is identical to DAgger. We note the no regret assumption holds for any unknown $p(\bx|\theta)$, even ones chosen adversarially thus the fact $\theta_i$ is updated with states potentially different than DAgger will not change the result, since it is still a Follow The Leader algorithm by maximizing over all states seen~\cite{ross2010reduction}.

Using Lemma \ref{lm:lipschitz}, we can bound the surrogate loss function as follows:

\begin{align*}
&\leq\frac{1}{N} \sum^N_{i=1} \int_{g_{\sigma}(\bx) =0} (2L)L_w(\bx)p(\bx|\theta_i)d_x+ \eta_N  +...
\end{align*}

Next by noting that the states evaluated under the worst case loss are within the decision boundary $g_{\sigma}$, we can apply Lemma \ref{lm:F_bound}.

\begin{align*}
&\leq (2L)F+\eta_N +...\\
&\leq  (2L)\mbox{log}(\frac{1}{\rho\nu})\sigma^2+\eta_N+  \epsilon_N + O(1/T)
\end{align*}
\end{proof}

\section{Discussion of Analysis}
Theorem \ref{thm:main_thereom} shows the bound on the expected surrogate loss is still linear in the time horizon, however an additional term is added dependent on the hyperparameters $\sigma$ and $\nu$. If the supervisor's policy has a high Lipschitz constant, $L$, then the risk sensitive parameter, $\sigma$ needs to be smaller proportionally to achieve less surrogate loss as shown in Theorem \ref{thm:main_thereom}.

We also recall the expected number of queries to a supervisor can be determined  by $T\int_\mathcal{X} \mathbf{1}(g_{\sigma}(\bx) = 0) p(\bx|\theta)d\bx$. Here we see that $\sigma$ directly effects the size of the decision boundary, which in turn controls the expected number of queries. A trade off exists then between supervisor burden and the performance at convergence, but experimentally we show on several different examples one can achieve the same performance as DAgger in significantly less queries (up to $70\%$).

\bibliographystyle{IEEEtranS}
\bibliography{references}

\end{document}

### 2016-02-22 paper.tex
stuff

@@
 However, an expert supervisor might not be needed for a large portion of the state space, which could be handled by less-skilled supervisors.
-We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, which first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy and then only consults an expert for harder to learn states.
+We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, that first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy.
+Then only consults an expert supervisor for harder to learn states.
 We demonstrate this approach in training a visuomotor deep network policy for 2D grasping in clutter on a 4-DOF Zymark Robot.
@@
 \section{Related Work}
-Below we summarize related work in reducing the number of queries to an expert in the Online LfD setting.\mlnote{Still a work in progress}
+Below we summarize related work in reducing the number of queries to an expert in the Online LfD setting.\mlnote{Still adding to this}
 
@@
 
+\mlnote{we can formally prove the following statements or point to the web similar to SHIV... it will be more trivial to write these out though if we have space}
+With respect to the theoretical analysis of DAgger's convergence rate, one can see that in our algorithm you are solving $M$ individual DAgger's ~\cite{ross2010reduction}.
+Thus, in the worst case you will converge to the supervisor at the top of the hierarchy $\tilde{\pi}_M$ in $\tilde{O}(M*T)$ iterations instead of DAgger's original $\tilde{O}(T)$.
+
+It should be noted though that as you iterate through the hierarchy of supervisors, each iteration starts out with an error bounded by $\int_{\mathcal{X}_{m,m+1}} ||\pi_{\theta_{0,m+1}}(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x})||^2_2 p(\mathbf{x}|\theta_{0,m+1}) d\mathbf{x} + \epsilon$.
+Thus, if the supervisors are able to agree on a large part of the state space, there should be less iterations with the expert supervisor than $\tilde{O}(T)$, which we experimentally show in our grasping in clutter task.
+
 \begin{figure*}[t]
@@
 Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave.
-Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm c) is closing the gripper and d) is rotating the turn table}
+Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm c) is closing the gripper and d) is rotating the turn table (WILL UPDATE THIS FIGURE)}
 \vspace*{-20pt}
@@
 \subsection{Task}
-We are interested in training a Zymark \mlnote{need make and model} to perform a grasping in clutter task on image data taken from a Logitech 2000 camera.
+We are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech 2000 camera.
 Examples of images from the camera can be seen in Fig.
@@
 There is $T=100$ time steps in a trajectory.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth, height=4cm]{f_figs/robot.pdf}
-\caption{ \footnotesize Shown above is a Zymark robot.
-The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table.
-The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}
-\vspace*{-10pt}
-\label{fig:robot}
-\end{figure}
 
@@
 
-\noindent \textbf{Expert Supervisor} Finally after training with the Analytical and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource, to provide corrections for a problem that would be non-obvious for someone who doesn't understand the physical limiations of the problem.
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth, height=4cm]{f_figs/robot.pdf}
+\caption{ \footnotesize Shown above is a Zymark robot.
+The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table.
+The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}
+\vspace*{-10pt}
+\label{fig:robot}
+\end{figure}
+
+\noindent \textbf{Expert Supervisor} Finally after training with the Analytical and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource, to provide corrections for states that would be non-obvious for someone who doesn't understand the physical limitations of the task.
 Examples of this could be joint limits of the robot or how some of the objects might respond in more advanced dynamics.
@@
 
-It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSource Supervisor.
+It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSourced Supervisor.
 
@@
 
-\section{Experiments}
+\section{Planned Experiments}
+All these experiments will be in the grasping clutter domain described above.
+This section is divided into experiments on reducing supervisor burden via hierarchical supervisor's and testing components on our large scale learning system.
 
-\mlnote{We need to nail down exactly what experiments are important.
-I suggest 1) main one is to show expert time withouth bootstrapping vs.
-with 2) can be different forms of how to handle the dataset aggregation (i.e.
-full retrain or batch update etc.) 3) analysis of the crowd source system and how effective that was (this would be a secondary follow up experiment though, 4) Can be also comparison with a previous way to reduce supervisor burden in high dimensional states (i.e.
-SHIV).
-}
+\subsection{A Gambler's DAgger}
+
+\noindent \textbf{Reducing Supervisor Burden}
+In this experiment, we will assign some cost to each supervisor Analytical could be 0.5, Crowdsource 2, and Expert 10 for example.
+Then compute how many times the expert had to of been queried by using the bootstraped method.
+We will then do a full DAgger with our experts for comparison to when you don't bootstrap.
+
+\noindent \textbf{When this Won't Work}
+In this experiment, we will look at using two analytical supervisors to try and teach the robot, however they will violate the definition of and not have an overlapping policy (need to think about this a bit).
+We should see that the supervisor deemed higher in the heirachy has to do roughly if not more queries than without bootstrapping.
+
+\subsection{System Experiments}
+
+\noindent \textbf{Finding a Neural Network Architecture for Policy Learning}
+I want to determine if we can use our analtyical method to find the right architecture by iterating through a dataset.
+The hypothesis is that you do not need to do roll-outs if you change architecture slightly for better performance (i.e.
+can I collect a data from rolling out when network and then iterate on that dataset to find the best architecture)
+
+We will see how close a different architectures who received lower training loss on the dataset are to the original trained network in terms of euclidean distance.
+
+\noindent \textbf{Reliability of Crowdsourced Supervisors}
+This experiment is more of a study looking for a few factors, how much data can we get, what is the price point and how lower quality is it to the expert.
+
+Anca and I discussed an experiment to measure performance against expert. We can then just report our observations in terms of data gathered, time it took and price paid.
 

### 2016-03-16 paper.tex
added figures and updated to draft v3

--- 2016-02-22 paper.tex
@@
 
-\title{A Gambler's DAgger: Reducing Supervisor Burden in Online Learning From Demonstration Learning  Through Hierarchical Supervisors}
+\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors for Deep Learning from Demonstrations}
 
-\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$,...,Florian T. Pokorny,\\
+\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$,Wesley Hseih$^1$,Florian T. Pokorny,\\
  Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
@@
 encounters new states while executing its current best policy.
-Traditionally there has only been one supervisor and it is deemed expert.
-However, an expert supervisor might not be needed for a large portion of the state space, which could be handled by less-skilled supervisors.
-We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, which first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy and then only consults an expert for harder to learn states.
-We demonstrate this approach in training a visuomotor deep network policy for 2D grasping in clutter on a 4-DOF Zymark Robot.
+Traditionally there has only been one supervisor and it is an expert.
+However, an expert supervisor is a costly resource that could be impractical for large scale learning tasks.
+However, there an expert supervisor might not be needed for a large portion of the state space , which could be handled by less-skilled supervisors.
+We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, that first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy.
+Then only consults an expert supervisor for harder to learn states.
+We demonstrate this approach in training a visuomotor deep network policy in TensorFlow for grasping in clutter on a 4-DOF Zymark Robot.
 We were able to reduce the number of queries to the final expert supervisor by $X$ and manage to collect $X$K examples by leveraging the hierarchical supervisor model.
@@
 \section{Introduction} 
-In model-free robot Learning from Demonstration (LfD), a robot learns to perform a task, such as driving or grasping an object in a cluttered environment, from examples provided by a  supervisor, usually a human.
-In such problems, the robot does not have access to either the cost function that it should optimize, nor the dynamics model.
-The former  when it is difficult to specify how to trade-off various aspects that matter, like a car trying to drive on the road with other cars~\cite{abbeel2004apprenticeship}.
-The latter occurs when either the system or the interaction with the world is difficult to characterize, like when a robot is trying to grasp an object in clutter and does not have an accurate model of the object dynamics.
+Consider a robot trying to reach an object on a cluttered shelf in a shipping warehouse, as illustrated by the Amazon Picking Challenge at ICRA 2015 \cite{mahler2016dexnet}, this is an important task for being able to efficiently ship and process orders.
+The robot is presented with a visual feed of the environment and must plan a series of motions to push the cluttered obstacles and grasp a goal object.
+A challenge could arise  when the robot encounters an unknown obstacle object that it does not have a known dynamics  for and must manipulate the environment to reach goal.
 
-Rather than explicitly learning the cost function as in Inverse Reinforcement Learning and the dynamics model, and then using optimization to produce a policy for the task, in model-free LfD the robot learns a policy directly from supervisor examples, mapping states to controls~\cite{argall2009survey}.
-Learning from demonstration has been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering~\cite{abbeel2007application}, car parking~\cite{abbeel2008apprenticeship},  and robot surgery~\cite{van2010superhuman}.
+One solution is to learn a manipulation policy across a variety of obstacle objects and try to generalize this approach to unknown obstacle in the environment.
+Reinforcement learning techniques are capable of being applied to this problem, however they could require a large amount of trials on the robot to accomplish the task when the dynamics are unknown and the state space is high dimensional image data~\cite{pinto2015supersizing}.
+
+Rather than using an unsupervised learning approach, we propose guiding the robot how on to interact with the environment via a supervisor, who knows how to accomplish the task~\cite{argall2009survey}.
+Learning from demonstration (LfD) algorithms, which have been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering~\cite{abbeel2007application}, car parking~\cite{abbeel2008apprenticeship},  and robot surgery~\cite{van2010superhuman}, is a form of how to provide this guidance.
 
  \begin{figure}
-\includegraphics[width=0.5\textwidth]{f_figs/teaser.pdf}
+\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
 \caption{Typical Initial States for our grasping in clutter task with a Zymark Robot.
 Red shapes indicate the clutter objects and the yellow circle indicates the goal object.
-The robot learns from raw image date to push the shapes and reach the yellow circle through our algorithm A Gambler's DAgger.
-The inscribed circle in the workspace prevents the robot from learning the trivial solution of simply pushing the red objects off the table.}
+The robot learns from 250x250 RGB image data to push the shapes and reach the yellow circle through our algorithm A Gambler's DAgger.}
 \vspace*{-20pt}
@@
 During execution, a small control error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.
-For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will eventually put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
+For example, a robot  trained on examples driving safely down the center of a lane, but even slight deviations will eventually put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
 Ross and Bagnell showed the number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
@@
 
-One drawback is that DAgger significantly increases the burden on the supervisor, who must label all states that the robot visits during training.
+One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot visits during training.
 Traditionally there has only been one supervisor and it is deemed an expert ~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}.
-However, an expert supervisor might not be needed for a large portion of the state space, which could be handled by less-skilled supervisors.
+However, when learning complicated tasks with high stochasticity in the environment this could require a large amount of the expert's time, which is a costly resource.
 
-Our key insight is that for a large portion of the task the supervisor's time is used teaching the robot something that a less costly supervisor could do.
-For instance in our grasping in clutter example, the robot spends a large portion of the time trying to learn how to go towards the goal object.
+Learning can be bootstrapped with a sequence of increasingly skilled supervisors.
+In our grasping in clutter example, the robot spends a large portion of the time learning how to go towards the goal object.
 Analytical techniques such as forward kinematics, template matching and motion planning are readily available to provide examples in these parts of the state space.
-However, traditional Online Lfd method exploit the expert supervisor for all parts of the state space.
 
-We propose bootstrapping a policy from a hierarchy of supervisors ranked by cost.
-Examples of such a hierarchy are analytical models with a simplified dynamics of the world, crowd-source Amazon Mechanical Turk workers and then finally an expert supervisor.
-We demonstrate this approach in training a deep neural network for the visuo-motor based task of 2D grasping in clutter on a Zymark Robot.
-Our robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the table.
-The objects dataset consists of 20 Medium Density Fiber extruded polygons taken from 2D projections of objects in the Dex-Net \cite{} database.
-Results show that by bootstrapping from less skilled experts, the total amount of burden on the expert supervisor is reduced and the task is successfully learned \mlnote{We need an objective measure of success}.
+We propose bootstrapping a policy from a hierarchy of supervisors ranked by cost: analytical models, crowd-sourced workers and an expert supervisor to learn the robot grasping in clutter task.
+We demonstrate this approach by training a deep neural network for the visuo-motor based task of  grasping in clutter on a Zymark Robot.
+Our robot consists of an 2DOF arm and a gripper that lie in a planar workspace.
+The objects dataset consists of 20  extruded polygons taken from 2D projections of objects in the Dex-Net \cite{mahler2016dexnet} database.
+Results show that by leveraging a hierarchy of less skilled experts, the total amount of cost incurred is reduced by X$\%$ and the task is $61\%$ successful on our test set of 20 object configurations of shapes not trained on \mlnote{need to think of a better teaser statement}
 
 \section{Related Work}
-Below we summarize related work in reducing the number of queries to an expert in the Online LfD setting.\mlnote{Still a work in progress}
+Below we summarize related work in Robotic Grasiping in Clutter,  Online LfD setting and then the field of Curriculum learning, which is similar to the concept of hierarchical supervisors.
+
+\noindent \textbf{Robotic Grasping in Clutter}
+Robotic grasping has been extensively studied over the
+past four decades~\cite{bicchi2000robotic}.
+A significant amount of prior work focuses on planning grasps given a known object.
+However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp ~\cite{katz2008can}.
+Prior work has addressed integrated perception and grasping
+in clutter where the objective is to grasp objects in an
+unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these
+methods do not specifically aim to grasp a single target object
+in clutter. 
+Leeper et al. ~\cite{} use a human operator for assistance to guide the
+robot through clutter with the objective of grasping a target
+object.
+However, the robot required the human to be present at all times and did not attempt to learn to operate autonomously.We are interested in only querying the supervisor for examples until the robot is successful at the task.
+
+Prior work has studied the issue of manipulating objects
+by performing pushing operations~\cite{}. Berenson et
+al. ~\cite{} use a sampling-based planner that considers clearance
+from obstacles in the environment to plan a grasp
+approach trajectory in cluttered environments. Cosgun et al.
+[3] and King et al. \cite{kingnonprehensile} consider the problem of planning
+a series of push operations that would place an object at a
+desired target location.
+Kiteav et al.
+planned a trajectory in a physics simulator using LQG based controllers \cite{kitaevphysics}.
+However, all of these works assume a known model of the world is given to them, we are interested in learning manipulation polices via leveraging an supervisors intuition for the the task.
+\mlnote{We should discuss how to distinguish our work (Properties of our approach are we assume raw image data, real time and unknown dynamics)}.
 
 \noindent \textbf{Online Lfd with an Expert Supervisor}
-Successful robotic examples of Online Learning From Demonstration where an expert have been employed have been in flying a quad-copter through a foster, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.
+Successful robotic examples of Online Learning From Demonstration where an expert has been employed in flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.
 
-However, to date these approaches have all used only an expert supervisor to label all parts of the state space.
-Our contribution consists of the use of a hierarchical structure of non-expert supervisors to reduce queries to the expert at the top of the hierarchy.
+However, to date these approaches have all used only one expert supervisor to provide examples for all parts of the state space.
+Our contribution consists of the use of a hierarchical structure of different skill level supervisors to reduce learning cost.
 
-\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reducing supervisor burden is applying active learning to only ask for queries one the robot is uncertain about the correct control to apply.
+\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reducing queries to the supervisor is applying active learning to only ask for queries one the robot is uncertain about the correct control to apply.
 Traditional active learning techniques like query-by-committee and uncertainty sampling have been applied by \cite{chernova2009interactive,judah2011active,grollman2007dogged}
 
-Kim et al.
-demonstrated that due to the non-stationarity of the problem traditional active learning techniques do not work because the underlying state distribution changes and thus the use of novelty detection is needed to be more conservative in determining uncertainty~\cite{kim2013maximum}.
+However, Kim et al.
+demonstrated that due to the non-stationarity of the problem traditional active learning techniques may not work because the underlying state distribution changes and thus the use of novelty detection is needed to be more conservative in determining uncertainty~\cite{kim2013maximum}.
+Laskey et al.
+introduced SHIV, for using active learning tailored to high dimensional and non-stationarity state distributions and  provided a modified version One Class SVM to reduce the from density estimation, which requires regression, to the simpler regularized binary classification ~\cite{laskey}.
 
-Laskey et al.
-created an approach, known as SHIV, for using active learning tailored to high dimensional and non-stationarity state distributions and  provided a modified version One Class SVM to reduce the problem to regularized binary classification~\cite{laskey}.
-However, the result that novelty detection is needed to reduce supervisor burden via active learning implies that for problems with high stochasticity, such as grasping in clutter with a large number of objects, the expert would be queried a significant number.
-Furthermore, with the advent of deep learning where the feature space changes each iteration, it becomes unclear as to what feature space to provide novelty detection in.
+Novelty detection being needed to reduce supervisor burden via active learning implies that for problems with high stochasticity, such as grasping in clutter, the expert would be queried a significant number.
+Furthermore, we are interested in using deep neural architectures to learn task specific features for the task.
+SHIV applies novelty detection in a known feature space, however the feature space now changes each iteration.
+Thus, it is not straightforward to apply existing techniques.
 
-\noindent\textbf{Training Policies Via Analytical Methods} Instead of relying on a costly human supervisor an alternative approach is to use knowledge of the underlying dynamics and train a policy via a computationally expensive analytical method such as a controller in a physics simulator~\cite{IGOR} or dynamic programming in a Atari video game~\cite{NIPS2014_5421}.
+\noindent\textbf{Curriculum Learning}
+\mlnote{TODO: add more curriculum}
+Our approach is similar to the area known as curriculum learning, where a neural network is trained via first  easier to learn examples and then gradually increasing the difficulty of the examples to learn ~\cite{bengio2009curriculum}.
 
-While this approach can "compile" the computationally expensive option into an quickly computed function, it can be limited when analytical models cannot explicitly model the environment.
-For instance in our grasping in clutter example, the robot has no knowledge of the mass or friction properties of the object, which would make this a challenging problem for such analytical methods.
-We thus propose using analytical methods not as the expert supervisor, but instead part of a hierarchy where they can be used to reduce the burden of the supervisors above them in the hierarchy.
+Sanger et al.
+used curriculum learning in robotics to gradually train a neural network policy to learn the inverse dynamics of a robot manipulator.
+They then varied then data collection scheme such that easily learned trajectories where shown first and then gradually increased the difficulty~\cite{sanger1994neural}.
+
+Our approach is different than curriculum learning in that a supervisor can be provide low quality examples in parts of the state space visited by the robot, which means it isn't neccesarily easier for the robot to learn one supervisor's policy versus another in the hierarchy.
+Combining hierarchical supervisors and curriculum learning could be a promising avenue for future work though.
 
@@
 
-\noindent\textbf{Modeling Choices and Assumptions}  We model the system dynamics as Markovian, stochastic, and stationary.
+\noindent\textbf{Assumptions and Modeling Choices } 
+We assume a known state space and set of controls.
+We also assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label.
+We additionally assume the supervisors can be noisy and imperfect, noting that a lower cost supervisor also has lower quality.
+
+ We model the system dynamics as Markovian, stochastic, and stationary.
 Stationary dynamics occur when, given a state and a control, the probability of the next state does not change over time.
 Note this is different from the non-stationary distribution over the states the robot encounters during learning.
-
 We model the initial state as sampled from a distribution over the state space.
-We assume a known state space and set of controls.
-We also assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.
-Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label.
-We additionally assume the supervisors can be noisy and imperfect, noting that the robot cannot surpass the level of performance of the current supervisor it is training with.
 
@@
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
-We furthermore consider a set $\mathcal{U}$ of allowable control inputs for the robot, which can be discrete or
-continuous. We model dynamics as Markovian, such that the probability of state $\mathbf{x_{t+1}}\in
+We denote by $\mathcal{U}$ a set of allowable control inputs for the robot, which can be discrete or
+continuous. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
 \mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
@@
 $$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
-We assume a probability density over initial states $p(\bx_0)$ that can be sampled from.
+We assume an unknown probability density over initial states $p(\bx_0)$.
 %We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.
 
-A trajectory $\hat{\tau}$ is a finite series of $T+1$ pairs of states visited and corresponding
+A demonstration (or trajectory )$\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
 control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
@@
 
-While a reward function exists for a task like grasping in clutter, such as a positive value for successfully reaching the goal object.
-It is often too delayed to provide useful information for quickly learning \cite{kitaevphysics}.
-We thus assume access to
-a supervisor that can achieve a desired level of performance on the task. The supervisor provides the robot an initial set
- of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
-which are the result of the supervisor applying their policy. This induces a training data set $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.
+The reward function  for a task like grasping in clutter, (i.e.
+successfully grasping the goal object) is delayed \cite{kitaevphysics}.
+The idea behind DAgger and SHIV is to query a supervisor for appropiate actions, to provide the robot a set of N stochastic demonstrations trajectories $\lbrace \hat{\tau}^1,...\hat{\tau}^N \rbrace$.
+This induces a training data set $\mathcal{D}$ of state-control input pairs.
 
@@
 
-Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how `close' the policy's
+Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how `close' the robot's policy's
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
-$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrogate loss relative to the supervisor's policy.
+$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrogate loss.
 
-Following~\cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
+Following~\cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss with respect to the most skilled supervisor, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
 
@@
 But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to~\cite{pomerleau1989alvinn}.
-This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing feedback.
-The feedback is in the form of control signals on states sampled from the robot's new distribution of states.
+This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing examples.
 
- \section{A Gambler's DAgger}
+We  introduce the concept of their being a set of supervisors each with an associated cost and skill level.
+Denote $\tilde{\pi}_M$ the most skilled and costly supervisor in this set.
+This supervisor could for example be a person with a Phd in machine learning and robotics.
+We formally define how each supervisor in the set is related to each other in Sec.
+\ref{sec:hS}.
+Every time a supervisor is queried a cost, $C_m$, is incurred this could be an hourly pay rate or computational time.
+
+While Eq.
+\ref{eq:LFD_obj} is the primary objective of our algorithm a secondary objective is to reduce the cumulative cost associated with training the robot.
+Thus, we are interested in solving the following objective
+
+ \vspace{-2ex}
+\begin{align}\label{eq:bugjet_LFD_obj}
+\underset{\theta,C_{m,j}}{\min} \: & \sum^J_{j=1} C_{m,j}\\
+ \mbox{s.t.} \: &E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}_M(\bx))] \leq \epsilon
+\end{align}
+
+where $J$ is the number of queries need to satisfy the constraint on expected surrogate loss, $C_{m,j}$ denotes the cost incurred by querying the supervisor at that iteration and $\epsilon$ is a user-defined threshold on how close robot policy is to match the highest quality supervisor.
+We present our algorithm, LEATHERMAN, which aims to solve Eq.
+\ref{eq:bugjet_LFD_obj}.
+
+ \section{Algorithm}
  In this section, we first recall the original DAgger algorithm.
@@
 
-\subsection{Hierarchy of Supervisors}
-Instead of one expert supervisor,we propose a hierarchy  of $M$ supervisors where for each supervisor $\tilde{\pi}_m$, there is an associated expected cumulative reward $R_m = \int \sum^T_{t=1} r(\mathbf{x}_t,\mathbf{u}_t) p(\mathbf{x}|\tilde{\pi}_m)d\mathbf{x})$, where $p(\mathbf{x}|\tilde{\pi}_m)$ denotes the average distribution of states the supervisor encounters.
+\subsection{Hierarchy of Supervisors}\label{sec:hS}
+Instead of one  supervisor,we propose a hierarchy  of $M$ supervisors where for each supervisor $\tilde{\pi}_m$, there is an associated expected cumulative reward $R_m = \int \sum^T_{t=1} r(\mathbf{x}_t, \tilde{\pi}_m(x)) p(\tau |\tilde{\pi}_m)d\tau$, where $p(\tau |\tilde{\pi}_m)$ denotes the average distribution of states the supervisor encounters.
 We also denote some measure of cost $C_m$ that is ascribed to the supervisor, such as computational time or monetary expense.
-We assume that the rank of supervisors in terms of cost is equivalent to the rank of supervisor in the terms of expected cumulative reward.
-Thus, the cheapest supervisor also receives the lowest expected cumulative reward.
+Generally the rank of supervisors in terms of cost is equivalent to the rank of supervisor in the terms of expected cumulative reward.
+Thus, the least costly supervisor will receive the lowest expected cumulative reward.
 
 Additionally for two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ to be in the hierarchy, they must only disagree in expectation on a subset of the work space to some precision $\tilde{\epsilon}$.
-Denote the set of states two supervisors disagree as $\mathcal{X}_{m,m+1} = \lbrace \mathbf{x} | ||\tilde{\pi}_m(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x}) ||^2_2 > \tilde{\epsilon} \rbrace$ .We make this condition because if two supervisors never provided the same examples then all states would have to be relabeled by the next supervisor in the hierarchy.
+Denote the set of states two supervisors disagree as $\mathcal{X}_{m,m+1} = \lbrace \mathbf{x} | ||\tilde{\pi}_m(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x}) ||^2_2 > \tilde{\epsilon} \rbrace$ .We enforce the condition $\mathcal{X}_{m,m+1} \subset \mathcal{X}$ because if two supervisors never provided the same examples then all states would have to be relabeled by the next supervisor in the hierarchy.
 
-We formally define two supervisor's in a hierarchy as follows
+We formally define an ordering on supervisors:
 
-\begin{definition} Two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ are in a hierarchy if  $C_m < C_{m+1}$ , $R_m < R_{m+1}$ and  $\mathcal{X}_{m,m+1} \subset \mathcal{X}$
+\begin{definition} Two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ are in a hierarchy if  $C_m < C_{m+1}$  and  $\mathcal{X}_{m,m+1} \subset \mathcal{X}$
 \end{definition}
 
-We note that a two hierarchical supervisors according to this definition also implies that supervisor $\tilde{\pi}_{m+1}$ in the hierarchy is higher than the set of supervisors $\lbrace \tilde{\pi}_i | \forall i \in [0,m] \rbrace$.
+Violation of this definition could result in no additional benefit from the LEATHERMAN algorithm or potentially worst a higher budget incurred than without using a hierarchy of supervisors.
 
-\subsection{A Gambler's DAgger}
+\subsection{DAgger with Supervisor Hierarchy}
+\mlnote{Anca and I wanted to justify the greedy allocation section, which we draw from the contextual arm bandit literature to do so... I can condense this}
+The hierarchical supervisor problem can be framed as a contextual multi-armed bandit, which is like a traditional multi-armed bandit except the sampled reward depends on an additional state term~\cite{li2010contextual}.
+At each iteration a supervisor is selected from $M$ supervisors  and the state is the current policy parameters or $\theta_k$.
+Then a sampled reward is received which is how well the trained policy performed on the sample surrogate loss measured against the $\tilde{\pi}_M$ or the supervisor at the top of the hierarchy.
+Note we only measure against the supervisor at the top of the hierarchy because that is our primary objective (i.e.
+Eq.
+\ref{eq:LFD_obj}).
+
+While a large amount of literature exists to solve contextual multi-armed bandit problems, a common assumption is that the sampled reward can be observed~~\cite{li2010contextual}.
+However, in our situation evaluation of the sampled reward requires querying the costliest supervisor every iteration.
+Thus, defeating the purpose of cost reduction.
+In light of this we propose a greedy allocation strategy where we train a policy with the cheapest supervisor first until convergence and then work up the hierarchy training with each supervisor.
+
 Our algorithm is as follows: first iterate through Step 1 and 2 of DAgger for a given supervisor, however after iteration $K$ or when the current policy, $\pi_{\theta_{m,k}}$ is able to achieve a loss $\epsilon$ on the sampled $J$ states at that current iteration (i.e):
@@
 Then iterate to the next supervisor in the hierarchy or $m = m+1$.
+The hyperparameter $\epsilon$ can be set as a measure of how different the controls applied between the robot's policy and the current supervisors a sequential process can tolerate.
+For example surgical sequential processes could warrant a very low threshold, but less precise sequential processes, like grasping in clutter, can tolerate a higher value.
+
 An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_K$ has examples from a different supervisor that receives a smaller expected cumulative reward.
-This could cause a learning algorithm to try and regress to both labels and diverge from the intended performance \cite{scholkopf2002learning}.
+This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
 
@@
 Thus, we propose only performing DAgger for each individual supervisor in the hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor.
-\mlnote{the last step about the dataset is something I want to empirically validate}
+We found empirically in Sec.
+\ref{sec:Exp} that it also beneficial to add to the new dataset the states and controls applied by the current policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance $\tilde{\epsilon}$.Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
 
-\begin{figure*}[t]
+\mlnote{we can formally prove the following statements or point to the web similar to SHIV... it will be alot easier to write these out though if we have space}
+With respect to the theoretical analysis of DAgger's convergence rate, one can see that in our algorithm you are solving $M$ individual DAgger's ~\cite{ross2010reduction}.
+Thus, in the worst case you will converge to the supervisor at the top of the hierarchy $\tilde{\pi}_M$ in $\tilde{O}(MT)$ iterations instead of DAgger's original $\tilde{O}(T)$.
+
+It should be noted though that as you iterate through the hierarchy of supervisors, each iteration starts out with an error bounded by $\int_{\mathcal{X}_{m,m+1}} ||\pi_{\theta_{0,m+1}}(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x})||^2_2 p(\mathbf{x}|\theta_{0,m+1}) d\mathbf{x} + \epsilon$.
+Thus, if the supervisors are able to agree on a large part of the state space, there should be less iterations with the expert supervisor than $\tilde{O}(T)$, which we experimentally show in our grasping in clutter task.
+
+\begin{figure}[t]
 \centering
 
-\includegraphics[width=\textwidth]{f_figs/Labeling_GUI.pdf}
+\includegraphics[width=\columnwidth, height=4cm]{f_figs/labeling.pdf}
 
@@
 Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave.
-Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm c) is closing the gripper and d) is rotating the turn table}
-\vspace*{-20pt}
+Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm.}
+\vspace*{-10pt}
 \label{fig:overlays}
-\end{figure*}
+\end{figure}
 
-\section{System for Grasping in Clutter Task}
-We now detail or experimental system for testing A Gambler's DAgger.
-First we describe the task itself, then each supervisor in the hierarchy and finally our deep network representation of the policy trained.
+\section{Robot Grasping in Clutter}
+We now describe the grasping in clutter problem, the supervisor hierarchy that we used to solve it and our deep learning policy architecture.
 
-\subsection{Task}
-We are interested in training a Zymark \mlnote{need make and model} to perform a grasping in clutter task on image data taken from a Logitech 2000 camera.
-Examples of images from the camera can be seen in Fig.
-\ref{fig:teaser}.
+\subsection{Grasping in Clutter}\label{sec:task}
+Consider a robot in an Amazon warehouse.
+The robot has an intended goal object for it to grasp on a shelf, however other objects could obstruct the path towards the goal object.
+These obstructions of movable objects prevent leveraging common motion planning techniques, because they do not posses a dynamics model of how the objects behave under different contact forces.
+~\cite{kitaevphysics,kingnonprehensile}.
 
-The objects in clutter are made Medium Density Fiberboard and each one is on average 4" in diameter.
-The objects deemed cluttered are painted Red and the goal object is painted yellow.
-There is an inscribed circle around the work space to keep the robot from pushing the objects outside of the work space.
-The inscribed circle makes the task more challenging because the robot cannot simply "sweep" the cluttered objects off the table.
+Thus, the robot must reason about how its interactions with the environment will affect the intended outcome.
+This can be hard for two reasons 1) it becomes hard to find a low dimensional state representation for the task because the environment dynamics are affected by the global shape of each object 2) the dynamics of the environment  involve modeling how K objects interact with each other under an arbitrary force \cite{kitaevphysics}.
 
-The robot, shown in Fig.
-\ref{fig:robot}, has a 4 dimensional internal state of base rotation, arm extension, gripper and turn table.
-The robot is commanded via state position requests, which are tracked by a tuned PID controller.
-The policy $\pi_\theta$ outputs delta positions that are bounded by $15\deg$ for the gripper and turntable, $1$ cm for the arm extension and $0.5$ cm for the gripper at each time step.
-There is $T=100$ time steps in a trajectory.
+In order to achieve real time grasping in clutter, which is important for a robot in a shipping warehouse, we leverage  visuo-motor deep learning to learn a control policy for the task over a large number of different configurations working with a hierarchy of supervisors.
+Deep learning has the potential to take high dimensional image data of the scene and learn task specific features relevant for grasping in clutter.
+Additionally a trained neural network policy is can be computational inexpensive to evaluate and can result in real time performance \cite{levine2015end}.
+
+\subsection{Supervisor Hierarchy}\label{sec:hier}
+In this section, we list each supervisor in the order they appear in our hierarchy. The first supervisor is deemed the least expensive.
+
+\noindent \textbf{Motion Planning Supervisor} Our first supervisor is a an analytical method that computes the trajectory the robot should move in to reach the goal object, or yellow circle, with a relax dynamic model of the environment.
+Our method employs template matching to identify the goal object in the image and the using the forward dynamics of the robot to computes the relative change in direction the robot should apply as an control.
+The template matching is implemented in OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}.
+
+In this stage, the motion planning supervisors only tries to teach the robot to move towards the goal.
+Note that the motion planning supervisor's advice does not have any knowledge about how the cluttered objects will respond to the forces applied via the robot arm, which results in sub-optimal polices.
+However, our motion planning supervisor is both computationally and monetarily inexpensive to run which allows us to provide a large number of examples.
+
+\noindent \textbf{CrowdSourced Supervisor} Our next level of supervisor relies on a crowd source service, called Amazon Mechanical Turk (AMT).
+Chung et al.
+demonstrated the reliable data learning from demonstration data could be obtained from an AMT platform.
+The AMT platform makes readily available thousands of human workers that can perform remedial task for a price range of \$0.1 per robot trajectory\cite{chung2014accelerating}.
+Thus potentially providing a higher quality supervisor who has an intuition for how the cluttered objects interact with the world, but at a slightly higher cost.
+
+In order to get examples from a CrowdSourced Supervisor, we designed an interface shown in Fig.
+\ref{fig:overlays}.
+The interface draws a transparent overlay that shows how the robot would respond provided the current control this allows for the AMT worker to see some of the effect of their control.
+We rely on their natural intuition for how objects to infer how the change in robot position will change the objects.
+
+We also design a tutorial for the work that first has them perform designated motions on a virtual robot and introduces them to a problem.
+We additionally provide a video of an expert providing corrections on three robot trajectories.
 
@@
 
-\subsection{Supervisor Hierarchy}
-In this section, we list each supervisor in the order they appear in our hierarchy. The first supervisor is deemed the least expensive.
+\noindent \textbf{Expert Supervisor} Finally after training with the Motion Planning and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource.
+An expert supervisor in this case is a Phd student in machine learning and robotics, which can cost on average ten times more than an AMT worker to employ \cite{}.
 
-\noindent \textbf{Analytical Supervisor} Our first supervisor is a an analytical method that computes the trajectory the robot should move in to reach the goal object, or yellow circle.
-Our method employs template matching to identify the goal object in the image and the using the forward dynamics of the robot to computes the relative change in direction the robot should apply as an control.
-The template matching is implemented in OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}.
+An expert supervisor can be used in a variety of scenarios.They first would have a better intuition of the physical limitations of the robot and environment, such as joint limits or how certain objects might behave under force.
+Furthermore, they would also understand how the examples given could lead to better training of the parameterized policy.
+For example, understanding the feature space the policy lies in can lead to the expert not providing contradictory examples.
 
-In this stage, the analytical supervisors only tries to teach the robot to move towards the goal.
-Note that the analytical supervisor's advice contains no information about how the cluttered objects will respond to the dynamics applied, which results in sub-optimal polices.
-However, our analytical supervisor is both computationally and monetarily inexpensive to run which allows us to provide a large number of examples.
+It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSourced Supervisor.
 
-\noindent \textbf{CrowdSourced Supervisor} Our next level of supervisor relies on a crowd source service, called Amazon Mechanical Turk (AMT).
-Chung et al.
-demonstrated the reliable data learning from demonstration data could be obtained from an AMT platform.
-The AMT platform makes readily available thousands of human workers that can perform remedial task for a price range of \$1-0.1\cite{chung2014accelerating}.
-Thus potentially providing a higher quality supervisor who has an intuition for how the cluttered objects interact with the world, but at a higher cost.
-
-In order to get quality example from a CrowdSourced Supervisor, we designed an interface shown in Fig.
-\ref{fig:overlays}.
-The interface draws a transparent overlay that shows how the robot would respond provided the current control this allows for the AMT worker to see some of the effect of their control.
-We rely on their natural intuition for how objects to infer how the change in robot position will change the objects.
-
-We also design a tutorial for the work that first has them perform designated motions on a virtual robot and introduces them to a problem.
-We additionally provide a video of an expert providing corrections on three robot trajectories.
-
-\noindent \textbf{Expert Supervisor} Finally after training with the Analytical and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource, to provide corrections for a problem that would be non-obvious for someone who doesn't understand the physical limiations of the problem.
-Examples of this could be joint limits of the robot or how some of the objects might respond in more advanced dynamics.
-\mlnote{After we run the AMT study it will become apparent where an expert is still needed}
-
-It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSource Supervisor.
-
-\subsection{Deep Neural Network Policy Architecture}
+\subsection{ Neural Network Policy Architecture}
 Our policy is represented as deep neural network, which was trained using TensorFlow~\cite{tensorflow2015-whitepaper}.
-Our network architecture consists of 1 convolutional layer with 5 channels, a fully connected layer with an output of 128 dimensions and a final layer that maps to a four dimensional control signal.
+Our network architecture consists of 1 convolutional layer with 5 channels and filters with size 11x11, a fully connected layer with an output of 128 dimensions and a final layer that maps to a four dimensional control signal.
 We used ReLus to separate the different layers and a final tanh on the output to scale the output between -1 and 1.
 
-To determine our architecture we created a set of 32,400 different architectures and then performed simulated annealing on the loss function trained after 400 iterations with a batch size of 200.
+The control examples was scaled between 1 and -1 for each dimension independently.
+To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise.
+We then validated that all information (i.e.
+location of the gripper, cluttered shapes and goal object) where still visible in the masked image.
+
+To determine our architecture we preformed a grid search ofver different architectures  trained after 400 iterations with a batch size of 200.
 The set of architectures consist of different network architectures as well as different momentum terms, and weight initialization schemes.
-
 We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
 
-\section{Experiments}
+\section{Experiments} \label{sec:Exp}
 
-\mlnote{We need to nail down exactly what experiments are important.
-I suggest 1) main one is to show expert time withouth bootstrapping vs.
-with 2) can be different forms of how to handle the dataset aggregation (i.e.
-full retrain or batch update etc.) 3) analysis of the crowd source system and how effective that was (this would be a secondary follow up experiment though, 4) Can be also comparison with a previous way to reduce supervisor burden in high dimensional states (i.e.
-SHIV).
-}
+\begin{figure*}[t]
+\centering
+
+\includegraphics{f_figs/results.eps}
+
+\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
+a) Represents states that are easy for the supervisor to provide labels for.
+b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
+\vspace*{-20pt}
+\label{fig:perf_results}
+\end{figure*}
+
+For an experiment in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera.
+Examples of images from the camera can be seen in Fig.
+\ref{fig:teaser}.
+
+The objects in clutter are made Medium Density Fiberboard and each one is on average 4" in diameter.
+The objects deemed cluttered are painted Red and the goal object is painted yellow.
+There is an inscribed circle around the work space to keep the robot from pushing the objects outside of the work space.
+The inscribed circle can make the task more challenging because the robot cannot simply "sweep" the cluttered objects off the table.
+
+The robot, shown in Fig.
+\ref{fig:robot}, has a 3 dimensional internal state of base rotation, arm extension and gripper.
+The robot is commanded via state position requests, which are tracked by a tuned PID controller.
+The policy $\pi_\theta$ outputs delta positions that are bounded by $15\deg$ for the gripper and turntable, $1$ cm for the arm extension and $0.5$ cm for the gripper at each time step.
+There is $T=100$ time steps in a trajectory.
+
+To test the performance of a policy, we created a test set composed of 20 different configurations each containing objects that were not trained on.
+The test set configurations varied in number of objects on the table, size of objects and relative pose of each object.
+We measure success as defined by three situations not successful, near successful, successful.
+We report total success as a score out of 2: 0 for not successful, 1 for near successful, 2 for successful.
+
+The not successful situation corresponds to the case when the robot's gripper is not touching the goal object at the end of a rollout.
+Examples of when this happens is when the robot fails to push the objects away or does not head in the direction of the yellow circle.
+The near successful situation is defined as the robot touches the goal object with its gripper, but it is not enclosed in the gripper.
+Examples of when this happens is when the robot gets a small obstacle object trapped in the gripper first, or when the root slightly misses the yellow circle on its approach.
+Successful is defined as getting the goal object inside the gripper at the end of a trajectory.
+
+\subsection{Hierarchical Supervisors}
+We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .
+We compare having an analytical only supervisor for a fixed amount of data of 160 demonstrations.
+The non-hierarchical policies trained with the expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.
+The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.
+
+Our results, shown in Fig.
+\ref{fig:perf_results}, are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
+Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance.
+However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.
+
+Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the
+
+\subsection{Quality Crowdsourced Supervisor}
+We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy.
+Thus, we perform an experiment using the AMT platform described in Sec.
+\ref{sec:hier}.
+We  test how well a crowdosurce supervisors performs as part of a hierarchy of supervisors, we had a policy train with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers.
+We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.
+
+Our results, shown in Fig.
+\ref{fig:perf_results}, are the policy trained with just the crowdsourced supervisor achieves a score of $?\%$.
+The policy trained with the hierarchical crowdsourced and MPIO supervisor receives $0.43\%$ on our test set compared to $0.55\%$ with the motion planning and expert supervisors hierarchy.
+The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
+
+\mlnote{talk about crowdosuce statistics}
+
+\subsection{Advancing in the Hierarchy}
+We further test how to advance between supervisors in the hierarchy.We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$ \mlnote{need to get this number off the local code, will update tomorrow}.
+Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
+
+We compare each strategy on a hierarchy of a MPIO supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.
+Our results reported in Fig.\ref{fig:cost_result} , show that aggregation strategy achieves $0.18\%$, the weight transfer strategy achieves $0.55\%$ and the regularized stochastic gradient update strategy achieves $0.63\%$.
+Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.
+
+\begin{figure}[t]
+
+\includegraphics{f_figs/cost_result.eps}
+
+\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
+a) Represents states that are easy for the supervisor to provide labels for.
+b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
+\vspace*{-20pt}
+\label{fig:cost_result}
+\end{figure}
+
+\subsection{Scaling the Hierarchy}
+The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: MPIO, crowdsourced and human expert.
+We ran each policy until we observed the pay out in terms of reward achieved was not increasing.
+This results in MPIO for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations.
+Thus resulting in 320 trials on the robot and 320,000 annotated images of what control the robot should apply.
+
+The results of our trained policy, as shown in Fig.
+\ref{fig:perf_results}, demonstrate that by leveraging a hierarchy we are able to achieve a score of $80\%$ with a cost of only 113.
+We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $0.66\%$.
+
+While our policy was able to do substantially better, to near successful mode a reasonable portion of the time.
+These failure modes where do to the robot not being able to accurately manipulate smaller objects, where slight perturbations could result them being pushed into the gripper, and accurately controlling the goal object to land in the circle (i.e.
+sometimes pushing against the side of the circle instead).
+We attribute this problem to a limit in the detail of precision our supervisors can currently give, future work will look at more precise analytical methods and fine tuning the policies via self-learning.
 

### 2016-03-16 paper.tex
.
Edit pass.

@@
 
-\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors for Deep Learning from Demonstrations}
+\title{Robotic Grasping in Clutter Using a Hierarchy of Supervisors for Deep Learning from Demonstrations}
 
-\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$,Wesley Hseih$^1$,Florian T. Pokorny,\\
+\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hseih$^1$, Florian T. Pokorny,\\
  Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
@@
 \begin{abstract}
-Online learning from demonstration algorithms such as
-DAgger can learn policies for problems where the system dynamics and
-the cost function are unknown. However they impose a
-burden on supervisors to respond to queries each time the robot
-encounters new states while executing its current best policy.
-Traditionally there has only been one supervisor and it is an expert.
-However, an expert supervisor is a costly resource that could be impractical for large scale learning tasks.
-However, there an expert supervisor might not be needed for a large portion of the state space , which could be handled by less-skilled supervisors.
-We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, that first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy.
-Then only consults an expert supervisor for harder to learn states.
-We demonstrate this approach in training a visuomotor deep network policy in TensorFlow for grasping in clutter on a 4-DOF Zymark Robot.
-We were able to reduce the number of queries to the final expert supervisor by $X$ and manage to collect $X$K examples by leveraging the hierarchical supervisor model.
+Recent progress in learning from demonstrations increasingly indicates that robots can acquire manipulation skills from
+large collections of training data. Online learning from demonstration algorithms such as DAgger can in particular learn
+policies for problems where the system dynamics and the cost function are unknown. Traditionally, these systems have
+been trained by skilled human supervisors providing feedback on the current learned policy. As the number of
+demonstrations increases, this approach can however incur a substantial time and labor cost. We study the grasping in
+clutter problem and propose a hierarchical approach to learning from demonstrations based on DAgger which also
+incorporates a deep learning architecture to learn policies directly from video sequences. In experiments with a 4-DOF
+Zymark Robot, we consider a hierarchy of three increasingly competent and costly supervisor types: an analytical grasp
+planner, a crowd-sourced human workers and a human expert supervisor. Our results indicate that training a policy
+hierarchically by bootstrapping with the analytical method, followed by crowd sourced and expert supervision improves
+test-time performance compared to training only with an expert supervisor by XX while reducing training cost by XX. We
+furthermore find that the addition of crowd-sourced supervisors compared to analytic pre-training followed by
+supervision by an expert improves performance significantly. [FP: Fine tune how we report main results here]
  \end{abstract}
@@
 \section{Introduction} 
-Consider a robot trying to reach an object on a cluttered shelf in a shipping warehouse, as illustrated by the Amazon Picking Challenge at ICRA 2015 \cite{mahler2016dexnet}, this is an important task for being able to efficiently ship and process orders.
-The robot is presented with a visual feed of the environment and must plan a series of motions to push the cluttered obstacles and grasp a goal object.
-A challenge could arise  when the robot encounters an unknown obstacle object that it does not have a known dynamics  for and must manipulate the environment to reach goal.
+As illustrated by the recent Amazon Picking Challenge at ICRA 2015, the grasping in clutter problem, where a robot needs
+to grasp an object that might be occluded by other objects in the environment poses an interesting challenge to robotic
+systems. Two fundamental approaches to grasping in clutter include the analytic model driven approach \cite{1,2,3},
+where the interaction dynamics between the robot and obstacles are formulated analytically. However, modeling all the 
+physical properties of interaction poses a highly challenging problem due to uncertainty in modeling parameters such as
+inertial properties and friction.
 
-One solution is to learn a manipulation policy across a variety of obstacle objects and try to generalize this approach to unknown obstacle in the environment.
-Reinforcement learning techniques are capable of being applied to this problem, however they could require a large amount of trials on the robot to accomplish the task when the dynamics are unknown and the state space is high dimensional image data~\cite{pinto2015supersizing}.
-
-Rather than using an unsupervised learning approach, we propose guiding the robot how on to interact with the environment via a supervisor, who knows how to accomplish the task~\cite{argall2009survey}.
-Learning from demonstration (LfD) algorithms, which have been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering~\cite{abbeel2007application}, car parking~\cite{abbeel2008apprenticeship},  and robot surgery~\cite{van2010superhuman}, is a form of how to provide this guidance.
+An alternative approach, which we propose here, is to approach the grasping in
+clutter problem in a model-free manner, where the interaction behavior is learned directly from data within the learning
+from demonstrations framework \cite{argall2009survey}. Learning from demonstration (LfD) algorithms have been used
+successfully in recent years for a large number of robotic tasks, including helicopter
+maneuvering~\cite{abbeel2007application}, car parking~\cite{abbeel2008apprenticeship},  and robot
+surgery~\cite{van2010superhuman}. Furthermore, deep learning, which we use to learn policies directly from raw video
+data, has emerged as a highly versatile technique used for this purpose ~\cite{pinto2015supersizing}.
 
@@
 \includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
-\caption{Typical Initial States for our grasping in clutter task with a Zymark Robot.
-Red shapes indicate the clutter objects and the yellow circle indicates the goal object.
-The robot learns from 250x250 RGB image data to push the shapes and reach the yellow circle through our algorithm A Gambler's DAgger.}
+\caption{
+Three roll-outs of a fully trained grasping in clutter policy (one per column, bottom to top) which was trained using a
+hierarchy of three supervisors consisting of analytical motion planning, crowd-sourcing and human expert. 
+Red shapes indicate clutter objects and the robot is trained to reach the yellow circle. {\color{blue}FP: how about we
+display the policy after each of the three training steps? One per column}}
 \vspace*{-20pt}
@@
 
-LfD algorithms can be categorized as offline, where the robot only observes demonstrations, or online, where the robot interacts with the world and receives feedback from the supervisor.
-In offline LfD, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.
-During execution, a small control error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.
-For example, a robot  trained on examples driving safely down the center of a lane, but even slight deviations will eventually put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}.
-Ross and Bagnell showed the number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.
+%LfD algorithms can be categorized as either \emph{offline}, where the robot only observes a set of finalized
+%demonstrations, or \emph{online}, where the robot rolls out a current policy and then receives feedback from the supervisor.
+%In offline LfD, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.  During execution, 
+%control error can accumulate, leading the robot away from the region of the state space where it was provided with
+%training data, leading to unpredictable behavior. For example, an autonomous car trained on examples of a cars driving
+%near the center of a lane might, due to deviations encounter new states far away from previously trained examples that
+%can result in failures~\cite{pomerleau1989alvinn}. For a class of supervised learning methods, Ross and Bagnell showed
+%that the number of errors made by the robot, can scale quadratically with the time horizon of the task, in particular~\cite{ross2010efficient}.
 
-Online LfD addresses this issue by iteratively requesting more examples from the supervisor in states the robot encounters~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}.
-One such algorithm, DAgger, learns a series of policies.
-At each iteration, the robot computes a policy based on the existing examples, then rolls out (executes) that policy, and the supervisor provides demonstrations for all states the robot visits.
-The new state/control examples are aggregated with the prior examples for the next iteration.
+Our approach is based on online Learning from Demonstrations (LfD) where a robot iteratively learns a policy and is
+provided by feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
+We build on, DAgger, an online LfD algorithm which at each iteration, computes a policy based on prior demonstrations,
+and then rolls out that policy. A supervisor then provides control signals as feedback on the current policy
+and new state/control examples are aggregated with the prior examples for the next iteration.
 DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
-In DAgger, under certain conditions, the number of errors scales only linearly with the time horizon of the task~\cite{ross2010reduction}.
+Ross et al. showed that DAgger, under a no-regret assumption, can be guaranteed to deviate from the supervisor's policy with an error
+at most linear in the time horizon for the task~\cite{ross2010reduction}.
 
-One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot visits during training.
-Traditionally there has only been one supervisor and it is deemed an expert ~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}.
-However, when learning complicated tasks with high stochasticity in the environment this could require a large amount of the expert's time, which is a costly resource.
+One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot
+visits during training.  Traditionally there has only been one supervisor and it is deemed an expert
+~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}. In this work, we propose to instead
+utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
+bootstrap the learning process. At the lowest level of the hierarchy, we in particular consider an analytic motion
+planner which acts as an affordable supervisor.
 
-Learning can be bootstrapped with a sequence of increasingly skilled supervisors.
+%Learning can be bootstrapped with a sequence of increasingly skilled supervisors.
 In our grasping in clutter example, the robot spends a large portion of the time learning how to go towards the goal object.
@@
 
-We propose bootstrapping a policy from a hierarchy of supervisors ranked by cost: analytical models, crowd-sourced workers and an expert supervisor to learn the robot grasping in clutter task.
+%We propose bootstrapping a policy from a hierarchy of supervisors ranked by cost: analytical models, crowd-sourced workers and an expert supervisor to learn the robot grasping in clutter task.
 We demonstrate this approach by training a deep neural network for the visuo-motor based task of  grasping in clutter on a Zymark Robot.
@@
 \section{Related Work}
-Below we summarize related work in Robotic Grasiping in Clutter,  Online LfD setting and then the field of Curriculum learning, which is similar to the concept of hierarchical supervisors.
+Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and then the field of
+Curriculum learning, which is related to the concept of hierarchical supervisors.
 
 \noindent \textbf{Robotic Grasping in Clutter}
-Robotic grasping has been extensively studied over the
-past four decades~\cite{bicchi2000robotic}.
-A significant amount of prior work focuses on planning grasps given a known object.
-However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp ~\cite{katz2008can}.
-Prior work has addressed integrated perception and grasping
-in clutter where the objective is to grasp objects in an
-unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these
-methods do not specifically aim to grasp a single target object
-in clutter. 
-Leeper et al. ~\cite{} use a human operator for assistance to guide the
-robot through clutter with the objective of grasping a target
-object.
-However, the robot required the human to be present at all times and did not attempt to learn to operate autonomously.We are interested in only querying the supervisor for examples until the robot is successful at the task.
+Robotic grasping is a well-established research topic in robotics that has been studied for several
+decades~\cite{bicchi2000robotic}. A significant amount of prior work focuses on planning grasps given a known object.
+However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp
+~\cite{katz2008can}. Prior work has addressed integrated perception and grasping in clutter where the objective is to
+grasp objects in an unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
+specifically aim to grasp a single target object in clutter. Leeper et al. ~\cite{} use a human operator for assistance
+to guide the robot through clutter with the objective of grasping a target object. However, the robot required the human
+to be present at all times and did not attempt to learn to operate autonomously. We are interested in a data-driven
+approach that only queries a supervisor at training time and which can operate autonomously thereafter.
 
-Prior work has studied the issue of manipulating objects
+Prior work has studied the problem of manipulating objects
 by performing pushing operations~\cite{}. Berenson et
-al. ~\cite{} use a sampling-based planner that considers clearance
+al. ~\cite{} in particular use a sampling-based planner that considers clearance
 from obstacles in the environment to plan a grasp
@@
 [3] and King et al. \cite{kingnonprehensile} consider the problem of planning
-a series of push operations that would place an object at a
-desired target location.
-Kiteav et al.
-planned a trajectory in a physics simulator using LQG based controllers \cite{kitaevphysics}.
-However, all of these works assume a known model of the world is given to them, we are interested in learning manipulation polices via leveraging an supervisors intuition for the the task.
+a series of push operations that move an object to a
+desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
+\cite{kitaevphysics}. However, all of these works assume a known model of of the object behavior is provided. We are
+interested in learning manipulation polices in a data-driven manner instead, leveraging a hierarchy of supervisors for
+training.  
 \mlnote{We should discuss how to distinguish our work (Properties of our approach are we assume raw image data, real time and unknown dynamics)}.
@@
 \noindent \textbf{Online Lfd with an Expert Supervisor}
-Successful robotic examples of Online Learning From Demonstration where an expert has been employed in flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.
+Successful robotic examples of Online Learning From Demonstration with an expert supervisor include applications to flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.
 
-However, to date these approaches have all used only one expert supervisor to provide examples for all parts of the state space.
-Our contribution consists of the use of a hierarchical structure of different skill level supervisors to reduce learning cost.
+However, to date, these approaches have used only one expert supervisor to provide training data for all parts of the
+state space. We propose to instead utilize hierarchy of supervisor of different skill level and cost to reduce the
+overall learning cost.
 
-\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reducing queries to the supervisor is applying active learning to only ask for queries one the robot is uncertain about the correct control to apply.
-Traditional active learning techniques like query-by-committee and uncertainty sampling have been applied by \cite{chernova2009interactive,judah2011active,grollman2007dogged}
+\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reduce the number of
+supervisor supervision is to apply active learning to only ask for supervision when the robot is uncertain about the
+correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
+in particular be utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}
 
-However, Kim et al.
-demonstrated that due to the non-stationarity of the problem traditional active learning techniques may not work because the underlying state distribution changes and thus the use of novelty detection is needed to be more conservative in determining uncertainty~\cite{kim2013maximum}.
-Laskey et al.
-introduced SHIV, for using active learning tailored to high dimensional and non-stationarity state distributions and  provided a modified version One Class SVM to reduce the from density estimation, which requires regression, to the simpler regularized binary classification ~\cite{laskey}.
-
-Novelty detection being needed to reduce supervisor burden via active learning implies that for problems with high stochasticity, such as grasping in clutter, the expert would be queried a significant number.
-Furthermore, we are interested in using deep neural architectures to learn task specific features for the task.
-SHIV applies novelty detection in a known feature space, however the feature space now changes each iteration.
-Thus, it is not straightforward to apply existing techniques.
+However, Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
+learning, the traditional active learning techniques may be suitable since the underlying state distribution changes.
+Thus the use of novelty detection was proposed~\cite{kim2013maximum}. Laskey et al. introduced SHIV, using an active
+learning approach tailored to high dimensional and non-stationarity state distributions and a modified version of the
+One Class SVM classifier. This enabled the authors to reduce the density estimation problem to a 
+simpler regularized binary classification~\cite{laskey}. However the grasping in clutter problem exhibits a high amount
+of stochasticity requiring a large training data set which poses a significant computational challenge to these methods.
+In the present paper, we hence consider using Deep Learning, as an underlying scalable learning algorithm in combination
+with DAgger.
 
 \noindent\textbf{Curriculum Learning}
-\mlnote{TODO: add more curriculum}
-Our approach is similar to the area known as curriculum learning, where a neural network is trained via first  easier to learn examples and then gradually increasing the difficulty of the examples to learn ~\cite{bengio2009curriculum}.
+Our approach is closely related to ideas from \emph{curriculum learning}, where a neural network is trained via 
+incrementally, first on easier examples and then gradually on data of increasing difficulty~\cite{bengio2009curriculum}.
 
-Sanger et al.
-used curriculum learning in robotics to gradually train a neural network policy to learn the inverse dynamics of a robot manipulator.
-They then varied then data collection scheme such that easily learned trajectories where shown first and then gradually increased the difficulty~\cite{sanger1994neural}.
+Sanger et al. used curriculum learning in robotics to gradually train a neural network policy to learn the inverse
+dynamics of a robot manipulator. They then considered a collection scheme where easily learned trajectories where shown
+to the robot first and then gradually increased the difficulty~\cite{sanger1994neural}.
 
-Our approach is different than curriculum learning in that a supervisor can be provide low quality examples in parts of the state space visited by the robot, which means it isn't neccesarily easier for the robot to learn one supervisor's policy versus another in the hierarchy.
-Combining hierarchical supervisors and curriculum learning could be a promising avenue for future work though.
+Our approach is different from curriculum learning in that a supervisor may occasionally provide low quality examples in
+parts of the state space visited by the robot, which implies that it is now necessarily easier for the robot to learn
+one supervisor's policy versus another in the hierarchy. In future work, we intend to study potential combinations of
+hierarchical supervisors and curriculum learning which we believe could provide a promising avenue for research.
 
 \section{Problem Statement}
-The goal of this work is to learn a policy that matches that of an expert supervisor's while asking expert supervisor with fewer queries than DAgger.
+Given a collection of increasingly able and costly supervisors $S_1, \ldots, S_M$, the goal of this work is to learn a
+policy that closely matches that of the most able supervisor $S_M$ while minimizing the overall cost of training a
+policy. We formalize this approach as follows.
 
@@
 \noindent\textbf{Policies and State Densities.}
-Following conventions from control theory, we denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of 
+Following conventions from control theory, we denote by $\mathcal{X}$ the set of observable states for a robot task, consisting, for example, of 
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
-We denote by $\mathcal{U}$ a set of allowable control inputs for the robot, which can be discrete or
-continuous. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
-\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
+We denote by $\mathcal{U}$ the set of allowable control inputs for the robot. $\mathcal{U}$ may be discrete or
+continuous in nature. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
+\mathcal{X}$ depends only oni the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
 \mathcal{U}$: 
@@
 We assume an unknown probability density over initial states $p(\bx_0)$.
-%We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.
 
-A demonstration (or trajectory )$\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
+A demonstration (or trajectory) $\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
 control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
@@
 Any such policy $\pi_{\theta}$ in an environment with probabilistic initial state density and Markovian dynamics
-induces a density on trajectories. Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
-$\pi_{\theta}$ from time $0$ to time $t-1$.  Following~\cite{ross2010reduction}, we can compute
+induces a density on trajectories.
+Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy $\pi_{\theta}$ from time $0$ to time $t-1$.
+Following~\cite{ross2010reduction}, we can compute
 the average density on states for any timepoint by $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
@@
 While we do not assume knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
-\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
+\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic robot or a simulator such that for any state
 $\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
-Therefore, when 'rolling out' trajectories under a policy
-$\pi_{\theta}$, we utilize the robot or a simulator to sample the resulting stochastic trajectories rather than
+Therefore, 'rolling out' trajectories under a policy
+$\pi_{\theta}$ in our experiments, we utilize the robot to sample the resulting stochastic trajectories rather than
 estimating $p(\bx|\theta)$ itself.
 
-\noindent\textbf{Objective.} The objective of  policy learning is to find a policy that maximizes some known cumulative reward function $\sum^T_{t=1} r(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$.
-The reward $r:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific.
-For example, in the task of inserting a peg into a hole, a function on distance between the peg's current and desired final state is used~\cite{levine2015end}.
+{\color{blue} FP: might make this and the above specific to grasping in clutter?}
+\noindent\textbf{Objective.} The objective of policy learning is to find a policy that maximizes some known cumulative
+reward function $\sum^T_{t=1} r(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The reward $r:\mathcal{X}\times
+\mathcal{U}\to \mathbb{R}$ is typically user defined and task specific \cite{1,2,3}. 
+For example, in the task of inserting a peg into a hole, a function quantifying a notion of distance between the peg's
+current and desired final state can be used~\cite{levine2015end}.
 
-The reward function  for a task like grasping in clutter, (i.e.
-successfully grasping the goal object) is delayed \cite{kitaevphysics}.
-The idea behind DAgger and SHIV is to query a supervisor for appropiate actions, to provide the robot a set of N stochastic demonstrations trajectories $\lbrace \hat{\tau}^1,...\hat{\tau}^N \rbrace$.
+Since grasp success is typically considered as a binary reward which is observed only at a delayed final state \cite{kitaevphysics}, 
+grasping in clutter poses a challenging problem for traditional reinforcement learning methods. We hence instead build
+upon DAgger which queries a supervisor for appropiate actions, to provide the robot a set of N stochastic demonstrations trajectories $\lbrace \hat{\tau}^1,...\hat{\tau}^N \rbrace$.
 This induces a training data set $\mathcal{D}$ of state-control input pairs.
+We define a `surrogate' loss function as in~\cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
+measure between any pair of control values. We consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2_2$.
 
-We define a `surrogate' loss function as in~\cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
-measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2_2$,
-while in the discrete case $l(\bu_0,\bu_1) = 1$ if $\bu_0 \neq \bu_1$ and $l(\bu_0, \bu_1)=0$ otherwise.
-
-Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how `close' the robot's policy's
+Given a candidate policy $\pi_{\theta}$, we DAgger uses the surrogate loss function to approximately measure how `close' the robot's policy's
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
-$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrogate loss.
-
-Following~\cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss with respect to the most skilled supervisor, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:
+$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is of DAgger is to produce a policy that minimizes the expected surrogate loss:
 
@@
 
- If the robot could learn the policy  perfectly, this state density would match the one encountered in user examples.
-But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to~\cite{pomerleau1989alvinn}.
-This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing examples.
+Instead of a single supervisor $S$, which classically is considered to be a skilled human teacher, we instead consider a
+hierarchy $S_1, \ldots, S_M$ of supervisors which we may be algorithms or humans and which follow policies $\pi_1, \ldots, \pi_M$ with
+associated expected cumulative rewards $R_i$ satisfying $R_1\le R_2 \le \ldots \le
+R_M$. Furthermore, we assume that the cost associated to providing a state
+label for supervisor $S_i$ is $C_i$ with $C_1\le C_2 \le \ldots C_M$, so that the ordering of supervisors is consistent
+with respect to both cost and skill level. We consider the problem of minimizing the expected surrogate loss of a
+trained policy with respect to the most skilled supervisor $S_M$ in the hierarchy while minimizing the overall training
+cost. In particular, this paper provides an empirical study of greedy combinations of three types of supervisors $S_1,
+S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
+Here, $S_1$ is an analytical motion planning algorithm with a cost $C_1=XX$, $S_2$ a supervisor
+consisting a crowd-sourced Amazon Mechanical Turk laborers with $C_2=YY$, and $S_3$ a skilled human supervisor with
+$C_3=ZZ$.
 
-We  introduce the concept of their being a set of supervisors each with an associated cost and skill level.
-Denote $\tilde{\pi}_M$ the most skilled and costly supervisor in this set.
-This supervisor could for example be a person with a Phd in machine learning and robotics.
-We formally define how each supervisor in the set is related to each other in Sec.
-\ref{sec:hS}.
-Every time a supervisor is queried a cost, $C_m$, is incurred this could be an hourly pay rate or computational time.
-
-While Eq.
-\ref{eq:LFD_obj} is the primary objective of our algorithm a secondary objective is to reduce the cumulative cost associated with training the robot.
-Thus, we are interested in solving the following objective
-
- \vspace{-2ex}
-\begin{align}\label{eq:bugjet_LFD_obj}
-\underset{\theta,C_{m,j}}{\min} \: & \sum^J_{j=1} C_{m,j}\\
- \mbox{s.t.} \: &E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}_M(\bx))] \leq \epsilon
-\end{align}
-
-where $J$ is the number of queries need to satisfy the constraint on expected surrogate loss, $C_{m,j}$ denotes the cost incurred by querying the supervisor at that iteration and $\epsilon$ is a user-defined threshold on how close robot policy is to match the highest quality supervisor.
-We present our algorithm, LEATHERMAN, which aims to solve Eq.
-\ref{eq:bugjet_LFD_obj}.
-
- \section{Algorithm}
- In this section, we first recall the original DAgger algorithm.
-Then introduce the notion and formal definition of a hierarchical supervisor and finally describe how to combine DAgger with a hierarchical supervisor to create a Gambler's DAgger.
-
- \subsection{DAgger: Dataset Aggregation}
- DAgger~\cite{ross2010reduction} solves the minimization in Eq.
-\ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
+\section{Approach and Background}
+ \subsection{Details on DAgger: Dataset Aggregation}
+Since the cumulative expected reward of a policy is difficult to optimize directly,
+DAgger~\cite{ross2010reduction} instead solves the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1)
+computing the policy parameter $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
 
@@
 $$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
+{\color{blue}FP: can we just have a neat algorithm box here?}
 %\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
@@
 
-\subsection{Hierarchy of Supervisors}\label{sec:hS}
-Instead of one  supervisor,we propose a hierarchy  of $M$ supervisors where for each supervisor $\tilde{\pi}_m$, there is an associated expected cumulative reward $R_m = \int \sum^T_{t=1} r(\mathbf{x}_t, \tilde{\pi}_m(x)) p(\tau |\tilde{\pi}_m)d\tau$, where $p(\tau |\tilde{\pi}_m)$ denotes the average distribution of states the supervisor encounters.
-We also denote some measure of cost $C_m$ that is ascribed to the supervisor, such as computational time or monetary expense.
-Generally the rank of supervisors in terms of cost is equivalent to the rank of supervisor in the terms of expected cumulative reward.
-Thus, the least costly supervisor will receive the lowest expected cumulative reward.
-
-Additionally for two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ to be in the hierarchy, they must only disagree in expectation on a subset of the work space to some precision $\tilde{\epsilon}$.
-Denote the set of states two supervisors disagree as $\mathcal{X}_{m,m+1} = \lbrace \mathbf{x} | ||\tilde{\pi}_m(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x}) ||^2_2 > \tilde{\epsilon} \rbrace$ .We enforce the condition $\mathcal{X}_{m,m+1} \subset \mathcal{X}$ because if two supervisors never provided the same examples then all states would have to be relabeled by the next supervisor in the hierarchy.
-
-We formally define an ordering on supervisors:
-
-\begin{definition} Two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ are in a hierarchy if  $C_m < C_{m+1}$  and  $\mathcal{X}_{m,m+1} \subset \mathcal{X}$
-\end{definition}
-
-Violation of this definition could result in no additional benefit from the LEATHERMAN algorithm or potentially worst a higher budget incurred than without using a hierarchy of supervisors.
-
 \subsection{DAgger with Supervisor Hierarchy}
-\mlnote{Anca and I wanted to justify the greedy allocation section, which we draw from the contextual arm bandit literature to do so... I can condense this}
-The hierarchical supervisor problem can be framed as a contextual multi-armed bandit, which is like a traditional multi-armed bandit except the sampled reward depends on an additional state term~\cite{li2010contextual}.
+{\color{blue}FP: Michael will rewrite this to give a simple explanation of the greedy approach here. We will argue about the choices in the experimental settings using sparsity}
+While the hierarchical supervisor problem can be framed as a contextual multi-armed bandit -- an extension of a traditional multi-armed bandit except the sampled reward depends on an additional state term~\cite{li2010contextual}.
 At each iteration a supervisor is selected from $M$ supervisors  and the state is the current policy parameters or $\theta_k$.
@@
 
-\subsection{ Neural Network Policy Architecture}
+\subsection{Neural Network Policy Architecture}
 Our policy is represented as deep neural network, which was trained using TensorFlow~\cite{tensorflow2015-whitepaper}.
@@
 \end{document}
+%\subsection{Hierarchies} If the robot could learn the policy  perfectly, this state density would match the one encountered in user examples.
+But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to~\cite{pomerleau1989alvinn}.
+This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing examples.
+We  introduce the concept of their being a set of supervisors each with an associated cost and skill level.
+Denote $\tilde{\pi}_M$ the most skilled and costly supervisor in this set.
+This supervisor could for example be a person with a Phd in machine learning and robotics.
+We formally define how each supervisor in the set is related to each other in Sec.
+\ref{sec:hS}.
+Every time a supervisor is queried a cost, $C_m$, is incurred this could be an hourly pay rate or computational time.
+While Eq.
+\ref{eq:LFD_obj} is the primary objective of our algorithm a secondary objective is to reduce the cumulative cost associated with training the robot.
+Thus, we are interested in solving the following objective
+
+%where $J$ is the number of queries need to satisfy the constraint on expected surrogate loss, $C_{m,j}$ denotes the cost incurred by querying the supervisor at that iteration and $\epsilon$ is a user-defined threshold on how close robot policy is to match the highest quality supervisor.
+We present our algorithm, LEATHERMAN, which aims to solve Eq.
+\ref{eq:bugjet_LFD_obj}.
+
+%\subsection{Hierarchy of Supervisors}\label{sec:hS} Instead of one  supervisor,we propose a hierarchy  of $M$ supervisors where for each supervisor $\tilde{\pi}_m$, there is an associated expected cumulative reward $R_m = \int \sum^T_{t=1} r(\mathbf{x}_t, \tilde{\pi}_m(x)) p(\tau |\tilde{\pi}_m)d\tau$, where $p(\tau |\tilde{\pi}_m)$ denotes the average distribution of states the supervisor encounters.
+We also denote some measure of cost $C_m$ that is ascribed to the supervisor, such as computational time or monetary expense.
+Generally the rank of supervisors in terms of cost is equivalent to the rank of supervisor in the terms of expected cumulative reward.
+Thus, the least costly supervisor will receive the lowest expected cumulative reward.
+
+%Additionally for two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ to be in the hierarchy, they must only disagree in expectation on a subset of the work space to some precision $\tilde{\epsilon}$.
+Denote the set of states two supervisors disagree as $\mathcal{X}_{m,m+1} = \lbrace \mathbf{x} | ||\tilde{\pi}_m(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x}) ||^2_2 > \tilde{\epsilon} \rbrace$ .We enforce the condition $\mathcal{X}_{m,m+1} \subset \mathcal{X}$ because if two supervisors never provided the same examples then all states would have to be relabeled by the next supervisor in the hierarchy.
+
+%We formally define an ordering on supervisors:
+
+%\begin{definition} Two supervisors $\tilde{\pi}_m$ and $\tilde{\pi}_{m+1}$ are in a hierarchy if  $C_m < C_{m+1}$  and  $\mathcal{X}_{m,m+1} \subset \mathcal{X}$ \end{definition}
+
+%Violation of this definition could result in no additional benefit from the LEATHERMAN algorithm or potentially worst a higher budget incurred than without using a hierarchy of supervisors.

### 2016-03-16 paper.tex
added 3 figures

@@
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth, height=4cm]{f_figs/robot.pdf}
-\caption{ \footnotesize Shown above is a Zymark robot.
-The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table.
-The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}
-\vspace*{-10pt}
-\label{fig:robot}
-\end{figure}
-
 \noindent \textbf{Expert Supervisor} Finally after training with the Motion Planning and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource.
@@
 \section{Experiments} \label{sec:Exp}
-
-\begin{figure*}[t]
+\begin{figure}[t]
 \centering
 
-\includegraphics{f_figs/results.eps}
+\includegraphics{f_figs/robot.eps}
+
+\caption{\footnotesize  Shown above is a Zymark robot.
+The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table.
+The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}
+
+\label{fig:perf_results}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics{f_figs/shapes_set.eps}
 
@@
 \label{fig:perf_results}
-\end{figure*}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics{f_figs/succes_measure.eps}
+
+\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
+a) Represents states that are easy for the supervisor to provide labels for.
+b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
+\vspace*{-20pt}
+\label{fig:perf_results}
+\end{figure}
 
@@
 \subsection{Hierarchical Supervisors}
+
+\begin{figure*}[t]
+\centering
+\includegraphics{f_figs/results.eps}
+
+\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
+a) Represents states that are easy for the supervisor to provide labels for.
+b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
+\vspace*{-20pt}
+\label{fig:perf_results}
+\end{figure*}
+
 We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .

### 2016-03-18 paper.tex
anca's feedback

@@
 
-\title{Robotic Grasping in Clutter Using a Hierarchy of Supervisors for Deep Learning from Demonstrations}
+\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors for \adnote{(Deep)} Learning from Demonstrations\adnote{I would remove deep but if you really want to keep it put it in parens?
+deep is not central to this and it pigeonholes you}}
 
-\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hseih$^1$, Florian T. Pokorny,\\
+\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hsieh$^1$, Florian T. Pokorny,\\
  Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
@@
 been trained by skilled human supervisors providing feedback on the current learned policy. As the number of
-demonstrations increases, this approach can however incur a substantial time and labor cost. We study the grasping in
-clutter problem and propose a hierarchical approach to learning from demonstrations based on DAgger which also
-incorporates a deep learning architecture to learn policies directly from video sequences. In experiments with a 4-DOF
-Zymark Robot, we consider a hierarchy of three increasingly competent and costly supervisor types: an analytical grasp
-planner, a crowd-sourced human workers and a human expert supervisor. Our results indicate that training a policy
-hierarchically by bootstrapping with the analytical method, followed by crowd sourced and expert supervision improves
-test-time performance compared to training only with an expert supervisor by XX while reducing training cost by XX. We
-furthermore find that the addition of crowd-sourced supervisors compared to analytic pre-training followed by
-supervision by an expert improves performance significantly. [FP: Fine tune how we report main results here]
+demonstrations increases, this approach can however incur a substantial time and labor cost.
+We propose that a hierarchy of supervisors that vary is expertise but also in cost can help alleviate this issue.
+We combine planning on a relaxed problem with crowdsourcing and with robotics experts, and hypothesize that leveraging this combination can lead to similar performance while substantially decreasing cost.
+We focus on the grasping in clutter problem, and use an architecture for learning from demonstration based on DAgger and deep learning to learn policies directly from image input.
+Our results ....[fill in]
+
  \end{abstract}
@@
 
-An alternative approach, which we propose here, is to approach the grasping in
-clutter problem in a model-free manner, where the interaction behavior is learned directly from data within the learning
-from demonstrations framework \cite{argall2009survey}. Learning from demonstration (LfD) algorithms have been used
+Another approach to the grasping in
+clutter problem in a data-driven manner, where the interaction behavior is learned directly from interactions with the environment and a supervisor, which can be an expert human or an analytical method \cite{argall2009survey}.
+Learning from demonstration (LfD) algorithms have been used
 successfully in recent years for a large number of robotic tasks, including helicopter
@@
 \caption{
-Three roll-outs of a fully trained grasping in clutter policy (one per column, bottom to top) which was trained using a
-hierarchy of three supervisors consisting of analytical motion planning, crowd-sourcing and human expert. 
-Red shapes indicate clutter objects and the robot is trained to reach the yellow circle. {\color{blue}FP: how about we
-display the policy after each of the three training steps? One per column}}
+Three roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, bottom to top) which was trained using a
+hierarchy of three supervisors consisting of an analytical motion planning, crowd-sourcing and human expert. 
+Red shapes indicate clutter objects and the robot is trained to reach the yellow circle.
+The trained manipulation policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in state position.
+The resulting policy learns to sweep away clutter objects and reach the goal object.
+}
 \vspace*{-20pt}
@@
 utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
-bootstrap the learning process. At the lowest level of the hierarchy, we in particular consider an analytic motion
-planner which acts as an affordable supervisor.
+bootstrap the learning process.
+
+\adnote{In particular, while model-based planners might not yet capture the full physical interaction among all objects, it is wasteful to completely throw them away and learn with an expert supervisor from scratch.
+Thus, at the lowest lever of the hierarchy, we use a motion planner on an \emph{relaxed} version of the problem.
+In our grasping application, we use a planner that ignores the clutter but can leverage knowledge of the kinematics and the goal.}
+The next supervisor in the hierarchy are crowdsource workers on Amazan Mechnical Turker\adnote{Turk not Turker}.
+Then finally the robot is trained with a Phd student in robotics, who is an expert human supervisor.
+Examples of the resulting learned grasping in clutter policy can be seen in Fig.
+\ref{fig:teaser}.
 
@@
 Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and then the field of
-Curriculum learning, which is related to the concept of hierarchical supervisors.
+Curriculum learning, which is related to the concept of hierarchical supervisors.\adnote{make sure to talk about guided policy search too, which is a way to combine deep nets with either human or planner supervision}
 
@@
 \noindent\textbf{Curriculum Learning}
-Our approach is closely related to ideas from \emph{curriculum learning}, where a neural network is trained via 
+Our approach is closely related to ideas from curriculum learning, where a neural network is trained via 
 incrementally, first on easier examples and then gradually on data of increasing difficulty~\cite{bengio2009curriculum}.
@@
 
-Our approach is different from curriculum learning in that a supervisor may occasionally provide low quality examples in
-parts of the state space visited by the robot, which implies that it is now necessarily easier for the robot to learn
-one supervisor's policy versus another in the hierarchy. In future work, we intend to study potential combinations of
-hierarchical supervisors and curriculum learning which we believe could provide a promising avenue for research.
+Our approach is different from curriculum learning, which assumes all training data presented to the neural network is valid.
+We  instead train on a completely different set of examples throughout the supervisor hierarchy.
+In these different set of examples, some could be very low-quality examples and will enforce a behavior that needs to be retrain with a more-skilled supervisor.
 
@@
 trained policy with respect to the most skilled supervisor $S_M$ in the hierarchy while minimizing the overall training
-cost. In particular, this paper provides an empirical study of greedy combinations of three types of supervisors $S_1,
+cost.
+
+ In particular, this paper provides an empirical study of greedy combinations of three types of supervisors $S_1,
 S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
-Here, $S_1$ is an analytical motion planning algorithm with a cost $C_1=XX$, $S_2$ a supervisor
-consisting a crowd-sourced Amazon Mechanical Turk laborers with $C_2=YY$, and $S_3$ a skilled human supervisor with
-$C_3=ZZ$.
+Here, $S_1$ is an analytical motion planning algorithm with a cost $C_1=0.01$, $S_2$ a supervisor
+consisting a crowd-sourced Amazon Mechanical Turk laborers with $C_2=0.1$, and $S_3$ a human expert supervisor with
+$C_3=1$.
 
@@
 \subsection{DAgger with Supervisor Hierarchy}
-{\color{blue}FP: Michael will rewrite this to give a simple explanation of the greedy approach here. We will argue about the choices in the experimental settings using sparsity}
-While the hierarchical supervisor problem can be framed as a contextual multi-armed bandit -- an extension of a traditional multi-armed bandit except the sampled reward depends on an additional state term~\cite{li2010contextual}.
-At each iteration a supervisor is selected from $M$ supervisors  and the state is the current policy parameters or $\theta_k$.
-Then a sampled reward is received which is how well the trained policy performed on the sample surrogate loss measured against the $\tilde{\pi}_M$ or the supervisor at the top of the hierarchy.
-Note we only measure against the supervisor at the top of the hierarchy because that is our primary objective (i.e.
-Eq.
-\ref{eq:LFD_obj}).
+Formulating a framework for selecting a supervisor can be difficult because we do not have a known model for how a supervisor selected affects the minimization of the surrogate loss.
+The reason we do not have a model is because this would require modeling what examples the supervisor will return, the $\theta$ parameters of the neural network policy after training and the states the robot is likely to visit given those parameters.
 
-While a large amount of literature exists to solve contextual multi-armed bandit problems, a common assumption is that the sampled reward can be observed~~\cite{li2010contextual}.
-However, in our situation evaluation of the sampled reward requires querying the costliest supervisor every iteration.
-Thus, defeating the purpose of cost reduction.
-In light of this we propose a greedy allocation strategy where we train a policy with the cheapest supervisor first until convergence and then work up the hierarchy training with each supervisor.
+We could learn a policy using model-free reinforcement learning algorithms ~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the best supervisor to select given the current policy.
+However, a problem occurs when applying these approaches because it requires evaluating the objective function, which is the surrogate loss with respect to the costliest and most-skilled supervisor, $S_M$.
+This requires exhaustively querying the costliest supervisor at each iteration and defeating the purpose of reducing cost.
 
-Our algorithm is as follows: first iterate through Step 1 and 2 of DAgger for a given supervisor, however after iteration $K$ or when the current policy, $\pi_{\theta_{m,k}}$ is able to achieve a loss $\epsilon$ on the sampled $J$ states at that current iteration (i.e):
+ In light of this, we propose a greedy allocation strategy, in terms of supervisor cost, where we train a policy with the cheapest supervisor first for a fix number of trials and then advance through the hierarchy training with each supervisor.
+Our algorithm is as follows: first iterate through Step 1 and 2 of DAgger for a given supervisor, however after iteration $K_m$.
+Then iterate to the next supervisor in the hierarchy or $m = m+1$.
 
-$$\frac{1}{J} \sum^J_{j=1} ||\pi_{\theta_{m,k}}(\mathbf{x}_j) - \tilde{\pi}_m(\mathbf{x}_j) ||^2_2 \leq \epsilon$$
+The number of iterations before advancing to the next supervisor can be challenging to set.
+In practice, we either advanced when the surrogate loss between supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving.
+The reason for different options was because some supervisors have very large variance (i.e.
+crowdsourcing), that a fix threshold on surrogate loss could be misleading without a sufficient number of examples.
 
-Then iterate to the next supervisor in the hierarchy or $m = m+1$.
-The hyperparameter $\epsilon$ can be set as a measure of how different the controls applied between the robot's policy and the current supervisors a sequential process can tolerate.
-For example surgical sequential processes could warrant a very low threshold, but less precise sequential processes, like grasping in clutter, can tolerate a higher value.
-
-An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_K$ has examples from a different supervisor that receives a smaller expected cumulative reward.
+An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
 This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
@@
 \ref{sec:Exp} that it also beneficial to add to the new dataset the states and controls applied by the current policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance $\tilde{\epsilon}$.Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
-
-\mlnote{we can formally prove the following statements or point to the web similar to SHIV... it will be alot easier to write these out though if we have space}
-With respect to the theoretical analysis of DAgger's convergence rate, one can see that in our algorithm you are solving $M$ individual DAgger's ~\cite{ross2010reduction}.
-Thus, in the worst case you will converge to the supervisor at the top of the hierarchy $\tilde{\pi}_M$ in $\tilde{O}(MT)$ iterations instead of DAgger's original $\tilde{O}(T)$.
-
-It should be noted though that as you iterate through the hierarchy of supervisors, each iteration starts out with an error bounded by $\int_{\mathcal{X}_{m,m+1}} ||\pi_{\theta_{0,m+1}}(\mathbf{x}) - \tilde{\pi}_{m+1}(\mathbf{x})||^2_2 p(\mathbf{x}|\theta_{0,m+1}) d\mathbf{x} + \epsilon$.
-Thus, if the supervisors are able to agree on a large part of the state space, there should be less iterations with the expert supervisor than $\tilde{O}(T)$, which we experimentally show in our grasping in clutter task.
 
@@
 
-\noindent \textbf{Motion Planning Supervisor} Our first supervisor is a an analytical method that computes the trajectory the robot should move in to reach the goal object, or yellow circle, with a relax dynamic model of the environment.
+\noindent \textbf{Motion Planning that Ignores Obstacles Supervisor} Our first supervisor, $S_1$, is a a motion planner that that computes the trajectory the robot should move in to reach the goal object, or yellow circle, by ignoring obstacles.
+Thus we refer to $S_1$ as Motion Planning that Ignores Obstacle (MPIO) supervisor.
 Our method employs template matching to identify the goal object in the image and the using the forward dynamics of the robot to computes the relative change in direction the robot should apply as an control.
@@
 
-In this stage, the motion planning supervisors only tries to teach the robot to move towards the goal.
-Note that the motion planning supervisor's advice does not have any knowledge about how the cluttered objects will respond to the forces applied via the robot arm, which results in sub-optimal polices.
-However, our motion planning supervisor is both computationally and monetarily inexpensive to run which allows us to provide a large number of examples.
+In this stage, the MPIO supervisors only tries to teach the robot to move towards the goal.
+Note that the MPIO supervisor's examples does not have any knowledge about how the cluttered objects will respond to the forces applied via the robot arm, which results in sub-optimal polices.
+However, the MPIO supervisor is both computationally and monetarily inexpensive to run which allows us to provide a large number of examples.
+Thus, the cost of the MPIO supervisor is $C_1 = 0.01$.
 
-\noindent \textbf{CrowdSourced Supervisor} Our next level of supervisor relies on a crowd source service, called Amazon Mechanical Turk (AMT).
-Chung et al.
-demonstrated the reliable data learning from demonstration data could be obtained from an AMT platform.
-The AMT platform makes readily available thousands of human workers that can perform remedial task for a price range of \$0.1 per robot trajectory\cite{chung2014accelerating}.
-Thus potentially providing a higher quality supervisor who has an intuition for how the cluttered objects interact with the world, but at a slightly higher cost.
+\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon Mechanical Turk (AMT).
+The AMT platform makes readily available thousands of human workers that can perform  provide examples for  \$0.12 per robot trial.
+Thus potentially providing a higher quality supervisor who has an intuition for how the cluttered objects interact with the world, but at a  higher cost, $C_2 = 0.1$.
 
@@
 \ref{fig:overlays}.
-The interface draws a transparent overlay that shows how the robot would respond provided the current control this allows for the AMT worker to see some of the effect of their control.
-We rely on their natural intuition for how objects to infer how the change in robot position will change the objects.
+The interface draws a transparent overlay that shows how the robot would respond provided the current control Thus, allowing for the AMT worker to see the magnitude and effect their example would have on the robot.
 
-We also design a tutorial for the work that first has them perform designated motions on a virtual robot and introduces them to a problem.
+We additionally designed a tutorial for the CrowdSourced Supervisor.
+First, we introduce them to a robot named Izzy and briefly explain that Izzy is trying to reach a yellow circle but has a tendency to "misbehave" and needs their help.
+Then we have them perform designated motions with a virtual Izzy, which helps them understand how the robot's dynamics behave.
 We additionally provide a video of an expert providing corrections on three robot trajectories.
+We lastly instruct the CrowdSourced Supervisor to only label when they are sure in their decision, in order to prevent contradictory examples associated with them second guessing themselves.
 
-\noindent \textbf{Expert Supervisor} Finally after training with the Motion Planning and Crowdsourced Supervisor we leverage the Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource.
-An expert supervisor in this case is a Phd student in machine learning and robotics, which can cost on average ten times more than an AMT worker to employ \cite{}.
+While completing a tutorial before providing examples can be beneficial, we still are not sure whether the CrowdSourced Supervisor can provide quality examples that can be used in learning.
+To help ensure quality, we give all CrowdSourced Supervisor  the same robot trial first and measure their examples against the examples form a  Human Expert Supervisor.
+If the average Squared-Euclidean distance between examples is above a threshold of the Human Expert's examples or the number of examples they provided is above a threshold of the number the Human Expert provided, the Crowdsource Supervisor is not asked to provide additional examples.
+
+\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource.
+An Human Expert Supervisor in this case is a Phd student in machine learning and robotics, which costs $C_3=1.0$.
+The Human Expert Supervisor uses the same interface , shown in Fig.
+\ref{fig:overlays}, to provide examples to the robot.
 
 An expert supervisor can be used in a variety of scenarios.They first would have a better intuition of the physical limitations of the robot and environment, such as joint limits or how certain objects might behave under force.
-Furthermore, they would also understand how the examples given could lead to better training of the parameterized policy.
-For example, understanding the feature space the policy lies in can lead to the expert not providing contradictory examples.
-
-It can still be hard for an expert to provide the correct feedback without knowing the magnitude of the controls suggested, so they use the same interface as the CrowdSourced Supervisor.
+Furthermore, they would also understand how the examples given could lead to better training of the robot's policy $\pi_\theta$.
+For example, understanding the feature space the policy lies in can lead the Human Expert to not providing contradictory examples.
 
 \subsection{Neural Network Policy Architecture}
+\mlnote{adding more details with figure tomorrow}
 Our policy is represented as deep neural network, which was trained using TensorFlow~\cite{tensorflow2015-whitepaper}.
@@
 
-To determine our architecture we preformed a grid search ofver different architectures  trained after 400 iterations with a batch size of 200.
+To determine our architecture we preformed a grid search over different architectures  trained after 400 iterations with a batch size of 200.
 The set of architectures consist of different network architectures as well as different momentum terms, and weight initialization schemes.
@@
 
-\label{fig:perf_results}
+\label{fig:robot}
 \end{figure}
@@
 
-\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
-a) Represents states that are easy for the supervisor to provide labels for.
-b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
-\vspace*{-20pt}
-\label{fig:perf_results}
+\caption{\footnotesize  The set of objects that the robot was trained on.
+The Training objects on the right are the four objects used in training.
+The test objects on the left represent represent objects that were found in our test configurations.
+The test objects vary in size and shape from the training objects, which can test how well the robot learns to manipulate unknown objects.
+Every test configuration contained at least one object from this set to guarantee it wasn't trained on.
+}
+
+\label{fig:shape_set}
 \end{figure}
@@
 
-\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
-a) Represents states that are easy for the supervisor to provide labels for.
-b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
+\caption{\footnotesize  The different measure of success used in our scoring metric for how well the robot performed.
+Not successful corresponds to when the gripper is never in contact with yellow circle.
+Near successful corresponds to when the robot ends with the gripper touching the yellow circle.
+Successful is defined as when the yellow circle is inside the gripper.
+}
 \vspace*{-20pt}
-\label{fig:perf_results}
+\label{fig:suc_meas}
 \end{figure}
 
+\adnote{start with a description of what we want to test: the main thing is that hierarchy maintains performance compared to expert but reduces cost; also mention secondary tings}
 For an experiment in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera.
@@
 The robot is commanded via state position requests, which are tracked by a tuned PID controller.
-The policy $\pi_\theta$ outputs delta positions that are bounded by $15\deg$ for the gripper and turntable, $1$ cm for the arm extension and $0.5$ cm for the gripper at each time step.
+We used relative state contorl because 1) it is easier to enforce stay out zones (such as where a human operator could be) in the robot configuration space and 2) registering state control to a labeling interface in Fig.
+\ref{fig:overlays} is more straightforward than motor commands.
+The policy $\pi_\theta$ outputs delta positions that are bounded by $15^\circ$ for the gripper and turntable, $1$ cm for the arm extension and $0.5$ cm for the gripper at each time step.
 There is $T=100$ time steps in a trajectory.
@@
 The test set configurations varied in number of objects on the table, size of objects and relative pose of each object.
+The objects that were trained on and those that were only tested on can be seen in Fig.
+\ref{fig:shape_set}.
 We measure success as defined by three situations not successful, near successful, successful.
-We report total success as a score out of 2: 0 for not successful, 1 for near successful, 2 for successful.
+Examples of the robot in these situations can be seen in Fig.
+\ref{fig:suc_meas}.
 
@@
 Successful is defined as getting the goal object inside the gripper at the end of a trajectory.
+We report total success as a score out of 2: 0 for not successful, 1 for near successful, 2 for successful.
+
+In all experiments we used a batch size of 20 trials per iterations or 2000 images, thus 100 trials corresponds to 5 iterations.
 
@@
 
-\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
-a) Represents states that are easy for the supervisor to provide labels for.
-b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
+\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported.
+The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
+The top row corresponds to policies only trained with one supervisor: MPIO, Crowdsourced or Human Expert.
+The bottom corresponds to policies trained with a hierarchy of supervisors: MPIO and Crowdsource, MPIO and Human Expert, MPIO, Crowdsourced and Human Expert.
+The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).
+}
 \vspace*{-20pt}
@@
 \end{figure*}
+\adnote{reorder: mpio, he, mpio->he (main experiment); then cs, mpio-cs, all; cs is missing score, hopefully it does not much better than mpio-cs; don't highlight bottom right option because technically its not suppoed to be better than expert; just use hypotheses to show your points.; also separate mpio-cs-he from rest becuase it is using double the data!
+not fair comparison!
+spread the legend horizontally at the top; }
 
 We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .
-We compare having an analytical only supervisor for a fixed amount of data of 160 demonstrations.
+We compare having an analytical only supervisor for a fixed amount of data \adnote{to having only an expert, and to having the hierarchy of both}.
 The non-hierarchical policies trained with the expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.
@@
 
+\adnote{We hypothesized that the hierarchy will perform on par with the expert while reducing cost.}
+
 Our results, shown in Fig.
-\ref{fig:perf_results}, are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
+\ref{fig:perf_results}, \adnote{support this hypothesis.
+The policy trained...
+achieved ...}are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
 Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance.
@@
 
-Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the
+Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the \adnote{expert.}
 
-\subsection{Quality Crowdsourced Supervisor}
+\subsection{Quality of Crowdsourced Supervisor}
 We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy.
@@
 \ref{sec:hier}.
-We  test how well a crowdosurce supervisors performs as part of a hierarchy of supervisors, we had a policy train with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers.
-We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.
+We  test how well a crowdosurce supervisor performs as part of a hierarchy of supervisors, \adnote{this sentence is not ending here?}we had a policy train with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers.
+We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations \mlnote{we need to test this policy tomorrow}\adnote{ok good so hopefully we will get that mpio->cs as good as cs}
 
@@
 
-\mlnote{talk about crowdosuce statistics}
+In total, we tested on 44 AMT workers.
+We asked them to provide examples for a single rollout and then if they passed quality check asked them if they wanted to exit or continue for an additional \$$0.12$ per demonstration.
+We found only 21 AMT workers were able to pass the quality check and continue providing demonstrations.
+On average a worker would provide 4 demonstrations before exiting the AMT HIT.
 
 \subsection{Advancing in the Hierarchy}
-We further test how to advance between supervisors in the hierarchy.We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$ \mlnote{need to get this number off the local code, will update tomorrow}.
+We further test how to advance between supervisors in the hierarchy.We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$.
 Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
@@
 
-\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for.
-a) Represents states that are easy for the supervisor to provide labels for.
-b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
+\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported.
+The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
+Each policy was trained with the MPIO to Human Expert hierarchical supervisor.
+From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
+Regularization achieves the highest performing score of (0.18) }
 \vspace*{-20pt}
@@
 
-While our policy was able to do substantially better, to near successful mode a reasonable portion of the time.
+While our policy was able to do substantially better, it did score a near successful  $40\%$.
 These failure modes where do to the robot not being able to accurately manipulate smaller objects, where slight perturbations could result them being pushed into the gripper, and accurately controlling the goal object to land in the circle (i.e.
@@
 \section{Discussions and Future Work}
+For highly stochastic domains like grasping in clutter, using a hierarchy of supervisors to bootstrap performance at a lower cost seems to be a very sensible thing to do.
+Our results suggest that we can scale up the amount of data needed to learn the task at a much lower cost than only querying the most-skilled supervisor.
+However, much work still needs to be done in determining how to appropriately select the next supervisor to receive examples from.
+While our current strategy worked well empirically, it remains to be seen if this would apply to other domains.
+
+Future work will also look at how to increase the success rate on the grasping in clutter domains.
+The current failure modes are associated with a lack of fine motor precision.
+Our current supervisors do not  have the ability to give finer motor control corrections, however using more sophisticated analytical methods might enable better performance.
+Furthermore, applying self-learning  to our current policy could be a way to "fine-tune" the current behavior and learn the precision.
 
@@
 National Science Foundation under Award IIS-1227536, NSF-Graduate Research Fellowship, by the Knut and Alice Wallenberg Foundation and the National Defense Science and Engineering Graduate Fellowship Program.
-We thank Pieter Abbeel, Sergey Levine and Sanjay Krishnan for insightful feedback.
+We thank Steve McKinely and Meng Guo for help in building the hardware setup.
 

### 2016-03-18 paper.tex
.

@@
 \subsection{DAgger with Supervisor Hierarchy}
-Formulating a framework for selecting a supervisor can be difficult because we do not have a known model for how a supervisor selected affects the minimization of the surrogate loss.
-The reason we do not have a model is because this would require modeling what examples the supervisor will return, the $\theta$ parameters of the neural network policy after training and the states the robot is likely to visit given those parameters.
+Formulating a framework for supervisor strategy selection poses a challenging problem since no formal model
+for the effect of supervisor selection on the surrogate loss minimization is available a priori and since the
+neural network policy parameters $\theta$ are additionally changing at each step of DAgger's iterative training process.
 
-We could learn a policy using model-free reinforcement learning algorithms ~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the best supervisor to select given the current policy.
-However, a problem occurs when applying these approaches because it requires evaluating the objective function, which is the surrogate loss with respect to the costliest and most-skilled supervisor, $S_M$.
-This requires exhaustively querying the costliest supervisor at each iteration and defeating the purpose of reducing cost.
+While one could consider to learn a policy using model-free reinforcement learning algorithms
+~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
+best supervisor to select given the current policy, this approach requires substantial numbers of 
+queries for supervision of the costliest supervisor at each iteration. In light of this, we propose a greedy allocation
+strategy.
 
- In light of this, we propose a greedy allocation strategy, in terms of supervisor cost, where we train a policy with the cheapest supervisor first for a fix number of trials and then advance through the hierarchy training with each supervisor.
-Our algorithm is as follows: first iterate through Step 1 and 2 of DAgger for a given supervisor, however after iteration $K_m$.
-Then iterate to the next supervisor in the hierarchy or $m = m+1$.
+We train a policy with the cheapest supervisor $S_1$ for a fixed number of $K_1$ iterations with DAgger and then advance
+linearly through the hierarchy $S_1, \ldots, S_M$, where the final Neural Network Parameters $\theta_i$ trained using
+$S_i$ are transferred iteratively to supervisor $S_{i+1}$ before further training the policy with DAgger.
+Each supervisor is trained for $K_i, i\in \{1, \ldots, M\}$ iterations in turn.
 
-The number of iterations before advancing to the next supervisor can be challenging to set.
-In practice, we either advanced when the surrogate loss between supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving.
-The reason for different options was because some supervisors have very large variance (i.e.
-crowdsourcing), that a fix threshold on surrogate loss could be misleading without a sufficient number of examples.
-
-An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
-This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
-
-We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the current $\theta_{m,K}$ weight parameters.
-Thus, we propose only performing DAgger for each individual supervisor in the hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor.
-We found empirically in Sec.
-\ref{sec:Exp} that it also beneficial to add to the new dataset the states and controls applied by the current policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance $\tilde{\epsilon}$.Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
+While for large numbers of iterations, convergence tests can be applied to determine a point of diminishing return at
+which a switch to the next supervisor in the hierarchy can be initiated, this approach can be challenging when only a
+limited numbers of roll-outs can be afforded. In practice, we either advanced when the surrogate loss between
+supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving empirically. 
+For crowdsourcing in particular, we chose the second option since, due to the large variance between demonstrations
+we were not able to determine a fixed threshold for the surrogate loss. We hope to significantly scale the number of
+training steps in future work to investigate various switching criterea in full detail.
 
@@
 
+An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
+This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
+
+We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the current $\theta_{m,K}$ weight parameters.
+Thus, we propose only performing DAgger for each individual supervisor in the hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor.
+We found empirically in Sec.
+\ref{sec:Exp} that it also beneficial to add to the new dataset the states and controls applied by the current policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance $\tilde{\epsilon}$.Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
+
 \subsection{Scaling the Hierarchy}

### 2016-03-18 paper.tex
anca's feedback incoporated

--- 2016-03-18 paper.tex
@@
 
-\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors for \adnote{(Deep)} Learning from Demonstrations\adnote{I would remove deep but if you really want to keep it put it in parens?
-deep is not central to this and it pigeonholes you}}
+\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with  (Deep) Learning from Demonstrations}
 
@@
 
-\adnote{In particular, while model-based planners might not yet capture the full physical interaction among all objects, it is wasteful to completely throw them away and learn with an expert supervisor from scratch.
-Thus, at the lowest lever of the hierarchy, we use a motion planner on an \emph{relaxed} version of the problem.
-In our grasping application, we use a planner that ignores the clutter but can leverage knowledge of the kinematics and the goal.}
-The next supervisor in the hierarchy are crowdsource workers on Amazan Mechnical Turker\adnote{Turk not Turker}.
+In particular, while model-based planners might not yet capture the full physical interaction among all objects, it can be wasteful to not leverage them and learn with an expert supervisor from scratch.
+Thus, at the lowest lever of the hierarchy, we use a motion planner on an relaxed version of the problem.
+In our grasping application, we use a planner that ignores the obstacles but can leverage knowledge of the kinematics and the goal.
+The next supervisor in the hierarchy are crowdsource workers on Amazan Mechnical Turk.
 Then finally the robot is trained with a Phd student in robotics, who is an expert human supervisor.
@@
 $$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
-{\color{blue}FP: can we just have a neat algorithm box here?}
+
 %\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
@@
 
-\adnote{start with a description of what we want to test: the main thing is that hierarchy maintains performance compared to expert but reduces cost; also mention secondary tings}
-For an experiment in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera.
+In this section, we first describe the grasping in clutter experimental setup.
+Then we test how the supervisor hierarchy performs versus not leveraging a hierarchy.
+We then test how high of Quality the CrowdSource supervisor is.
+Then, we experiment with different ways to advance in the hierarchy.
+Finally, we look at using all three supervisors and to train a robot for the grasping in clutter task.
+
+\subsection{Experimental Setup}
+For experimenting in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera.
 Examples of images from the camera can be seen in Fig.
@@
 We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .
-We compare having an analytical only supervisor for a fixed amount of data \adnote{to having only an expert, and to having the hierarchy of both}.
-The non-hierarchical policies trained with the expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.
+We compare having only a MPIO Supervisor for a fixed amount of data to having only an Human Expert, and to having the hierarchy of both .
+The non-hierarchical policies trained with the human expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.
 The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.
 
-\adnote{We hypothesized that the hierarchy will perform on par with the expert while reducing cost.}
-
 Our results, shown in Fig.
-\ref{fig:perf_results}, \adnote{support this hypothesis.
-The policy trained...
-achieved ...}are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
+\ref{fig:perf_results}, are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
 Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance.
@@
 
-Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the \adnote{expert.}
+Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the Human Expert Supervisor.
+
+\begin{figure}[t]
+
+\includegraphics{f_figs/cost_result.eps}
+
+\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported.
+The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
+Each policy was trained with the MPIO to Human Expert hierarchical supervisor.
+From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
+Regularization achieves the highest performing score of (0.18) }
+\label{fig:cost_result}
+\end{figure}
 
@@
 \ref{sec:hier}.
-We  test how well a crowdosurce supervisor performs as part of a hierarchy of supervisors, \adnote{this sentence is not ending here?}we had a policy train with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers.
-We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations \mlnote{we need to test this policy tomorrow}\adnote{ok good so hopefully we will get that mpio->cs as good as cs}
+We  first test how well a crowdosurce supervisor performs as part of a hierarchy of supervisors.
+We trained a policy with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers.
+We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.
 
@@
 
-\begin{figure}[t]
-
-\includegraphics{f_figs/cost_result.eps}
-
-\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported.
-The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
-Each policy was trained with the MPIO to Human Expert hierarchical supervisor.
-From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
-Regularization achieves the highest performing score of (0.18) }
-\vspace*{-20pt}
-\label{fig:cost_result}
-\end{figure}
-
 \subsection{Scaling the Hierarchy}
@@
 We attribute this problem to a limit in the detail of precision our supervisors can currently give, future work will look at more precise analytical methods and fine tuning the policies via self-learning.
+
+\begin{figure}[t]
+\includegraphics{f_figs/big_data.eps}
+
+\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported.
+The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
+The top row corresponds to policies only trained with one supervisor: MPIO, Crowdsourced or Human Expert.
+The bottom corresponds to policies trained with a hierarchy of supervisors: MPIO and Crowdsource, MPIO and Human Expert, MPIO, Crowdsourced and Human Expert.
+The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).
+}
+\vspace*{-20pt}
+\label{fig:big_data}
+\end{figure}
 

### 2016-03-18 paper.tex
added latest changes

@@
 
-\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with  (Deep) Learning from Demonstrations}
+\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with Learning from Demonstrations}
 
@@
 to grasp an object that might be occluded by other objects in the environment poses an interesting challenge to robotic
-systems. Two fundamental approaches to grasping in clutter include the analytic model driven approach \cite{1,2,3},
+systems.
+This problem is relevant to industrial applications such as warehouse shipping operations and flexible manufacturing in a semi-structured environments.
+One fundamental approach to grasping in clutter is the analytic model driven approach~\cite{bicchi2000robotic},
 where the interaction dynamics between the robot and obstacles are formulated analytically. However, modeling all the 
@@
 Another approach to the grasping in
-clutter problem in a data-driven manner, where the interaction behavior is learned directly from interactions with the environment and a supervisor, which can be an expert human or an analytical method \cite{argall2009survey}.
+clutter problem is a data-driven manner, where the interaction behavior is learned directly from interactions with the environment and a supervisor, which can be an expert human or an analytical method \cite{argall2009survey}.
 Learning from demonstration (LfD) algorithms have been used
@@
 In particular, while model-based planners might not yet capture the full physical interaction among all objects, it can be wasteful to not leverage them and learn with an expert supervisor from scratch.
-Thus, at the lowest lever of the hierarchy, we use a motion planner on an relaxed version of the problem.
+Thus, at the lowest level of the hierarchy, we use a motion planner on an relaxed version of the problem.
 In our grasping application, we use a planner that ignores the obstacles but can leverage knowledge of the kinematics and the goal.
@@
 Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and then the field of
-Curriculum learning, which is related to the concept of hierarchical supervisors.\adnote{make sure to talk about guided policy search too, which is a way to combine deep nets with either human or planner supervision}
+Curriculum learning, which is related to the concept of hierarchical supervisors.
 
@@
 grasp objects in an unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
-specifically aim to grasp a single target object in clutter. Leeper et al. ~\cite{} use a human operator for assistance
+specifically aim to grasp a single target object in clutter.
+
+However, prior work has studied the problem of manipulating objects
+by performing pushing operations~\cite{mason1986mechanics}.  Cosgun et al.~\cite{cosgun2011push} and King et al. \cite{kingnonprehensile} consider the problem of planning
+a series of push operations that move an object to a
+desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
+\cite{kitaevphysics}.
+However, all of these works assume known properties of the object model, such as mass and friction coefficient  or access to an object model in a physics simulator, which could be difficult to obtain for unknown objects.
+
+Leeper et al. ~\cite{leeper2012strategies} used a human operator for assistance
 to guide the robot through clutter with the objective of grasping a target object. However, the robot required the human
 to be present at all times and did not attempt to learn to operate autonomously. We are interested in a data-driven
-approach that only queries a supervisor at training time and which can operate autonomously thereafter.
+approach that only queries a supervisor at training time and  can operate autonomously thereafter.
 
-Prior work has studied the problem of manipulating objects
-by performing pushing operations~\cite{}. Berenson et
-al. ~\cite{} in particular use a sampling-based planner that considers clearance
-from obstacles in the environment to plan a grasp
-approach trajectory in cluttered environments. Cosgun et al.
-[3] and King et al. \cite{kingnonprehensile} consider the problem of planning
-a series of push operations that move an object to a
-desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
-\cite{kitaevphysics}. However, all of these works assume a known model of of the object behavior is provided. We are
-interested in learning manipulation polices in a data-driven manner instead, leveraging a hierarchy of supervisors for
-training.  
-\mlnote{We should discuss how to distinguish our work (Properties of our approach are we assume raw image data, real time and unknown dynamics)}.
+A learning model-free based approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}.
+However, this assumes a known low-dimensional state representation to both estimate dynamics and perform LQG in.
+In the grasping in clutter domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape when planning a pushing strategy.
 
 \noindent \textbf{Online Lfd with an Expert Supervisor}
-Successful robotic examples of Online Learning From Demonstration with an expert supervisor include applications to flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.
+Successful robotic examples of Online Learning From Demonstration with an expert supervisor include applications to flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskeyshiv}.
 
@@
 One Class SVM classifier. This enabled the authors to reduce the density estimation problem to a 
-simpler regularized binary classification~\cite{laskey}. However the grasping in clutter problem exhibits a high amount
+simpler regularized binary classification~\cite{laskeyshiv}. However the grasping in clutter problem exhibits a high amount
 of stochasticity requiring a large training data set which poses a significant computational challenge to these methods.
@@
 
-{\color{blue} FP: might make this and the above specific to grasping in clutter?}
 \noindent\textbf{Objective.} The objective of policy learning is to find a policy that maximizes some known cumulative
 reward function $\sum^T_{t=1} r(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The reward $r:\mathcal{X}\times
-\mathcal{U}\to \mathbb{R}$ is typically user defined and task specific \cite{1,2,3}. 
+\mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
 For example, in the task of inserting a peg into a hole, a function quantifying a notion of distance between the peg's
@@
 Since grasp success is typically considered as a binary reward which is observed only at a delayed final state \cite{kitaevphysics}, 
-grasping in clutter poses a challenging problem for traditional reinforcement learning methods. We hence instead build
+grasping in clutter poses a challenging problem for traditional reinforcement learning methods. Hence, we instead build
 upon DAgger which queries a supervisor for appropiate actions, to provide the robot a set of N stochastic demonstrations trajectories $\lbrace \hat{\tau}^1,...\hat{\tau}^N \rbrace$.
@@
 
- In particular, this paper provides an empirical study of greedy combinations of three types of supervisors $S_1,
+ In particular, this paper provides an empirical study of greedy, with respect to cost, combinations of three types of supervisors $S_1,
 S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
@@
 queries for supervision of the costliest supervisor at each iteration. In light of this, we propose a greedy allocation
-strategy.
+strategy with respect the cost of the supervisor.
 
@@
 
-\begin{figure}[t]
-\centering
-
-\includegraphics[width=\columnwidth, height=4cm]{f_figs/labeling.pdf}
-
-\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task.
-The pink overlay indicates the desire change in the robot position with respect to the current robot state.
-Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave.
-Each window shows a correction in a degree of freedom a) is the rotation of the robots base b) is extending the robot's arm.}
-\vspace*{-10pt}
-\label{fig:overlays}
-\end{figure}
-
 \section{Robot Grasping in Clutter}
@@
 \subsection{Grasping in Clutter}\label{sec:task}
-Consider a robot in an Amazon warehouse.
+\mlnote{Should we just merge this with the original, problem objective?}
+Consider a robot in an shipping warehouse.
 The robot has an intended goal object for it to grasp on a shelf, however other objects could obstruct the path towards the goal object.
-These obstructions of movable objects prevent leveraging common motion planning techniques, because they do not posses a dynamics model of how the objects behave under different contact forces.
+In the shipping warehouse, setting these objects are most likely unknown to the robot and it would not have a stored model of their mass and friction properties.
+These obstructions of unknown  movable objects prevent leveraging  control techniques, because the robot does not posses a dynamics model of how the objects behave under different contact forces.
 ~\cite{kitaevphysics,kingnonprehensile}.
 
-Thus, the robot must reason about how its interactions with the environment will affect the intended outcome.
-This can be hard for two reasons 1) it becomes hard to find a low dimensional state representation for the task because the environment dynamics are affected by the global shape of each object 2) the dynamics of the environment  involve modeling how K objects interact with each other under an arbitrary force \cite{kitaevphysics}.
+Instead of purely using analytical planning techniques, the robot could learn from past experiences how to reach a goal object surrounded by a set of training objects.
+Then the robot applies that manipulation policy to a set of  visually similar objects.
 
-In order to achieve real time grasping in clutter, which is important for a robot in a shipping warehouse, we leverage  visuo-motor deep learning to learn a control policy for the task over a large number of different configurations working with a hierarchy of supervisors.
-Deep learning has the potential to take high dimensional image data of the scene and learn task specific features relevant for grasping in clutter.
-Additionally a trained neural network policy is can be computational inexpensive to evaluate and can result in real time performance \cite{levine2015end}.
+We are thus interested in teaching a robot, $\pi_\theta$ on a state space $\mathcal{X}$, which is image data of  K collision objects and goal object in a bounded workspace.
+The underlying reward function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, is the binary evaluation of successfully grasping the goal object.
+This reward function can be too delayed to optimize directly.
+Thus, we leverage a hierarchy of supervisors and Online LfD (described previously) to minimize the expected surrogate loss between the robot's policy $\pi_\theta$ and the most skilled supervisor's, $\tilde{\pi}_M$.
 
@@
 
+\begin{figure}[t]
+\centering
+
+\includegraphics[]{f_figs/labeling.eps}
+
+\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task.
+The pink overlay indicates the desire change in the robot position with respect to the current robot state.
+Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave.
+On the left side is an example of a robot state and on the right side is an example a human supervisor would provide via a Computer Mouse.}
+\vspace*{-10pt}
+\label{fig:overlays}
+\end{figure}
+
 \noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon Mechanical Turk (AMT).
@@
 We additionally designed a tutorial for the CrowdSourced Supervisor.
-First, we introduce them to a robot named Izzy and briefly explain that Izzy is trying to reach a yellow circle but has a tendency to "misbehave" and needs their help.
-Then we have them perform designated motions with a virtual Izzy, which helps them understand how the robot's dynamics behave.
+We first desribe the learning task to them as a robot that is trying to reach a yellow cynlider and needs their help learning how to get it.
+Then we have them perform designated motions with a virtual robot, which helps them understand how the robot's dynamics behave.
 We additionally provide a video of an expert providing corrections on three robot trajectories.
@@
 
-While completing a tutorial before providing examples can be beneficial, we still are not sure whether the CrowdSourced Supervisor can provide quality examples that can be used in learning.
 To help ensure quality, we give all CrowdSourced Supervisor the same robot trial first and measure their examples against the examples form a  Human Expert Supervisor.
@@
 \subsection{Neural Network Policy Architecture}
-\mlnote{adding more details with figure tomorrow}
 Our policy is represented as deep neural network, which was trained using TensorFlow~\cite{tensorflow2015-whitepaper}.
@@
 \caption{\footnotesize  Shown above is a Zymark robot.
-The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table.
-The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}
+The robot consists of an 3DOF arm that lies in a planar workspace.
+It is able to extend its arm and rotate about a fixed base.
+The robot can also open and close its gripper.}
 
@@
 
-\caption{\footnotesize  The different measure of success used in our scoring metric for how well the robot performed.
-Not successful corresponds to when the gripper is never in contact with yellow circle.
-Near successful corresponds to when the robot ends with the gripper touching the yellow circle.
-Successful is defined as when the yellow circle is inside the gripper.
+\caption{\footnotesize  The different measures of performance used in our scoring metric for how well the robot performed.
+Not  Contact corresponds to when the gripper is never in contact with yellow circle.
+Contact corresponds to when the robot ends with the gripper in contact with yellow circle.
+Grasped is defined as when the yellow circle is inside the gripper.
 }
@@
 
-The objects in clutter are made Medium Density Fiberboard and each one is on average 4" in diameter.
+The objects in clutter are made of Medium Density Fiberboard and each one is on average 4" in diameter.
 The objects deemed cluttered are painted Red and the goal object is painted yellow.
@@
 The robot is commanded via state position requests, which are tracked by a tuned PID controller.
-We used relative state contorl because 1) it is easier to enforce stay out zones (such as where a human operator could be) in the robot configuration space and 2) registering state control to a labeling interface in Fig.
+We used relative state control because 1) it is easier to enforce stay out zones (such as where a human operator might be)  and 2) registering state control to a labeling interface in Fig.
 \ref{fig:overlays} is more straightforward than motor commands.
@@
 \ref{fig:shape_set}.
-We measure success as defined by three situations not successful, near successful, successful.
+We measure success as defined by three situations: Not Contact, Contact and Grasped.
 Examples of the robot in these situations can be seen in Fig.
@@
 
-The not successful situation corresponds to the case when the robot's gripper is not touching the goal object at the end of a rollout.
+The Not Contact situation corresponds to the case when the robot's gripper is not touching the goal object at the end of a rollout.
 Examples of when this happens is when the robot fails to push the objects away or does not head in the direction of the yellow circle.
-The near successful situation is defined as the robot touches the goal object with its gripper, but it is not enclosed in the gripper.
+The Contact situation is defined as the robot touches the goal object with its gripper, but it is not enclosed in the gripper.
 Examples of when this happens is when the robot gets a small obstacle object trapped in the gripper first, or when the root slightly misses the yellow circle on its approach.
-Successful is defined as getting the goal object inside the gripper at the end of a trajectory.
+Grapsed is defined as getting the goal object inside the gripper at the end of a trajectory.
 We report total success as a score out of 2: 0 for not successful, 1 for near successful, 2 for successful.
@@
 The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).
-}
-\vspace*{-20pt}
+(WILL CLEAN UP ONCE WE DESCRIBE SCORE)  }
+
 \label{fig:perf_results}
 \end{figure*}
-\adnote{reorder: mpio, he, mpio->he (main experiment); then cs, mpio-cs, all; cs is missing score, hopefully it does not much better than mpio-cs; don't highlight bottom right option because technically its not suppoed to be better than expert; just use hypotheses to show your points.; also separate mpio-cs-he from rest becuase it is using double the data!
-not fair comparison!
-spread the legend horizontally at the top; }
 
@@
 \begin{figure}[t]
-
+\centering 
 \includegraphics{f_figs/cost_result.eps}
@@
 Our results, shown in Fig.
-\ref{fig:perf_results}, are the policy trained with just the crowdsourced supervisor achieves a score of $?\%$.
+\ref{fig:perf_results}, are the policy trained with just the crowdsourced supervisor achieves a score of $0.41\%$.
 The policy trained with the hierarchical crowdsourced and MPIO supervisor receives $0.43\%$ on our test set compared to $0.55\%$ with the motion planning and expert supervisors hierarchy.
@@
 On average a worker would provide 4 demonstrations before exiting the AMT HIT.
+
+\begin{figure}[t]
+\includegraphics{f_figs/big_data.eps}
+\centering 
+\caption{ \footnotesize The performance and cost of right the full hierarchy, which achieves the best performance (0.8).
+The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
+(WILL CLEAN UP ONCE WE DESCRIBE SCORE)   }
+\vspace*{-20pt}
+\label{fig:big_data}
+\end{figure}
 
@@
 This results in MPIO for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations.
-Thus resulting in 320 trials on the robot and 320,000 annotated images of what control the robot should apply.
+Thus resulting in 320 trials on the robot and approximately 210,000 annotated images of what control the robot should apply.
+Note there is less images that total states visited because the human supervisors only labeled when confident in their decisions.
 
 The results of our trained policy, as shown in Fig.
-\ref{fig:perf_results}, demonstrate that by leveraging a hierarchy we are able to achieve a score of $80\%$ with a cost of only 113.
+\ref{fig:big_data}, demonstrate that by leveraging a hierarchy we are able to achieve a score of $80\%$ with a cost of only 113.
 We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $0.66\%$.
@@
 
-\begin{figure}[t]
-\includegraphics{f_figs/big_data.eps}
-
-\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported.
-The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
-The top row corresponds to policies only trained with one supervisor: MPIO, Crowdsourced or Human Expert.
-The bottom corresponds to policies trained with a hierarchy of supervisors: MPIO and Crowdsource, MPIO and Human Expert, MPIO, Crowdsourced and Human Expert.
-The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).
-}
-\vspace*{-20pt}
-\label{fig:big_data}
-\end{figure}
-
 \section{Discussions and Future Work}
-For highly stochastic domains like grasping in clutter, using a hierarchy of supervisors to bootstrap performance at a lower cost seems to be a very sensible thing to do.
+For highly stochastic domains like grasping in clutter, using a hierarchy of supervisors to bootstrap performance at a lower cost is an interesting avenue of research.
 Our results suggest that we can scale up the amount of data needed to learn the task at a much lower cost than only querying the most-skilled supervisor.

### 2016-03-18 paper.tex
.

@@
  Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
-\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu, \small staszass@rose-hulman.edu} }%
+\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu} }%
 \thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
@@
 \section{Robot Grasping in Clutter}
-We now describe the grasping in clutter problem, the supervisor hierarchy that we used to solve it and our deep learning policy architecture.
+Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
+object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
+planar objects obstruct the path towards the goal object.
+Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledte of explicit object or dynamics models and instead learn a grasping policy directly from labelled
+overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
+camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. As the underlying reward
+function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
+signals given by delta values of joint angles. We consider the following three supervisors $S_1, S_2, S_3$.
 
-\subsection{Grasping in Clutter}\label{sec:task}
-\mlnote{Should we just merge this with the original, problem objective?}
-Consider a robot in an shipping warehouse.
-The robot has an intended goal object for it to grasp on a shelf, however other objects could obstruct the path towards the goal object.
-In the shipping warehouse, setting these objects are most likely unknown to the robot and it would not have a stored model of their mass and friction properties.
-These obstructions of unknown  movable objects prevent leveraging  control techniques, because the robot does not posses a dynamics model of how the objects behave under different contact forces.
-~\cite{kitaevphysics,kingnonprehensile}.
-
-Instead of purely using analytical planning techniques, the robot could learn from past experiences how to reach a goal object surrounded by a set of training objects.
-Then the robot applies that manipulation policy to a set of  visually similar objects.
-
-We are thus interested in teaching a robot, $\pi_\theta$ on a state space $\mathcal{X}$, which is image data of  K collision objects and goal object in a bounded workspace.
-The underlying reward function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, is the binary evaluation of successfully grasping the goal object.
-This reward function can be too delayed to optimize directly.
-Thus, we leverage a hierarchy of supervisors and Online LfD (described previously) to minimize the expected surrogate loss between the robot's policy $\pi_\theta$ and the most skilled supervisor's, $\tilde{\pi}_M$.
-
-\subsection{Supervisor Hierarchy}\label{sec:hier}
-In this section, we list each supervisor in the order they appear in our hierarchy. The first supervisor is deemed the least expensive.
-
-\noindent \textbf{Motion Planning that Ignores Obstacles Supervisor} Our first supervisor, $S_1$, is a a motion planner that that computes the trajectory the robot should move in to reach the goal object, or yellow circle, by ignoring obstacles.
-Thus we refer to $S_1$ as Motion Planning that Ignores Obstacle (MPIO) supervisor.
-Our method employs template matching to identify the goal object in the image and the using the forward dynamics of the robot to computes the relative change in direction the robot should apply as an control.
-The template matching is implemented in OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}.
-
-In this stage, the MPIO supervisors only tries to teach the robot to move towards the goal.
-Note that the MPIO supervisor's examples does not have any knowledge about how the cluttered objects will respond to the forces applied via the robot arm, which results in sub-optimal polices.
-However, the MPIO supervisor is both computationally and monetarily inexpensive to run which allows us to provide a large number of examples.
-Thus, the cost of the MPIO supervisor is $C_1 = 0.01$.
-
+\noindent \textbf{Algorithmic Supervisor (AS)} Our first supervisor, $S_1$, is a first order motion planner that that computes
+control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. Our
+method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
+computes the relative change in direction the robot should apply as a control. The template matching is implemented in
+OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is intentionally
+simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
+We assign a cost of $C_1 = \$0.01$ to this supervisor.
 \begin{figure}[t]
@@
 
-\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon Mechanical Turk (AMT).
-The AMT platform makes readily available thousands of human workers that can perform  provide examples for  \$0.12 per robot trial.
-Thus potentially providing a higher quality supervisor who has an intuition for how the cluttered objects interact with the world, but at a  higher cost, $C_2 = 0.1$.
+\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
+Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
+supervision examples for approximately \$0.1 per robot trial. 
+We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
+the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
+showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree to
+the current roll-out.
 
-In order to get examples from a CrowdSourced Supervisor, we designed an interface shown in Fig.
-\ref{fig:overlays}.
-The interface draws a transparent overlay that shows how the robot would respond provided the current control Thus, allowing for the AMT worker to see the magnitude and effect their example would have on the robot.
+We additionally designed a tutorial for the CrowdSourced Supervisor. We first desribe the learning task to them as a
+robot that is trying to reach a yellow cynlider and needs their help learning how to get it. In a tutorial, they are then trained
+to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
+provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the CrowdSourced
+Supervisor to only label when they are sure in their decision, in order to minimize contradictory examples associated
+with random guesses.
 
-We additionally designed a tutorial for the CrowdSourced Supervisor.
-We first desribe the learning task to them as a robot that is trying to reach a yellow cynlider and needs their help learning how to get it.
-Then we have them perform designated motions with a virtual robot, which helps them understand how the robot's dynamics behave.
-We additionally provide a video of an expert providing corrections on three robot trajectories.
-We lastly instruct the CrowdSourced Supervisor to only label when they are sure in their decision, in order to prevent contradictory examples associated with them second guessing themselves.
+To help ensure quality, we provide all CrowdSourced Supervisors with the same robot trial first and measure their
+performance against the performance of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
+signals between examples is above a threshold, then the Crowdsource Supervisor is not asked to provide additional examples.
 
-To help ensure quality, we give all CrowdSourced Supervisor the same robot trial first and measure their examples against the examples form a  Human Expert Supervisor.
-If the average Squared-Euclidean distance between examples is above a threshold of the Human Expert's examples or the number of examples they provided is above a threshold of the number the Human Expert provided, the Crowdsource Supervisor is not asked to provide additional examples.
+\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of
+achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a Phd student in
+machine learning and robotics, to which we assign a cost of $C_3=1.0$. The Human Expert Supervisor uses the same
+interface as the CrowdSourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.
 
-\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of achieving high cumulative reward but is a limited resource.
-An Human Expert Supervisor in this case is a Phd student in machine learning and robotics, which costs $C_3=1.0$.
-The Human Expert Supervisor uses the same interface , shown in Fig.
-\ref{fig:overlays}, to provide examples to the robot.
-
-An expert supervisor can be used in a variety of scenarios.They first would have a better intuition of the physical limitations of the robot and environment, such as joint limits or how certain objects might behave under force.
-Furthermore, they would also understand how the examples given could lead to better training of the robot's policy $\pi_\theta$.
-For example, understanding the feature space the policy lies in can lead the Human Expert to not providing contradictory examples.
-
-\subsection{Neural Network Policy Architecture}
-Our policy is represented as deep neural network, which was trained using TensorFlow~\cite{tensorflow2015-whitepaper}.
-Our network architecture consists of 1 convolutional layer with 5 channels and filters with size 11x11, a fully connected layer with an output of 128 dimensions and a final layer that maps to a four dimensional control signal.
-We used ReLus to separate the different layers and a final tanh on the output to scale the output between -1 and 1.
-
-The control examples was scaled between 1 and -1 for each dimension independently.
-To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise.
-We then validated that all information (i.e.
-location of the gripper, cluttered shapes and goal object) where still visible in the masked image.
-
-To determine our architecture we preformed a grid search over different architectures  trained after 400 iterations with a batch size of 200.
-The set of architectures consist of different network architectures as well as different momentum terms, and weight initialization schemes.
-We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
+An expert supervisor can utilize a variety of knowledge about the physical limitations of the robot and environment,
+joint limits and experience in how certain objects might behave under force. Furthermore, the expert supervisor might
+have an intuition for how training examples could lead to better training of the robot's policy $\pi_\theta$.
 
@@
 
-In this section, we first describe the grasping in clutter experimental setup.
-Then we test how the supervisor hierarchy performs versus not leveraging a hierarchy.
-We then test how high of Quality the CrowdSource supervisor is.
-Then, we experiment with different ways to advance in the hierarchy.
-Finally, we look at using all three supervisors and to train a robot for the grasping in clutter task.
+We discuss our experimental setup and test the performance of using a supervisor hierarchy versus a baseline approach
+with one supervisor. We then evaluate the quality the CrowdSource supervisors.
 
 \subsection{Experimental Setup}
-For experimenting in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera.
-Examples of images from the camera can be seen in Fig.
-\ref{fig:teaser}.
-
-The objects in clutter are made of Medium Density Fiberboard and each one is on average 4" in diameter.
-The objects deemed cluttered are painted Red and the goal object is painted yellow.
-There is an inscribed circle around the work space to keep the robot from pushing the objects outside of the work space.
-The inscribed circle can make the task more challenging because the robot cannot simply "sweep" the cluttered objects off the table.
-
+We work with a Zymark robot to perform a grasping in clutter task.
 The robot, shown in Fig.
@@
 The robot is commanded via state position requests, which are tracked by a tuned PID controller.
-We used relative state control because 1) it is easier to enforce stay out zones (such as where a human operator might be)  and 2) registering state control to a labeling interface in Fig.
-\ref{fig:overlays} is more straightforward than motor commands.
-The policy $\pi_\theta$ outputs delta positions that are bounded by $15^\circ$ for the gripper and turntable, $1$ cm for the arm extension and $0.5$ cm for the gripper at each time step.
-There is $T=100$ time steps in a trajectory.
+We used
+relative state control because this enabled us to easily enforce stay out zones (such as where a human operator might
+be) to register state controlsignals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
+robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
+an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.
 
-To test the performance of a policy, we created a test set composed of 20 different configurations each containing objects that were not trained on.
-The test set configurations varied in number of objects on the table, size of objects and relative pose of each object.
-The objects that were trained on and those that were only tested on can be seen in Fig.
-\ref{fig:shape_set}.
-We measure success as defined by three situations: Not Contact, Contact and Grasped.
-Examples of the robot in these situations can be seen in Fig.
-\ref{fig:suc_meas}.
+We consider objects made of Medium Density Fiberboard with an average 4" diameter. The objects used to form clutter are
+painted Red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
+surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
+the workspace, and thus adding to the difficulty of the task challenging.
 
-The Not Contact situation corresponds to the case when the robot's gripper is not touching the goal object at the end of a rollout.
-Examples of when this happens is when the robot fails to push the objects away or does not head in the direction of the yellow circle.
-The Contact situation is defined as the robot touches the goal object with its gripper, but it is not enclosed in the gripper.
-Examples of when this happens is when the robot gets a small obstacle object trapped in the gripper first, or when the root slightly misses the yellow circle on its approach.
-Grapsed is defined as getting the goal object inside the gripper at the end of a trajectory.
-We report total success as a score out of 2: 0 for not successful, 1 for near successful, 2 for successful.
+Our policy $\pi_{\theta}$ is represented as a deep neural network, which was trained using
+TensorFlow~\cite{tensorflow2015-whitepaper}. Our network architecture consists of 1 convolutional layer with 5 channels
+and filters with size 11x11, a fully connected layer with an output of 128 dimensions and a final layer that maps to a
+four dimensional control signal. We used ReLus to separate the different layers and a final tanh on the output to scale
+the output between -1 and 1. Each policy runs for a total of $T=100$ timesteps.
 
-In all experiments we used a batch size of 20 trials per iterations or 2000 images, thus 100 trials corresponds to 5 iterations.
+The control examples were scaled between 1 and -1 for each dimension independently.
+To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise.
+We then validated that all information (i.e.
+location of the gripper, cluttered shapes and goal object) where still visible in the masked image.
+The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
+Originally we considered also controlling two additional degrees of freedom of the arm: a turn-table motor controlling
+the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, in initial
+experiments controlling the turn table proved unintuitive and was rarely used and the gripper degree of freedom was only used at the end of a policy.
+As a result, we labelled to set these output degrees of freedom with zero and instead automatically closed the gripper
+at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
+extension degree of freedom.
+
+To determine our network architecture we preformed a search over {\color{blue} FP: how many?} different architectures trained after 400 iterations with a batch size of 200.
+The set of architectures consist of different network architectures as well as different momentum
+terms { \color{blue} FP: what?
+details}, and weight initialization schemes.
+We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
+
+To test the performance of a policy, we created a test set composed of 20 different configurations each containing
+objects that were not in the training set.  The test set configurations varied in the number of objects on the table
+{\color{blue} FP: how many?}, size of objects and relative pose of each object. The training objects and the novel
+objects introduced during testing are shown in Fig. \ref{fig:shape_set}.  We measure success by weather the object was
+in the gripper at the final timestep. Examples are displayed in Fig. \ref{fig:suc_meas}. 
+Per iteration of DAgger we roll out 20 trajectories which corresponds to 2000 video frame images.
+Thus 100 robotic trials correspond to 5 iterations of DAgger.
 
@@
 
-\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported.
-The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
-The top row corresponds to policies only trained with one supervisor: MPIO, Crowdsourced or Human Expert.
-The bottom corresponds to policies trained with a hierarchy of supervisors: MPIO and Crowdsource, MPIO and Human Expert, MPIO, Crowdsourced and Human Expert.
+\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported. The bar graphs
+shows the breakdown in terms of situations the policy encountered on the test set. The top row corresponds to policies
+only trained with one supervisor: AS, Crowdsourced or Human Expert. The bottom corresponds to policies trained with a
+hierarchy of supervisors: AS and Crowdsource, AS and Human Expert, AS, Crowdsourced and Human Expert.
 The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).
@@
 
-We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .
-We compare having only a MPIO Supervisor for a fixed amount of data to having only an Human Expert, and to having the hierarchy of both .
-The non-hierarchical policies trained with the human expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.
-The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.
+We first test that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain
+similar performance . We compare having only a AS Supervisor for a fixed amount of data to having only an Human Expert,
+and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for
+160 demonstrations or only the AS supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
+first receives  100 demonstrations from the AS supervisor and  60 demonstrations from the expert supervisor.
 
 Our results, shown in Fig.
-\ref{fig:perf_results}, are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
+\ref{fig:perf_results}, are the policy trained with just the AS supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
 Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance.
@@
 
-\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported.
-The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
-Each policy was trained with the MPIO to Human Expert hierarchical supervisor.
+\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The
+bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
+with the AS to Human Expert hierarchical supervisor.
 From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
@@
 \subsection{Quality of Crowdsourced Supervisor}
-We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy.
-Thus, we perform an experiment using the AMT platform described in Sec.
-\ref{sec:hier}.
-We  first test how well a crowdosurce supervisor performs as part of a hierarchy of supervisors.
-We trained a policy with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers.
+We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy. Thus, we perform an
+experiment using the Amazon Mechanical Turk (AMT) platform described in Sec. \ref{sec:hier}. We  first test how well a crowdosurce supervisor
+performs as part of a hierarchy of supervisors.
+We trained a policy with 100  demonstrations  from the algorithmic supervisor , then had 60 demonstrations provided by AMT workers.
 We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.
 
-Our results, shown in Fig.
-\ref{fig:perf_results}, are the policy trained with just the crowdsourced supervisor achieves a score of $0.41\%$.
-The policy trained with the hierarchical crowdsourced and MPIO supervisor receives $0.43\%$ on our test set compared to $0.55\%$ with the motion planning and expert supervisors hierarchy.
+Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
+a score of $41\%$.
+The policy trained with the hierarchical crowdsourced and algorithmic supervisor receives $43\%$ on our test set compared to $55\%$ with the motion planning and expert supervisors hierarchy.
 The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
@@
 \subsection{Advancing in the Hierarchy}
-We further test how to advance between supervisors in the hierarchy.We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$.
+We further test how to advance between supervisors in the hierarchy.
+We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$ at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$.
 Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
 
-We compare each strategy on a hierarchy of a MPIO supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.
-Our results reported in Fig.\ref{fig:cost_result} , show that aggregation strategy achieves $0.18\%$, the weight transfer strategy achieves $0.55\%$ and the regularized stochastic gradient update strategy achieves $0.63\%$.
+We compare each strategy on a hierarchy of an algorithmic supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.
+Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves $0.18\%$, the weight transfer strategy achieves $0.55\%$ and the regularized stochastic gradient update strategy achieves $0.63\%$.
 Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.
 
-An issue arises though when performing this iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
+An issue arises though when performing these iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
 This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
 
-We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the current $\theta_{m,K}$ weight parameters.
-Thus, we propose only performing DAgger for each individual supervisor in the hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor.
-We found empirically in Sec.
-\ref{sec:Exp} that it also beneficial to add to the new dataset the states and controls applied by the current policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance $\tilde{\epsilon}$.Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
+We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the
+current $\theta_{m,K}$ weight parameters. Thus, we propose only performing DAgger for each individual supervisor in the
+hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically
+in Sec. \ref{sec:Exp} that it is also beneficial to add the new dataset the states and controls applied by the current
+policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
+$\tilde{\epsilon}$ {\color{blue}FP:what epsilon?}.
+Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
 
 \subsection{Scaling the Hierarchy}
-The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: MPIO, crowdsourced and human expert.
-We ran each policy until we observed the pay out in terms of reward achieved was not increasing.
-This results in MPIO for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations.
+The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: AS, crowdsourced and human
+expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in
+AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations.
 Thus resulting in 320 trials on the robot and approximately 210,000 annotated images of what control the robot should apply.
@@
 
+\subsection{Discussion of Failure Modes}
+{\color{blue} FP: Michael, please add a 3x3 figure of "hard" examples and discuss failure modes.}
+
 \section{Discussions and Future Work}
-For highly stochastic domains like grasping in clutter, using a hierarchy of supervisors to bootstrap performance at a lower cost is an interesting avenue of research.
-Our results suggest that we can scale up the amount of data needed to learn the task at a much lower cost than only querying the most-skilled supervisor.
-However, much work still needs to be done in determining how to appropriately select the next supervisor to receive examples from.
-While our current strategy worked well empirically, it remains to be seen if this would apply to other domains.
+Our results suggest learning to grasp in clutter can more cost-efficiently be learned by employing a hierarchy of
+supervisors. In future work, we intend to investigate algorithmic approaches to determining how to appropriately select
+the next supervisor in a hierarchy automatically. While our current strategy worked well empirically, it remains to be 
+investigated how this approach can be utilized in different application domains.
 

### 2016-03-19 paper.tex
added stuff

@@
 \begin{abstract}
-Recent progress in learning from demonstrations increasingly indicates that robots can acquire manipulation skills from
-large collections of training data. Online learning from demonstration algorithms such as DAgger can in particular learn
-policies for problems where the system dynamics and the cost function are unknown. Traditionally, these systems have
-been trained by skilled human supervisors providing feedback on the current learned policy. As the number of
-demonstrations increases, this approach can however incur a substantial time and labor cost.
-We propose that a hierarchy of supervisors that vary is expertise but also in cost can help alleviate this issue.
-We combine planning on a relaxed problem with crowdsourcing and with robotics experts, and hypothesize that leveraging this combination can lead to similar performance while substantially decreasing cost.
-We focus on the grasping in clutter problem, and use an architecture for learning from demonstration based on DAgger and deep learning to learn policies directly from image input.
-Our results ....[fill in]
+For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other objects that block direct access.
+This can be difficult to program explicitly due to uncertainty in friction and push mechanics and the large number of objects that can be encountered.
+Online Learning from Demonstration (LfD) algorithms such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost function are unknown.
+To reduce the burden on human experts to provide control demonstrations, we propose using a hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.
+We consider 3 levels of supervisor, a fast motion planner that ignores obstacles, crowdsourced human workers who
+provide appropriate robot control values via online videos, and local human experts.
+Experiments suggest that we can leverage a hiearchy of supervisors to obtain 22,000 examples and achieve 80\% success on a held out test set of unknown objects.
 
@@
 \caption{
-Three roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, bottom to top) which was trained using a
+Three roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to bottom) which was trained using a
 hierarchy of three supervisors consisting of an analytical motion planning, crowd-sourcing and human expert. 
@@
 planar objects obstruct the path towards the goal object.
-Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledte of explicit object or dynamics models and instead learn a grasping policy directly from labelled
+Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledge of explicit object or dynamics models and instead learn a grasping policy directly from labeled
 overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
@@
 
-\noindent \textbf{Algorithmic Supervisor (AS)} Our first supervisor, $S_1$, is a first order motion planner that that computes
+\noindent \textbf{Algorithmic Supervisor} Our first supervisor, $S_1$, is a first order motion planner that that computes
 control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. Our
@@
 simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
-We assign a cost of $C_1 = \$0.01$ to this supervisor.
+We assign a cost of $C_1 = \$0.01$ to this supervisor, which stems from the amtorized cost need to implement this supervisor. 
 \begin{figure}[t]
@@
 the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
-showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree to
+showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree and maximal extension deviation of 1cm  to
 the current roll-out.
@@
 \section{Experiments} \label{sec:Exp}
+
+\begin{figure}[t]
+\centering
+
+\includegraphics{f_figs/binary_segment.eps}
+
+\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data.
+As you can see it reduces the dimensionality of each channel's pixel value from the range of [0,255] to [0,1], which can allow for less data needed during learning and robustness to small lighting conditions.
+}
+
+\label{fig:b_seg}
+\end{figure}
+
 \begin{figure}[t]
@@
 
-\caption{\footnotesize  The different measures of performance used in our scoring metric for how well the robot performed.
-Not  Contact corresponds to when the gripper is never in contact with yellow circle.
-Contact corresponds to when the robot ends with the gripper in contact with yellow circle.
-Grasped is defined as when the yellow circle is inside the gripper.
+\caption{\footnotesize  On the right is examples of training configurations we presented to the robot.
+The shapes were arranged around the goal object in different poses and in different parts of the workspace.
+At testing time, we had similar configurations but some shapes were unknown objects that were not trained on.
 }
@@
 relative state control because this enabled us to easily enforce stay out zones (such as where a human operator might
-be) to register state controlsignals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
+be) and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
 robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
@@
 We consider objects made of Medium Density Fiberboard with an average 4" diameter. The objects used to form clutter are
-painted Red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
+painted red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
 surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
@@
 The control examples were scaled between 1 and -1 for each dimension independently.
-To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise.
-We then validated that all information (i.e.
-location of the gripper, cluttered shapes and goal object) where still visible in the masked image.
+To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise, each channel is shown in Fig.
+\ref{fig:b_seg}.
 The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
@@
 experiments controlling the turn table proved unintuitive and was rarely used and the gripper degree of freedom was only used at the end of a policy.
-As a result, we labelled to set these output degrees of freedom with zero and instead automatically closed the gripper
+As a result, we labeled to set these output degrees of freedom with zero and instead automatically closed the gripper
 at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
@@
 
-To determine our network architecture we preformed a search over {\color{blue} FP: how many?} different architectures trained after 400 iterations with a batch size of 200.
-The set of architectures consist of different network architectures as well as different momentum
-terms { \color{blue} FP: what?
-details}, and weight initialization schemes.
-We trained all networks on a dataset of 6K images labeled with the Analytical Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
+To determine our network architecture we preformed a search over 40 different architectures trained after 400 iterations with a batch size of 200  The set of architectures consisted of different network architectures in terms of convolutional layers, fully connected layers and size of each one as well as different gradient descent momentum
+terms used in learning, and weight initialization schemes.
+In finding an architecture, we trained all networks on a dataset of 6K images labeled with the Algorithmic Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
 
 To test the performance of a policy, we created a test set composed of 20 different configurations each containing
-objects that were not in the training set.  The test set configurations varied in the number of objects on the table
-{\color{blue} FP: how many?}, size of objects and relative pose of each object. The training objects and the novel
-objects introduced during testing are shown in Fig. \ref{fig:shape_set}.  We measure success by weather the object was
-in the gripper at the final timestep. Examples are displayed in Fig. \ref{fig:suc_meas}. 
-Per iteration of DAgger we roll out 20 trajectories which corresponds to 2000 video frame images.
-Thus 100 robotic trials correspond to 5 iterations of DAgger.
+objects that were not in the training set.  The training objects and test
+objects introduced during testing are shown in Fig.
+\ref{fig:shape_set}.
+The test set configurations varied by placing unknown objects from Fig.
+\ref{fig:shape_set} in addition to the object trained on.
+Examples of training and test configurations are shown in Fig.
+\ref{fig:suc_meas}.
+We measure success by whether the object was
+in the gripper at the final timestep. 
+Per iteration of DAgger we roll out 20 trajectories which corresponds to 2000 video frame images. Thus 100 robotic trials correspond to 5 iterations of DAgger.
 
@@
 
-\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported. The bar graphs
-shows the breakdown in terms of situations the policy encountered on the test set. The top row corresponds to policies
-only trained with one supervisor: AS, Crowdsourced or Human Expert. The bottom corresponds to policies trained with a
-hierarchy of supervisors: AS and Crowdsource, AS and Human Expert, AS, Crowdsourced and Human Expert.
-The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).
-(WILL CLEAN UP ONCE WE DESCRIBE SCORE)  }
+\caption{ \footnotesize The Score (or \% Succesful) and cost of each policy trained with a supervisor is reported. The bar graphs
+shows how many successful and failed situations occurred.
+The top row corresponds to the experiments on hierarchical supervisors: Algorithmic, Human Expert and the hierarchy of Algorithmic to Human Expert.
+ The bottom corresponds to experiments on testing a crowdsourced supervisor: Crowdsourced and the hierarchy Algorithmic and Crowdsourced, AS and Human Expert, AS, Crowdsourced and Human Expert.   }
 
@@
 We first test that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain
-similar performance . We compare having only a AS Supervisor for a fixed amount of data to having only an Human Expert,
+similar performance . We compare having only a Algorithmic Supervisor for a fixed amount of data to having only an Human Expert,
 and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for
@@
 Our results, shown in Fig.
-\ref{fig:perf_results}, are the policy trained with just the AS supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.
+\ref{fig:perf_results}, are the policy trained with just the Algorithmic Supervisor achieves a score of $30\%$, the policy trained with just the Human Expert Supervisor achieves $55\%$ and the policy trained with a hierarchy of supervisor achieves $60\%$.
 Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance.
@@
 Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the Human Expert Supervisor.
-
-\begin{figure}[t]
-\centering 
-\includegraphics{f_figs/cost_result.eps}
-
-\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The
-bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
-with the AS to Human Expert hierarchical supervisor.
-From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
-Regularization achieves the highest performing score of (0.18) }
-\label{fig:cost_result}
-\end{figure}
 
@@
 Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
-a score of $41\%$.
-The policy trained with the hierarchical crowdsourced and algorithmic supervisor receives $43\%$ on our test set compared to $55\%$ with the motion planning and expert supervisors hierarchy.
+a score of $35\%$.
+The policy trained with the hierarchical crowdsourced and algorithmic supervisor receives $45\%$ on our test set compared to $60\%$ with the motion planning and expert supervisors hierarchy.
 The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
@@
 
-\begin{figure}[t]
-\includegraphics{f_figs/big_data.eps}
-\centering 
-\caption{ \footnotesize The performance and cost of right the full hierarchy, which achieves the best performance (0.8).
-The bar graphs shows the breakdown in terms of situations the policy encountered on the test set.
-(WILL CLEAN UP ONCE WE DESCRIBE SCORE)   }
-\vspace*{-20pt}
-\label{fig:big_data}
-\end{figure}
-
 \subsection{Advancing in the Hierarchy}
@@
 We compare each strategy on a hierarchy of an algorithmic supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.
-Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves $0.18\%$, the weight transfer strategy achieves $0.55\%$ and the regularized stochastic gradient update strategy achieves $0.63\%$.
+Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves $15\%$, the weight transfer strategy achieves $55\%$ and the regularized stochastic gradient update strategy achieves $65\%$.
 Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.
@@
 policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
-$\tilde{\epsilon}$ {\color{blue}FP:what epsilon?}.
+$\tilde{\epsilon} = 0.01$.
 Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
+
+\begin{figure}[t]
+\includegraphics{f_figs/big_data.eps}
+\centering 
+\caption{ \footnotesize  The performance and cost of the policy trained on the full hierarchy with of Algorithmic, Crowdsourced and Human Expert.
+The policy achieves a success rate or score of $80\%$ success.
+The total cost though after 320 trials is only 113.
+}
+\vspace*{-20pt}
+\label{fig:big_data}
+\end{figure}
 
@@
 AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations.
-Thus resulting in 320 trials on the robot and approximately 210,000 annotated images of what control the robot should apply.
+Thus resulting in 320 trials on the robot and approximately 22,000 annotated images of what control the robot should apply.
 Note there is less images that total states visited because the human supervisors only labeled when confident in their decisions.
@@
 \ref{fig:big_data}, demonstrate that by leveraging a hierarchy we are able to achieve a score of $80\%$ with a cost of only 113.
-We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $0.66\%$.
+We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $55\%$.
 
-While our policy was able to do substantially better, it did score a near successful  $40\%$.
-These failure modes where do to the robot not being able to accurately manipulate smaller objects, where slight perturbations could result them being pushed into the gripper, and accurately controlling the goal object to land in the circle (i.e.
-sometimes pushing against the side of the circle instead).
-We attribute this problem to a limit in the detail of precision our supervisors can currently give, future work will look at more precise analytical methods and fine tuning the policies via self-learning.
+The behavior of the learned policy appears to find gaps in between the clutter objects and sweeps left to right,  until the objects are pushed apart and then moves towards the goal object, as illustrated in Fig.
+\ref{fig:teaser}.
+We noticed the amount of sweeping is proportional to the size of the gap in the between the cluttered objects.
+Small gaps tend to cause a high frequency of sweeping versus large gaps in which the robot may only push the objects away in one sweep.
 
-\subsection{Discussion of Failure Modes}
-{\color{blue} FP: Michael, please add a 3x3 figure of "hard" examples and discuss failure modes.}
+While our policy was able to do  better with the full hierarchy.
+There still persists some failure modes in our test configurations are shown in Fig.
+\ref{fig:failure_modes}.
+The cause of the failure modes are either the robot sweeps to far and jams the objects against the inscribed circle around the workspace or  an obstacle object falls into the gripper while being pushed.
+Furthermore, it is unclear how well these results will generalize to configurations that are not cluttered objects placed around the goal object.
+
+\begin{figure}[t]
+\centering 
+\includegraphics{f_figs/failure_modes.eps}
+
+\caption{\footnotesize The four failure modes in our test set on the fully trained policy.
+On the left the robot sweeps to far and the collision objects jam up against the edge of the work space.
+On the right, both the banana and the boot are prone to get entrapped in the gripper during pushing and prevent the gripper from reaching the circle.
+}
+\label{fig:failure_modes}
+\end{figure}
+
+\begin{figure}[t]
+\centering 
+\includegraphics{f_figs/cost_result.eps}
+
+\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The
+bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
+with the AS to Human Expert hierarchical supervisor.
+From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
+Regularization achieves the highest performing score of (0.65) }
+\label{fig:cost_result}
+\end{figure}
 
@@
 Furthermore, applying self-learning  to our current policy could be a way to "fine-tune" the current behavior and learn the precision.
+
+Further information, video and code can be found at the following \url{http://berkeleyautomation.github.io/HierSupCASE/}.
 

### 2016-03-19 paper.tex
Edit pass.

@@
 \begin{abstract}
-For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other objects that block direct access.
-This can be difficult to program explicitly due to uncertainty in friction and push mechanics and the large number of objects that can be encountered.
-Online Learning from Demonstration (LfD) algorithms such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost function are unknown.
-To reduce the burden on human experts to provide control demonstrations, we propose using a hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.
-We consider 3 levels of supervisor, a fast motion planner that ignores obstacles, crowdsourced human workers who
-provide appropriate robot control values via online videos, and local human experts.
-Experiments suggest that we can leverage a hiearchy of supervisors to obtain 22,000 examples and achieve 80\% success on a held out test set of unknown objects.
+For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other
+objects that block direct access.  This can be difficult to program explicitly due to uncertainty in friction and push
+mechanics and the large number of objects that can be encountered. Online Learning from Demonstration (LfD) algorithms
+such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost
+function are unknown. To reduce the burden on human experts to provide control demonstrations, we propose using a
+hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.  We consider 3 levels of
+supervisors, a fast motion planner that ignores obstacles, crowdsourced human workers who
+provide appropriate robot control values via online videos, and local human experts.  Experiments suggest that we can
+leverage a hiearchy of supervisors to obtain 22,000 labelled training data examples and achieve 80\% success on a held out test set of unknown objects.
 
@@
 \caption{
-Three roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to bottom) which was trained using a
-hierarchy of three supervisors consisting of an analytical motion planning, crowd-sourcing and human expert. 
-Red shapes indicate clutter objects and the robot is trained to reach the yellow circle.
-The trained manipulation policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in state position.
-The resulting policy learns to sweep away clutter objects and reach the goal object.
-}
+    \footnotesize
+Three policy roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to
+bottom) which was trained using a hierarchy of three supervisors consisting of a motion planning algorithm, crowd-sourcing and a human expert. 
+Red shapes indicate clutter objects and the robot is trained to reach the yellow cylinder. The trained manipulation
+policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in
+state position. The resulting policy learns to sweep away clutter objects to reach the goal object. }
 \vspace*{-20pt}
@@
 
-Our approach is based on online Learning from Demonstrations (LfD) where a robot iteratively learns a policy and is
-provided by feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
+Our approach is based on Online Learning from Demonstrations where a robot iteratively learns a policy and is
+provided feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
 We build on, DAgger, an online LfD algorithm which at each iteration, computes a policy based on prior demonstrations,
@@
 One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot
-visits during training.  Traditionally there has only been one supervisor and it is deemed an expert
+visits during training.  Previously a single expert supervisor has been considered 
 ~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}. In this work, we propose to instead
 utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
-bootstrap the learning process.
-
-In particular, while model-based planners might not yet capture the full physical interaction among all objects, it can be wasteful to not leverage them and learn with an expert supervisor from scratch.
-Thus, at the lowest level of the hierarchy, we use a motion planner on an relaxed version of the problem.
-In our grasping application, we use a planner that ignores the obstacles but can leverage knowledge of the kinematics and the goal.
-The next supervisor in the hierarchy are crowdsource workers on Amazan Mechnical Turk.
-Then finally the robot is trained with a Phd student in robotics, who is an expert human supervisor.
-Examples of the resulting learned grasping in clutter policy can be seen in Fig.
-\ref{fig:teaser}.
+bootstrap the learning process. In particular, while model-based planners might not capture physical interactions with
+complete realism, we propose to leverage them in the initial training phase rather than to utilize an expensive
+expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on an simplified
+version of the grasping in clutter problem that ignores ambient obstacles. As the next supervisor in the hierarchy 
+we consider crowdsourced workers on Amazan Mechnical Turk and finally the robot is trained with a Phd student in
+robotics, who is considered an expert human supervisor. Examples of the resulting learned grasping in clutter policy can be seen in Fig. \ref{fig:teaser}.
 
@@
 \section{Related Work}
-Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and then the field of
-Curriculum learning, which is related to the concept of hierarchical supervisors.
+Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and Curriculum learning.
 
@@
 ~\cite{katz2008can}. Prior work has addressed integrated perception and grasping in clutter where the objective is to
-grasp objects in an unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
+grasp objects in an unorganized pile~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
 specifically aim to grasp a single target object in clutter. 
-
-However, prior work has studied the problem of manipulating objects
-by performing pushing operations~\cite{mason1986mechanics}.  Cosgun et al.~\cite{cosgun2011push} and King et al. \cite{kingnonprehensile} consider the problem of planning
-a series of push operations that move an object to a
+Prior work has studied the problem of manipulating objects
+by performing pushing operations~\cite{mason1986mechanics}.
+Cosgun et al.~\cite{cosgun2011push} and King et al.
+\cite{kingnonprehensile} consider the problem of planning a series of push operations that move an object to a
 desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
-\cite{kitaevphysics}.
-However, all of these works assume known properties of the object model, such as mass and friction coefficient  or access to an object model in a physics simulator, which could be difficult to obtain for unknown objects.
-
+\cite{kitaevphysics}. However, all of these works assume known properties of the object model, such as mass and friction
+coefficient  or access to an object model in a physics simulator, which can be difficult to obtain for unknown objects. 
 Leeper et al. ~\cite{leeper2012strategies} used a human operator for assistance
@@
 
-A learning model-free based approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}.
-However, this assumes a known low-dimensional state representation to both estimate dynamics and perform LQG in.
-In the grasping in clutter domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape when planning a pushing strategy.
+A model-free approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}. However, this assumes a
+known low-dimensional state representation to both estimate dynamics and perform LQG in. In the grasping in clutter
+domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape.
 
-\noindent \textbf{Online Lfd with an Expert Supervisor}
+\noindent \textbf{Online LfD with an Expert Supervisor}
 Successful robotic examples of Online Learning From Demonstration with an expert supervisor include applications to flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskeyshiv}.
-
 However, to date, these approaches have used only one expert supervisor to provide training data for all parts of the
@@
 
-\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reduce the number of
-supervisor supervision is to apply active learning to only ask for supervision when the robot is uncertain about the
+\noindent\textbf{Reducing Supervisor Burden in Online LfD} 
+Active learning approaches to reducing supervisor burden only ask for supervision when the robot is uncertain about the
 correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
 in particular be utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}
-
-However, Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
-learning, the traditional active learning techniques may be suitable since the underlying state distribution changes.
+Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
+learning, the traditional active learning techniques may not be suitable.
 Thus the use of novelty detection was proposed~\cite{kim2013maximum}. Laskey et al. introduced SHIV, using an active
 learning approach tailored to high dimensional and non-stationarity state distributions and a modified version of the
-One Class SVM classifier. This enabled the authors to reduce the density estimation problem to a 
+One Class SVM classifier. This reduced the density estimation problem to a 
 simpler regularized binary classification~\cite{laskeyshiv}. However the grasping in clutter problem exhibits a high amount
-of stochasticity requiring a large training data set which poses a significant computational challenge to these methods.
-In the present paper, we hence consider using Deep Learning, as an underlying scalable learning algorithm in combination
+of variability in parameters requiring a large training data set. This poses a significant computational challenge to these methods.
+In the present paper, we hence consider using Deep Learning, as a scalable learning algorithm in combination
 with DAgger.
@@
 \noindent\textbf{Curriculum Learning}
-Our approach is closely related to ideas from curriculum learning, where a neural network is trained via 
+Our approach is closely related to ideas from curriculum learning, where a neural network is trained  
 incrementally, first on easier examples and then gradually on data of increasing difficulty~\cite{bengio2009curriculum}.
-
-Sanger et al. used curriculum learning in robotics to gradually train a neural network policy to learn the inverse
+Sanger et al. used curriculum learning to gradually train a neural network policy to learn the inverse
 dynamics of a robot manipulator. They then considered a collection scheme where easily learned trajectories where shown
 to the robot first and then gradually increased the difficulty~\cite{sanger1994neural}.
-
-Our approach is different from curriculum learning, which assumes all training data presented to the neural network is valid.
-We  instead train on a completely different set of examples throughout the supervisor hierarchy.
-In these different set of examples, some could be very low-quality examples and will enforce a behavior that needs to be retrain with a more-skilled supervisor.
+We avoid the complexity of ranking training data by difficulty and instead propose an iterative scheme where
+data is presented in an unbiased manner to a hierarchy of supervisors.
 
@@
 We assume a known state space and set of controls.
-We also assume access to a robot or simulator, such that we  can sample from the state sequences induced by a sequence of controls.Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label.
+We also assume access to a robot or simulator, such that we can sample from the state sequences induced by a sequence of controls.
+Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label.
 We additionally assume the supervisors can be noisy and imperfect, noting that a lower cost supervisor also has lower quality.
@@
 \noindent\textbf{Policies and State Densities.}
-Following conventions from control theory, we denote by $\mathcal{X}$ the set of observable states for a robot task, consisting, for example, of 
+We denote by $\mathcal{X}$ the set of observable states for a robot task, consisting, for example, of 
 high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
@@
 continuous in nature. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
-\mathcal{X}$ depends only oni the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
+\mathcal{X}$ depends only only the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
 \mathcal{U}$: 
@@
 We assume an unknown probability density over initial states $p(\bx_0)$.
-
 A demonstration (or trajectory) $\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
@@
 $\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
-Therefore, 'rolling out' trajectories under a policy
+Therefore, `rolling out' trajectories under a policy
 $\pi_{\theta}$ in our experiments, we utilize the robot to sample the resulting stochastic trajectories rather than
@@
 
-Given a candidate policy $\pi_{\theta}$, we DAgger uses the surrogate loss function to approximately measure how `close' the robot's policy's
+Given a candidate policy $\pi_{\theta}$, DAgger uses the surrogate loss function to approximately measure how `close' the robot's policy's
 returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
@@
 
- In particular, this paper provides an empirical study of greedy, with respect to cost, combinations of three types of supervisors $S_1,
+In particular, this paper provides an empirical study of greedy (with respect to cost) combinations of three types of supervisors $S_1,
 S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
@@
 DAgger~\cite{ross2010reduction} instead solves the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1)
-computing the policy parameter $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.
+computing the policy parameter $\theta$ using the training data $\mathcal{D}$ thus far, and 2) by executing the policy
+induced by the current $\theta$, and asking for labels for the encountered states.
 
@@
 
-This sub-problem is a supervised learning problem, solvable by estimators like a support vector machine or a neural net.
-Performance can vary though with the selection of a the estimator~ Selecting the correct function class depends on the task being consider and knowledge of the problem, see for a guide~\cite{scholkopf2002learning}.
+This sub-problem is a supervised learning problem, which we solve with a deep neural network. Other approaches such as
+support vector machines can also be considered~\cite{scholkopf2002learning}.
 
  \subsubsection{Step 2}
-The second step  DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.
+The second step at iteration $k$, DAgger rolls out the current policy, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.
 For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
@@
 The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
-$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
+$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})|t\in\{0,\ldots,T\}\} $$
 
-%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
-
-Steps 1 and 2 are repeated for $K$ iterations or until 
-the robot has achieved sufficient performance on the task\footnote{In the original DAgger the policy rolled out
-was stochastically mixed with the supervisor, thus with probability $\beta$ it would either take the supervisor's action
-or the robots. The use of this stochastically mix policy was for theoretical analysis. In practice, it is recommended
-to set $\beta = 0$ to avoid biasing the sampling~\cite{NIPS2014_5421,ross2010reduction}}.
+Steps 1 and 2 are repeated for $K$ iterations or until the robot has achieved sufficient performance on the
+task\footnote{In the original DAgger the policy rollout was stochastically mixed with the supervisor, thus with
+    probability $\beta$ it would either take the supervisor's action or the robots. The use of this stochastically mix
+    policy was for theoretical analysis and in practice, it was recommended to set $\beta = 0$ to avoid biasing the
+sampling~\cite{NIPS2014_5421,ross2010reduction}}.
 
@@
 
-While one could consider to learn a policy using model-free reinforcement learning algorithms
-~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
+While one could consider to learn a policy using model-free reinforcement learning algorithms~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
 best supervisor to select given the current policy, this approach requires substantial numbers of 
@@
 supervisors was sufficiently low or when the performance on the grasping in clutter task was not improving empirically. 
-For crowdsourcing in particular, we chose the second option since, due to the large variance between demonstrations
-we were not able to determine a fixed threshold for the surrogate loss. We hope to significantly scale the number of
+For crowdsourcing in particular, we chose the second option since, due to the large variance between demonstrations,
+we were not able to determine a fixed supervisor switching threshold for the surrogate loss. We hope to significantly scale the number of
 training steps in future work to investigate various switching criterea in full detail.
@@
 function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
-signals given by delta values of joint angles. We consider the following three supervisors $S_1, S_2, S_3$.
+signals given by delta values of joint angles, we consider {\color{blue} [WHAT IS IT??]}. We consider the following three supervisors $S_1, S_2, S_3$.
 
@@
 
-\noindent \textbf{CrowdSourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
+\noindent \textbf{Crowd-Sourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
 Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
@@
 
-We additionally designed a tutorial for the CrowdSourced Supervisor. We first desribe the learning task to them as a
+We additionally designed a tutorial for the Crowd-Sourced Supervisor. We first desribe the learning task to them as a
 robot that is trying to reach a yellow cynlider and needs their help learning how to get it. In a tutorial, they are then trained
 to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
-provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the CrowdSourced
+provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the Crowd-Sourced
 Supervisor to only label when they are sure in their decision, in order to minimize contradictory examples associated
@@
 
-To help ensure quality, we provide all CrowdSourced Supervisors with the same robot trial first and measure their
+To help ensure quality, we provide all Crowd-Sourced Supervisors with the same robot trial first and measure their
 performance against the performance of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
@@
 machine learning and robotics, to which we assign a cost of $C_3=1.0$. The Human Expert Supervisor uses the same
-interface as the CrowdSourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.
+interface as the Crowd-Sourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.
 
@@
 
-\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data.
-As you can see it reduces the dimensionality of each channel's pixel value from the range of [0,255] to [0,1], which can allow for less data needed during learning and robustness to small lighting conditions.
-}
+\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data. As can be seen
+it reduces the range of each channel's pixel value from the range of [0,255] to [0,1], increasing robustness to small
+lighting condition changes.  }
 
@@
 \caption{\footnotesize  Shown above is a Zymark robot.
-The robot consists of an 3DOF arm that lies in a planar workspace.
+The robot consists of an 3DOF arm in a planar workspace.
 It is able to extend its arm and rotate about a fixed base.
@@
 
-\caption{\footnotesize  The set of objects that the robot was trained on.
-The Training objects on the right are the four objects used in training.
-The test objects on the left represent represent objects that were found in our test configurations.
-The test objects vary in size and shape from the training objects, which can test how well the robot learns to manipulate unknown objects.
-Every test configuration contained at least one object from this set to guarantee it wasn't trained on.
-}
+\caption{\footnotesize  The Training objects on the right are the four objects used in training. The test objects on the
+left represent represent objects that were added in our test configurations. Every test configuration contained at least
+one of the objects on the right.}
 
@@
 
-\caption{\footnotesize  On the right is examples of training configurations we presented to the robot.
-The shapes were arranged around the goal object in different poses and in different parts of the workspace.
-At testing time, we had similar configurations but some shapes were unknown objects that were not trained on.
-}
+\caption{\footnotesize  Right: examples of training configurations we presented to the robot. The shapes were arranged
+around the goal object in different poses and in different parts of the workspace. At test time, we considered similar configurations but 
+added some unknown objects not present in the test set. }
 \vspace*{-20pt}
@@
 We discuss our experimental setup and test the performance of using a supervisor hierarchy versus a baseline approach
-with one supervisor. We then evaluate the quality the CrowdSource supervisors.
+with one supervisor. We then evaluate the quality the Crowd-Source supervisors.
 
 \subsection{Experimental Setup}
-We work with a Zymark robot to perform a grasping in clutter task.
-The robot, shown in Fig.
-\ref{fig:robot}, has a 3 dimensional internal state of base rotation, arm extension and gripper.
-The robot is commanded via state position requests, which are tracked by a tuned PID controller.
-We used
-relative state control because this enabled us to easily enforce stay out zones (such as where a human operator might
-be) and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
+We work with a Zymark robot to perform a grasping in clutter task. The robot, shown in Fig. \ref{fig:robot}, has a 3
+dimensional internal state of base rotation, arm extension and gripper opening width. The robot is commanded via position 
+control with a tuned PID controller. We used
+relative state control because this enabled us to easily enforce stay out zones for safety
+and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
 robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
@@
 surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
-the workspace, and thus adding to the difficulty of the task challenging.
+the workspace, thus adding to the difficulty of the task.
 
@@
 
-The control examples were scaled between 1 and -1 for each dimension independently.
-To be robust to lighting and reduce the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB image, the mask would set to 1 values above 125 and 0 other wise, each channel is shown in Fig.
-\ref{fig:b_seg}.
+The control examples were scaled between 1 and -1 for each dimension independently. To be robust to lighting and reduce
+the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB video frames setting
+values above 125 to one and 0 otherwise. Each channel is shown in Fig. \ref{fig:b_seg}.
 The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
@@
 the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, in initial
-experiments controlling the turn table proved unintuitive and was rarely used and the gripper degree of freedom was only used at the end of a policy.
-As a result, we labeled to set these output degrees of freedom with zero and instead automatically closed the gripper
+experiments controlling the turn table proved unintuitive and was rarely used by human supervisors and the gripper degree of freedom was only used at the end of a policy.
+As a result, we labeled these output degrees of freedom with zero and instead automatically closed the gripper
 at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
@@
 
-To determine our network architecture we preformed a search over 40 different architectures trained after 400 iterations with a batch size of 200  The set of architectures consisted of different network architectures in terms of convolutional layers, fully connected layers and size of each one as well as different gradient descent momentum
+To determine our network architecture we preformed a search over 40 different architectures trained after 400 iterations
+with a batch size of 200. The set of architectures consisted of different network architectures in terms of
+convolutional layers, fully connected layers and size of each one as well as different gradient descent momentum
 terms used in learning, and weight initialization schemes.
@@
 objects that were not in the training set.  The training objects and test
-objects introduced during testing are shown in Fig.
-\ref{fig:shape_set}.
-The test set configurations varied by placing unknown objects from Fig.
-\ref{fig:shape_set} in addition to the object trained on.
+objects introduced during testing are shown in Fig. \ref{fig:shape_set}. The test set configurations varied by placing
+unknown objects from Fig.
+\ref{fig:shape_set} in addition to the objects we trained on.
 Examples of training and test configurations are shown in Fig.
 \ref{fig:suc_meas}.
-We measure success by whether the object was
-in the gripper at the final timestep. 
-Per iteration of DAgger we roll out 20 trajectories which corresponds to 2000 video frame images. Thus 100 robotic trials correspond to 5 iterations of DAgger.
+We measure success by whether the object was in the gripper at the final timestep.
+Per iteration of DAgger, we roll out 20 trajectories which corresponds to 2000 video frame images. Thus 100 robotic trials correspond to 5 iterations of DAgger.
 
@@
 
-\caption{ \footnotesize The Score (or \% Succesful) and cost of each policy trained with a supervisor is reported. The bar graphs
-shows how many successful and failed situations occurred.
-The top row corresponds to the experiments on hierarchical supervisors: Algorithmic, Human Expert and the hierarchy of Algorithmic to Human Expert.
- The bottom corresponds to experiments on testing a crowdsourced supervisor: Crowdsourced and the hierarchy Algorithmic and Crowdsourced, AS and Human Expert, AS, Crowdsourced and Human Expert.   }
+\caption{ \footnotesize The \% of Grasp Success Score and cost of each policy trained with a supervisor is reported. The bar graphs
+show how many successful and failed grasps in clutter occurred. The top row 
+reports results for the Algorithmic and human expert supervisor in isolation and a hierarchical experiment
+utilizing only the algorithmic and human expert supervisor.
+The bottom row corresponds to experiments testing a crowdsourced supervisor: Left: Crowdsourced supervisor training in
+isolation, Right: A hierarchy of Algorithmic and Crowdsourced supervisor.}
 
@@
 similar performance . We compare having only a Algorithmic Supervisor for a fixed amount of data to having only an Human Expert,
-and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for
+and to having the hierarchy of both. The non-hierarchical policies trained with the human expert supervisor only for
 160 demonstrations or only the AS supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
@@
 
-Our results, shown in Fig.
-\ref{fig:perf_results}, are the policy trained with just the Algorithmic Supervisor achieves a score of $30\%$, the policy trained with just the Human Expert Supervisor achieves $55\%$ and the policy trained with a hierarchy of supervisor achieves $60\%$.
-Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance.
-However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.
-
-Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the Human Expert Supervisor.
+Our results, shown in Fig. \ref{fig:perf_results}, show that the policy trained with just the Algorithmic Supervisor
+achieves a score of $30\%$, the policy trained with just the Human Expert Supervisor achieves $55\%$ and the policy
+trained with a hierarchy of supervisor achieves $60\%$.  Thus, the hierarchical supervisor and expert supervisor achieve
+approximately the same performance. However, training with a two step hierarchy of both yields a $40\%$ reduction in
+cost incurred compared to the policy trained with only an expert supervisor.
+Thus indicating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the Human Expert Supervisor.
 
@@
 experiment using the Amazon Mechanical Turk (AMT) platform described in Sec. \ref{sec:hier}. We  first test how well a crowdosurce supervisor
-performs as part of a hierarchy of supervisors.
-We trained a policy with 100  demonstrations  from the algorithmic supervisor , then had 60 demonstrations provided by AMT workers.
-We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.
+performs as part of a hierarchy of supervisors. We trained a policy with 100  demonstrations provided by the algorithmic
+supervisor, then had 60 demonstrations provided by AMT workers. We also compare how well the crowdsource supervisors
+performs in isolation, by having them provide all 160 demonstrations.
 
 Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
-a score of $35\%$.
-The policy trained with the hierarchical crowdsourced and algorithmic supervisor receives $45\%$ on our test set compared to $60\%$ with the motion planning and expert supervisors hierarchy.
-The total cost received with the only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
+a score of $35\%$. The policy trained with the hierarchical crowdsourced and algorithmic supervisor obtained a score of
+$45\%$ on our test set compared to $60\%$ with the motion planning and expert supervisors hierarchy. The total cost of
+using only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
 
-In total, we tested on 44 AMT workers.
-We asked them to provide examples for a single rollout and then if they passed quality check asked them if they wanted to exit or continue for an additional \$$0.12$ per demonstration.
-We found only 21 AMT workers were able to pass the quality check and continue providing demonstrations.
-On average a worker would provide 4 demonstrations before exiting the AMT HIT.
+In total, we utilized 44 AMT workers and asked them to provide examples for a single rollout and then if they passed
+quality check asked them if they wanted to exit or continue for an additional \$$0.12$ per demonstration. We found only
+21 AMT workers were able to pass the quality check and continue providing demonstrations. On average a worker would
+provide 4 demonstrations before exiting the AMT HIT. {\color{blue} [WHAT IS HIT?]}
 
 \subsection{Advancing in the Hierarchy}
-We further test how to advance between supervisors in the hierarchy.
-We examine three different strategies for dataset management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2) transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the first's supervisors dataset completely 3) transferring only the weights of the neural network policy but adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$ at parts of the states visited that the current supervisor is close to agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2 < 0.01$.
-Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
+We further test how to advance between supervisors in the hierarchy. We examine three different strategies for dataset
+management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2)
+transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the
+previous supervisors' demonstration dataset completely 3) transferring only the weights of the neural network policy but
+adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$ at parts of the states visited that the
+current supervisor is in close agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2
+< 0.01$.
+Thus, acting as a regularization on the optimization since stochastic gradient on a section of the mini-batch update would be zero for examples where the next supervisor agrees with the previous.
 
@@
 Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.
+An issue arises though when performing these iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
 
-An issue arises though when performing these iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
-This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
-
-We are thus interested in not storing the dataset collected from the previous supervisor and only remembering the
-current $\theta_{m,K}$ weight parameters. Thus, we propose only performing DAgger for each individual supervisor in the
-hierarchy and using the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically
-in Sec. \ref{sec:Exp} that it is also beneficial to add the new dataset the states and controls applied by the current
-policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
-$\tilde{\epsilon} = 0.01$.
+%This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
+%We are thus interested in only remembering the current $\theta_{m,K}$ weight parameters as we transition between
+%different supervisors. Thus, we propose only performing DAgger for each individual supervisor in the
+%hierarchy and use the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically
+%in Sec. \ref{sec:Exp} that it is also beneficial to add the new dataset the states and controls applied by the current
+%policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
+%$\tilde{\epsilon} = 0.01$.
 Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
@@
 \subsection{Scaling the Hierarchy}
-The final experiment we ran is to run our algorithm on a hierarchy with 3 supervisors: AS, crowdsourced and human
+Here, we ran our algorithm on a hierarchy with 3 supervisors: Algorithmic supervisor, crowdsourced and human
 expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in
-AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations.
-Thus resulting in 320 trials on the robot and approximately 22,000 annotated images of what control the robot should apply.
-Note there is less images that total states visited because the human supervisors only labeled when confident in their decisions.
+AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting
+in 320 trials on the robot and approximately 22,000 images annotated by control supervision labels. Note however that
+fewer images had non-zero delta-control labels because the human supervisors only labeled when confident in their
+decisions. {\color{blue} [HOW MANY?]}
 
@@
 
-The behavior of the learned policy appears to find gaps in between the clutter objects and sweeps left to right,  until the objects are pushed apart and then moves towards the goal object, as illustrated in Fig.
-\ref{fig:teaser}.
-We noticed the amount of sweeping is proportional to the size of the gap in the between the cluttered objects.
-Small gaps tend to cause a high frequency of sweeping versus large gaps in which the robot may only push the objects away in one sweep.
+Investigating the learned policy, we observed that it appears to find gaps in between the clutter objects and sweeps
+left to right,  until the objects are pushed apart and then moves towards the goal object, as illustrated in Fig.
+\ref{fig:teaser}. We noticed that the magnitude of the sweeping motion appeared anti-proportional to the size of the gap in
+the between the cluttered objects. Small gaps tended to cause a high frequency of sweeping while for large gaps the
+robot appeared to sweep away objects in a single motion.
 
-While our policy was able to do  better with the full hierarchy.
-There still persists some failure modes in our test configurations are shown in Fig.
-\ref{fig:failure_modes}.
-The cause of the failure modes are either the robot sweeps to far and jams the objects against the inscribed circle around the workspace or  an obstacle object falls into the gripper while being pushed.
-Furthermore, it is unclear how well these results will generalize to configurations that are not cluttered objects placed around the goal object.
+While our policy showed improved performance when trained using a hierarchy, failure modes persisted in our test
+configurations are shown in Fig. \ref{fig:failure_modes}. The cause of the failure modes are either that the robot
+sweeps too far and jams the objects against the inscribed circle around the workspace or an obstacle object was caught
+in the gripper while being pushed. At present, it is unclear how well these results will generalize to very different configurations 
+of objects.
 
@@
 
-\caption{\footnotesize The four failure modes in our test set on the fully trained policy.
-On the left the robot sweeps to far and the collision objects jam up against the edge of the work space.
-On the right, both the banana and the boot are prone to get entrapped in the gripper during pushing and prevent the gripper from reaching the circle.
-}
+\caption{\footnotesize The four failure modes in our test set on the fully trained policy. On the left the robot sweeps
+to far and the collision objects jam up against the edge of the work space. On the right, both the banana-shaped object
+and the boot-shaped object are prone to get entrapped in the gripper during pushing and prevent the gripper from reaching the circle.  }
 \label{fig:failure_modes}
@@
 \section{Discussions and Future Work}
-Our results suggest learning to grasp in clutter can more cost-efficiently be learned by employing a hierarchy of
+Our results suggest that learning to grasp in clutter can be more cost-efficiently learned by employing a hierarchy of
 supervisors. In future work, we intend to investigate algorithmic approaches to determining how to appropriately select
-the next supervisor in a hierarchy automatically. While our current strategy worked well empirically, it remains to be 
-investigated how this approach can be utilized in different application domains.
-
-Future work will also look at how to increase the success rate on the grasping in clutter domains.
-The current failure modes are associated with a lack of fine motor precision.
-Our current supervisors do not  have the ability to give finer motor control corrections, however using more sophisticated analytical methods might enable better performance.
-Furthermore, applying self-learning  to our current policy could be a way to "fine-tune" the current behavior and learn the precision.
-
+the next supervisor in a hierarchy automatically, which we believe will require a significant scaling of the number of
+training iterations due to the sparsity of the current data set. While our current strategy worked well empirically, it remains to be 
+investigated how this approach can be utilized in different application domains and higher degree of freedom robots.
+A current challenge of our setup appears to be related to a lack of fine motor precision. 
+Our current supervisors do not have the ability to give fine motor control corrections. Furthermore, the use of more
+sophisticated analytical methods as supervisors might enable better performance. 
 Further information, video and code can be found at the following \url{http://berkeleyautomation.github.io/HierSupCASE/}.

### 2016-03-20 paper.tex
added stuff

@@
 provide appropriate robot control values via online videos, and local human experts.  Experiments suggest that we can
-leverage a hiearchy of supervisors to obtain 22,000 labelled training data examples and achieve 80\% success on a held out test set of unknown objects.
+leverage a hiearchy of supervisors to obtain 22,000 labeled training data examples and achieve 80\% success on a held out test set of cluttered object configurations that contain objects not trained on.
 
@@
 visits during training.  Previously a single expert supervisor has been considered 
-~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}. In this work, we propose to instead
+~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}.
+
+In this work, we propose to instead
 utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
 bootstrap the learning process. In particular, while model-based planners might not capture physical interactions with
-complete realism, we propose to leverage them in the initial training phase rather than to utilize an expensive
+complete realism. We propose to leverage model-based planners in the initial training phase rather than to utilize an expensive
 expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on an simplified
-version of the grasping in clutter problem that ignores ambient obstacles. As the next supervisor in the hierarchy 
-we consider crowdsourced workers on Amazan Mechnical Turk and finally the robot is trained with a Phd student in
-robotics, who is considered an expert human supervisor. Examples of the resulting learned grasping in clutter policy can be seen in Fig. \ref{fig:teaser}.
+version of the grasping in clutter problem that ignores ambient obstacles. As the next supervisor in the hierarchy, 
+we consider crowdsourced workers on Amazon Mechanical Turk and finally the robot is trained with a Phd student in
+robotics, who is considered an expert human supervisor.
+When trained with the full hierarchy the robot is able to achieve an 80\% success rate on 20 configurations that each contain new objects.
+Examples of the resulting learned grasping in clutter policy can be seen in Fig.
+\ref{fig:teaser}.
 
@@
 correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
-in particular be utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}
+been utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}
 Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
@@
 S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
-Here, $S_1$ is an analytical motion planning algorithm with a cost $C_1=0.01$, $S_2$ a supervisor
-consisting a crowd-sourced Amazon Mechanical Turk laborers with $C_2=0.1$, and $S_3$ a human expert supervisor with
-$C_3=1$.
+Here, $S_1$ is a motion planning algorithm that ignores ambient obstacles, $S_2$ a supervisor
+consisting a crowd-sourced Amazon Mechanical Turk laborers with, and $S_3$ a human expert supervisor.
 
@@
 For every state visited, DAgger requests the supervisor to provide the appropriate control/label.
-Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
+Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a  zero mean noise term, for $t\in \{0, \ldots, T\}$.
 The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
@@
 Formulating a framework for supervisor strategy selection poses a challenging problem since no formal model
-for the effect of supervisor selection on the surrogate loss minimization is available a priori and since the
-neural network policy parameters $\theta$ are additionally changing at each step of DAgger's iterative training process.
+for the effect of supervisor selection on the surrogate loss minimization is available a priori. Additionally, the
+neural network policy parameters $\theta$ are  changing at each step of DAgger's iterative training process.
 
-While one could consider to learn a policy using model-free reinforcement learning algorithms~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
-best supervisor to select given the current policy, this approach requires substantial numbers of 
+One could consider to learn a policy using model-free reinforcement learning algorithms~\cite{sutton1998reinforcement}, where a selection strategy will query different supervisors and learn over time the
+best supervisor to select given the current policy. However, this approach requires substantial numbers of 
 queries for supervision of the costliest supervisor at each iteration. In light of this, we propose a greedy allocation
@@
 we were not able to determine a fixed supervisor switching threshold for the surrogate loss. We hope to significantly scale the number of
-training steps in future work to investigate various switching criterea in full detail.
+training steps in future work to investigate various switching criteria in full detail.
 
-\section{Robot Grasping in Clutter}
+\section{Robot Grasping in Clutter}\label{sec:sys}
 Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
@@
 overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
-camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. As the underlying reward
-function, or $r: \mathcal{X}\times \mathcal{U} \rightarrow \lbrace 0, 1\rbrace$, where $U$ denotes continuous control
-signals given by delta values of joint angles, we consider {\color{blue} [WHAT IS IT??]}. We consider the following three supervisors $S_1, S_2, S_3$.
+camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. $U$ denotes the set of continuous control
+signals given by delta values of joint angles, we consider control of the robots arm extension, base rotation and gripper, as shown in \ref{fig:robot}.
+We consider the following three supervisors $S_1, S_2, S_3$, which try to optimize the underlying reward
+function of $1$ if a trajectory ends with the goal object in the gripper and $0$ otherwise.
 
-\noindent \textbf{Algorithmic Supervisor} Our first supervisor, $S_1$, is a first order motion planner that that computes
-control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. Our
+\noindent \textbf{Motion Planner Ignoring Obstacle Supervisor} Our first supervisor, $S_1$, is a first order motion planner that computes
+control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. We refer to this supervisor as a Motion Planner  Ignoring Obstacles (MPIO). Our
 method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
-computes the relative change in direction the robot should apply as a control. The template matching is implemented in
+compute the relative change in direction the robot should apply as a control. The template matching is implemented in
 OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is intentionally
 simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
-We assign a cost of $C_1 = \$0.01$ to this supervisor, which stems from the amtorized cost need to implement this supervisor. 
+We assign a cost of $C_1 = \$0.01$ to this supervisor, which stems from the amtorized cost need to implement this supervisor. This cost is set as an example of what one could consider. 
 \begin{figure}[t]
@@
 Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
-supervision examples for approximately \$0.1 per robot trial. 
+supervision examples for approximately \$0.10 per robot trial. We use as an example cost $C_2 = 0.1$, which is based on the crowdsource pay rate. 
 We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
@@
 
-We additionally designed a tutorial for the Crowd-Sourced Supervisor. We first desribe the learning task to them as a
-robot that is trying to reach a yellow cynlider and needs their help learning how to get it. In a tutorial, they are then trained
+We additionally designed a tutorial for the Crowd-Sourced Supervisor. We first describe the learning task to them as a
+robot that is trying to reach a yellow cylinder and needs their help learning how to get it. In a tutorial, they are then trained
 to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
@@
 \noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of
-achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a Phd student in
-machine learning and robotics, to which we assign a cost of $C_3=1.0$. The Human Expert Supervisor uses the same
+achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a PhD student in
+machine learning and robotics, to which we assign a cost of $C_3=1.0$ to signify a higher pay rate than the previous supervisor. The Human Expert Supervisor uses the same
 interface as the Crowd-Sourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.
@@
 and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
-robot as degrees of freedom which are controled by a neural network policy $\pi_{\theta}$ trained on image data taken by
+robot as degrees of freedom which are controlled by a neural network policy $\pi_{\theta}$ trained on image data taken by
 an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.
 
-We consider objects made of Medium Density Fiberboard with an average 4" diameter. The objects used to form clutter are
+We consider objects made of Medium Density Fiberboard with an average 4" diameter and 3" in height. The objects used to form clutter are
 painted red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
-surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being sweeped off
+surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being swept off
 the workspace, thus adding to the difficulty of the task.
@@
 
-To determine our network architecture we preformed a search over 40 different architectures trained after 400 iterations
+To determine our network architecture we performed a search over 40 different architectures trained after 400 iterations
 with a batch size of 200. The set of architectures consisted of different network architectures in terms of
@@
 terms used in learning, and weight initialization schemes.
-In finding an architecture, we trained all networks on a dataset of 6K images labeled with the Algorithmic Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
+In finding an architecture, we trained all networks on a dataset of 6K images labeled with the MPIO Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
 
@@
 objects introduced during testing are shown in Fig. \ref{fig:shape_set}. The test set configurations varied by placing
-unknown objects from Fig.
-\ref{fig:shape_set} in addition to the objects we trained on.
+test objects from Fig.
+\ref{fig:shape_set} in with objects we trained on in similar configurations.
 Examples of training and test configurations are shown in Fig.
@@
 We measure success by whether the object was in the gripper at the final timestep.
+We define reliability of $\rho$ as the percentage of successful configurations.
 Per iteration of DAgger, we roll out 20 trajectories which corresponds to 2000 video frame images. Thus 100 robotic trials correspond to 5 iterations of DAgger.
@@
 
-\caption{ \footnotesize The \% of Grasp Success Score and cost of each policy trained with a supervisor is reported. The bar graphs
+\caption{ \footnotesize The reliability or $\rho$ and the amount of trials of each policy trained with a supervisor is reported. The bar graphs
 show how many successful and failed grasps in clutter occurred. The top row 
-reports results for the Algorithmic and human expert supervisor in isolation and a hierarchical experiment
-utilizing only the algorithmic and human expert supervisor.
-The bottom row corresponds to experiments testing a crowdsourced supervisor: Left: Crowdsourced supervisor training in
-isolation, Right: A hierarchy of Algorithmic and Crowdsourced supervisor.}
+reports results for the MPIO ($\rho = 30\%$), Crowdsource ($\rho = 35\%$) and  Human Expert ($\rho = 55\%$) supervisor in isolation.
+The bottom row corresponds to hierarchical supervisors: MPIO then CrowdSourced ($\rho = 45\%$), MPIO then Human Expert ($\rho = 60\%$) and MPIO then CrowdSourced then Human Expert ($\rho = 80\%$).
+All policies expect for the full hierarchy are trained on 160 trials.
+The final full hierarchy is able to scale to 320 trials on the robot and achieve a reliability of $80\%$}
 
@@
 We first test that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain 
-similar performance . We compare having only a Algorithmic Supervisor for a fixed amount of data to having only an Human Expert,
+similar performance . We compare having only the MPIO Supervisor for a fixed amount of data to having only an Human Expert,
 and to having the hierarchy of both. The non-hierarchical policies trained with the human expert supervisor only for
-160 demonstrations or only the AS supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
-first receives  100 demonstrations from the AS supervisor and  60 demonstrations from the expert supervisor.
+160 demonstrations or only the MPIO supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
+first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.
 
-Our results, shown in Fig. \ref{fig:perf_results}, show that the policy trained with just the Algorithmic Supervisor
-achieves a score of $30\%$, the policy trained with just the Human Expert Supervisor achieves $55\%$ and the policy
-trained with a hierarchy of supervisor achieves $60\%$.  Thus, the hierarchical supervisor and expert supervisor achieve
-approximately the same performance. However, training with a two step hierarchy of both yields a $40\%$ reduction in
-cost incurred compared to the policy trained with only an expert supervisor.
+Our results, shown in Fig. \ref{fig:perf_results}, show that the policy trained with just the MPIO Supervisor
+achieves a reliability( or \% success) of $\rho = 30\%$, the policy trained with just the Human Expert Supervisor achieves $\rho=55\%$ and the policy
+trained with a hierarchy of supervisor achieves $\rho=60\%$.  Thus, the hierarchical supervisor and expert supervisor achieve
+approximately the same performance.
+We hypothesize the slight increase in performance was an effect of the neural network finding a better local minima with an easier to learn function first (i.e.
+curriculum learning \cite{bengio2009curriculum}).
+However, training with a two step hierarchy of both yields a $40\%$ reduction in
+cost, for our cost examples, incurred compared to the policy trained with only an expert supervisor.
 Thus indicating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the Human Expert Supervisor.
@@
 We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy. Thus, we perform an
-experiment using the Amazon Mechanical Turk (AMT) platform described in Sec. \ref{sec:hier}. We  first test how well a crowdosurce supervisor
-performs as part of a hierarchy of supervisors. We trained a policy with 100  demonstrations provided by the algorithmic
+experiment using the Amazon Mechanical Turk (AMT) platform described in Sec. \ref{sec:sys}. We  first test how well a crowdosurce supervisor
+performs as part of a hierarchy of supervisors. We trained a policy with 100  demonstrations provided by the MPIO
 supervisor, then had 60 demonstrations provided by AMT workers. We also compare how well the crowdsource supervisors
@@
 Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
-a score of $35\%$. The policy trained with the hierarchical crowdsourced and algorithmic supervisor obtained a score of
-$45\%$ on our test set compared to $60\%$ with the motion planning and expert supervisors hierarchy. The total cost of
-using only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
+a reliability of $\rho=35\%$. The policy trained with MPIO and then crowdsourced  supervisor obtained a reliability of
+$\rho=45\%$ on our test set compared to $\rho=60\%$ with the motion planning and expert supervisors hierarchy. The total cost, based on our  example assignments, was
+only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
 
@@
 21 AMT workers were able to pass the quality check and continue providing demonstrations. On average a worker would
-provide 4 demonstrations before exiting the AMT HIT. {\color{blue} [WHAT IS HIT?]}
+provide 4 demonstrations before choosing to not provide any more.
 
@@
 
-We compare each strategy on a hierarchy of an algorithmic supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.
-Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves $15\%$, the weight transfer strategy achieves $55\%$ and the regularized stochastic gradient update strategy achieves $65\%$.
+We compare each strategy on a hierarchy of the MPIO supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.
+Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves reliability, $\rho=15\%$, the weight transfer strategy achieves $\rho=55\%$ and the regularized stochastic gradient update strategy achieves $\rho=65\%$.
 Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.
-An issue arises though when performing these iterations because now the current dataset $\mathcal{D}_{K_m}$ has examples from a different supervisor that receives a smaller expected cumulative reward.
 
@@
 
-\begin{figure}[t]
-\includegraphics{f_figs/big_data.eps}
-\centering 
-\caption{ \footnotesize  The performance and cost of the policy trained on the full hierarchy with of Algorithmic, Crowdsourced and Human Expert.
-The policy achieves a success rate or score of $80\%$ success.
-The total cost though after 320 trials is only 113.
-}
-\vspace*{-20pt}
-\label{fig:big_data}
-\end{figure}
-
 \subsection{Scaling the Hierarchy}
-Here, we ran our algorithm on a hierarchy with 3 supervisors: Algorithmic supervisor, crowdsourced and human
+Here, we ran our algorithm on a hierarchy with 3 supervisors: MPIO supervisor, crowdsourced and human
 expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in
-AS for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting
+MPIO for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting
 in 320 trials on the robot and approximately 22,000 images annotated by control supervision labels. Note however that
 fewer images had non-zero delta-control labels because the human supervisors only labeled when confident in their
-decisions. {\color{blue} [HOW MANY?]}
+decisions, which on average results in a 55\% of the robot trial.
 
 The results of our trained policy, as shown in Fig.
-\ref{fig:big_data}, demonstrate that by leveraging a hierarchy we are able to achieve a score of $80\%$ with a cost of only 113.
+\ref{fig:perf_results}, demonstrate that by leveraging a hierarchy we are able to achieve a reliability of $\rho=80\%$ with a cost, based on our assigned examples, of only 113.
 We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $55\%$.
@@
 \ref{fig:teaser}. We noticed that the magnitude of the sweeping motion appeared anti-proportional to the size of the gap in
-the between the cluttered objects. Small gaps tended to cause a high frequency of sweeping while for large gaps the
+ between the cluttered objects. Small gaps tended to cause a high frequency of sweeping while for large gaps the
 robot appeared to sweep away objects in a single motion.
@@
 While our policy showed improved performance when trained using a hierarchy, failure modes persisted in our test
-configurations are shown in Fig. \ref{fig:failure_modes}. The cause of the failure modes are either that the robot
+configurations as shown in Fig. \ref{fig:failure_modes}. The cause of the failure modes are either that the robot
 sweeps too far and jams the objects against the inscribed circle around the workspace or an obstacle object was caught
@@
 bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
-with the AS to Human Expert hierarchical supervisor.
+with the MPIO then Human Expert hierarchical supervisor.
 From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
-Regularization achieves the highest performing score of (0.65) }
+Regularization achieves the highest performing reliability of ($\rho = 0.65\%$) }
 \label{fig:cost_result}

### 2016-04-29 paper.tex
added figs

@@
 
-\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with Learning from Demonstrations}
+\title{Robot Grasping in Clutter:\\
+ Using a Hierarchy of Supervisors for Learning from Demonstrations}
 
-\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hsieh$^1$, Florian T. Pokorny,\\
+\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hsieh$^1$, Florian T. Pokorny$^1$,\\
  Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
-\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu} }%
+\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, jonathan\textunderscore lee, calebchuck, dgealy, wesleyhsieh, ftpokorny, anca\}@berkeley.edu} }%
 \thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
@@
 \begin{abstract}
-For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other
-objects that block direct access.  This can be difficult to program explicitly due to uncertainty in friction and push
-mechanics and the large number of objects that can be encountered. Online Learning from Demonstration (LfD) algorithms
-such as DAgger and SHIV have potential to learn robot control policies for tasks where the system dynamics and the cost
-function are unknown. To reduce the burden on human experts to provide control demonstrations, we propose using a
-hierarchy of supervisors and a Deep Learning network to learn a grasping in clutter task.  We consider 3 levels of
-supervisors, a fast motion planner that ignores obstacles, crowdsourced human workers who
-provide appropriate robot control values via online videos, and local human experts.  Experiments suggest that we can
-leverage a hiearchy of supervisors to obtain 22,000 labeled training data examples and achieve 80\% success on a held out test set of cluttered object configurations that contain objects not trained on.
+For applications such as Amazon warehouse order fulfillment, robots must grasp a desired object amid clutter: other objects that block direct access.
+This can be difficult to program explicitly due to uncertainty in friction and push mechanics and the variety of objects that can be encountered.
+Deep Learning networks combined with Online Learning from Demonstration (LfD) algorithms such as DAgger and SHIV have potential to learn robot control policies for such tasks where the input is a camera image and system dynamics and the cost function are unknown.
+To explore this idea, we introduce a version of the grasping in clutter problem where a yellow cylinder must be grasped by a planar robot arm amid extruded objects in a variety of shapes and positions.
+To reduce the burden on human experts to provide demonstrations, we propose using a hierarchy of three levels of supervisors: a fast motion planner that ignores obstacles, crowd-sourced human workers who provide appropriate robot control values remotely via online videos, and a local human expert.
+Physical experiments suggest that with a fixed budget of 160 expert demonstrations, using the hierarchy of supervisors can increase the probability of a successful grasp (reliability) from $55\%$ to $90\%$.
 
@@
 systems.
-This problem is relevant to industrial applications such as warehouse shipping operations and flexible manufacturing in a semi-structured environments.
+This problem is relevant to industrial applications such as warehouse shipping operations and flexible manufacturing in semi-structured environments.
 One fundamental approach to grasping in clutter is the analytic model driven approach~\cite{bicchi2000robotic},
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
+\includegraphics[width=0.5\textwidth]{f_figs/teaser_h.eps}
 \caption{
     \footnotesize
-Three policy roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per column, top to
-bottom) which was trained using a hierarchy of three supervisors consisting of a motion planning algorithm, crowd-sourcing and a human expert. 
+Three policy roll-outs on a Zymark 3-DOF Robot of a fully trained grasping in clutter policy (one per row, left to
+right) which was trained using a hierarchy of three supervisors consisting of a motion planning algorithm, crowd-sourcing and a human expert. 
 Red shapes indicate clutter objects and the robot is trained to reach the yellow cylinder. The trained manipulation
-policy is represented as a deep neural network that recieves as input an image of the scene and outputs a change in
+policy is represented as a deep neural network that receives as input an image of the scene and outputs a change in
 state position. The resulting policy learns to sweep away clutter objects to reach the goal object. }
@@
 and new state/control examples are aggregated with the prior examples for the next iteration.
-DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
+DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight, natural language and Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.
 Ross et al. showed that DAgger, under a no-regret assumption, can be guaranteed to deviate from the supervisor's policy with an error
@@
 visits during training.  Previously a single expert supervisor has been considered 
-~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}.
+~\cite{ross2010efficient,laskeyshiv,ross2010reduction,ross2013learning,duvallet2013imitation}.
 
-In this work, we propose to instead
-utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
-bootstrap the learning process. In particular, while model-based planners might not capture physical interactions with
-complete realism. We propose to leverage model-based planners in the initial training phase rather than to utilize an expensive
-expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on an simplified
+We  propose to instead
+utilize a hierarchy of supervisors  to incrementally
+bootstrap the learning process, as opposed to utilizing an expensive
+expert supervisor from scratch. Thus, at the lowest level of the hierarchy, we use a motion planner on a simplified
 version of the grasping in clutter problem that ignores ambient obstacles. As the next supervisor in the hierarchy, 
-we consider crowdsourced workers on Amazon Mechanical Turk and finally the robot is trained with a Phd student in
+we consider crowd-sourced workers on Amazon Mechanical Turk and finally the robot is trained with a PhD student in
 robotics, who is considered an expert human supervisor.
-When trained with the full hierarchy the robot is able to achieve an 80\% success rate on 20 configurations that each contain new objects.
-Examples of the resulting learned grasping in clutter policy can be seen in Fig.
-\ref{fig:teaser}.
-
+Experiments suggest that with a fix budget of 160 expert demonstrations leveraging a hierarchy of supervisors can increase reliability from $55\%$ to $90\%$ on a test set of unknown object configurations.
 %Learning can be bootstrapped with a sequence of increasingly skilled supervisors.
@@
 \section{Related Work}
-Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and Curriculum learning.
+Below, we summarize related work in Robotic Grasping in Clutter, the Online LfD setting and Curriculum learning.
 
@@
 However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp
-~\cite{katz2008can}. Prior work has addressed integrated perception and grasping in clutter where the objective is to
-grasp objects in an unorganized pile~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
-specifically aim to grasp a single target object in clutter. 
+~\cite{katz2008can}.
+
 Prior work has studied the problem of manipulating objects
@@
 \cite{kingnonprehensile} consider the problem of planning a series of push operations that move an object to a
-desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
-\cite{kitaevphysics}. However, all of these works assume known properties of the object model, such as mass and friction
-coefficient  or access to an object model in a physics simulator, which can be difficult to obtain for unknown objects. 
+desired target location. We are interested in reaching a desire goal object, not how to move an object to a specific pose.
+
+Additionally prior work has studied the use of hierarchical approaches for motion planning amid movable obstacles ~\cite{stilman2007manipulation,van2009path}.
+The approach is to use sampling-based methods to compute a high-level plan to move objects our of the way and get to a goal location.
+Dogar and Srinivasa applied this approach to push-grasping in clutter that plans a trajectory towards a grasp by maintaining a set of movable objects~\cite{dogar2011framework}.
+Our approach could be potentially integrated with a high level planner for more advance problems, where removing objects from the environment is needed.
+
+Dogar et al.
+proposed a physics-based grasp planning approach that pre-computes and caches interactions with obstacles in the environment, which allows for fast real evaluation for a planner~\cite{dogar2012physics}.
+However, it does not account for inter-object interactions, which can be significant in cluttered environments.
+A supervisor could potentially impart an intuition for inter-object interaction while training the robot.
+Kiteav et al.
+planned a trajectory in a physics simulator using LQG based controllers
+\cite{kitaevphysics} to reach a goal object surrounded by movable obstacles.
+They demonstrated that leveraging knowledge of object dynamics can lead to higher success than only motion planning.
+However, for unknown objects it can be difficult to know parameters such as mass and friction coefficient, which are important for simulation.
+
 Leeper et al. ~\cite{leeper2012strategies} used a human operator for assistance
@@
 
+Prior work has addressed integrated perception and grasping in clutter where the objective is to
+grasp objects in an unorganized pile~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
+specifically aim to grasp a single target object in clutter. We train a robot specifically to move towards a goal object and treat other objects as clutter.
+
 A model-free approach to robotic manipulation is Guided Policy Search~\cite{levine2015end}. However, this assumes a
-known low-dimensional state representation to both estimate dynamics and perform LQG in. In the grasping in clutter
+known low-dimensional state representation to both estimate dynamics and apply an LQG controller. In the grasping in clutter
 domain, it can be hard to specify such a low dimensional representation due the dependence on the objects' shape.
@@
 One Class SVM classifier. This reduced the density estimation problem to a 
-simpler regularized binary classification~\cite{laskeyshiv}. However the grasping in clutter problem exhibits a high amount
-of variability in parameters requiring a large training data set. This poses a significant computational challenge to these methods.
-In the present paper, we hence consider using Deep Learning, as a scalable learning algorithm in combination
-with DAgger.
+simpler regularized binary classification~\cite{laskeyshiv}.
+
+However, all of these works focus on reducing the duration of the demonstration an expert needs to provide.
+We focus on reducing the number of demonstrations the expert needs to provide, not the duration.
 
@@
 
-\section{Problem Statement}
-Given a collection of increasingly able and costly supervisors $S_1, \ldots, S_M$, the goal of this work is to learn a
-policy that closely matches that of the most able supervisor $S_M$ while minimizing the overall cost of training a
-policy. We formalize this approach as follows.
+\section{Robot Grasping in Clutter}\label{sec:sys}
+ We consider a robot grasping an
+object in a cluttered environment. The robot's goal is to grasp a  target, or goal, object in the presence of extruded
+ objects obstructing the path towards the goal object.
+Kiteav et al.
+demonstrated that applying only a motion planner to this problem is not as successful as incorporating knowledge of object dynamics \cite{kitaevphysics}.
+However, since contact dynamics can be difficult to model without  information such as friction coefficient and mass \cite{kitaevphysics,kingnonprehensile}, we do not assume knowledge of explicit object or dynamics models and instead learn a grasping policy directly from demonstrations.
+We consider the following robot system, three supervisors $S_1, S_2, S_3$ and neural network policy architecture:
+
+\noindent \textbf{Robot System}
+The robot, shown in Fig. \ref{fig:robot}, has a 3
+dimensional internal state of base rotation, arm extension and gripper opening width.
+The state space of the environment, $\mathcal{X}$, is captured by  an overhead Logitech C270 camera, which is positioned to capture the workspace that contains all cluttered objects, the goal object and the robot arm.
+Examples of images from the camera can be seen in Fig.
+\ref{fig:teaser}.
+The robot is commanded via position
+control with a  PID controller.
+Similar to \cite{laskeyshiv}, the controls, $\mathcal{U}$, to the robot are bounded changes in the internal state, which allows for us to easily register control signals to the demonstrations provided by supervisors as opposed to torque control.
+The control signals for each degree of freedom are continuous values with the following ranges: base rotation, $[-15^\circ,15^\circ]$, arm extension $[-1,1]$.
+The units are degrees for base rotation and centimeters for arm extension.
+The precision of control signal is $0.001$ for each degree of freedom.
+As opposed to unsupervised learning, where discretization of controls helps reduce computational complexity.
+In supervised learning, or regression, it is common to use a high level of precision for control signals ~\cite{levine2015end, laskeyshiv,kim2013maximum}.
+
+The robot receives feedback from a supervisor by first executing a trajectory that has a time horizon, $T$, or $T=100$.
+The trajectory, which is composed of $100$ states, or images captured by the camera, is then given to a supervisor, who provides a demonstration.
+A demonstration is defined as the supervisor providing  the control they would apply if it was in the robot's current state, for each state in the trajectory.
+The robot then uses these demonstrations  in an approach similar to supervisor learning,  described in Sec.
+\ref{sec:PS}, to  update its current manipulation policy.
+
+\begin{figure}[t]
+\centering
+
+\includegraphics{f_figs/robot.eps}
+
+\caption{\footnotesize  Shown above is a Zymark robot.
+The robot consists of a 3DOF arm in a planar workspace.
+It is able to extend its arm and rotate about a fixed base.
+The robot can also open and close its gripper.}
+\vspace*{-20pt}
+
+\label{fig:robot}
+\end{figure}
+
+\noindent \textbf{MPIO: Motion Planner Ignoring Obstacles Supervisor} Supervisor, $S_1$, is a first order motion planner that computes
+control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. We refer to this supervisor as Motion Planner  Ignoring Obstacles (MPIO). Our
+method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
+compute the relative change in direction the robot should apply as a control. The template matching is implemented in
+OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is designed to just provide an initial improvement of a random neural network policy.
+
+\begin{figure}[t]
+\centering
+
+\includegraphics[]{f_figs/labeling.eps}
+
+\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task.
+The pink overlay indicates the desire desire control, which is a bounded change in internal state, the robot should apply.
+Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave.
+On the left side is an example of a robot state and on the right side is an example a human supervisor would provide via a Computer Mouse.}
+\vspace*{-20pt}
+\label{fig:overlays}
+\end{figure}
+
+\noindent \textbf{Crowd-Sourced Supervisor} Supervisor, $S_2$, uses a crowd source service, called Amazon
+Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that can provide 
+supervision for \$0.10 per demonstration. The time to provide a demonstration to the robot takes 50s, since the robot trial is slowed down to a half second per time-step in the trajectory.
+
+In order to have the AMT workers provide demonstrations, we designed the supervision interface shown in Fig.
+\ref{fig:overlays}.
+The interface displays a video of a trajectory in the image state space and allows the human supervisors to command an overlay visualization of the robot arm to
+demonstrate the correct control the robot should be applied.
+The interface is controlled via a mouse, which when held down a robot visualization appears and can be dragged to the desired control (or change in state) the robot should apply.
+The desired control is bounded by the range in controls listed above.
+
+We  designed a tutorial for the Crowd-Sourced Supervisor. We first describe the learning task to them as a
+robot that is trying to reach a yellow cylinder and needs their help learning how to get it. In a tutorial, they are then trained
+to perform designated motions with a virtual robot, to help them understand  the robot's kinematics. We additionally
+provide a video of an expert providing corrections on three robot trajectories. We instruct the Crowd-Sourced
+Supervisor to only provide a control when they are confident. If a state in the demonstration does not receive a label that state is not added to the training set.
+
+To help ensure quality, we provide all Crowd-Sourced Supervisors with the same trajectory first and compare their
+demonstration against a demonstration of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
+signals between demonstrations is above a threshold, then the CrowdSource Supervisor is not asked to provide additional demonstrations.
+The threshold is set with the intention to only remove  AMT workers, who provide arbitrary demonstrations, no demonstrations or possibly adversarial demonstrations.
+
+\noindent \textbf{Expert Supervisor} Supervisor, $S_3$ is the  Expert Supervisor, who is capable of
+a better understanding of the problem domain but is a limited resource. An Expert Supervisor in this case is a PhD student in
+machine learning and robotics. The Expert Supervisor uses the same
+interface as the Crowd-Sourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.
+
+An Expert Supervisor can utilize a variety of knowledge about the physical limitations of the robot and environment,
+joint limits and experience in how certain objects might behave under force. Furthermore, the Expert Supervisor might
+have an intuition for how training examples could lead to better training of the robot.
+
+\noindent \textbf{Neural Network Policy Architecture}
+In Online LfD, a  robot is trained by learning a policy, or function mapping state space $\mathcal{X}$ to control space $\mathcal{U}$.
+Commonly, a policy is a specific function in some function class such as linear regression, kernelized ridge regression, or a neural network.
+To handle the high dimensional image space of the problem, we are interested in representing the robot's policy as a deep neural network.
+Deep learning can be advantageous because it has the potential to learn features relevant for manipulation~\cite{levine2015end,pinto2015supersizing}.
+Furthermore as opposed to kernel based methods, neural networks readily support online updates (i.e.
+the ability to add more demonstrations without having to retrain on previous demonstrations)~\cite{scholkopf2002learning}, which can be important when switching supervisors in the hierarchy.
+
+To facilitate training the neural network, we scaled the controls  between 1 and -1 for each dimension independently, which is common for training ~\cite{tensorflow2015-whitepaper}.
+To be robust to lighting and reduce
+the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB images setting
+values above 125 to one and 0 otherwise.
+The policy  outputs a 4 dimensional control signals, or delta state positions, for a given input image or state.
+The network also has the ability to control the turn-table motor controlling the rotation of the disc workspace and the single degree of freedom of the robot gripper.
+However, we do not use these controls in experiments and in the training data set those controls to $0$.
+
+ Our network architecture was designed as follows.
+First, to work with image data we used a convolutional layer with 5 channels and 11x11 filters.
+Then we added a Rectified Linear Unit (i.e.
+$\mbox{max}(0,x)$) or ReLu,  to add a non-linearity between layers.
+ReLus have been shown to allow for faster training than other non-linear separators~\cite{krizhevsky2012imagenet}.
+After the non-linearity we added a fully connected layer, or a weight matrix with an out dimension of 128.
+Then  another ReLu  followed by a weight matrix that maps to the 4 dimensional output.
+We place a final $\mbox{tanh}$ function on the output, which  enforces the output is between $-1$ and $1$.
+
+To determine parameters of the network architecture described we performed a search over 30 different architectures trained after 400 iterations
+with a batch size of 200. The set of architectures consisted of different network architectures in terms of
+convolutional layers, filter size,  fully connected layers and output dimension of each layer.
+In finding an architecture, we trained all networks on a dataset of 6K state/control pairs from the MPIO Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
+All networks were trained using Stochastic Gradient Descent with Momentum in TensorFlow ~\cite{tensorflow2015-whitepaper}.
+Momentum is a method to control the magnitude of the gradient based on how large previous gradients were.
+We used a gradient step size,or learning rate of $0.01$ and a momentum term of $0.9$.
+
+\section{Online Learning From Demonstrations}\label{sec:PS}
+Given a collection of increasingly skilled supervisors $S_1, \ldots, S_M$, the goal of this work is to learn a
+policy that closely matches that of the most skilled supervisor $S_M$ while minimizing the overall number of queries to the more skilled supervisors.
 
@@
 Lastly, we assume access to a set of supervisors who can, given a state, provide a control signal label.
-We additionally assume the supervisors can be noisy and imperfect, noting that a lower cost supervisor also has lower quality.
+We additionally assume the supervisors can be noisy and imperfect.
 
@@
 This sub-problem is a supervised learning problem, which we solve with a deep neural network. Other approaches such as
-support vector machines can also be considered~\cite{scholkopf2002learning}.
+kernel based regression can also be considered~\cite{scholkopf2002learning}.
 
@@
 
-\section{Robot Grasping in Clutter}\label{sec:sys}
-Let us now describe how we apply the above approach for the grasping in clutter problem. We consider a robot grasping an
-object in a cluttered environment. The robot's goal is to grasp a yellow cylindrical target object while other extruded
-planar objects obstruct the path towards the goal object.
-Since contact dynamics are difficult to model \cite{kitaevphysics,kingnonprehensile}, we do not assume the knowledge of explicit object or dynamics models and instead learn a grasping policy directly from labeled
-overhead video data. The state space space $\mathcal{X}$, is hence given by an image from an overhead video
-camera, observing a set of K objects, the robot arm and a goal object in a bounded workspace. $U$ denotes the set of continuous control
-signals given by delta values of joint angles, we consider control of the robots arm extension, base rotation and gripper, as shown in \ref{fig:robot}.
-We consider the following three supervisors $S_1, S_2, S_3$, which try to optimize the underlying reward
-function of $1$ if a trajectory ends with the goal object in the gripper and $0$ otherwise.
-
-\noindent \textbf{Motion Planner Ignoring Obstacle Supervisor} Our first supervisor, $S_1$, is a first order motion planner that computes
-control signals for the robot to reach the goal object in a straight line, ignoring the presence of obstacles. We refer to this supervisor as a Motion Planner  Ignoring Obstacles (MPIO). Our
-method employs template matching to identify the goal object in the image and uses the forward dynamics of the robot to
-compute the relative change in direction the robot should apply as a control. The template matching is implemented in
-OpenCV and uses the normalized cross-correlation filter~\cite{opencv_library}. This supervisor is intentionally
-simplistic to execute and implement, and is designed to just provide an initial improvement of a random neural network policy.
-We assign a cost of $C_1 = \$0.01$ to this supervisor, which stems from the amtorized cost need to implement this supervisor. This cost is set as an example of what one could consider. 
-\begin{figure}[t]
-\centering
-
-\includegraphics[]{f_figs/labeling.eps}
-
-\caption{\footnotesize  The interface AMT workers see for providing feedback to the robot for the grasping in clutter task.
-The pink overlay indicates the desire change in the robot position with respect to the current robot state.
-Then AMT workers can use their intuition for how objects respond to force to provide examples of how the robot should behave.
-On the left side is an example of a robot state and on the right side is an example a human supervisor would provide via a Computer Mouse.}
-\vspace*{-10pt}
-\label{fig:overlays}
-\end{figure}
-
-\noindent \textbf{Crowd-Sourced Supervisor} The second supervisor, $S_2$, relies on a crowd source service, called Amazon
-Mechanical Turk (AMT). The AMT platform makes readily available thousands of human workers that we can query to provide robot
-supervision examples for approximately \$0.10 per robot trial. We use as an example cost $C_2 = 0.1$, which is based on the crowdsource pay rate. 
-We designed the supervision interface shown in Fig. \ref{fig:overlays}. The interface displays a video of a roll-out of
-the current robot policy and allows the human supervisors to command an overlay visualization of the robot arm to
-showcase a deviation to the current policy that should be applied with a maximal angle joint deviation of 15 degree and maximal extension deviation of 1cm  to
-the current roll-out.
-
-We additionally designed a tutorial for the Crowd-Sourced Supervisor. We first describe the learning task to them as a
-robot that is trying to reach a yellow cylinder and needs their help learning how to get it. In a tutorial, they are then trained
-to perform designated motions with a virtual robot, to help them understand how the robot's kinematics. We additionally
-provide a video of an expert providing corrections on three robot trajectories. We lastly instruct the Crowd-Sourced
-Supervisor to only label when they are sure in their decision, in order to minimize contradictory examples associated
-with random guesses.
-
-To help ensure quality, we provide all Crowd-Sourced Supervisors with the same robot trial first and measure their
-performance against the performance of a Human Expert Supervisor. If the average Squared-Euclidean distance over control
-signals between examples is above a threshold, then the Crowdsource Supervisor is not asked to provide additional examples.
-
-\noindent \textbf{Human Expert Supervisor} The final supervisor, $S_3$ is the Human Expert supervisor, who is capable of
-achieving high cumulative reward but is a limited resource. An Human Expert Supervisor in this case is a PhD student in
-machine learning and robotics, to which we assign a cost of $C_3=1.0$ to signify a higher pay rate than the previous supervisor. The Human Expert Supervisor uses the same
-interface as the Crowd-Sourced supervisors, shown in Fig. \ref{fig:overlays}, to provide examples to the robot.
-
-An expert supervisor can utilize a variety of knowledge about the physical limitations of the robot and environment,
-joint limits and experience in how certain objects might behave under force. Furthermore, the expert supervisor might
-have an intuition for how training examples could lead to better training of the robot's policy $\pi_\theta$.
-
 \section{Experiments} \label{sec:Exp}
-
-\begin{figure}[t]
-\centering
-
-\includegraphics{f_figs/binary_segment.eps}
-
-\caption{\footnotesize Example of how the binary mask applied to each RGB channel affects the input data. As can be seen
-it reduces the range of each channel's pixel value from the range of [0,255] to [0,1], increasing robustness to small
-lighting condition changes.  }
-
-\label{fig:b_seg}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-
-\includegraphics{f_figs/robot.eps}
-
-\caption{\footnotesize  Shown above is a Zymark robot.
-The robot consists of an 3DOF arm in a planar workspace.
-It is able to extend its arm and rotate about a fixed base.
-The robot can also open and close its gripper.}
-
-\label{fig:robot}
-\end{figure}
 
@@
 
-We discuss our experimental setup and test the performance of using a supervisor hierarchy versus a baseline approach
-with one supervisor. We then evaluate the quality the Crowd-Source supervisors.
+\subsection{Experimental Setup}
+For the grasping in clutter task, we consider objects made of Medium Density Fiberboard with an average 4" diameter and 3" in height.
+The objects used to form clutter are red extruded polygons while the goal object is a yellow cylinder.
+The robot workspace, which is green, consists of a  30" disk region which is
+surrounded by an elevated plate constraining the objects to a ring and prohibiting them from leaving the camera's field of view.
 
-\subsection{Experimental Setup}
-We work with a Zymark robot to perform a grasping in clutter task. The robot, shown in Fig. \ref{fig:robot}, has a 3
-dimensional internal state of base rotation, arm extension and gripper opening width. The robot is commanded via position 
-control with a tuned PID controller. We used
-relative state control because this enabled us to easily enforce stay out zones for safety
-and to register control signals to the labeling interface in Fig. \ref{fig:overlays}. We utilize the two main rotational joints of the
-robot as degrees of freedom which are controlled by a neural network policy $\pi_{\theta}$ trained on image data taken by
-an overhead Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.
-
-We consider objects made of Medium Density Fiberboard with an average 4" diameter and 3" in height. The objects used to form clutter are
-painted red while the goal object is a yellow cylinder. The robot workspace consists of a disk region which is
-surrounded by an elevated plate constraining the objects to the workspace and prohibiting them from being swept off
-the workspace, thus adding to the difficulty of the task.
-
-Our policy $\pi_{\theta}$ is represented as a deep neural network, which was trained using
-TensorFlow~\cite{tensorflow2015-whitepaper}. Our network architecture consists of 1 convolutional layer with 5 channels
-and filters with size 11x11, a fully connected layer with an output of 128 dimensions and a final layer that maps to a
-four dimensional control signal. We used ReLus to separate the different layers and a final tanh on the output to scale
-the output between -1 and 1. Each policy runs for a total of $T=100$ timesteps.
-
-The control examples were scaled between 1 and -1 for each dimension independently. To be robust to lighting and reduce
-the dimensionality of the problem, we applied a binary mask to each channel of the 250x250 RGB video frames setting
-values above 125 to one and 0 otherwise. Each channel is shown in Fig. \ref{fig:b_seg}.
-The policy $\pi_\theta$ outputs delta position control signals for a given input video frame.
-Originally we considered also controlling two additional degrees of freedom of the arm: a turn-table motor controlling
-the rotation of the disc workspace and the single degree of freedom of the robot gripper. However, in initial
-experiments controlling the turn table proved unintuitive and was rarely used by human supervisors and the gripper degree of freedom was only used at the end of a policy.
-As a result, we labeled these output degrees of freedom with zero and instead automatically closed the gripper
-at the final T=100 timestep. The joint controls were limited to $\pm 15$ degrees for rotation and $1$ cm for the
-extension degree of freedom.
-
-To determine our network architecture we performed a search over 40 different architectures trained after 400 iterations
-with a batch size of 200. The set of architectures consisted of different network architectures in terms of
-convolutional layers, fully connected layers and size of each one as well as different gradient descent momentum
-terms used in learning, and weight initialization schemes.
-In finding an architecture, we trained all networks on a dataset of 6K images labeled with the MPIO Supervisor on a Nvidia Tesla K40 GPU, which is able to train each network in an average of 10 minutes.
-
-To test the performance of a policy, we created a test set composed of 20 different configurations each containing
+To test the performance of each robot policy, we created a test set composed of 20 different configurations each containing
 objects that were not in the training set.  The training objects and test
@@
 test objects from Fig.
-\ref{fig:shape_set} in with objects we trained on in similar configurations.
+\ref{fig:shape_set} with objects we trained on in similar configurations.
 Examples of training and test configurations are shown in Fig.
 \ref{fig:suc_meas}.
+During training and testing, we manually place the objects in configurations.
+However, a hardware mechanism that moves the objects around, such as a pre-defined sweeping motion from the robot arm, could be used in future work.
 We measure success by whether the object was in the gripper at the final timestep.
-We define reliability of $\rho$ as the percentage of successful configurations.
-Per iteration of DAgger, we roll out 20 trajectories which corresponds to 2000 video frame images. Thus 100 robotic trials correspond to 5 iterations of DAgger.
+We define reliability or $\rho$ as the percentage of successful configurations.
 
-\subsection{Hierarchical Supervisors}
+Per iteration of Hierarchical DAgger, we collect 20 trajectories on different training configurations and then have a supervisor provide 20 demonstrations.
+We do this to sample a variety of configurations with the current policy before updating the weights.
+Thus 100 robotic trials correspond to 5 iterations of DAgger.
+
+\subsection{Three Types of Supervisors}
 
@@
 
-\caption{ \footnotesize The reliability or $\rho$ and the amount of trials of each policy trained with a supervisor is reported. The bar graphs
-show how many successful and failed grasps in clutter occurred. The top row 
-reports results for the MPIO ($\rho = 30\%$), Crowdsource ($\rho = 35\%$) and  Human Expert ($\rho = 55\%$) supervisor in isolation.
-The bottom row corresponds to hierarchical supervisors: MPIO then CrowdSourced ($\rho = 45\%$), MPIO then Human Expert ($\rho = 60\%$) and MPIO then CrowdSourced then Human Expert ($\rho = 80\%$).
-All policies expect for the full hierarchy are trained on 160 trials.
-The final full hierarchy is able to scale to 320 trials on the robot and achieve a reliability of $80\%$}
-
+\caption{ \footnotesize The reliability or $\rho$, which is a measure of performance on previously unseen objects, of each policy trained with a supervisor is reported. The bar graphs
+shows the number of successful and failed trials. The top row 
+reports results for the MPIO ($\rho = 30\%$), Crowd-Sourced ($\rho = 35\%$) and  Expert ($\rho = 55\%$) supervisor in isolation.
+The bottom  left and middle correspond to hierarchical supervisors: MPIO then Crowd-Sourced ($\rho = 45\%$) and MPIO then Expert ($\rho = 60\%$).
+All policies expect for the full hierarchy (bottom right) are trained on 160 demonstrations.
+The full hierarchy (bottom right)  has a fix budget of 160 Expert demonstrations, but  first leverages MPIO and Crowd-Sourced Supervisors until no improvement in reward from their demonstrations and is able to achieve a reliability of $\rho = 90\%$}
+\vspace*{-20pt}
 \label{fig:perf_results}
@@
 
-We first test that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain 
-similar performance . We compare having only the MPIO Supervisor for a fixed amount of data to having only an Human Expert,
-and to having the hierarchy of both. The non-hierarchical policies trained with the human expert supervisor only for
-160 demonstrations or only the MPIO supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor
-first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.
+We first compare each supervisors' performance.
+We train the robot with MPIO Supervisor, Crowd-Sourced Supervisor or the Expert Supervisor for a fixed amount of 160 demonstrations on the training configurations.
+Our results shown in Fig.
+\ref{fig:perf_results}, show that for our fix budget of 160 trials the supervisors receive a reliability of $\rho = 30\%$, $\rho = 35\%$ and $\rho = 55\%$, respectively.
 
-Our results, shown in Fig. \ref{fig:perf_results}, show that the policy trained with just the MPIO Supervisor
-achieves a reliability( or \% success) of $\rho = 30\%$, the policy trained with just the Human Expert Supervisor achieves $\rho=55\%$ and the policy
-trained with a hierarchy of supervisor achieves $\rho=60\%$.  Thus, the hierarchical supervisor and expert supervisor achieve
-approximately the same performance.
-We hypothesize the slight increase in performance was an effect of the neural network finding a better local minima with an easier to learn function first (i.e.
-curriculum learning \cite{bengio2009curriculum}).
-However, training with a two step hierarchy of both yields a $40\%$ reduction in
-cost, for our cost examples, incurred compared to the policy trained with only an expert supervisor.
-Thus indicating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the Human Expert Supervisor.
+When testing the Crowd-Sourced Supervisor, we hired  44 AMT workers. We found only
+21 AMT workers were able to pass the quality check and continue providing demonstrations as described in Sec. \ref{sec:sys}. On average a worker would
+provide 8 demonstrations before choosing to not provide any more. A single demonstrations would take 50s to provide.
 
-\subsection{Quality of Crowdsourced Supervisor}
-We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy. Thus, we perform an
-experiment using the Amazon Mechanical Turk (AMT) platform described in Sec. \ref{sec:sys}. We  first test how well a crowdosurce supervisor
-performs as part of a hierarchy of supervisors. We trained a policy with 100  demonstrations provided by the MPIO
-supervisor, then had 60 demonstrations provided by AMT workers. We also compare how well the crowdsource supervisors
-performs in isolation, by having them provide all 160 demonstrations.
+We are next interested in testing how the supervisors perform in the hierarchy.
+We divide the original budget of 160 demonstrations to 100 MPIO demonstrations and 60 demonstrations of a higher skill supervisor (i.e.
+Crowd-Sourced or Expert).
+The choice of 100 demonstrations was made due to no improvement in reward from the MPIO Supervisor after 100 demonstrations.
 
-Our results, shown in Fig. \ref{fig:perf_results}, indicate that the policy trained with just the crowdsourced supervisor achieves
-a reliability of $\rho=35\%$. The policy trained with MPIO and then crowdsourced  supervisor obtained a reliability of
-$\rho=45\%$ on our test set compared to $\rho=60\%$ with the motion planning and expert supervisors hierarchy. The total cost, based on our  example assignments, was
-only crowdsource supervisor was 15, while the hierarchical supervisor was 7.
+Results shown in Fig.
+\ref{fig:perf_results}, suggest that a hierarchy of supervisor with MPIO and Crowd-Sourced achieves a reliability of $\rho = 45\%$ and MPIO and Expert achieves a reliability of $\rho = 60\%$.
+This suggests that a hierarchy of supervisors can be beneficial to increase reliability of a robot at a lower cost than only with an Expert Supervisor.
 
-In total, we utilized 44 AMT workers and asked them to provide examples for a single rollout and then if they passed
-quality check asked them if they wanted to exit or continue for an additional \$$0.12$ per demonstration. We found only
-21 AMT workers were able to pass the quality check and continue providing demonstrations. On average a worker would
-provide 4 demonstrations before choosing to not provide any more.
-
-\subsection{Advancing in the Hierarchy}
-We further test how to advance between supervisors in the hierarchy. We examine three different strategies for dataset
-management when changing supervisors 1) aggregating the dataset of the data collected with both supervisors 2)
-transferring only the weights of the nerural network policy or $\theta$ vector between the supervisors and removing the
-previous supervisors' demonstration dataset completely 3) transferring only the weights of the neural network policy but
-adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$ at parts of the states visited that the
-current supervisor is in close agreement with as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2
-< 0.01$.
-Thus, acting as a regularization on the optimization since stochastic gradient on a section of the mini-batch update would be zero for examples where the next supervisor agrees with the previous.
-
-We compare each strategy on a hierarchy of the MPIO supervisor trained with 100 iterations and then advancing to a human expert supervisor trained with 60 iterations.
-Our results reported in Fig.\ref{fig:cost_result}, show that aggregation strategy achieves reliability, $\rho=15\%$, the weight transfer strategy achieves $\rho=55\%$ and the regularized stochastic gradient update strategy achieves $\rho=65\%$.
-Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.
-
-%This could cause a learning algorithm to try and fit to contradictory examples  and be worse than either supervisor trained with \cite{scholkopf2002learning}.
-%We are thus interested in only remembering the current $\theta_{m,K}$ weight parameters as we transition between
-%different supervisors. Thus, we propose only performing DAgger for each individual supervisor in the
-%hierarchy and use the resulting weight vector to bootstrap the learning of the next supervisor. We found empirically
-%in Sec. \ref{sec:Exp} that it is also beneficial to add the new dataset the states and controls applied by the current
-%policy $\pi_{\theta_{m,k}}$ that the current supervisor agreed with by some euclidean distance
-%$\tilde{\epsilon} = 0.01$.
-Thus, acting as a regularization on the optimization since stochastic gradient on a section of the min-batch update would be zero for examples where the next supervisor agrees with the previous.
-
-\subsection{Scaling the Hierarchy}
-Here, we ran our algorithm on a hierarchy with 3 supervisors: MPIO supervisor, crowdsourced and human
-expert. We ran each policy until we observed the pay out in terms of reward achieved was not increasing. This results in
-MPIO for 100 demonstrations, crowdsourced for 120 demonstrations and human expert for 100 demonstrations. Thus resulting
-in 320 trials on the robot and approximately 22,000 images annotated by control supervision labels. Note however that
-fewer images had non-zero delta-control labels because the human supervisors only labeled when confident in their
-decisions, which on average results in a 55\% of the robot trial.
-
-The results of our trained policy, as shown in Fig.
-\ref{fig:perf_results}, demonstrate that by leveraging a hierarchy we are able to achieve a reliability of $\rho=80\%$ with a cost, based on our assigned examples, of only 113.
-We note that policy trained with the human expert supervisor, which incurred a cost of $160$, was only able to achieve a score of $55\%$.
+\subsection{Full Hierarchy}
+Given a fixed budget of 160 Expert Supervisor demonstrations, which achieves $55\%$ reliability,  we are interested in increasing relaibility by leveraging the less costly supervisors, MPIO and Crowd-Sourced.
+We thus had MPIO and Crowd-Sourced supervisor provide demonstrations until we observed the reward achieved was not increasing.
+This results in the
+MPIO Supervisors providing 100 demonstrations, the Crowd-Sourced Supervisor providing 120 demonstrations.
+We then had the Expert Supervisor provide a fix budget of 160 demonstrations.
+The resulting policy had a reliability of $90\%$ as shown in Fig.
+\ref{fig:perf_results}.
 
@@
 \ref{fig:teaser}. We noticed that the magnitude of the sweeping motion appeared anti-proportional to the size of the gap in
- between the cluttered objects. Small gaps tended to cause a high frequency of sweeping while for large gaps the
-robot appeared to sweep away objects in a single motion.
+ between the cluttered objects.
+For example, two cluttered objects placed close together in front of the goal object would  cause a high frequency of sweeping.
+While a single object in front of the goal object would often result in a single sweeping motion pushing the obstacle away from the goal object.
+We also noticed that the robot would in general stop once it reached the goal object.
+However, it was rare to see the robot go backwards and correct itself, despite those demonstrations being given.
 
  While our policy showed improved performance when trained using a hierarchy, failure modes persisted in our test
-configurations as shown in Fig. \ref{fig:failure_modes}. The cause of the failure modes are either that the robot
-sweeps too far and jams the objects against the inscribed circle around the workspace or an obstacle object was caught
-in the gripper while being pushed. At present, it is unclear how well these results will generalize to very different configurations 
-of objects.
+configurations. Common failure modes are either that the robot
+sweeps too far and jams the objects against the inscribed circle around the workspace or a smaller obstacle object was caught in the gripper while being pushed.
 
-\begin{figure}[t]
-\centering 
-\includegraphics{f_figs/failure_modes.eps}
+\subsection{Advancing in the Hierarchy}
+We lastly test how to advance between supervisors in the hierarchy.
+We examine the situation where the robot is first trained with the MPIO supervisor for 100 demonstrations and then the Expert Supervisor for 60 demonstrations.
 
-\caption{\footnotesize The four failure modes in our test set on the fully trained policy. On the left the robot sweeps
-to far and the collision objects jam up against the edge of the work space. On the right, both the banana-shaped object
-and the boot-shaped object are prone to get entrapped in the gripper during pushing and prevent the gripper from reaching the circle.  }
-\label{fig:failure_modes}
-\end{figure}
+We are interested in testing the following strategies for changing supervisors 1) aggregating the two datasets of the demonstrations collected with both MPIO and Expert Supervisors 2)
+transferring only the weights of the neural network policy or $\theta$  to initialize training with the Expert and not retraining on the MPIO Supervisor's demonstrations 3) transferring only the weights of the neural network policy but
+adding the values output by $\pi_\theta(\bx)$  instead of $\tilde{\pi}_m(\bx)$ in the states visited that the
+Expert Supervisor's demonstrations are similar too the output of the policy as measured by the following $||\tilde{\pi}_m(\bx) - \pi_\theta(\bx)||^2_2
+< 0.01$.
+Thus, acting as a form of regularization on the optimization since stochastic gradient on a section of the mini-batch update would be zero for examples where the policy trained with the MPIO Supervisor matches that of the Expert.
+
+ Our results reported in Fig.\ref{fig:cost_result}, show that the aggregation strategy achieves reliability, $\rho=15\%$, the weight transfer strategy achieves $\rho = 60\%$ and the regularized stochastic gradient update strategy achieves $\rho=65\%$.
+Thus, suggesting that techniques to help the policy remain close to the previously trained supervisor are useful for effectively switching between supervisors.
 
@@
 \caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The
-bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained
-with the MPIO then Human Expert hierarchical supervisor.
-From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization.
+bar graph show the breakdown in terms of Failure and Success on the test configurations.Each policy was trained with the MPIO and then the Human Expert supervisor.
+From left to right , we display the following: Dataset Aggregation, Weight Transfer and Regularization.
 Regularization achieves the highest performing reliability of ($\rho = 0.65\%$) }
+
 \label{fig:cost_result}
+\vspace*{-22pt}
 \end{figure}
@@
 \section{Discussions and Future Work}
-Our results suggest that learning to grasp in clutter can be more cost-efficiently learned by employing a hierarchy of
-supervisors. In future work, we intend to investigate algorithmic approaches to determining how to appropriately select
-the next supervisor in a hierarchy automatically, which we believe will require a significant scaling of the number of
-training iterations due to the sparsity of the current data set. While our current strategy worked well empirically, it remains to be 
-investigated how this approach can be utilized in different application domains and higher degree of freedom robots.
-A current challenge of our setup appears to be related to a lack of fine motor precision. 
-Our current supervisors do not have the ability to give fine motor control corrections. Furthermore, the use of more
-sophisticated analytical methods as supervisors might enable better performance. 
+Robot grasping in clutter is a challenging problem for automation in warehouse order assembly and home cleaning due to uncertainty arising from sensing and control and the inherent complexity of push mechanics.
+We introduce a version of the problem where a yellow cylinder must be grasped by a planar robot arm amid extruded objects with a variety of shapes and positions.
+Results suggest that this task is amenable to a Learning from Demonstrations approach such as DAgger or SHIV but can put a burden on human experts.
+
+To reduce the burden, we consider two alternative supervisors:  one is a motion planner that ignores obstacles (MPIO) and the second is crowd-sourced workers from Amazon Mechanical Turk who provide demonstrations using a novel overlay interface.
+Results show as expected that the reliability of the policies depend on the skill level of the demonstrations.
+We introduce a hierarchical approach where supervisors with differing skill levels are combined.
+Results suggest that staging supervisors in terms of increasing skill level can bootstrap LfD to learn reliable policies, in this case the robot learns a counter-intuitive policy where the it sweeps the gripper back and forth to clear obstacles before grasping.
+
+To our knowledge this is the first study of hierarchical supervisors for Learning from Demonstrations.
+In future work, we will perform more experiments in this context with added noise in perception and control, and study how the policies generalize to a broader variety of objects and different configurations.
+We will also study the comparative performance of other motion planning-based supervisors and study how hierarchical approaches can be applied to tasks such as driving and assembly.
 Further information, video and code can be found at the following \url{http://berkeleyautomation.github.io/HierSupCASE/}.
